### 2016-09-22 eacl2017.tex
first commit

%
% File eacl2017.tex
%
%% Based on the style files for ACL-2016
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{eacl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[pdftex]{graphicx}

\def \eg {e.g.,\@ }
\def \ie {i.e.,\@ }
\def \al {al.\@ }

%\eaclfinalcopy % Uncomment this line for the final submission
%\def\eaclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Unsupervised acquisition of comprehensive multiword lexicons \\ using competition in an $n$-gram lattice}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Background and Related work}

In this paper we are attempting to identify \textit{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, who defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized. In computational linguistics, the most common term used to describe multiword lexical units is \textit{multiword expression} or MWE \cite{Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas. This distinction is not a new one, for instance it exists to some extent in the MWE annotation of Schneider \cite{Schneider14a}, who distinguishes between weak (collocational) and strong (non-compositional) MWEs, but it is our contention is that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we included to disregard or minimize the larger formulaticity of language simply because it is not the dominant focus of MWE research. Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \emph{there is something going on}, \emph{it is more important than ever to\ldotz}, \emph{\ldotsdo not know what it is like to\ldots},\emph{it would be great if * could}, \emph{there is no shortage of\ldots}, \emph{the rise and fall of\ldots}, \emph{now is not the time to\ldots}, \etc as well as tens of thousands of other such phrases which, along with less compositional, clearly MWE formulas like \textit{be worth * weight in gold}, are identified by the FS-extraction system presented here.

\begin{figure}[!tb]
\center{\includegraphics{FS_diagram_1.png}}
\caption{Multiword Terminology}

\end{figure}

Figure 1 shows our conception of the terminology for multiword relationships, including FS, MWE, as well as collocations and (multiword) named entities. We use the term \textit{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS. MWEs, again, are a non-compositional subset of FS, and they overlap with named entities. In this regard, we disagree with the MWE annotation schema of Schneider \cite{Schneider14a} which simply includes any named entity as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \textit{Tintman Nationwide Tints Ltd} or \textit{Hickory Furniture Mart} which are easily identifiable as named entities based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names). The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition. Some well-known named entities are obviously good MWEs (\eg \textit{George Washington}, \textit{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.

Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen. Only some of these measures generalize beyond two words, for example PMI \cite{Church90}, the log ratio of the joint probability to the product of the marginal probabilities. Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word. The lexical predictability ratio (LPR) of Brooke et \al \cite{Brooke15b} is a association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily $n$-gram could be replaced by a single word \cite{Riedl15}.

Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb/noun combinations \cite{Fazly09}. The recent work of Schneider et \al \shortcite{Schneider14b} is a rare example of a comprehensive MWE identification model which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have be mixed \cite{Riedl16}. Otherwise, gaps in MWEs have generally addressed by using full syntactic representations \cite{Seretan11}.

Beyond association metrics, other general unsupervised approaches to the multiword unit identification include that of Newman et \al \shortcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary. Gimpel and Smith \shortcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation. The drawback to these generative methods, relative to association metrics, is scalability and lack of determinacy. Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS identification in  larger corpora, first using the conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on marginal and conditional probabilities.

%Within corpus linguistics, multiword sequences are studied with the use of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold. In order to get very reliable phrases, the threshold is typically set high enough (Biber et \al use 40 occurrences in 1 million words) to filter out the vast majority of expressions in the process. Lexical bundles generally involve larger phrasal chunks that would be missed by traditional collocation extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indiciative of particular genres (\eg university lectures).  Lexical bundles have been applied, in particular, to learner language: for example, Chen and Baker \shortcite{Chen10} showed that non-native student writers use severely a restricted range of lexical bundle types, and tend to overuse those types, while Granger and Bestgen \shortcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.

%Unlikely with true MWEs there is no other single necessary condition for some collection of words to be a formulaic sequence, but there are many indicators: Wray \shortcite{Wray08} lists 11 diagnostic criteria, including exact repetition, a lack of semantic transparency, genre associations, pragmatic effects, non-standard syntax, statistical irregularity, and phonological properties. We also want to distinguish FS from collocations, which are

%Wray's conception of formulaic language is explicitly not that of mere exception to the combinatorial creativity of syntax and semantics; she argues that most language can be viewed to some degree as formulaic, and that the use of formulaic sequences is the default mode for most genres, both written and oral. Moreover, her view is that the processing of language in general should be viewed not so much as a bottom-up construction of larger phrases from individual lexical units, but rather as a top-down process where larger chunks are split apart and analyzed as discrete parts only when there is clear evidence for flexibility, a strategy that has a direct analogy in the decomposition approach used here. Another important aspect of the theory is a focus on the linear sequence rather than some other kind of syntactic abstraction (\eg a dependency relationship) as being primary to the internal representation of multiword phenomena, a perspective which allows for much cleaner analysis of longer and more varied expressions: when cases of sequence-internal flexibility occur, they are handled by the inclusion of a slot or gap which is also part of the sequence. Note that, since humans are fairly skilled at interpreting noisy input of various kinds, the notion of sequence as the default glue of the internal multiword lexicon does not rule out the possibility of greater creativity (\eg reversing word order), but this should be understood as the speaker abandoning one of the benefits of formulaic sequences (easy processing) for other communicative purposes (\eg humor).

%Second language acquisition is one of the major areas of application for work on formulaic sequences \cite{Ellis08}. Wray \shortcite{Wray08} posits that the difficulty many adult second language learners have reaching fluency reflects, at least in part, an inattention to the role of formulaic sequences, coupled with an expectation that a language should allow for free combination of words governed only by the basic rules of syntax. Modern communicative approaches to teaching tend to encourage learners to express themselves freely so long as they are able to make themselves understood, \ie to satisfy the short-term communicative goal. However, if full fluency and social integration into the culture of native speakers is a long-term goal, as it is for many immigrant learners for instance, these learners also need to correctly process and eventually produce a wide range of formulaic sequences. Creating high-coverage vocabularies based on real, modern language usage is a first step in helping learners with these challenging but ubiquitous units of language.

\section{Method}

The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus. Our method for FS extraction assumes such a initial set of $n$-grams, and focuses on identifying the true FS, and excluding those sequences which can be explained away due to the syntax of the language and/or the existence of other FS. The former can be captured to some extent using a syntax-sensitive association measure like LPR, but the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary.

Our approach to FS identification involves optimization of the total cost of a lattice where each node corresponds to an $n$-gram type derived from a large corpus. The cost of the whole lattice is defined simply as a product of the costs of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), with the base cost of being off simply a variation on the LPR association measure. Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \emph{keep * under wraps} would, for instance be connected ``upwards'' to the node \emph{keep everything under wraps} and connected ``downwards'' to \emph{under wraps}. These directional relationships allow for two basic effects between nodes in the lattice when a node is turned on: \emph{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \emph{keep * under wraps} is on, the model will tend not to choose \emph{under wraps} as an FS); and \emph{clearing}, which inhibits nodes above a turned-on node (\eg, if \emph{keep * under wraps} is on, the model would avoid selecting \emph{keep everything under wraps} as an FS). A third, undirected mechanism is \emph{overlapping}, where nodes inhibit each other due to (non-subsuming) overlaps in the corpus (\eg having both \emph{keep * under wraps} and \emph{be keep * under} as FS will be avoided). Given these relationships, we minimize the cost of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.

\subsection{Collecting statistics}

The first step in the process is derive a set of $n$-grams and related statistics from a large untagged corpus of text. Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows Brooke et \al \shortcite{Brooke15b} up until the last stage. An initial requirement of any such method is a $n$-gram threshold cutoff, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \cite{Schneider14a} which indicates very good (over 90\%) type-level coverage excepting those highly particular proper names which would be better handled by a named entity recognition system. Note that our $n$-grams also include gappy versions; the definition of gaps is language specific, and we will discuss the individual languages further in section XXXXX. In general, though, putting in a restriction of this sort is important because it greatly lowers the number of gappy $n$-gram types. We also lower our number of types generally by excluding punctuation and by lemmatizing.  Note that as long as the count threshold is signifcantly above 1, efficient extraction of all $n$-grams can be done iteratively (one pass through the corpus per $n$) for both types in combination.

Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \emph{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected. Again, LPR measures how statistically unlikely a particular word is relative to how predictable the word is given the same amount of syntactic context. Formally, the LPR for some word $w_i$ in the context of a sequence of words of length $n$ which have a corresponding set of sequence of POS tags $t$, is given by:

\begin{displaymath}
LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}

These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts. We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gap $n$-gram statistics, not regular $n$-gram statistics.

In Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but this is not an appropriate choice here: instead, the base ``off'' cost for a node in our lattice is the minimum LPR across the words in the sequence (minLPR):

\begin{displaymath}
minLPR(w_{0,n}) = \min_{0 \leq i < n }{LPR(w_i,w_{0,n})}
\end{displaymath}

The use of minimum here should be understood in the context of competition between nodes in the lattice: minLPR for a particular $n$-gram does not reflect the \emph{overall}
degree to which an $n$-gram holds together, instead it focuses on the word which is its weakest link. For example, in the case we are evaluating the quality of \emph{be keep * under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \emph{keep} and \emph{under}, but the minLPR is focused on the weaker relationship between \emph{be} and \emph{keep * under}.

% Some sample minLPR values are given in Table XXXXX (???).

\subsection{Node cost functions}

For each node, there are two cost functions, one which is used if the node on ($C_{1}$), and the other if the node is off ($C_{0}$). The base value of $C_{0}$ is the minLPR metric discussed above. The base value of $C_{1}$ is a parameter to the model which, for nodes not influenced by one of the other factors discussed below, is equivalent to an initial threshold for building a vocabulary using the minLPR association measure. The lower bound on both costs is 1. There is no necessary upper bound on $C_{1}$, but we note here that there is a fairly small range of good choices for $C_{1}$; we have found that setting it too high ($>5$, corresponding to being five times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) will allow in too much random noise.

In general, we will be expanding these cost functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it. Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count. First, lets define $C_0$ as the minLPR based taken to the power of some as yet undefined function $d$:

\begin{displaymath}
C_0(t) = minLPR(t)^{d_0(t)}
\end{displaymath}

LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words. As such, it is common for more complex association measures to include multiplication by the count, or logarithm of the count. In the context of this model, multiplying our cost by even the logarithm of the count would be far too extreme, but we can give apply a more restricted increase to $C_0$, forcing the model to give more weight to relatively common expressions, as follows: Let $c(\dot)$ be the count function, and $c(min)$ and $c(max)$ refer to the lowest and highest count $n$-gram in the lattice (not including unigrams).

\begin{displaymath}
d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}}
\end{displaymath}

This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d$ results in a squaring of the initial LPR-ratio.

\begin{figure*}[!tb]
\center{\includegraphics{FS_diagram_2.png}}
\caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
\end{figure*}[!tb]

\subsection{Node interactions}

The most important node interaction is \textit{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice. Our model includes two types of covering: hard and soft. Hard covering is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \emph{keep * under wraps} and 152 counts of \emph{under wraps}, the presence of \emph{keep * under wraps} almost completely explains \emph{under wraps}, and it is better if we collapse these two decisions into one. We do this by permanently disabling any covered node, and giving the covering node the maximum minLPR among all the nodes it covers; this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and besides being effective it also greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well. Finally, we also use hard covering to partially address the rather challenging problem of pronouns, which, due to pragmatic biases in particular corpora, often have higher than desirable LPR ratios, but cannot reasonably be excluded either since many common FS contain them. In our model, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun.

Soft covering is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, \emph{keep * under} is not hard-covered by \emph{keep * under wraps} (since there are FS such as \emph{keep * under surveillance}, \emph{keep it under your hat}, \etc), but if \emph{keep * under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \emph{keep * under} counts that correspond to \emph{keep * under wraps}. We accomplish this by lowering the turned-off cost function of {keep * under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\ldots_m$ be any turned-on nodes which are above $t$ in the lattice. Then, then the new $d_0$, $d_0'$ for a node $t$ is:

\begin{displaymath}
d_{0}'(t) = \frac{c(t) - \sum{c(s_1)\ldots c(s_m)}}{c(t))} d_0(t)

\end{displaymath}

\noindent
This equation is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.

In general, covering prefers turning on longer, covering $n$-grams since doing so lowers the turned-off cost function of nodes lower in the lattice. Not surprisingly, it is important to have a mechanism working in opposition, \ie one which generally prefers shorter $n$-grams. \textit{Clearing} does this by changing the $C_0$ of nodes higher in the lattice when a lower node is turned-on. The basic mechanism is the same as covering, except that we cannot make direct make use of counts in the same way; whereas it makes sense to discount the turned-off cost of covered nodes in proportion to the (lower) relative counts of their covering nodes, in the reverse direction this logic entirely fails. A simple but effective solution is to use the minLPR value: a turned-on node will clear any node higher in the lattice which has a minLPR that is lower than it. We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.

To give an example of its effect, if the node \emph{keep * under wraps} is turned on, then, assuming that their minLPR is lower, the $C_0$ of nodes such as \emph{be keep * under wraps} and \emph{keep * under wraps for} will be lowered to zero. This dissuades (but does not prevent) the model from turning on these nodes. Note that the effect of both covering and clearing is to lower the cost function for covered/clears nodes, which encourages the model to turn \emph{keep * under wraps} on, even potentially in cases where its minLPR is relatively low.

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. Though there are some token-level exceptions (\eg coordinated compound nouns), it is generally the case that independent formulaic sequences do not overlap. For example, given that \emph{be keep * under} and \emph{keep * under wraps} often appear together, overlapping on the tokens \emph{keep * under}, we do not want both being selected as an FS, even in the case where both had high minLPR. To address this problem, we use a mechanism somewhat different than above: rather than lowering the off-cost, we raise the on-cost. Let $oc(x,y)$ refer to number of times nodes $x$ and $y$ overlapped in the corpus, and $o_1\ldots o_m$ refer to \emph{turned-on} nodes which overlap with our target node $t$. With analogy to $m_0$ above, we define an $m_1$ exponential term for our target node $t$ as:

\begin{displaymath}
m_{1}(t) = \frac{c(t)}{c(t) - \sum{oc(o_1)\ldots oc(o_m)}}}
\end{displaymath}

The effect of overlaps on the cost is hyperbolic: small amounts of overlapping have little effect, but as the amount of overlapping approaches the total count of the node, the cost becomes prohibitive, effectively forcing one of nodes to turn off. The idea behind lowering the cost when covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but we do not want to encourage nodes which overlap at all, so instead we apply a penalty which increases the cost of turning on pairs of nodes which overlap.

\subsection{Optimization}

The complex interaction between nodes discussed in the preceding section prohibit a global optimization of the lattice. Fortunately, though a majority of nodes in the lattice are connected to each other though some path, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we do this has a significant effect on the result: among the obvious options, we have found that we get the best results by ordering our nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.

%The algorithm for optimization procedure is given in Figure X (???).

Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node; If, for instance, one or more of \emph{be keep * under wraps}, \emph{under wraps}, or \emph{be keep * under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \emph{keep * under wraps} from being correctly activated. Instead, the algorithm identifies a small set of nodes which are the most relevant to status of the node under consideration whose status should be considered simultaneously. Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.  Once the relevant nodes have been identified, all (including turned-off nodes) nodes whose cost function is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.

In practice, we apply the following restrictions which significantly reduce the runtime of the algorithm without sacrificing the quality of the output lexicon:

\begin{itemize}
\item The complexity of the algorithm increases exponentially with the number of ``relevant'' nodes, so we limit the total number to 5. When there are more than 5 nodes turned on the in the vicinity of the target node, they are selected by ranking in terms of the relative influence on each other given by the relative change in cost functions as defined in preceding section.
\item The total number of pairwise $n$-gram overlaps in a large corpus is too big too effectively store or search, and so we exclude overlaps with a count of less than 5 from our lattice.
\item Many nodes have a minLPR which is a little larger than 1. There is very little chance these nodes will be activated by the algorithm, and so to save time we simply do not consider activating nodes with a minLPR of less than 2.
\end{itemize}

%One more restriction is necessary to make the use of overlaps feasible: without any restrictions, the number of connections resulting from overlaps is too large. We resolved this problem by excluding as possible active nodes.

%a separate analysis of the that corpus showed the contents of most gapped FS in English were simple nouns or some portion thereof; this is somewhat less true for the more free word-order langauges we are also considering, but still a usuable heuristic.

%which be described by the following (Penn Treebank) POS regular expression:

%\vspace{3mm}
%\noindent
% PP$\,$|$\,$[(PDT)(DT)JJ*[NN$\,$|$\,$NP]*(POS$\,$|$\,$PP\$)JJ*NN*]
%\vspace{1mm}

%(Our POS tags are given by the TreeTagger)

% For our main evaluation in English, our corpus is a 890 million version of the tier 1 texts in the ICWSM 2009 blog corpus \cite{ICWSM} which has been filtered to remove duplicates and near duplicates.
\bibliography{mybib}
\bibliographystyle{eacl2017}

\end{document}

### 2016-09-27 eacl2017.tex
added evaluation

@@
 \def \al {al.\@ }
+\def \etc {etc.\@ }
 
@@
 
-In this paper we are attempting to identify \textit{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, who defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
-In computational linguistics, the most common term used to describe multiword lexical units is \textit{multiword expression} or MWE \cite{Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas.
+In this paper we are attempting to identify \emph{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, who defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
+In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or MWE \cite{Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas.
 This distinction is not a new one, for instance it exists to some extent in the MWE annotation of Schneider \cite{Schneider14a}, who distinguishes between weak (collocational) and strong (non-compositional) MWEs, but it is our contention is that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we included to disregard or minimize the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \emph{there is something going on}, \emph{it is more important than ever to\ldotz}, \emph{\ldotsdo not know what it is like to\ldots},\emph{it would be great if * could}, \emph{there is no shortage of\ldots}, \emph{the rise and fall of\ldots}, \emph{now is not the time to\ldots}, \etc as well as tens of thousands of other such phrases which, along with less compositional, clearly MWE formulas like \textit{be worth * weight in gold}, are identified by the FS-extraction system presented here.
+Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \emph{there is something going on}, \emph{it is more important than ever to\ldots}, \emph{\ldotsdo not know what it is like to\ldots},\emph{it would be great if * could}, \emph{there is no shortage of\ldots}, \emph{the rise and fall of\ldots}, \emph{now is not the time to\ldots}, \etc as well as tens of thousands of other such phrases which, along with less compositional, clearly MWE formulas like \emph{be worth * weight in gold}, are identified by the FS-extraction system presented here.
 
@@
 These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts.
-We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gap $n$-gram statistics, not regular $n$-gram statistics.
+We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics, not regular $n$-gram statistics.
 
@@
 Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count.
-First, lets define $C_0$ as the minLPR based taken to the power of some as yet undefined function $d$:
+First, lets define $C_0$ as the minLPR based taken to the power of some as yet undefined function $d_0$:
 
@@
 \begin{displaymath}
-d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}}
+d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
 \end{displaymath}
 
-This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d$ results in a squaring of the initial LPR-ratio.
+This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.
 
@@
 For instance, \emph{keep * under} is not hard-covered by \emph{keep * under wraps} (since there are FS such as \emph{keep * under surveillance}, \emph{keep it under your hat}, \etc), but if \emph{keep * under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \emph{keep * under} counts that correspond to \emph{keep * under wraps}.
-We accomplish this by lowering the turned-off cost function of {keep * under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\ldots_m$ be any turned-on nodes which are above $t$ in the lattice.
+We accomplish this by lowering the turned-off cost function of \emph{keep * under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\ldots_m$ be any turned-on nodes which are above $t$ in the lattice.
 Then, then the new $d_0$, $d_0'$ for a node $t$ is:
@@
 \begin{displaymath}
-d_{0}'(t) = \frac{c(t) - \sum{c(s_1)\ldots c(s_m)}}{c(t))} d_0(t)
+d_{0}'(t) = \frac{c(t) - \sum{c(s_1)\ldots c(s_m)}}{c(t)} d_0(t)
 
@@
 The basic mechanism is the same as covering, except that we cannot make direct make use of counts in the same way; whereas it makes sense to discount the turned-off cost of covered nodes in proportion to the (lower) relative counts of their covering nodes, in the reverse direction this logic entirely fails.
-A simple but effective solution is to use the minLPR value: a turned-on node will clear any node higher in the lattice which has a minLPR that is lower than it.
+A simple but effective solution is make use of the minLPR value: in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft clearing which lowers  $C_{0}(t)$ based on the ratio between the minLPR for the two relevant nodes, \ie
+
+\begin{displaymath}
+C_{0}'(t) = max(1, C_{0}(t) \prod{\frac{minLPR(t)}{minLPR(s_i)})}
+
+\end{displaymath}
+\noindent
+where $s_i$ is the $i$th clearing node.
 We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
-
-To give an example of its effect, if the node \emph{keep * under wraps} is turned on, then, assuming that their minLPR is lower, the $C_0$ of nodes such as \emph{be keep * under wraps} and \emph{keep * under wraps for} will be lowered to zero.
+To give an example of its effect, if the node \emph{keep * under wraps} is turned on, then, assuming that their minLPR is lower, under hard clearing the $C_0$ of nodes such as \emph{be keep * under wraps} and \emph{keep * under wraps for} will be set to 1.
 This dissuades (but does not prevent) the model from turning on these nodes.
-Note that the effect of both covering and clearing is to lower the cost function for covered/clears nodes, which encourages the model to turn \emph{keep * under wraps} on, even potentially in cases where its minLPR is relatively low.
+Note that the effect of both covering and clearing is to lower the cost function for covered/clears nodes, which encourages the model to turn an $n$-gram like \emph{keep * under wraps} on, even supposing its minLPR were relatively low.
 
@@
 Let $oc(x,y)$ refer to number of times nodes $x$ and $y$ overlapped in the corpus, and $o_1\ldots o_m$ refer to \emph{turned-on} nodes which overlap with our target node $t$.
-With analogy to $m_0$ above, we define an $m_1$ exponential term for our target node $t$ as:
+With analogy to $d_0$ above, we define an $d_1$ exponential term for our target node $t$ as:
 
 \begin{displaymath}
-m_{1}(t) = \frac{c(t)}{c(t) - \sum{oc(o_1)\ldots oc(o_m)}}}
+d_{1}(t) = \frac{c(t)}{c(t) - \sum{oc(o_1)\ldots oc(o_m)}}
 \end{displaymath}
 
-The effect of overlaps on the cost is hyperbolic: small amounts of overlapping have little effect, but as the amount of overlapping approaches the total count of the node, the cost becomes prohibitive, effectively forcing one of nodes to turn off.
-The idea behind lowering the cost when covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but we do not want to encourage nodes which overlap at all, so instead we apply a penalty which increases the cost of turning on pairs of nodes which overlap.
+The effect of overlaps on the cost is hyperbolic: small amounts of overlapping has little effect, but with significant overlap the cost becomes prohibitive, effectively forcing one of nodes to turn off.
+The idea behind lowering the cost when covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but we do not want to encourage nodes that just happen to overlap with others; a penalty is a more appropriate mechanism.
 
@@
 
-The complex interaction between nodes discussed in the preceding section prohibit a global optimization of the lattice.
+The interaction between nodes discussed in the preceding section prohibit a global optimization of the lattice.
 Fortunately, though a majority of nodes in the lattice are connected to each other though some path, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
@@
 For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice.
-The order that we do this has a significant effect on the result: among the obvious options, we have found that we get the best results by ordering our nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
+The order that we do this has an effect on the result: among the obvious options, we have found that we get the best results by ordering our nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
 
@@
 \item The complexity of the algorithm increases exponentially with the number of ``relevant'' nodes, so we limit the total number to 5.
-When there are more than 5 nodes turned on the in the vicinity of the target node, they are selected by ranking in terms of the relative influence on each other given by the relative change in cost functions as defined in preceding section.
+When there are more than 5 nodes turned on in the vicinity of the target node, they are selected by ranking in terms of the relative influence on each other given by the relative change in cost functions as defined in preceding section.
 \item The total number of pairwise $n$-gram overlaps in a large corpus is too big too effectively store or search, and so we exclude overlaps with a count of less than 5 from our lattice.
@@
 \end{itemize}
+
+\section{Evaluation}
+
+We evaluate our approach across three different languages including evaluation sets derived from five different corpora.
+In English, we follow Brooke et \al \shortcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
+To facilitate a comparison with Newman et \al \shortcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon and test set using the 100M token BNC \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
+Lemmatization included removing all inflectional marking from both words and POS tags.
+For English, we took the same gap definition as used in Brooke et \al \shortcite{Brooke15b}, which includes simple nouns and portions thereof.
+
+The other two languages evaluated are Croatian and Japanese: these two languages were selected in part because of their difference from English, and in particular their reputation for being relatively free-word order; we were interested in the challenges associated with using an $n$-gram approach in such a context.
+For Croatian, ....
+Japanese
+
+Brooke et \al \shortcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a proper F-score for any model.
+We use the earlier test set built for the ICWSM corpus, and applied the same methodology (a majority annotation from 3 trained annotators) to build a new tests sets for the BNC, and for the Japanese and Croatian corpora; our new test sets consist of 500 contiguous $n$-grams and another of 500 gapped $n$-grams for each corpus.
+We keep the two types separate because, although rarer, gapped FS are often excluded in relevant work, and, we think, deserve special attention.
+For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.
+In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.
+
+Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b} and, for the BNC, the DP-seg model from Newman et \al \shortcite{Newman12}, though the latter only handles sequential output.
+Both these models have been compared against a wide range of co-occurrence measures; we do not repeat all all comparisons here, but we do consider a lexicon built from ranking $n$-grams according to our primarily measure (minLPR) as well as the standard PMI.
+For both association measures we choose a threshold which maximizes $f$-score.
+All comparisons here are subject to the same $n$-gram frequency cutoff as the main model; since the content of our test sets are linked to this $n$-gram cutoff, it is not trivial to change it.
+
+We created small development sets for each corpus and used them to do a thorough testing of a variety of parameter settings and other options, some of which we have excluded from our  discussion here.
+We found that we were always able to get at least near-optimal results using a $C_1$ (the on-cost) of 4, and we do not present variations on this, nor on the use of covering, which we take as fundamental to the model.
+Parameters that we considered in the final comparison include modulation of the off-cost using counts \emph{+cnt}, the use of hard clearing (\emph{+hcl}) or soft clearing (\emph{+scl}), and the application of penalties for overlaps \emph{+ovr}.
+
+\section{Results}
+
+ \begin{table*}[!bt]
+
+ \begin{center}
+  \caption{ F-score for formulaic sequence identification in various test sets; LLR = log-likelihood ratio C = contiguous $n$-grams, G = gapped $n$-grams. Bold is best in column.}
+ \begin{tabular}{lcccccccccccccc}
+
+       \hline
+        \hline
+				& \multicolumn{8}{c}{\bf{English}} & & \multicolumn{2}{c}{\bf{Croatian}} & & \multicolumn{2}{c}{\bf{Japanese}} \\
+       \cline{2-9}			
+       & \multicolumn{2}{c}{\bf{ICWSM}} & &  \multicolumn{2}{c}{\bf{MWE}} & &  \multicolumn{2}{c}{\bf{BNC}} & & &  && & \\
+       \cline{2-3} \cline{5-6} \cline{8-9} \cline{11-12} \cline{14-15}
+           \multicolumn{1}{c}{\bf{Source}}    & C & G &   & C & G &   & C & G &  & C & G & & C & G  \\
+            \hline
+           \hline
+
+Human agreement & & & & & & & & & & & & & &\\
+
+ \hline
+LLR ranking & & & & & & & & & & & & & &\\ 
+LPR ranking & & & & & & & & & & & & & &\\ 
+Newman al \al (2012)  & & & & & & & & & & & & & &\\ 
+Brooke et \al (2015)  & & & & & & & & & & & & & &\\ 
+  \hline
+	Lattice\emph{+cnt+hcl+ovr} & & & & & & & & & & & & & & \\
+
+	Lattice \emph{+hcl+ovr} & & & & & & & & & & & & & & \\  	
+		Lattice \emph{+cnt+ovr} & & & & & & & & & & & & & & \\  
+			Lattice \emph{+cnt+scl+ovr} & & & & & & & & & & & & & & \\  
+				Lattice \emph{+cnt+hcl} & & & & & & & & & & & & & & \\
+
+            \hline
+           \hline
+
+ \end{tabular}
+
+ \end{center}
+ \end{table*}
 

### 2016-09-28 eacl2017.tex
Formatting tweaks

@@
 \usepackage{url}
+\usepackage{xspace}
 \usepackage{latexsym}
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+
+% TJB macros
+\newcommand{\dotts}{...}
+\newcommand{\gap}{$*$\xspace}
+\newcommand{\ex}[1]{\textit{#1}\xspace}
+\newcommand{\termdef}[1]{\textbf{#1}\xspace}
+\newcommand{\termemph}[1]{\textit{#1}\xspace}
 
@@
 
-In this paper we are attempting to identify \emph{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, who defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
+In this paper we are attempting to identify \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, who defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
 In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or MWE \cite{Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas.
 This distinction is not a new one, for instance it exists to some extent in the MWE annotation of Schneider \cite{Schneider14a}, who distinguishes between weak (collocational) and strong (non-compositional) MWEs, but it is our contention is that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we included to disregard or minimize the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \emph{there is something going on}, \emph{it is more important than ever to\ldots}, \emph{\ldotsdo not know what it is like to\ldots},\emph{it would be great if * could}, \emph{there is no shortage of\ldots}, \emph{the rise and fall of\ldots}, \emph{now is not the time to\ldots}, \etc as well as tens of thousands of other such phrases which, along with less compositional, clearly MWE formulas like \emph{be worth * weight in gold}, are identified by the FS-extraction system presented here.
+Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{it would be great if \gap could}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional, clearly MWE formulas like \ex{be worth \gap weight in gold}, are identified by the FS-extraction system presented here.
 
-\begin{figure}[!tb]
-\center{\includegraphics{FS_diagram_1.png}}
+\begin{figure}[!t]
+\center{\includegraphics[width=0.35\textwidth]{FS_diagram_1.pdf}}
 \caption{Multiword Terminology}
@@
 Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), with the base cost of being off simply a variation on the LPR association measure.
-Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \emph{keep * under wraps} would, for instance be connected ``upwards'' to the node \emph{keep everything under wraps} and connected ``downwards'' to \emph{under wraps}.
-These directional relationships allow for two basic effects between nodes in the lattice when a node is turned on: \emph{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \emph{keep * under wraps} is on, the model will tend not to choose \emph{under wraps} as an FS); and \emph{clearing}, which inhibits nodes above a turned-on node (\eg, if \emph{keep * under wraps} is on, the model would avoid selecting \emph{keep everything under wraps} as an FS).
-A third, undirected mechanism is \emph{overlapping}, where nodes inhibit each other due to (non-subsuming) overlaps in the corpus (\eg having both \emph{keep * under wraps} and \emph{be keep * under} as FS will be avoided).
+Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
+These directional relationships allow for two basic effects between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
+A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to (non-subsuming) overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
 Given these relationships, we minimize the cost of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.
@@
 
-Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \emph{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected.
+Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected.
 Again, LPR measures how statistically unlikely a particular word is relative to how predictable the word is given the same amount of syntactic context.
@@
 degree to which an $n$-gram holds together, instead it focuses on the word which is its weakest link.
-For example, in the case we are evaluating the quality of \emph{be keep * under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \emph{keep} and \emph{under}, but the minLPR is focused on the weaker relationship between \emph{be} and \emph{keep * under}.
+For example, in the case we are evaluating the quality of \ex{be keep \gap under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \ex{keep} and \ex{under}, but the minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
 
@@
 
-The most important node interaction is \textit{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice.
+The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice.
 Our model includes two types of covering: hard and soft.
-Hard covering is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \emph{keep * under wraps} and 152 counts of \emph{under wraps}, the presence of \emph{keep * under wraps} almost completely explains \emph{under wraps}, and it is better if we collapse these two decisions into one.
+Hard covering is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
 We do this by permanently disabling any covered node, and giving the covering node the maximum minLPR among all the nodes it covers; this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
@@
 Soft covering is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, \emph{keep * under} is not hard-covered by \emph{keep * under wraps} (since there are FS such as \emph{keep * under surveillance}, \emph{keep it under your hat}, \etc), but if \emph{keep * under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \emph{keep * under} counts that correspond to \emph{keep * under wraps}.
-We accomplish this by lowering the turned-off cost function of \emph{keep * under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\ldots_m$ be any turned-on nodes which are above $t$ in the lattice.
+For instance, \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to \ex{keep \gap under wraps}.
+We accomplish this by lowering the turned-off cost function of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\dotts_m$ be any turned-on nodes which are above $t$ in the lattice.
 Then, then the new $d_0$, $d_0'$ for a node $t$ is:
@@
 d_{0}'(t) = \frac{c(t) - \sum{c(s_1)\ldots c(s_m)}}{c(t)} d_0(t)
-
 \end{displaymath}
@@
 Not surprisingly, it is important to have a mechanism working in opposition, \ie one which generally prefers shorter $n$-grams.
-\textit{Clearing} does this by changing the $C_0$ of nodes higher in the lattice when a lower node is turned-on.
+\termdef{Clearing} does this by changing the $C_0$ of nodes higher in the lattice when a lower node is turned-on.
 The basic mechanism is the same as covering, except that we cannot make direct make use of counts in the same way; whereas it makes sense to discount the turned-off cost of covered nodes in proportion to the (lower) relative counts of their covering nodes, in the reverse direction this logic entirely fails.
@@
 C_{0}'(t) = max(1, C_{0}(t) \prod{\frac{minLPR(t)}{minLPR(s_i)})}
-
 \end{displaymath}
-\noindent
 where $s_i$ is the $i$th clearing node.
 We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
-To give an example of its effect, if the node \emph{keep * under wraps} is turned on, then, assuming that their minLPR is lower, under hard clearing the $C_0$ of nodes such as \emph{be keep * under wraps} and \emph{keep * under wraps for} will be set to 1.
+To give an example of its effect, if the node \ex{keep \gap under wraps} is turned on, then, assuming that their minLPR is lower, under hard clearing the $C_0$ of nodes such as \ex{be keep \gap under wraps} and \ex{keep \gap under wraps for} will be set to 1.
 This dissuades (but does not prevent) the model from turning on these nodes.
-Note that the effect of both covering and clearing is to lower the cost function for covered/clears nodes, which encourages the model to turn an $n$-gram like \emph{keep * under wraps} on, even supposing its minLPR were relatively low.
+Note that the effect of both covering and clearing is to lower the cost function for covered/clears nodes, which encourages the model to turn an $n$-gram like \ex{keep \gap under wraps} on, even supposing its minLPR were relatively low.
 
@@
 Though there are some token-level exceptions (\eg coordinated compound nouns), it is generally the case that independent formulaic sequences do not overlap.
-For example, given that \emph{be keep * under} and \emph{keep * under wraps} often appear together, overlapping on the tokens \emph{keep * under}, we do not want both being selected as an FS, even in the case where both had high minLPR.
+For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both had high minLPR.
 To address this problem, we use a mechanism somewhat different than above: rather than lowering the off-cost, we raise the on-cost.
-Let $oc(x,y)$ refer to number of times nodes $x$ and $y$ overlapped in the corpus, and $o_1\ldots o_m$ refer to \emph{turned-on} nodes which overlap with our target node $t$.
+Let $oc(x,y)$ refer to number of times nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to \termemph{turned-on} nodes which overlap with our target node $t$.
 With analogy to $d_0$ above, we define an $d_1$ exponential term for our target node $t$ as:
@@
 
-Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node; If, for instance, one or more of \emph{be keep * under wraps}, \emph{under wraps}, or \emph{be keep * under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \emph{keep * under wraps} from being correctly activated.
+Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node; If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
 Instead, the algorithm identifies a small set of nodes which are the most relevant to status of the node under consideration whose status should be considered simultaneously.
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-09-28 eacl2017.tex
Tweaks to diagrams and text

@@
 
+\newcommand{\figref}[2][]{Figure#1~\ref{#2}\xspace}
+
 \title{Unsupervised acquisition of comprehensive multiword lexicons \\ using competition in an $n$-gram lattice}
@@
 
-In this paper we are attempting to identify \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, who defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
-In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or MWE \cite{Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas.
-This distinction is not a new one, for instance it exists to some extent in the MWE annotation of Schneider \cite{Schneider14a}, who distinguishes between weak (collocational) and strong (non-compositional) MWEs, but it is our contention is that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we included to disregard or minimize the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{it would be great if \gap could}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional, clearly MWE formulas like \ex{be worth \gap weight in gold}, are identified by the FS-extraction system presented here.
+In this paper we are attempting to identify \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
+In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas.
+This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalised and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational) and strong (non-compositional) MWEs.
+It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research.
+Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, come under the umbrella of FSs.
 
@@
 \caption{Multiword Terminology}
-
+\label{fig:terminology}
 \end{figure}
 
-Figure 1 shows our conception of the terminology for multiword relationships, including FS, MWE, as well as collocations and (multiword) named entities.
-We use the term \textit{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS.
-MWEs, again, are a non-compositional subset of FS, and they overlap with named entities.
-In this regard, we disagree with the MWE annotation schema of Schneider \cite{Schneider14a} which simply includes any named entity as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \textit{Tintman Nationwide Tints Ltd} or \textit{Hickory Furniture Mart} which are easily identifiable as named entities based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names).
+\figref{fig:terminology} shows our conception of the relationship between FS, MWE and (multiword) named entities.
+%We use the term \termdef{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS.
+% TJB: I'd suggest staying away from talking about collocations altogether: it's an overloaded term; many MWEs are *not* collocations under this definition; and it's not needed for this paper
+MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs).
+In this regard, we disagree with the MWE annotation schema of \newcite{Schneider14a} which includes any NE as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \ex{Tintman Nationwide Tints Ltd} or \ex{Hickory Furniture Mart} which are easily identifiable as NEs based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers.% (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names).
+% TJB: too subtle/controversial a point for this paper
 The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition.
-Some well-known named entities are obviously good MWEs (\eg \textit{George Washington}, \textit{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.
+Some well-known named entities are obviously good MWEs (\eg \ex{George Washington}, \ex{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.
 
@@
 \begin{figure*}[!tb]
-\center{\includegraphics{FS_diagram_2.png}}
+\center{\includegraphics[width=0.8\textwidth]{FS_diagram_2.pdf}}
 \caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
-\end{figure*}[!tb]
+\end{figure*}
 

### 2017-01-16 eacl2017.tex
New draft with all major content sections filled in

@@
 \newcommand{\figref}[2][]{Figure#1~\ref{#2}\xspace}
+\newcommand{\tabref}[2][]{Table#1~\ref{#2}\xspace}
+\newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}
 
-\title{Unsupervised acquisition of comprehensive multiword lexicons \\ using competition in an $n$-gram lattice}
+\title{Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice}
 
@@
 
-\section{Background and Related work}
+\section{Background and Related Work}
 
-In this paper we are attempting to identify \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being lexicalized.
-In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a superset which includes MWEs but also (apparently) compositional linguistic formulas.
-This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalised and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational) and strong (non-compositional) MWEs.
+In this paper we will refer to the targets of lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
+Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FS that are shared by a recognizable language community.
+In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes most MWEs but also (apparently) compositional linguistic formulas.
+This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to even more confusion with respect to in its interpretation.
+Though in some contexts it has been used in way that is similar to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}}  and strong (non-compositional) MWEs.
 It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, come under the umbrella of FSs.
+Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella.
+Another reason to consider a different terminology is that there are classes of what is typically considered MWE that don't fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}).
+Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.
+Barbara W.
+Smith} or \ex{Smith Garden Supplies Ltd}).
+\figref{fig:terminology} show the conception of the relationship between FS, MWE and (multiword) named entities that we assume for this paper.
 
@@
 
-\figref{fig:terminology} shows our conception of the relationship between FS, MWE and (multiword) named entities.
 %We use the term \termdef{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS. 
 % TJB: I'd suggest staying away from talking about collocations altogether: it's an overloaded term; many MWEs are *not* collocations under this definition; and it's not needed for this paper
-MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs).
+%MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs).
 In this regard, we disagree with the MWE annotation schema of \newcite{Schneider14a} which includes any NE as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \ex{Tintman Nationwide Tints Ltd} or \ex{Hickory Furniture Mart} which are easily identifiable as NEs based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers.% (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names).
 % TJB: too subtle/controversial a point for this paper
-The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition.
+%The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition.
 Some well-known named entities are obviously good MWEs (\eg \ex{George Washington}, \ex{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.
 
-Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen.
-Only some of these measures generalize beyond two words, for example PMI \cite{Church90}, the log ratio of the joint probability to the product of the marginal probabilities.
+Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen.
+Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
 Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
-The lexical predictability ratio (LPR) of Brooke et \al \cite{Brooke15b} is a association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
+Similarly, the lexical predictability ratio (LPR) of Brooke et \al \cite{Brooke15b} is a association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability (as provided by part-of-speech information) from the overall conditional probability for each word given the other words in the phrase.
 Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily $n$-gram could be replaced by a single word \cite{Riedl15}.
 
+Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
+The algorithm of da Silva and Lopes \shortcite{daSilva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, appears limited \cite{Ramisch12}.
+Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on tradeoff between marginal and conditional statistics (\ie LPR).
+Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of Newman et \al \shortcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases.
+Gimpel and Smith \shortcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation.
+A general drawback to these generative methods, relative to approaching involving association metrics, is scalability and lack of determinacy.
+
 Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb/noun combinations \cite{Fazly09}.
-The recent work of Schneider et \al \shortcite{Schneider14b} is a rare example of a comprehensive MWE identification model which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have be mixed \cite{Riedl16}.
-Otherwise, gaps in MWEs have generally addressed by using full syntactic representations \cite{Seretan11}.
+The work of Schneider et \al \shortcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.
 
-Beyond association metrics, other general unsupervised approaches to the multiword unit identification include that of Newman et \al \shortcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary.
-Gimpel and Smith \shortcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation.
-The drawback to these generative methods, relative to association metrics, is scalability and lack of determinacy.
-Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS identification in  larger corpora, first using the conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on marginal and conditional probabilities.
-
-%Within corpus linguistics, multiword sequences are studied with the use of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold.
-In order to get very reliable phrases, the threshold is typically set high enough (Biber et \al use 40 occurrences in 1 million words) to filter out the vast majority of expressions in the process.
-Lexical bundles generally involve larger phrasal chunks that would be missed by traditional collocation extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indiciative of particular genres (\eg university lectures).
+The motivation for building lexicons of formulaic sequences naturally overlaps of those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units (citation needed?????????), as can parsing \cite{Constant16}.
+One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses.
+Within corpus linguistics, multiword sequences have studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold: in order to get very reliable phrases, the threshold is typically set rather high (Biber et \al use 40 occurrences in 1 million words).
+Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures).
 Lexical bundles have been applied, in particular, to learner language: for example, Chen and Baker \shortcite{Chen10} showed that non-native student writers use severely a restricted range of lexical bundle types, and tend to overuse those types, while Granger and Bestgen \shortcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.
+Sakaguchi et \al \shortcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; Brooke et \al \shortcite{Brooke15b} explcitly argues for FS lexicons as a way to identify, track, and improve learner proficiency.
 
@@
 
-The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus.
+Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech combinations, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
+Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases; the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS.
+The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary which best explain the statistics extracted from the corpus.
+
+%The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus.
 Our method for FS extraction assumes such a initial set of $n$-grams, and focuses on identifying the true FS, and excluding those sequences which can be explained away due to the syntax of the language and/or the existence of other FS.
@@
 
-Our approach to FS identification involves optimization of the total cost of a lattice where each node corresponds to an $n$-gram type derived from a large corpus.
+Our approach to FS identification involves optimization of the total cost of a lattice where each node corresponds to an $n$-gram type.
 The cost of the whole lattice is defined simply as a product of the costs of the individual nodes.
-Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), with the base cost of being off simply a variation on the LPR association measure.
+Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and incur different costs depending on their status.
 Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
-These directional relationships allow for two basic effects between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
-A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to (non-subsuming) overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
+These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
+A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
 Given these relationships, we minimize the cost of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.
@@
 
-The first step in the process is derive a set of $n$-grams and related statistics from a large untagged corpus of text.
+The first step in the process is derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text.
 Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows Brooke et \al \shortcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is a $n$-gram threshold cutoff, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \cite{Schneider14a} which indicates very good (over 90\%) type-level coverage excepting those highly particular proper names which would be better handled by a named entity recognition system.
-Note that our $n$-grams also include gappy versions; the definition of gaps is language specific, and we will discuss the individual languages further in section XXXXX.
-In general, though, putting in a restriction of this sort is important because it greatly lowers the number of gappy $n$-gram types.
-We also lower our number of types generally by excluding punctuation and by lemmatizing.
-Note that as long as the count threshold is signifcantly above 1, efficient extraction of all $n$-grams can be done iteratively (one pass through the corpus per $n$) for both types in combination.
+An initial requirement of any such method is a $n$-gram frequency threshold, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of Schneider et \al \shortcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification.
+Note that our set of $n$-grams also include gapped or non-contiguous $n$-grams; the definition of gaps is language specific---we will discuss the gaps for individual languages further in \secref{sec:evaluation}---but the general idea (and this is confirmed by empirical analysis) is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence.
+In a part-of-speech tagged corpus, potential gaps can be identified by a part-of-speech regular expression.
+Putting in such a restriction is useful because it greatly lowers the number of gapped $n$-gram types, increasing precision and improving speed.
+Another way the number of types are lowered is by excluding punctuation and by lemmatizing.
+Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination.
 
 Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected.
-Again, LPR measures how statistically unlikely a particular word is relative to how predictable the word is given the same amount of syntactic context.
+LPR measures how predictable a word is in a lexical context as compared to how predictable it is given only syntactic context (over the same span of words).
 Formally, the LPR for some word $w_i$ in the context of a sequence of words of length $n$ which have a corresponding set of sequence of POS tags $t$, is given by:
@@
 We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics, not regular $n$-gram statistics.
+Note that identification of the best ratio across all possible choices of context, not just the largest ,is important for longer FS, where the entire POS context alone might uniquely identify the phrase (and hence the word), resulting in a ratio of 1.
+It also ensures that the lower bound of LPR is 1, since the ratio for a word with no context at all is trivially 1.
 
-In Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but this is not an appropriate choice here: instead, the base ``off'' cost for a node in our lattice is the minimum LPR across the words in the sequence (minLPR):
+In the segmentation approach of Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here the base ``off'' cost for a node in our lattice is the minimum LPR across the words in the sequence (minLPR):
 
@@
 
-For each node, there are two cost functions, one which is used if the node on ($C_{1}$), and the other if the node is off ($C_{0}$).
+The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of minimizing the overall cost of the lattice.
+It is useful to define the cost of a node in terms of two cost functions.
+The rationale is that turning on a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to explain its existence.
+When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
+Let $C_{1}$ be the cost of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $C_{0}$ be the cost of a node when it off.
 The base value of $C_{0}$ is the minLPR metric discussed above.
-The base value of $C_{1}$ is a parameter to the model which, for nodes not influenced by one of the other factors discussed below, is equivalent to an initial threshold for building a vocabulary using the minLPR association measure.
-The lower bound on both costs is 1.
-There is no necessary upper bound on $C_{1}$, but we note here that there is a fairly small range of good choices for $C_{1}$; we have found that setting it too high ($>5$, corresponding to being five times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) will allow in too much random noise.
+The base value of $C_{1}$, which we will call just $C$, is a parameter to the model which, for nodes not influenced by one of the other factors discussed below, is equivalent to an initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS.
+There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.
 
-In general, we will be expanding these cost functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
-Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count.
-First, lets define $C_0$ as the minLPR based taken to the power of some as yet undefined function $d_0$:
+%Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count.
+
+We will influence these cost functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
+Let's define $C_0$, then, as the minLPR based taken to the power of some as yet undefined function $d_0$:
 
@@
 \end{displaymath}
+\noident
 
-LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words.
+And $C_1$ is the cost parameter $C$ taken to the power of an analogous function $d_1$
+
+\begin{displaymath}
+C_1(t) = C^{d_1(t)}
+\end{displaymath}
+\noident
+
+$d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes.
+They are also restricted to always being positive: as such, the lower bound on both costs is 1.
+
+%LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words.
 As such, it is common for more complex association measures to include multiplication by the count, or logarithm of the count.
@@
 
-\begin{displaymath}
-d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
-\end{displaymath}
+%\begin{displaymath}
+%d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
+%\end{displaymath}
 
-This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.
+%This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.
 
@@
 \caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
+\label{fig:example}
 \end{figure*}
@@
 
+\subsubsection{Covering}
+
 The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice.
 Our model includes two types of covering: hard and soft.
-Hard covering is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
-We do this by permanently disabling any covered node, and giving the covering node the maximum minLPR among all the nodes it covers; this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
-This is done as a preprocessing step, and besides being effective it also greatly improves the tractability of the iterative optimization of the lattice.
+\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
+We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers, (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
+This is done as a preprocessing step, and so it greatly improves the tractability of the iterative optimization of the lattice.
 Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.
-Finally, we also use hard covering to partially address the rather challenging problem of pronouns, which, due to pragmatic biases in particular corpora, often have higher than desirable LPR ratios, but cannot reasonably be excluded either since many common FS contain them.
-In our model, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun.
+We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR ratios \cite{Brooke15b}.
+In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.
 
-Soft covering is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to \ex{keep \gap under wraps}.
-We accomplish this by lowering the turned-off cost function of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $t$ be the target node, and $s_1\dotts_m$ be any turned-on nodes which are above $t$ in the lattice.
-Then, then the new $d_0$, $d_0'$ for a node $t$ is:
+%Another source of error are somewhat flexible FS which fall below our $n$-gram threshold but where some portion of the FS is above the threshold: to address this, we collect additional statistics and remove as a post-processing step any FS which are hard covered by an $n$-gram not in our lattice.
+
+\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
+For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that corresponds to occurrences of \ex{keep \gap under wraps}.
+This is accomplished by lowering the turned-off cost function of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\dot)$ be the count function,and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
+Then, then the $d_0$ for a covered node $t$ is:
 
 \begin{displaymath}
-d_{0}'(t) = \frac{c(t) - \sum{c(s_1)\ldots c(s_m)}}{c(t)} d_0(t)
+d_{0}(t) = \frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}
 \end{displaymath}
@@
 
+\subsubsection{Clearing}
+
 In general, covering prefers turning on longer, covering $n$-grams since doing so lowers the turned-off cost function of nodes lower in the lattice.
-Not surprisingly, it is important to have a mechanism working in opposition, \ie one which generally prefers shorter $n$-grams.
+Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which generally prefers shorter $n$-grams.
 \termdef{Clearing} does this by changing the $C_0$ of nodes higher in the lattice when a lower node is turned-on.
-The basic mechanism is the same as covering, except that we cannot make direct make use of counts in the same way; whereas it makes sense to discount the turned-off cost of covered nodes in proportion to the (lower) relative counts of their covering nodes, in the reverse direction this logic entirely fails.
-A simple but effective solution is make use of the minLPR value: in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft clearing which lowers  $C_{0}(t)$ based on the ratio between the minLPR for the two relevant nodes, \ie
+The basic mechanism is similar to covering, except that counts cannot be made use of in the same way; whereas it makes sense to discount the turned-off cost of covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are due to the covering $n$-gram), in the reverse direction this logic fails.
+A simple but effective solution which avoids introducing parameters makes use of the minLPR values of the relevant nodes.
+In the most common (two node) situation, we lower the  $C_{0}(t)$ of the higher node according to the ratio between the minLPR of two nodes, though only if the minLPR of the lower node is higher.
+Generalized to consider the (rare) case of multiple clearing nodes, this is:
+
+%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft
 
 \begin{displaymath}
-C_{0}'(t) = max(1, C_{0}(t) \prod{\frac{minLPR(t)}{minLPR(s_i)})}
+C_{0}'(t) = max(1, C_{0}(t) \frac{minLPR(t)}{\prod{minLPR(s_i)})}
 \end{displaymath}
@@
 We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
-To give an example of its effect, if the node \ex{keep \gap under wraps} is turned on, then, assuming that their minLPR is lower, under hard clearing the $C_0$ of nodes such as \ex{be keep \gap under wraps} and \ex{keep \gap under wraps for} will be set to 1.
+To give an example of its effect, if the node \ex{keep \gap under wraps} in \figref{fig:example} is turned on and has a minLPR of 8, then, if the minLPR of a node such as\ex{keep \gap under wraps for} is 4, the $C_{0}$ will be lowered to 2 ($4/(8/4)$) by clearing.
 This dissuades (but does not prevent) the model from turning on these nodes.
@@
 
+\subsubsection{Overlap}
+
 The third mechanism of node interaction involves $n$-grams which overlap in the corpus.
-Though there are some token-level exceptions (\eg coordinated compound nouns), it is generally the case that independent formulaic sequences do not overlap.
+Though there are some exceptions, it is generally the case that independent formulaic sequences do not overlap.
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both had high minLPR.
 To address this problem, we use a mechanism somewhat different than above: rather than lowering the off-cost, we raise the on-cost.
-Let $oc(x,y)$ refer to number of times nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to \termemph{turned-on} nodes which overlap with our target node $t$.
-With analogy to $d_0$ above, we define an $d_1$ exponential term for our target node $t$ as:
+The idea behind lowering the cost when covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but we do not want to encourage nodes that just happen to overlap with others; a penalty is a more appropriate mechanism.
+Let $oc(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to \termemph{turned-on} nodes which overlap with our target node $t$.
+We define an $d_1$ exponential term for the $C_1$ our target node $t$ as:
 
 \begin{displaymath}
-d_{1}(t) = \frac{c(t)}{c(t) - \sum{oc(o_1)\ldots oc(o_m)}}
+d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{oc(o_i)}}
 \end{displaymath}
@@
 The effect of overlaps on the cost is hyperbolic: small amounts of overlapping has little effect, but with significant overlap the cost becomes prohibitive, effectively forcing one of nodes to turn off.
-The idea behind lowering the cost when covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but we do not want to encourage nodes that just happen to overlap with others; a penalty is a more appropriate mechanism.
 
@@
 
-The interaction between nodes discussed in the preceding section prohibit a global optimization of the lattice.
+The dependence of the cost functions of nodes on their neighbors as discussed in the preceding section effectively prohibit a global optimization of the lattice.
 Fortunately, though a majority of nodes in the lattice are connected to each other though some path, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
@@
 For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice.
-The order that we do this has an effect on the result: among the obvious options, we have found that we get the best results by ordering our nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
+The order that we do this has an effect on the result: among the obvious options, good results are obtained when ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
 
@@
 Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node; If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
-Instead, the algorithm identifies a small set of nodes which are the most relevant to status of the node under consideration whose status should be considered simultaneously.
+Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to status of the node under consideration whose status should be considered simultaneously.
 Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
-Once the relevant nodes have been identified, all (including turned-off nodes) nodes whose cost function is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.
+Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose cost function is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.
 
-In practice, we apply the following restrictions which significantly reduce the runtime of the algorithm without sacrificing the quality of the output lexicon:
+In practice, we apply the following restrictions which significantly reduce the runtime of the algorithm without sacrificing the quality of the output lexicon (based on development set testing):
 
 \begin{itemize}
-\item The complexity of the algorithm increases exponentially with the number of ``relevant'' nodes, so we limit the total number to 5.
-When there are more than 5 nodes turned on in the vicinity of the target node, they are selected by ranking in terms of the relative influence on each other given by the relative change in cost functions as defined in preceding section.
-\item The total number of pairwise $n$-gram overlaps in a large corpus is too big too effectively store or search, and so we exclude overlaps with a count of less than 5 from our lattice.
+\item The complexity of the algorithm increases exponentially with the number of relevant nodes, so we limit the total number to 5.
+When there are more than 5 nodes turned on in the vicinity of the target node, relevant nodes are selected by ranking in terms of the influence of the nodes on each other as given by the relative change in their cost functions.
+\item The full set of pairwise $n$-gram overlaps in a large corpus is too big too effectively store, and so we exclude overlaps with a count of less than 5 from our lattice.
 \item Many nodes have a minLPR which is a little larger than 1.
-There is very little chance these nodes will be activated by the algorithm, and so to save time we simply do not consider activating nodes with a minLPR of less than 2.
+There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering we do not consider activating nodes with a minLPR of less than 2.
 \end{itemize}
-
-\section{Evaluation}
-
-We evaluate our approach across three different languages including evaluation sets derived from five different corpora.
-In English, we follow Brooke et \al \shortcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
-To facilitate a comparison with Newman et \al \shortcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon and test set using the 100M token BNC \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
-Lemmatization included removing all inflectional marking from both words and POS tags.
-For English, we took the same gap definition as used in Brooke et \al \shortcite{Brooke15b}, which includes simple nouns and portions thereof.
-
-The other two languages evaluated are Croatian and Japanese: these two languages were selected in part because of their difference from English, and in particular their reputation for being relatively free-word order; we were interested in the challenges associated with using an $n$-gram approach in such a context.
-For Croatian, ....
-Japanese
-
-Brooke et \al \shortcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a proper F-score for any model.
-We use the earlier test set built for the ICWSM corpus, and applied the same methodology (a majority annotation from 3 trained annotators) to build a new tests sets for the BNC, and for the Japanese and Croatian corpora; our new test sets consist of 500 contiguous $n$-grams and another of 500 gapped $n$-grams for each corpus.
-We keep the two types separate because, although rarer, gapped FS are often excluded in relevant work, and, we think, deserve special attention.
-For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.
-In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.
-
-Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b} and, for the BNC, the DP-seg model from Newman et \al \shortcite{Newman12}, though the latter only handles sequential output.
-Both these models have been compared against a wide range of co-occurrence measures; we do not repeat all all comparisons here, but we do consider a lexicon built from ranking $n$-grams according to our primarily measure (minLPR) as well as the standard PMI.
-For both association measures we choose a threshold which maximizes $f$-score.
-All comparisons here are subject to the same $n$-gram frequency cutoff as the main model; since the content of our test sets are linked to this $n$-gram cutoff, it is not trivial to change it.
-
-We created small development sets for each corpus and used them to do a thorough testing of a variety of parameter settings and other options, some of which we have excluded from our  discussion here.
-We found that we were always able to get at least near-optimal results using a $C_1$ (the on-cost) of 4, and we do not present variations on this, nor on the use of covering, which we take as fundamental to the model.
-Parameters that we considered in the final comparison include modulation of the off-cost using counts \emph{+cnt}, the use of hard clearing (\emph{+hcl}) or soft clearing (\emph{+scl}), and the application of penalties for overlaps \emph{+ovr}.
-
-\section{Results}
 
@@
  \begin{center}
-  \caption{ F-score for formulaic sequence identification in various test sets; LLR = log-likelihood ratio C = contiguous $n$-grams, G = gapped $n$-grams. Bold is best in column.}
- \begin{tabular}{lcccccccccccccc}
+  \caption{ Statistics for test sets}
+	 \label{tab:stats}
+	 \begin{tabular}{lccccc}
+
+       \hline
+			& Contiguous FS & Contiguous non-FS & Gapped FS & Gapped non-FS & Fleiss Kappa\\
+			 \hline
+			ICWSM & 169 & 702 & 29 & 916& 0.84 \\
+			BNC & 33 & 395 & 7 & 474 & 0.75 \\
+			Croatian & 64 & 382 & 11 & 456 & 0.87 \\
+			Japanese & 124 & 286 & 36 & 341 & 0.81\\
+       \hline
+ \end{tabular}
+
+ \end{center}
+
+ \end{table*}
+
+\section{Evaluation} \label{sec:evaluation}
+
+We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
+In English, we follow Brooke et \al \shortcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
+To facilitate a comparison with Newman et \al \shortcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
+Lemmatization included removing all inflectional marking from both words and POS tags.
+For English, we took the same POS regex used in Brooke et \al \shortcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.
+
+The other two languages we include in our evaluation are Croatian and Japanese.
+Relative to English, both languages are free-word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS extraction in such languages.
+For Croatian, we used the X corpus, a collection of X.
+The POS regex for Croatian included XXX.
+....
+For Japanese we used a portion of the X corpus of roughly the same size (by token) as the ICWSM.
+The POS regex for Japanese...
+
+Brooke et \al \shortcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
+We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: based on written guidelines derived from the definitions of Wray \cite{Wray08} and at least one practice round,three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
+
+Other than the inclusion of new languages, our test sets differ from Brooke et \al \shortcite{Brooke15b} in two ways.
+First, instead of relying on strict majority annotation, we entirely excluded $n$-grams which just one annotator marked as FS.
+One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to an task with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving the reliability of evaluation at the cost of some representativeness.
+Second, for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
+The rationale is that the number of positive gapped examples was too low (particularly for the BNC and the Croatian corpus) to provide a reliable independent F-score (see further of discussion of gapped phrases in \secref{sec:discussion}).
+Statistics for the four test sets are given in \tabref{tab:stats}.
+
+% For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.
+
+%In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.
+
+Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b}.
+For the BNC, we also compare, separately, the DP-seg model from Newman et \al \shortcite{Newman12}: because the latter only handles sequential output, we use only the sequential part of the BNC test set.
+Both these models have been compared against a wide range of association measures;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
+Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $n-1$-gram, likelihood ratios must consider all combinations of all component $n-1,2,3\ldots$-grams, including, in our case, not only contiguous but also non-contiguous components.
+The corresponding exponential increase in complexity renders it and other such methods impractical for unrestricted FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
+All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
+
+We created small development sets for each corpus and used them to do a thorough testing of parameter settings and other options, many of which we have excluded from our discussion here.
+Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all 4 corpora.
+We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
+
+ \begin{table*}[!bt]
+
+ \begin{center}
+  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
+Bold is best in column.}
+	 \label{tab:main}
+ \begin{tabular}{lcccccccccccccccc}
 
@@
         \hline
-				& \multicolumn{8}{c}{\bf{English}} & & \multicolumn{2}{c}{\bf{Croatian}} & & \multicolumn{2}{c}{\bf{Japanese}} \\
+				& \multicolumn{7}{c}{\bf{English}} & & \multicolumn{3}{c}{\bf{Croatian}} & & \multicolumn{3}{c}{\bf{Japanese}} \\
        \cline{2-9}			
-       & \multicolumn{2}{c}{\bf{ICWSM}} & &  \multicolumn{2}{c}{\bf{MWE}} & &  \multicolumn{2}{c}{\bf{BNC}} & & &  && & \\
-       \cline{2-3} \cline{5-6} \cline{8-9} \cline{11-12} \cline{14-15}
-           \multicolumn{1}{c}{\bf{Source}}    & C & G &   & C & G &   & C & G &  & C & G & & C & G  \\
+       & \multicolumn{3}{c}{\bf{ICWSM}} & &  \multicolumn{3}{c}{\bf{BNC}} & & &&&  && & \\
+       \cline{2-4} \cline{6-8} \cline{10-12} \cline{14-16}
+           \multicolumn{1}{c}{\bf{Source}}    & P & R & F &   & P & R & F &   & P & R & F &  & P & R & F \\
             \hline
@@
 
-Human agreement & & & & & & & & & & & & & &\\
+PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.24 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.23& 0.09 & 0.15 \\ 
+minLPRrank & 0.49& 0.31 & 0.39 & & 0.25& 0.45 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.51 & 0.14 & 0.22 \\
 
+LPR-seg  &0.53 & 0.42 & 0.47 && 0.38 & 0.44 & 0.41 & & 0.41 & 0.47  & 0.43 &  & 0.77 & 0.34 & 0.47 \\ 
   \hline
-LLR ranking & & & & & & & & & & & & & &\\ 
-LPR ranking & & & & & & & & & & & & & &\\ 
-Newman al \al (2012)  & & & & & & & & & & & & & &\\ 
-Brooke et \al (2015)  & & & & & & & & & & & & & &\\ 
-  \hline
-	Lattice\emph{+cnt+hcl+ovr} & & & & & & & & & & & & & & \\
 
-	Lattice \emph{+hcl+ovr} & & & & & & & & & & & & & & \\  	
-		Lattice \emph{+cnt+ovr} & & & & & & & & & & & & & & \\  
-			Lattice \emph{+cnt+scl+ovr} & & & & & & & & & & & & & & \\  
-				Lattice \emph{+cnt+hcl} & & & & & & & & & & & & & & \\
+	Lattice \emph{-cl} & 0.57& 0.42 & 0.49 & & 0.34& 0.59 & 0.43 & & 0.39 & 0.56 & 0.46 & & 0.74 & 0.39 & 0.51 \\
 
+	Lattice \emph{-ovr} & 0.52& \bf{0.53} & 0.53 & & 0.34& \bf{0.60} & 0.43& & 0.35 & \bf{0.65} & 0.45 & & 0.69 & \bf{0.51} & \bf{0.59} \\
+
+				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.39}& 0.59 & \bf{0.47} & &\bf{0.42} & 0.57 & \bf{0.48} & & \bf{0.86} & 0.39 & 0.54 \\ 
             \hline
@@
  \end{center}
+
  \end{table*}
 
+ \begin{table}[!bt]
+
+ \begin{center}
+  \caption{ Results of formulaic sequence identification in sequential BNC test set; DP-seg = method of Newman et \al (2012)}
+	\label{tab:BNC}
+
+	 \begin{tabular}{lccc}
+
+       \hline
+			& P & R & F\\
+			 \hline
+			minLPRrank & 0.34 & 0.45 & 0.39 \\
+			LPR-seg & 0.42 & 0.45 & 0.43 \\
+			DP-seg & 0.34 & 0.71 & 0.46 \\
+			Lattice & 0.46 & 0.61 & 0.53 \\
+       \hline
+ \end{tabular}
+
+ \end{center}
+
+ \end{table}
+
+\section{Results}
+
+The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
+As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
+The LPRseg method of Brooke et \al \shortcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistently across languages, though the margin is slightly larger for English corpora.
+Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical with in Croatian, and in Japanese precision is already high enough relative to recall that the f-score is not improved.
+The ICWSM corpus also has relatively high precision, whereas both the BNC and Croatian corpus have low precision and high recall.
+
+In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that the DP-seg method of Newman \cite{Newman12} was also able to beat our baseline methods, but with regards to F-score, it was inferior to our Lattice method.
+Some of that difference seems attributable to a severe precision/recall imbalance, though it was one we unable to improve by changing the parameters of the model from recommended settings.
+
+\section{Discussion} \label{sec:discussion}
+
+Though the results across the four corpora are reasonably similar with respect to overall f-score, there are a significant discrepancies.
+By using the UniDict morpheme representation for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
+The result is that there are many more FS for Japanese.
+Precision is very high, and recall is relatively low.
+Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to f-score, which explains why the full model is not the best in that case.
+Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM, or almost 14\% of all $n$-gram types.
+One idea for future work is to automatically adapt to the particular properties of the input language/corpus, though it might also be worth considering whether f-score is the most appropriate metric, given that high precision seems particularly desirable in a lexical resource.
+
+At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively low size: whereas the $n$-gram threshold we have used here results in a minimum counts of in the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times.
+This might be resolved, of course, by increasing the $n$-gram threshold, or simply avoiding small corpora altogether, but it may be useful to focus effort on how to building comprehensive FS lexicons even in relatively low resource situations.
+One idea we are actively pursing is modifying the calculation of the LPR metric to integrating uncertainty due to low counts.
+
+There is one another more general explanation for the precision/recall imbalances we see across the four corpora: Both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, in particularly newswire.
+The ICWSM and the Japanese corpus, on the other hand, are mostly blogs and other internet genres.
+Though all genres have FS, there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres.
+The fact that last than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
+
+We were interested in addressing Croatian and Japanese in part because of their tendency towards relatively free word order, and whether allowing gaps in our FS would help with these languages.
+We discovered however, that free word order actually results in \emph{more} of a tendancy towards contiguous FS rather than less.
+Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is the relatively fixed-order of English that sometimes keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints.
+The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS.
+This phenomena actually highlights a problem with the model, in that gapped and contiguous version of the same $n$-gram sequence are, at present, considered entirely independently.
+Alternatives for dealing with this range from collapsing statistics to create a single node, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.
+
+A third, more ambitious option would be to switch to a dependency representation.
+This option actually requires very little change to the model presented here, since all the basic relationships in the lattice as well as the LPR metric could be straightforwardly defined in terms of subgraphs instead of strings.
+One clear negative is the need for a dependency parser for the language and domain of interest, and that there is no potential for the use of FS to improve parsing.
+A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for syntactic gaps in order to represent a full range of FS: there are a small category of gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \ie \ex{no amount of * can}.
+
+As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations.
+Another connection could be based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, for instance, learning that verb-particle constructions are generally likely to be FS.
+Our investigations thus far suggest that it may be difficult to apply this idea without merely amplifying existing biases in the LPR measure.
+Bringing in other information, for instance some simple distributional statistics which might help us identify which $n$-grams have non-compositional semantics, would, could, in combination with the existing lattice competition, help us focus the model on detecting MWEs, which could then serve as a reliable basis for generalizing to $n$-gram for which the raw LPR statistics are an unreliable indicator.
+
+Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, since precision and recall are both dependent on the number of positive examples, f-scores are unreliable when there are few positive examples.
+To do a independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling.
+One option we could consider is a adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without hopelessly biasing the evaluation, both in terms of the specific $n$-grams evaluated as well as the ratio between positive and negative examples.
+
+%Otherwise, gaps in MWEs have generally addressed by using full syntactic representations \cite{Seretan11}.
 %One more restriction is necessary to make the use of overlaps feasible: without any restrictions, the number of connections resulting from overlaps is too large.

### 2017-01-18 tacl.tex
Switched to TACL tex, added abstract/intro/conclusion

--- 2017-01-16 eacl2017.tex
@@
 %
-% File eacl2017.tex
+% File acl2012.tex
 %
-%% Based on the style files for ACL-2016
-%% Based on the style files for ACL-2015, with some improvements
-%%  taken from the NAACL-2016 style
-%% Based on the style files for ACL-2014, which were, in turn,
-%% Based on the style files for ACL-2013, which were, in turn,
-%% Based on the style files for ACL-2012, which were, in turn,
-%% based on the style files for ACL-2011, which were, in turn, 
-%% based on the style files for ACL-2010, which were, in turn, 
-%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
-%% based on the style files for EACL-2009 and IJCNLP-2008...
+% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
+%%
+%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
+%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn
 
-%% Based on the style files for EACL 2006 by 
-%%e.agirre@ehu.es or Sergi.Balari@uab.es
-%% and that of ACL 08 by Joakim Nivre and Noah Smith
-
-\documentclass[11pt]{article}
-\usepackage{eacl2017}
+\documentclass[11pt,letterpaper]{article}
+\usepackage[letterpaper]{geometry}
+\usepackage{acl2012}
 \usepackage{times}
+\usepackage{latexsym}
+\usepackage{amsmath}
+\usepackage{multirow}
 \usepackage{url}
 \usepackage{xspace}
-\usepackage{latexsym}
 \usepackage[pdftex]{graphicx}
+\makeatletter
+\newcommand{\@BIBLABEL}{\@emptybiblabel}
+\newcommand{\@emptybiblabel}[1]{}
+\makeatother
+\usepackage[hidelinks]{hyperref}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\setlength\titlebox{6.5cm}    % Expanding the titlebox
 
@@
 
+We present a new model for acquiring unrestricted multiword lexicons from large corpora based on  competition among $n$-gram candidates.
+In contrast to the standard approach of simple ranking by association measure, in our model $n$-grams are arranged in a lattice structure based on subsumption and overlap relationships, with nodes inhibiting other nodes in their vicinity when they are selected as a lexical item.
+We show how the configuration of such a lattice can be optimized tractably, and our evaluation using annotations of sampled $n$-grams indicates that it is consistently outperforms alternatives by at least 0.05 f-score across several corpora and languages.
+
 \end{abstract}
@@
 
+Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers both produce and process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard unit for most research in modern NLP.
+The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work.
+We present a effective, expandable, and above all tractable new approach in comprehensive multiword lexicon acquisition that aims to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which fail to scale to the large corpora which are now the main sources of the distributional information which are central to lexical knowledge in modern NLP systems.
+
+Our model involves competition among a large set of contiguous and non-contiguous $n$-gram types---connected to each other based on subsumption and overlap relations in a lattice-shaped graph---to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical (and not syntactic) affinity.
+We test our model across 4 large corpora in 3 languages, including 2 relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms recently proposed alternatives, offering both scalability and many avenues for future enhancement.
+
 \section{Background and Related Work}
 
-In this paper we will refer to the targets of lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
 Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FS that are shared by a recognizable language community.
@@
 Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
-The algorithm of da Silva and Lopes \shortcite{daSilva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, appears limited \cite{Ramisch12}.
+The algorithm of Silva and Lopes \shortcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, appears limited \cite{Ramisch12}.
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on tradeoff between marginal and conditional statistics (\ie LPR).
@@
 
-And $C_1$ is the cost parameter $C$ taken to the power of an analogous function $d_1$
+And $C_1$ is the cost parameter $C$ taken to the power of an analogous function $d_1$:
 
@@
 
-$d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes.
+The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes.
 They are also restricted to always being positive: as such, the lower bound on both costs is 1.
@@
 We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
-To give an example of its effect, if the node \ex{keep \gap under wraps} in \figref{fig:example} is turned on and has a minLPR of 8, then, if the minLPR of a node such as\ex{keep \gap under wraps for} is 4, the $C_{0}$ will be lowered to 2 ($4/(8/4)$) by clearing.
+To give an example of its effect, if the node \ex{keep \gap under wraps} in \figref{fig:example} is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, the $C_{0}$ will be lowered to 2 ($4/(8/4)$) by clearing.
 This dissuades (but does not prevent) the model from turning on these nodes.
@@
 			ICWSM & 169 & 702 & 29 & 916& 0.84 \\
-			BNC & 33 & 395 & 7 & 474 & 0.75 \\
+			BNC & 49 & 403 & 8 & 475 & 0.84 \\
 			Croatian & 64 & 382 & 11 & 456 & 0.87 \\
@@
 
-% For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.
-
-%In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.
-
-Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b}.
-For the BNC, we also compare, separately, the DP-seg model from Newman et \al \shortcite{Newman12}: because the latter only handles sequential output, we use only the sequential part of the BNC test set.
-Both these models have been compared against a wide range of association measures;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
-Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $n-1$-gram, likelihood ratios must consider all combinations of all component $n-1,2,3\ldots$-grams, including, in our case, not only contiguous but also non-contiguous components.
-The corresponding exponential increase in complexity renders it and other such methods impractical for unrestricted FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
-For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
-All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
-
-We created small development sets for each corpus and used them to do a thorough testing of parameter settings and other options, many of which we have excluded from our discussion here.
-Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all 4 corpora.
-We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
-
  \begin{table*}[!bt]
@@
  \begin{center}
-  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
+  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
 Bold is best in column.}
@@
 
-PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.24 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.23& 0.09 & 0.15 \\ 
-minLPRrank & 0.49& 0.31 & 0.39 & & 0.25& 0.45 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.51 & 0.14 & 0.22 \\
+PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.23& 0.09 & 0.15 \\ 
+minLPRrank & 0.49& 0.31 & 0.39 & & 0.25& 0.44 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.51 & 0.14 & 0.22 \\
 
-LPR-seg  &0.53 & 0.42 & 0.47 && 0.38 & 0.44 & 0.41 & & 0.41 & 0.47  & 0.43 &  & 0.77 & 0.34 & 0.47 \\ 
+LPR-seg  &0.53 & 0.42 & 0.47 && 0.37 & 0.44 & 0.40 & & 0.41 & 0.47  & 0.43 &  & 0.77 & 0.34 & 0.47 \\ 
   \hline
 
-	Lattice \emph{-cl} & 0.57& 0.42 & 0.49 & & 0.34& 0.59 & 0.43 & & 0.39 & 0.56 & 0.46 & & 0.74 & 0.39 & 0.51 \\
+	Lattice \emph{-cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.74 & 0.39 & 0.51 \\
 
-	Lattice \emph{-ovr} & 0.52& \bf{0.53} & 0.53 & & 0.34& \bf{0.60} & 0.43& & 0.35 & \bf{0.65} & 0.45 & & 0.69 & \bf{0.51} & \bf{0.59} \\
+	Lattice \emph{-ovr} & 0.52& \bf{0.53} & 0.53 & & 0.33& \bf{0.60} & 0.43& & 0.35 & \bf{0.65} & 0.45 & & 0.69 & \bf{0.51} & \bf{0.59} \\
 
-				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.39}& 0.59 & \bf{0.47} & &\bf{0.42} & 0.57 & \bf{0.48} & & \bf{0.86} & 0.39 & 0.54 \\ 
+				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.41}& 0.56 & \bf{0.47} & &\bf{0.42} & 0.57 & \bf{0.48} & & \bf{0.86} & 0.39 & 0.54 \\ 
             \hline
@@
  \begin{center}
-  \caption{ Results of formulaic sequence identification in sequential BNC test set; DP-seg = method of Newman et \al (2012)}
+  \caption{ Results of formulaic sequence identification in sequential BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
 	\label{tab:BNC}
@@
 			 \hline
+			LocalMaxs & \bf{0.58} & 0.14 & 0.23 \\
 			minLPRrank & 0.34 & 0.45 & 0.39 \\
 			LPR-seg & 0.42 & 0.45 & 0.43 \\
-			DP-seg & 0.34 & 0.71 & 0.46 \\
-			Lattice & 0.46 & 0.61 & 0.53 \\
+			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
+			Lattice & 0.46 & 0.61 & \bf{0.53} \\
        \hline
@@
 
+% For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.
+
+%In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.
+
+Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b}.
+For the BNC, we also compare, separately, the DP-seg model from Newman et \al \shortcite{Newman12}, and the LocalMaxs algorithm of Silva and Lopes \shortcite{Silva99}; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
+All these approaches have been compared against a wide range of association measures;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
+Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $n-1$-gram, likelihood ratios must consider all combinations of all component $n-1,2,3\ldots$-grams, including, in our case, not only contiguous but also non-contiguous components.
+The corresponding exponential increase in complexity renders it and other such methods impractical for unrestricted FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
+All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
+
+We created small development sets for each corpus and used them to do a thorough testing of parameter settings.
+Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all 4 corpora.
+We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
+
 \section{Results}
@@
 As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
-The LPRseg method of Brooke et \al \shortcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistently across languages, though the margin is slightly larger for English corpora.
-Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical with in Croatian, and in Japanese precision is already high enough relative to recall that the f-score is not improved.
+The LPRseg method of Brooke et \al \shortcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
+Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical with in Croatian.
 The ICWSM corpus also has relatively high precision, whereas both the BNC and Croatian corpus have low precision and high recall.
 
-In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that the DP-seg method of Newman \cite{Newman12} was also able to beat our baseline methods, but with regards to F-score, it was inferior to our Lattice method.
+In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that the LocalMaxs algorithm did fairly poorly, whereas the DP-seg method of Newman \cite{Newman12} was also able to beat our baseline methods, but with regards to F-score, it was inferior to our Lattice method.
 Some of that difference seems attributable to a severe precision/recall imbalance, though it was one we unable to improve by changing the parameters of the model from recommended settings.
@@
 Though the results across the four corpora are reasonably similar with respect to overall f-score, there are a significant discrepancies.
-By using the UniDict morpheme representation for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
+By using the UniDict morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
 The result is that there are many more FS for Japanese.
 Precision is very high, and recall is relatively low.
-Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to f-score, which explains why the full model is not the best in that case.
-Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM, or almost 14\% of all $n$-gram types.
-One idea for future work is to automatically adapt to the particular properties of the input language/corpus, though it might also be worth considering whether f-score is the most appropriate metric, given that high precision seems particularly desirable in a lexical resource.
+Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to f-score, which explains why the full model is not the best in that one case.
+Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM, or almost 14\% of all $n$-gram types.
+One idea for future work is to automatically adapt to the particular properties of the input language/corpus, though it might also be worth considering whether f-score is the most appropriate metric for evaluation, given that high precision seems particularly desirable in a lexical resource.
 
@@
 There is one another more general explanation for the precision/recall imbalances we see across the four corpora: Both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, in particularly newswire.
-The ICWSM and the Japanese corpus, on the other hand, are mostly blogs and other internet genres.
+The ICWSM and the Japanese corpus, on the other hand, are mostly blogs.
 Though all genres have FS, there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres.
@@
 We were interested in addressing Croatian and Japanese in part because of their tendency towards relatively free word order, and whether allowing gaps in our FS would help with these languages.
-We discovered however, that free word order actually results in \emph{more} of a tendancy towards contiguous FS rather than less.
-Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is the relatively fixed-order of English that sometimes keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints.
+We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS rather than less.
+Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is the relatively fixed-order of English that more often keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints.
 The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS.
-This phenomena actually highlights a problem with the model, in that gapped and contiguous version of the same $n$-gram sequence are, at present, considered entirely independently.
-Alternatives for dealing with this range from collapsing statistics to create a single node, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.
+This phenomena actually highlights a problem with the current model, in that gapped and contiguous version of the same $n$-gram sequence are, at present, considered entirely independently.
+Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.
 
 A third, more ambitious option would be to switch to a dependency representation.
-This option actually requires very little change to the model presented here, since all the basic relationships in the lattice as well as the LPR metric could be straightforwardly defined in terms of subgraphs instead of strings.
-One clear negative is the need for a dependency parser for the language and domain of interest, and that there is no potential for the use of FS to improve parsing.
-A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for syntactic gaps in order to represent a full range of FS: there are a small category of gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \ie \ex{no amount of * can}.
+This option actually requires very little change to the structure of the model presented here, since all the basic relationships in the lattice as well as the minLPR measure could be straightforwardly defined in terms of subgraphs instead of strings.
+One clear negative is the need for a dependency parser for the language and domain of interest, and that there is then no potential for using of FS to improve parsing.
+A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for gaps in order to represent a full range of FS: there are gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \ie \ex{no amount of * can}.
 
 As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations.
-Another connection could be based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, for instance, learning that verb-particle constructions are generally likely to be FS.
-Our investigations thus far suggest that it may be difficult to apply this idea without merely amplifying existing biases in the LPR measure.
-Bringing in other information, for instance some simple distributional statistics which might help us identify which $n$-grams have non-compositional semantics, would, could, in combination with the existing lattice competition, help us focus the model on detecting MWEs, which could then serve as a reliable basis for generalizing to $n$-gram for which the raw LPR statistics are an unreliable indicator.
+One of the major benefits of this model as compared to alternatives is the relative ease at which additional kinds of interactions between nodes could be implemented.
+Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, for instance, learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
+Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
+Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaiticity.
 
-Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, since precision and recall are both dependent on the number of positive examples, f-scores are unreliable when there are few positive examples.
+Given our interest in methods which work well on large corpora, the speed of the model is worth mentioning.
+Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of Brooke et \al \shortcite{Brooke15a}, we found that the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary for to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
+We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.
+
+Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, the fact that precision and recall are both dependent on the number of positive examples means that f-scores become unreliable when there are very few positive examples.
 To do a independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling.
-One option we could consider is a adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without hopelessly biasing the evaluation, both in terms of the specific $n$-grams evaluated as well as the ratio between positive and negative examples.
+Rather than brute force annotation, one option we could consider is a adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without significantly biasing the evaluation.
+
+\section{Conclusion}
+
+We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice.
+Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
+A tool which implements the method as well as the acquired lexicons and test sets are available here.\footnote{removed for anonymity}
 
@@
 \bibliography{mybib}
-\bibliographystyle{eacl2017}
+\bibliographystyle{acl2012}
 

### 2017-01-19 tacl.tex
Switched from cost to expainedness

@@
 Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
-The algorithm of Silva and Lopes \shortcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, appears limited \cite{Ramisch12}.
+The algorithm of Silva and Lopes \shortcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on tradeoff between marginal and conditional statistics (\ie LPR).
@@
 
-Our approach to FS identification involves optimization of the total cost of a lattice where each node corresponds to an $n$-gram type.
-The cost of the whole lattice is defined simply as a product of the costs of the individual nodes.
-Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and incur different costs depending on their status.
+Our approach to FS identification involves optimization of the total explanatory power of a lattice where each node corresponds to an $n$-gram type.
+The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes.
+Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and explainedness will be calculated differently depending on their status.
 Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
@@
 A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
-Given these relationships, we minimize the cost of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.
+Given these relationships, we maximize the explanatory power of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.
 
@@
 
-In the segmentation approach of Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here the base ``off'' cost for a node in our lattice is the minimum LPR across the words in the sequence (minLPR):
+In the segmentation approach of Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (minLPR):
 
@@
 
-\subsection{Node cost functions}
+\subsection{Node explainedness functions}
 
-The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of minimizing the overall cost of the lattice.
-It is useful to define the cost of a node in terms of two cost functions.
-The rationale is that turning on a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to explain its existence.
+The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of minimizing the overall explanatory power of the lattice.
+Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained.
+It will be useful to define the explainedness of a node in terms of two functions: the rationale for having two functions is that the on/off status of a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence.
 When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
-Let $C_{1}$ be the cost of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $C_{0}$ be the cost of a node when it off.
-The base value of $C_{0}$ is the minLPR metric discussed above.
-The base value of $C_{1}$, which we will call just $C$, is a parameter to the model which, for nodes not influenced by one of the other factors discussed below, is equivalent to an initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS.
+Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it off.
+The base value of $E_{0}$ is the inverse of the minLPR metric discussed above: when the minLPR metric is 1, corresponding to a case when the syntactic content predicts one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1.
+The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS.
 There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.
@@
 
-We will influence these cost functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
-Let's define $C_0$, then, as the minLPR based taken to the power of some as yet undefined function $d_0$:
+We will influence these functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
+Let's define $E_0$, then, as the minLPR based taken to the negative power of some as yet undefined function $d_0$:
 
 \begin{displaymath}
-C_0(t) = minLPR(t)^{d_0(t)}
+E_0(t) = minLPR(t)^{-d_0(t)}
 \end{displaymath}
@@
 
-And $C_1$ is the cost parameter $C$ taken to the power of an analogous function $d_1$:
+And $E_1$ is the cost parameter $C$ taken to the negative power of an analogous function $d_1$:
 
 \begin{displaymath}
-C_1(t) = C^{d_1(t)}
+E_1(t) = C^{-d_1(t)}
 \end{displaymath}
@@
 The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes.
-They are also restricted to always being positive: as such, the lower bound on both costs is 1.
+They are also restricted to always being positive.
 
@@
 For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that corresponds to occurrences of \ex{keep \gap under wraps}.
-This is accomplished by lowering the turned-off cost function of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\dot)$ be the count function,and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
+This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\dot)$ be the count function,and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
 Then, then the $d_0$ for a covered node $t$ is:
@@
 \begin{displaymath}
-d_{0}(t) = \frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}
+cover(t) = max(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)})
 \end{displaymath}
@@
 
-In general, covering prefers turning on longer, covering $n$-grams since doing so lowers the turned-off cost function of nodes lower in the lattice.
-Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which generally prefers shorter $n$-grams.
-\termdef{Clearing} does this by changing the $C_0$ of nodes higher in the lattice when a lower node is turned-on.
-The basic mechanism is similar to covering, except that counts cannot be made use of in the same way; whereas it makes sense to discount the turned-off cost of covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are due to the covering $n$-gram), in the reverse direction this logic fails.
+In general, covering prefers turning on longer, covering $n$-grams since doing so explains nodes lower in the lattice.
+Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer ones which contain them, beyond the FS-neutral syntactic explanation provided by minLPR.
+\termdef{Clearing} does this by changing the $E_0$ of nodes higher in the lattice when a lower node is turned-on.
+The basic mechanism is similar to covering, except that counts cannot be made use of in the same way; whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
 A simple but effective solution which avoids introducing parameters makes use of the minLPR values of the relevant nodes.
-In the most common (two node) situation, we lower the  $C_{0}(t)$ of the higher node according to the ratio between the minLPR of two nodes, though only if the minLPR of the lower node is higher.
-Generalized to consider the (rare) case of multiple clearing nodes, this is:
+In the most common (two node) situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher, which greatly restricts its effect.
+Generalized to consider the (rare) case of multiple clearing nodes, we define clear(t) as:
 
@@
 \begin{displaymath}
-C_{0}'(t) = max(1, C_{0}(t) \frac{minLPR(t)}{\prod{minLPR(s_i)})}
+clear(t) = \prod_{i=1}^{m}{ min(1,\frac{minLPR(t)}{minLPR(u_i)})}
 \end{displaymath}
-where $s_i$ is the $i$th clearing node.
+where $u_i$ is the $i$th clearing node of $t$.
 We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
-To give an example of its effect, if the node \ex{keep \gap under wraps} in \figref{fig:example} is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, the $C_{0}$ will be lowered to 2 ($4/(8/4)$) by clearing.
-This dissuades (but does not prevent) the model from turning on these nodes.
-Note that the effect of both covering and clearing is to lower the cost function for covered/clears nodes, which encourages the model to turn an $n$-gram like \ex{keep \gap under wraps} on, even supposing its minLPR were relatively low.
+For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, clear(t) will be 0.5.
+We can now define d_{0}(t) as:
+
+\begin{displaymath}
+d_0(t) = cover(t) \cdot clear(t)
+\end{displaymath}
+
+Note that the effect of both covering and clearing is to  increase explainedness for covered/cleared nodes, which indirectly encourages the model to turn an $n$-gram like \ex{keep \gap under wraps} on in order to explain nodes in its vicinity, even supposing its minLPR were relatively low.
 
@@
 Though there are some exceptions, it is generally the case that independent formulaic sequences do not overlap.
-For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both had high minLPR.
-To address this problem, we use a mechanism somewhat different than above: rather than lowering the off-cost, we raise the on-cost.
-The idea behind lowering the cost when covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but we do not want to encourage nodes that just happen to overlap with others; a penalty is a more appropriate mechanism.
-Let $oc(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to \termemph{turned-on} nodes which overlap with our target node $t$.
-We define an $d_1$ exponential term for the $C_1$ our target node $t$ as:
+For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both have high minLPR.
+To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of having turned-off nodes, we decrease the explainedness of the turned-on nodes, which serves to express confusion at having overlapping FS.
+The idea behind covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but for overlaps a penalty is a more appropriate mechanism.
+Let $oc(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to turned-on nodes which overlap with our target node $t$.
+We define $d_1$, the exponential term for the $E_1(t)$ as:
 
@@
 
-The effect of overlaps on the cost is hyperbolic: small amounts of overlapping has little effect, but with significant overlap the cost becomes prohibitive, effectively forcing one of nodes to turn off.
+The effect of overlaps on the explainedness is hyperbolic: small amounts of overlapping has little effect, but with significant overlap it becomes prohibitive, effectively forcing one of the nodes to turn off.
 
@@
 
-The dependence of the cost functions of nodes on their neighbors as discussed in the preceding section effectively prohibit a global optimization of the lattice.
+The dependence of the explainedness of nodes on their neighbors as discussed in the preceding section effectively prohibit a global optimization of the lattice.
 Fortunately, though a majority of nodes in the lattice are connected to each other though some path, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
@@
 Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
-Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose cost function is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.
+Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.
 
@@
 \item The complexity of the algorithm increases exponentially with the number of relevant nodes, so we limit the total number to 5.
-When there are more than 5 nodes turned on in the vicinity of the target node, relevant nodes are selected by ranking in terms of the influence of the nodes on each other as given by the relative change in their cost functions.
-\item The full set of pairwise $n$-gram overlaps in a large corpus is too big too effectively store, and so we exclude overlaps with a count of less than 5 from our lattice.
+When there are more than 5 nodes turned on in the vicinity of the target node, relevant nodes are selected by ranking in terms of the influence of the nodes on each other as given by the relative change in their explainedness functions.
+\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice.
 \item Many nodes have a minLPR which is a little larger than 1.
@@
 
-	Lattice \emph{-ovr} & 0.52& \bf{0.53} & 0.53 & & 0.33& \bf{0.60} & 0.43& & 0.35 & \bf{0.65} & 0.45 & & 0.69 & \bf{0.51} & \bf{0.59} \\
+	Lattice \emph{-ovr} & 0.52& \bf{0.51} & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.69 & \bf{0.51} & \bf{0.58} \\
 
-				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.41}& 0.56 & \bf{0.47} & &\bf{0.42} & 0.57 & \bf{0.48} & & \bf{0.86} & 0.39 & 0.54 \\ 
+				Lattice & \bf{0.67} & 0.43 & \bf{0.52} & & \bf{0.40}& 0.60 & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.87} & 0.39 & 0.53 \\ 
             \hline
@@
 			 \hline
-			LocalMaxs & \bf{0.58} & 0.14 & 0.23 \\
+			PMIrank & 0.20 & 0.29 & 0.23 \\
 			minLPRrank & 0.34 & 0.45 & 0.39 \\
 			LPR-seg & 0.42 & 0.45 & 0.43 \\
+			LocalMaxs & \bf{0.56} & 0.39 & 0.46 \\
 			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
-			Lattice & 0.46 & 0.61 & \bf{0.53} \\
+			Lattice & 0.47 & 0.63 & \bf{0.54} \\
        \hline
@@
 
-Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b}.
-For the BNC, we also compare, separately, the DP-seg model from Newman et \al \shortcite{Newman12}, and the LocalMaxs algorithm of Silva and Lopes \shortcite{Silva99}; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
-All these approaches have been compared against a wide range of association measures;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
+Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
+For the BNC, we also compare, separately, the DP-seg model from Newman et \al \shortcite{Newman12} with recommended settings, and the LocalMaxs algorithm of Silva and Lopes \shortcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
+All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
 Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $n-1$-gram, likelihood ratios must consider all combinations of all component $n-1,2,3\ldots$-grams, including, in our case, not only contiguous but also non-contiguous components.
@@
 The LPRseg method of Brooke et \al \shortcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
-Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical with in Croatian.
-The ICWSM corpus also has relatively high precision, whereas both the BNC and Croatian corpus have low precision and high recall.
+Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
+The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
 
-In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that the LocalMaxs algorithm did fairly poorly, whereas the DP-seg method of Newman \cite{Newman12} was also able to beat our baseline methods, but with regards to F-score, it was inferior to our Lattice method.
-Some of that difference seems attributable to a severe precision/recall imbalance, though it was one we unable to improve by changing the parameters of the model from recommended settings.
+In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method.
+Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.
 
@@
 Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM, or almost 14\% of all $n$-gram types.
-One idea for future work is to automatically adapt to the particular properties of the input language/corpus, though it might also be worth considering whether f-score is the most appropriate metric for evaluation, given that high precision seems particularly desirable in a lexical resource.
+One idea for future work is to automatically adapt to the particular properties of the input language/corpus in order to ensure a good balance between precision and recall.
 
-At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively low size: whereas the $n$-gram threshold we have used here results in a minimum counts of in the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times.
+At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in a minimum counts of in the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times.
 This might be resolved, of course, by increasing the $n$-gram threshold, or simply avoiding small corpora altogether, but it may be useful to focus effort on how to building comprehensive FS lexicons even in relatively low resource situations.
@@
 
-There is one another more general explanation for the precision/recall imbalances we see across the four corpora: Both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, in particularly newswire.
+There is one another more general explanation for the precision/recall imbalances we see across the four corpora: Both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, particularly news.
 The ICWSM and the Japanese corpus, on the other hand, are mostly blogs.
-Though all genres have FS, there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres.
-The fact that last than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
+Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres.
+The fact that last than 20\% of the FS derived from the BNC appears in the lexicon for the ICWSM is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
 

### 2017-01-19 tacl.tex
Edits to end of Section 2 + added \newcite

@@
 \maketitle
+
 \begin{abstract}
-
 We present a new model for acquiring unrestricted multiword lexicons from large corpora based on  competition among $n$-gram candidates.
 In contrast to the standard approach of simple ranking by association measure, in our model $n$-grams are arranged in a lattice structure based on subsumption and overlap relationships, with nodes inhibiting other nodes in their vicinity when they are selected as a lexical item.
-We show how the configuration of such a lattice can be optimized tractably, and our evaluation using annotations of sampled $n$-grams indicates that it is consistently outperforms alternatives by at least 0.05 f-score across several corpora and languages.
-
+We show how the configuration of such a lattice can be optimized tractably, and demonstrate using annotations of sampled $n$-grams that our method consistently outperforms alternatives by at least 0.05 F-score across several corpora and languages.
 \end{abstract}
@@
 
-Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers both produce and process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard unit for most research in modern NLP.
+Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers both produce and process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard processing unit for most research in modern NLP.
 The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work.
-We present a effective, expandable, and above all tractable new approach in comprehensive multiword lexicon acquisition that aims to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which fail to scale to the large corpora which are now the main sources of the distributional information which are central to lexical knowledge in modern NLP systems.
+We present a effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition that aims to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which fail to scale to the large corpora which are the main sources of the distributional information in modern NLP systems.
 
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
-Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FS that are shared by a recognizable language community.
-In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes most MWEs but also (apparently) compositional linguistic formulas.
-This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to even more confusion with respect to in its interpretation.
-Though in some contexts it has been used in way that is similar to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}}  and strong (non-compositional) MWEs.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
+Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FSs that are shared by a recognizable language community.
+
+In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes many MWEs but also (apparently) compositional linguistic formulas.
+This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to confusion with respect to its interpretation.
+Though in some contexts it has been used in a way that is similar to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}.}  and strong (non-compositional) MWEs.
 It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research.
 Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella.
-Another reason to consider a different terminology is that there are classes of what is typically considered MWE that don't fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}).
-Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.
-Barbara W.
-Smith} or \ex{Smith Garden Supplies Ltd}).
-\figref{fig:terminology} show the conception of the relationship between FS, MWE and (multiword) named entities that we assume for this paper.
+Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that don't fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}).
+Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
+\figref{fig:terminology} shows the conception of the relationship between FS, MWE and (multiword) named entities that we assume for this paper.
 
@@
 Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen.
-Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
+Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e.\ the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
 Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
-Similarly, the lexical predictability ratio (LPR) of Brooke et \al \cite{Brooke15b} is a association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability (as provided by part-of-speech information) from the overall conditional probability for each word given the other words in the phrase.
-Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily $n$-gram could be replaced by a single word \cite{Riedl15}.
+Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability (as provided by part-of-speech information) from the overall conditional probability for each word given the other words in the phrase.
+Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word \cite{Riedl15}.
 
 Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
-The algorithm of Silva and Lopes \shortcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
-Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on tradeoff between marginal and conditional statistics (\ie LPR).
-Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of Newman et \al \shortcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases.
-Gimpel and Smith \shortcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation.
+The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
+\newcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics (\ie LPR).
+Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of \newcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases.
+\newcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation.
 A general drawback to these generative methods, relative to approaching involving association metrics, is scalability and lack of determinacy.
@@
 Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb/noun combinations \cite{Fazly09}.
-The work of Schneider et \al \shortcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.
+The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.
 
-The motivation for building lexicons of formulaic sequences naturally overlaps of those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units (citation needed?????????), as can parsing \cite{Constant16}.
+The motivation for building lexicons of formulaic sequences naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
 One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses.
-Within corpus linguistics, multiword sequences have studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold: in order to get very reliable phrases, the threshold is typically set rather high (Biber et \al use 40 occurrences in 1 million words).
+Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold: in order to get very reliable phrases, the threshold is typically set rather high (Biber et \al use 40 occurrences in 1 million words).
 Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures).
-Lexical bundles have been applied, in particular, to learner language: for example, Chen and Baker \shortcite{Chen10} showed that non-native student writers use severely a restricted range of lexical bundle types, and tend to overuse those types, while Granger and Bestgen \shortcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.
-Sakaguchi et \al \shortcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; Brooke et \al \shortcite{Brooke15b} explcitly argues for FS lexicons as a way to identify, track, and improve learner proficiency.
+Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.
+\newcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explcitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.
 
@@
 The first step in the process is derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text.
-Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows Brooke et \al \shortcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is a $n$-gram frequency threshold, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of Schneider et \al \shortcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification.
+Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows \newcite{Brooke15b} up until the last stage.
+An initial requirement of any such method is a $n$-gram frequency threshold, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification.
 Note that our set of $n$-grams also include gapped or non-contiguous $n$-grams; the definition of gaps is language specific---we will discuss the gaps for individual languages further in \secref{sec:evaluation}---but the general idea (and this is confirmed by empirical analysis) is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence.
@@
 
-In the segmentation approach of Brooke et \al \shortcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (minLPR):
+In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (minLPR):
 
@@
 \end{displaymath}
-\noident
-
 And $E_1$ is the cost parameter $C$ taken to the negative power of an analogous function $d_1$:
@@
 \end{displaymath}
-\noident
-
 The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes.
@@
 For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, clear(t) will be 0.5.
-We can now define d_{0}(t) as:
+We can now define $d_{0}(t)$ as:
 
@@
 We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
-In English, we follow Brooke et \al \shortcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
-To facilitate a comparison with Newman et \al \shortcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
+In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
+To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
 Lemmatization included removing all inflectional marking from both words and POS tags.
-For English, we took the same POS regex used in Brooke et \al \shortcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.
+For English, we took the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.
 
@@
 
-Brooke et \al \shortcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
+\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
 We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: based on written guidelines derived from the definitions of Wray \cite{Wray08} and at least one practice round,three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
 
-Other than the inclusion of new languages, our test sets differ from Brooke et \al \shortcite{Brooke15b} in two ways.
+Other than the inclusion of new languages, our test sets differ from \newcite{Brooke15b} in two ways.
 First, instead of relying on strict majority annotation, we entirely excluded $n$-grams which just one annotator marked as FS.
@@
 
-Our primary comparison is with the heuristic LPR model from Brooke et \al \shortcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
-For the BNC, we also compare, separately, the DP-seg model from Newman et \al \shortcite{Newman12} with recommended settings, and the LocalMaxs algorithm of Silva and Lopes \shortcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
+Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
+For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
 All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
@@
 As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
-The LPRseg method of Brooke et \al \shortcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
+The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
 Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
@@
 Given our interest in methods which work well on large corpora, the speed of the model is worth mentioning.
-Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of Brooke et \al \shortcite{Brooke15a}, we found that the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary for to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
+Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15a}, we found that the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary for to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
 We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.

### 2017-01-20 tacl.tex
typos and removed unused texts

@@
 \def \etc {etc.\@ }
-
-%\eaclfinalcopy % Uncomment this line for the final submission
-%\def\eaclpaperid{***} %  Enter the acl Paper ID here
-
-%\setlength\titlebox{5cm}
-% You can expand the titlebox if you need extra space
-% to show all the authors. Please do not make the titlebox
-% smaller than 5cm (the original size); we will check this
-% in the camera-ready version and ask you to change it back.
 
@@
 
-%We use the term \termdef{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS. 
-% TJB: I'd suggest staying away from talking about collocations altogether: it's an overloaded term; many MWEs are *not* collocations under this definition; and it's not needed for this paper
-%MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs).
-In this regard, we disagree with the MWE annotation schema of \newcite{Schneider14a} which includes any NE as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \ex{Tintman Nationwide Tints Ltd} or \ex{Hickory Furniture Mart} which are easily identifiable as NEs based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers.% (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names).
-% TJB: too subtle/controversial a point for this paper
-%The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition.
-Some well-known named entities are obviously good MWEs (\eg \ex{George Washington}, \ex{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.
-
 Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen.
@@
 
-%Unlikely with true MWEs there is no other single necessary condition for some collection of words to be a formulaic sequence, but there are many indicators: Wray \shortcite{Wray08} lists 11 diagnostic criteria, including exact repetition, a lack of semantic transparency, genre associations, pragmatic effects, non-standard syntax, statistical irregularity, and phonological properties.
-We also want to distinguish FS from collocations, which are
-
-%Wray's conception of formulaic language is explicitly not that of mere exception to the combinatorial creativity of syntax and semantics; she argues that most language can be viewed to some degree as formulaic, and that the use of formulaic sequences is the default mode for most genres, both written and oral.
-Moreover, her view is that the processing of language in general should be viewed not so much as a bottom-up construction of larger phrases from individual lexical units, but rather as a top-down process where larger chunks are split apart and analyzed as discrete parts only when there is clear evidence for flexibility, a strategy that has a direct analogy in the decomposition approach used here.
-Another important aspect of the theory is a focus on the linear sequence rather than some other kind of syntactic abstraction (\eg a dependency relationship) as being primary to the internal representation of multiword phenomena, a perspective which allows for much cleaner analysis of longer and more varied expressions: when cases of sequence-internal flexibility occur, they are handled by the inclusion of a slot or gap which is also part of the sequence.
-Note that, since humans are fairly skilled at interpreting noisy input of various kinds, the notion of sequence as the default glue of the internal multiword lexicon does not rule out the possibility of greater creativity (\eg reversing word order), but this should be understood as the speaker abandoning one of the benefits of formulaic sequences (easy processing) for other communicative purposes (\eg humor).
-
-%Second language acquisition is one of the major areas of application for work on formulaic sequences \cite{Ellis08}.
-Wray \shortcite{Wray08} posits that the difficulty many adult second language learners have reaching fluency reflects, at least in part, an inattention to the role of formulaic sequences, coupled with an expectation that a language should allow for free combination of words governed only by the basic rules of syntax.
-Modern communicative approaches to teaching tend to encourage learners to express themselves freely so long as they are able to make themselves understood, \ie to satisfy the short-term communicative goal.
-However, if full fluency and social integration into the culture of native speakers is a long-term goal, as it is for many immigrant learners for instance, these learners also need to correctly process and eventually produce a wide range of formulaic sequences.
-Creating high-coverage vocabularies based on real, modern language usage is a first step in helping learners with these challenging but ubiquitous units of language.
-
 \section{Method}
@@
 The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary which best explain the statistics extracted from the corpus.
-
-%The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus.
-Our method for FS extraction assumes such a initial set of $n$-grams, and focuses on identifying the true FS, and excluding those sequences which can be explained away due to the syntax of the language and/or the existence of other FS.
-The former can be captured to some extent using a syntax-sensitive association measure like LPR, but the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary.
 
@@
 
-% Some sample minLPR values are given in Table XXXXX (???).
-
 \subsection{Node explainedness functions}
 
-The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of minimizing the overall explanatory power of the lattice.
+The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of maximizing the overall explanatory power of the lattice.
 Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained.
@@
 There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.
-
-%Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count.
 
@@
 They are also restricted to always being positive.
-
-%LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words.
-As such, it is common for more complex association measures to include multiplication by the count, or logarithm of the count.
-In the context of this model, multiplying our cost by even the logarithm of the count would be far too extreme, but we can give apply a more restricted increase to $C_0$, forcing the model to give more weight to relatively common expressions, as follows: Let $c(\dot)$ be the count function, and $c(min)$ and $c(max)$ refer to the lowest and highest count $n$-gram in the lattice (not including unigrams).
-
-%\begin{displaymath}
-%d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
-%\end{displaymath}
-
-%This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.
 
@@
 In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.
-
-%Another source of error are somewhat flexible FS which fall below our $n$-gram threshold but where some portion of the FS is above the threshold: to address this, we collect additional statistics and remove as a post-processing step any FS which are hard covered by an $n$-gram not in our lattice.
 
@@
 The order that we do this has an effect on the result: among the obvious options, good results are obtained when ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
-
-%The algorithm for optimization procedure is given in Figure X (???).
 
@@
 
-% For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.
-
-%In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.
-
 Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
@@
 
-%Otherwise, gaps in MWEs have generally addressed by using full syntactic representations \cite{Seretan11}.
-%One more restriction is necessary to make the use of overlaps feasible: without any restrictions, the number of connections resulting from overlaps is too large.
-We resolved this problem by excluding as possible active nodes.
-
-%a separate analysis of the that corpus showed the contents of most gapped FS in English were simple nouns or some portion thereof; this is somewhat less true for the more free word-order langauges we are also considering, but still a usuable heuristic.
-
-%which be described by the following (Penn Treebank) POS regular expression:
-
-%\vspace{3mm}
-%\noindent
-% PP$\,$|$\,$[(PDT)(DT)JJ*[NN$\,$|$\,$NP]*(POS$\,$|$\,$PP\$)JJ*NN*]
-%\vspace{1mm}
-
-%(Our POS tags are given by the TreeTagger)
-
-% For our main evaluation in English, our corpus is a 890 million version of the tier 1 texts in the ICWSM 2009 blog corpus \cite{ICWSM} which has been filtered to remove duplicates and near duplicates.
 \bibliography{mybib}

### 2017-01-22 tacl.tex
Added blurb for Japanese, plus other minor fixes

@@
 
-Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech combinations, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
+Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
 Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases; the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS.
-The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary which best explain the statistics extracted from the corpus.
+The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence compete with each other to form a compact, parsimonious formulaic vocabulary which best explains the statistics extracted from the corpus.
 
@@
 The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes.
-Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and explainedness will be calculated differently depending on their status.
-Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $n+1$-grams which subsume them and $n-1$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
+Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and explainedness will be calculated differently depending on this status.
+Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance, be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
 These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
@@
 Formally, the LPR for some word $w_i$ in the context of a sequence of words of length $n$ which have a corresponding set of sequence of POS tags $t$, is given by:
-
 \begin{displaymath}
@@
 In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (minLPR):
-
 \begin{displaymath}
@@
 Let's define $E_0$, then, as the minLPR based taken to the negative power of some as yet undefined function $d_0$:
-
 \begin{displaymath}
@@
 \end{displaymath}
-And $E_1$ is the cost parameter $C$ taken to the negative power of an analogous function $d_1$:
-
+and $E_1$ is the cost parameter $C$ taken to the negative power of an analogous function $d_1$:
 \begin{displaymath}
@@
 Then, then the $d_0$ for a covered node $t$ is:
-
 \begin{displaymath}
-cover(t) = max(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)})
+cover(t) = \max(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)})
 \end{displaymath}
@@
 Generalized to consider the (rare) case of multiple clearing nodes, we define clear(t) as:
-
 %in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
-
 \begin{displaymath}
@@
 We can now define $d_{0}(t)$ as:
-
 \begin{displaymath}
@@
 We define $d_1$, the exponential term for the $E_1(t)$ as:
-
 \begin{displaymath}
@@
 ....
-For Japanese we used a portion of the X corpus of roughly the same size (by token) as the ICWSM.
-The POS regex for Japanese...
+For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008} which was roughly the same size (in terms of token count) as the English corpus.
+We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}, and performed noun chunking based on a simple regex over the POS output.
+% TJB: worth including the respective POS regexes in an appendix?
 

### 2017-01-23 tacl.tex
Comments to end of Section 3.2

@@
 \newcommand{\termemph}[1]{\textit{#1}\xspace}
+
+\newcommand{\LPR}{\ensuremath{\text{LPR}}}
+\newcommand{\minLPR}{\ensuremath{\text{minLPR}}}
 
@@
 
-Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
+Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech (``POS'') combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
 Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases; the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS.
@@
 
-The first step in the process is derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text.
-Since our primary association measure is an adaption of LPR, our approach in this subsection mostly follows \newcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is a $n$-gram frequency threshold, which for us (like Brooke et \al 2015) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification.
-Note that our set of $n$-grams also include gapped or non-contiguous $n$-grams; the definition of gaps is language specific---we will discuss the gaps for individual languages further in \secref{sec:evaluation}---but the general idea (and this is confirmed by empirical analysis) is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence.
-In a part-of-speech tagged corpus, potential gaps can be identified by a part-of-speech regular expression.
-Putting in such a restriction is useful because it greatly lowers the number of gapped $n$-gram types, increasing precision and improving speed.
-Another way the number of types are lowered is by excluding punctuation and by lemmatizing.
+The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text.
+Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage.
+An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification.
+% TJB: is this a subset of proper names? the "excepting ..." qualification is a bit vague
+Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams.
+The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
+% TJB: added citation and removed "this is confirmed by empirical analysis" as it begs details of the specific analysis, which I think is more of a distraction than anything else at this point
+ In a POS-tagged corpus, potential gaps can be identified by a POS regular expression.
+This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall.
+We also exclude punctuation and lemmatize the corpus.
 Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination.
+% TJB: this last sentence is a bit opaque
 
-Once a set of relevant $n$-grams is identified (and counted), other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected.
-LPR measures how predictable a word is in a lexical context as compared to how predictable it is given only syntactic context (over the same span of words).
-Formally, the LPR for some word $w_i$ in the context of a sequence of words of length $n$ which have a corresponding set of sequence of POS tags $t$, is given by:
+Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected.
+LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
+Formally, the LPR for word $w_i$ in the context of a word sequence $w_0, w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
 \begin{displaymath}
-LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
+\LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
 \end{displaymath}
+% TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
 
-These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts.
-We can use the same equation for gap $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics, not regular $n$-gram statistics.
-Note that identification of the best ratio across all possible choices of context, not just the largest ,is important for longer FS, where the entire POS context alone might uniquely identify the phrase (and hence the word), resulting in a ratio of 1.
-It also ensures that the lower bound of LPR is 1, since the ratio for a word with no context at all is trivially 1.
+%These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts. 
+% TJB: removed; seems to state the obvious
+We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics.
+Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase (and hence the word), resulting in a ratio of 1.
+% TJB: is this a good thing or bad thing? slight lack of clarity here
+It also ensures that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1.
 
-In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (minLPR):
+In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (``\minLPR''):
 \begin{displaymath}
-minLPR(w_{0,n}) = \min_{0 \leq i < n }{LPR(w_i,w_{0,n})}
+\minLPR(w_{0,n}) = \min_{0 \leq i < n }{\LPR(w_i,w_{0,n})}
 \end{displaymath}
-
-The use of minimum here should be understood in the context of competition between nodes in the lattice: minLPR for a particular $n$-gram does not reflect the \emph{overall}
-degree to which an $n$-gram holds together, instead it focuses on the word which is its weakest link.
-For example, in the case we are evaluating the quality of \ex{be keep \gap under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \ex{keep} and \ex{under}, but the minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
+The use of minimum here should be understood in the context of competition between nodes in the lattice: minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which an $n$-gram holds together, instead it focuses on the word which is its weakest link.
+For example, in the case we are evaluating the quality of \ex{be keep \gap under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
 
@@
 Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained.
-It will be useful to define the explainedness of a node in terms of two functions: the rationale for having two functions is that the on/off status of a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence.
-When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
-Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it off.
-The base value of $E_{0}$ is the inverse of the minLPR metric discussed above: when the minLPR metric is 1, corresponding to a case when the syntactic content predicts one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1.
-The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS.
-There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.
+We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence; when a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
+Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it is off.
+The base value of $E_{0}$ is the inverse of minLPR: when the minLPR metric is 1, corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1.
+The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
+There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
 
-We will influence these functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
-Let's define $E_0$, then, as the minLPR based taken to the negative power of some as yet undefined function $d_0$:
+We weight these functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
+We define $E_0$, then, as minLPR to the negative power of some as yet undefined non-negative function $d_0$:
 \begin{displaymath}
-E_0(t) = minLPR(t)^{-d_0(t)}
+E_0(t) = \minLPR(t)^{-d_0(t)}
 \end{displaymath}
-and $E_1$ is the cost parameter $C$ taken to the negative power of an analogous function $d_1$:
+and $E_1$ is the cost parameter $C$ to the negative power of an analogous non-negative function $d_1$:
 \begin{displaymath}
@@
 \end{displaymath}
-The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not being influenced by other nodes.
-They are also restricted to always being positive.
+The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not influenced by other nodes.
 
@@
 \begin{displaymath}
-clear(t) = \prod_{i=1}^{m}{ min(1,\frac{minLPR(t)}{minLPR(u_i)})}
+clear(t) = \prod_{i=1}^{m}{ min(1,\frac{\minLPR(t)}{\minLPR(u_i)})}
 \end{displaymath}

### 2017-01-23 tacl.tex
Edits to end of Section 3

@@
 \newcommand{\minLPR}{\ensuremath{\text{minLPR}}}
+\newcommand{\cover}{\ensuremath{\text{cover}}\xspace}
+\newcommand{\clear}{\ensuremath{\text{clear}}\xspace}
 
@@
 \end{displaymath}
-The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice, but are both 1 when a node is not influenced by other nodes.
+The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.
 
@@
 Our model includes two types of covering: hard and soft.
-\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
-We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers, (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
-This is done as a preprocessing step, and so it greatly improves the tractability of the iterative optimization of the lattice.
+\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
+We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
+This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice.
 Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.
@@
 This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\dot)$ be the count function,and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
-Then, then the $d_0$ for a covered node $t$ is:
+Then, the $\cover(t)$ score for a covered node $t$ is:
 \begin{displaymath}
-cover(t) = \max(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)})
+\cover(t) = \max(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)})
 \end{displaymath}
-
-\noindent
 This equation is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
@@
 The basic mechanism is similar to covering, except that counts cannot be made use of in the same way; whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
+
 A simple but effective solution which avoids introducing parameters makes use of the minLPR values of the relevant nodes.
 In the most common (two node) situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher, which greatly restricts its effect.
-Generalized to consider the (rare) case of multiple clearing nodes, we define clear(t) as:
+Generalized to consider the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
 %in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
 \begin{displaymath}
-clear(t) = \prod_{i=1}^{m}{ min(1,\frac{\minLPR(t)}{\minLPR(u_i)})}
+\clear(t) = \prod_{i=1}^{m}{\min(1,\frac{\minLPR(t)}{\minLPR(u_i)})}
 \end{displaymath}
@@
 We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
-For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, clear(t) will be 0.5.
+For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.
+
 We can now define $d_{0}(t)$ as:
 \begin{displaymath}
-d_0(t) = cover(t) \cdot clear(t)
+d_0(t) = \cover(t) \cdot \clear(t)
 \end{displaymath}
-
 Note that the effect of both covering and clearing is to  increase explainedness for covered/cleared nodes, which indirectly encourages the model to turn an $n$-gram like \ex{keep \gap under wraps} on in order to explain nodes in its vicinity, even supposing its minLPR were relatively low.
@@
 The third mechanism of node interaction involves $n$-grams which overlap in the corpus.
-Though there are some exceptions, it is generally the case that independent formulaic sequences do not overlap.
+Though there are exceptions, it is generally the case that independent formulaic sequences do not overlap.
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both have high minLPR.
@@
 Let $oc(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to turned-on nodes which overlap with our target node $t$.
-We define $d_1$, the exponential term for the $E_1(t)$ as:
+We define $d_1(t)$, the exponential term for the $E_1(t)$, as:
 \begin{displaymath}
@@
 
-The effect of overlaps on the explainedness is hyperbolic: small amounts of overlapping has little effect, but with significant overlap it becomes prohibitive, effectively forcing one of the nodes to turn off.
+The effect of overlaps on the explainedness is hyperbolic: small amounts of overlap have little effect, but with significant overlap it becomes prohibitive, effectively forcing one of the nodes to turn off.
 
@@
 
-The dependence of the explainedness of nodes on their neighbors as discussed in the preceding section effectively prohibit a global optimization of the lattice.
+The dependence of the explainedness of nodes on their neighbors as discussed in the preceding section effectively prohibits a global optimization of the lattice.
 Fortunately, though a majority of nodes in the lattice are connected to each other though some path, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
@@
 For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice.
-The order that we do this has an effect on the result: among the obvious options, good results are obtained when ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
+The order that we perform this has an effect on the result: among the obvious options, good results are obtained when ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
 
-Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node; If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
-Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to status of the node under consideration whose status should be considered simultaneously.
-Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
+Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node.
+If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
+Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to the status of the node under consideration whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
 Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.
+% TJB: greedy how (in terms of ordering of nodes)? frequency based as per above?
 
-In practice, we apply the following restrictions which significantly reduce the runtime of the algorithm without sacrificing the quality of the output lexicon (based on development set testing):
-
+In practice, we apply the following restrictions, which significantly reduce the runtime of the algorithm without sacrificing the quality of the output lexicon (based on development set testing):
 \begin{itemize}
@@
 When there are more than 5 nodes turned on in the vicinity of the target node, relevant nodes are selected by ranking in terms of the influence of the nodes on each other as given by the relative change in their explainedness functions.
+% TJB: say more -- relative change how?
 \item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice.
 \item Many nodes have a minLPR which is a little larger than 1.
-There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering we do not consider activating nodes with a minLPR of less than 2.
+There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with a minLPR of less than 2.
 \end{itemize}

### 2017-01-24 tacl.tex
Responded to Tim's section 3 comments

@@
 Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}), excepting those highly particular proper names which we consider outside the scope of FS identification.
+An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) when proper names which we consider outside the scope of FS identification (as discussed earlier) are excluded.
 % TJB: is this a subset of proper names? the "excepting ..." qualification is a bit vague
@@
 We also exclude punctuation and lemmatize the corpus.
-Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination.
+Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $i+1$-grams which are also over the threshold.
 % TJB: this last sentence is a bit opaque
@@
 LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
-Formally, the LPR for word $w_i$ in the context of a word sequence $w_0, w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
+Formally, the LPR for word $w_i$ in the context of a word sequence $w_0,..., w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
 \begin{displaymath}
@@
 \end{displaymath}
+
+\noindent
+where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively. 
 % TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
@@
 We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics.
-Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase (and hence the word), resulting in a ratio of 1.
+Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
 % TJB: is this a good thing or bad thing? slight lack of clarity here
@@
 Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to the status of the node under consideration whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
-Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes starting from an `all-on' state.
+Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.
 % TJB: greedy how (in terms of ordering of nodes)? frequency based as per above?
 
-In practice, we apply the following restrictions, which significantly reduce the runtime of the algorithm without sacrificing the quality of the output lexicon (based on development set testing):
+In practice, we apply the following restrictions, which significantly reduce the runtime without sacrificing the quality of the output lexicon (based on development set testing):
 \begin{itemize}
-\item The complexity of the algorithm increases exponentially with the number of relevant nodes, so we limit the total number to 5.
-When there are more than 5 nodes turned on in the vicinity of the target node, relevant nodes are selected by ranking in terms of the influence of the nodes on each other as given by the relative change in their explainedness functions.
+\item We limit the total number of relevant nodes to 5.
+When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation.
 % TJB: say more -- relative change how?
@@
 Though the results across the four corpora are reasonably similar with respect to overall f-score, there are a significant discrepancies.
-By using the UniDict morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
+By using the UNIDIC morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
 The result is that there are many more FS for Japanese.

### 2017-01-25 tacl.tex
Edits to end

@@
 \usepackage{xspace}
+\usepackage{paralist}
 \usepackage[pdftex]{graphicx}
@@
 Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) when proper names which we consider outside the scope of FS identification (as discussed earlier) are excluded.
-% TJB: is this a subset of proper names? the "excepting ..." qualification is a bit vague
+An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.
 Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams.
 The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
-% TJB: added citation and removed "this is confirmed by empirical analysis" as it begs details of the specific analysis, which I think is more of a distraction than anything else at this point
  In a POS-tagged corpus, potential gaps can be identified by a POS regular expression.
@@
 We also exclude punctuation and lemmatize the corpus.
-Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $i+1$-grams which are also over the threshold.
-% TJB: this last sentence is a bit opaque
+Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $(i+1)$-grams which are also over the threshold.
 
@@
 \end{displaymath}
-
-\noindent
 where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively.
-% TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
 
@@
 Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.
-% TJB: greedy how (in terms of ordering of nodes)? frequency based as per above?
 
 In practice, we apply the following restrictions, which significantly reduce the runtime without sacrificing the quality of the output lexicon (based on development set testing):
-\begin{itemize}
+\begin{compactitem}
 \item We limit the total number of relevant nodes to 5.
 When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation.
-% TJB: say more -- relative change how?
 \item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice.
@@
 There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with a minLPR of less than 2.
-\end{itemize}
+\end{compactitem}
 
@@
 
-\section{Evaluation} \label{sec:evaluation}
+\section{Evaluation} 
+\label{sec:evaluation}
 
@@
 In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
-To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
+To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM corpus, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
 Lemmatization included removing all inflectional marking from both words and POS tags.
@@
 The other two languages we include in our evaluation are Croatian and Japanese.
-Relative to English, both languages are free-word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS extraction in such languages.
+Both these languages are relatively free-word order, providing valuable test cases of the challenges associated with using an $n$-gram approach to FS extraction in such languages.
 For Croatian, we used the X corpus, a collection of X.
@@
 
-\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
-We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: based on written guidelines derived from the definitions of Wray \cite{Wray08} and at least one practice round,three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
+\newcite{Brooke15b} introduced a method for evaluating FS extraction without a reference lexicon or direct annotation of the output of a model.
+Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
+We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above.
+Based on written guidelines derived from the definitions of \newcite{Wray08} and at least one practice round, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
 
@@
 The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
-Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
+Generally, clearing and overlap node interactions offer a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
 The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
 
-In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method.
-Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.
+In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
+Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the F-score by changing the parameters from recommended settings for either model.
 
@@
 
-Though the results across the four corpora are reasonably similar with respect to overall f-score, there are a significant discrepancies.
+Though the results across the four corpora are reasonably similar with respect to overall F-score, there are significant discrepancies.
 By using the UNIDIC morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
@@
 Precision is very high, and recall is relatively low.
-Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to f-score, which explains why the full model is not the best in that one case.
-Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM, or almost 14\% of all $n$-gram types.
+Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to F-score, which explains why the full model is not the best in that one case.
+Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM corpus, or almost 14\% of all $n$-gram types.
 One idea for future work is to automatically adapt to the particular properties of the input language/corpus in order to ensure a good balance between precision and recall.
 
-At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in a minimum counts of in the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times.
+At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times.
 This might be resolved, of course, by increasing the $n$-gram threshold, or simply avoiding small corpora altogether, but it may be useful to focus effort on how to building comprehensive FS lexicons even in relatively low resource situations.
-One idea we are actively pursing is modifying the calculation of the LPR metric to integrating uncertainty due to low counts.
+One idea we are actively pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.
 
-There is one another more general explanation for the precision/recall imbalances we see across the four corpora: Both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, particularly news.
-The ICWSM and the Japanese corpus, on the other hand, are mostly blogs.
+There is one other more general explanation for the precision/recall imbalances we see across the four corpora: both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, particularly news.
+The ICWSM corpus and the Japanese corpus, on the other hand, are mostly blogs and web pages.
 Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres.
-The fact that last than 20\% of the FS derived from the BNC appears in the lexicon for the ICWSM is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
+The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
 
-We were interested in addressing Croatian and Japanese in part because of their tendency towards relatively free word order, and whether allowing gaps in our FS would help with these languages.
+We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether allowing gaps in our FS would help with these languages.
 We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS rather than less.
@@
 Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.
+% TJB: would be good to have some examples of gapped expressions to better make this point (yes, space permitting)
 
@@
 This option actually requires very little change to the structure of the model presented here, since all the basic relationships in the lattice as well as the minLPR measure could be straightforwardly defined in terms of subgraphs instead of strings.
-One clear negative is the need for a dependency parser for the language and domain of interest, and that there is then no potential for using of FS to improve parsing.
-A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for gaps in order to represent a full range of FS: there are gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \ie \ex{no amount of * can}.
+One clear negative is the need for a dependency parser for the language and domain of interest, and that there is then no potential for using FS to improve parsing.
+A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for gaps in order to represent a full range of FS: there are gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \eg \ex{no amount of \gap can}.
 
 As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations.
-One of the major benefits of this model as compared to alternatives is the relative ease at which additional kinds of interactions between nodes could be implemented.
-Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, for instance, learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
+One of the major benefits of this model as compared to alternatives is the relative ease with which additional kinds of interactions between nodes could be implemented.
+Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, \eg, learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaiticity.
+Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaticity.
 
 Given our interest in methods which work well on large corpora, the speed of the model is worth mentioning.
-Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15a}, we found that the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary for to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
-We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.
+Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15a}, but the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
+We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at a majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.
 
-Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, the fact that precision and recall are both dependent on the number of positive examples means that f-scores become unreliable when there are very few positive examples.
-To do a independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling.
-Rather than brute force annotation, one option we could consider is a adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without significantly biasing the evaluation.
+Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, the fact that precision and recall are both dependent on the number of positive examples means that F-scores become unreliable when there are very few positive examples.
+To do an independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling.
+Rather than brute force annotation, one option we could consider is adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without significantly biasing the evaluation.
 
@@
 Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
-A tool which implements the method as well as the acquired lexicons and test sets are available here.\footnote{removed for anonymity}
+A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{removed for anonymity}
 

### 2017-01-27 tacl.tex
First round of Jan stuff

--- 2017-01-24 tacl.tex
@@
 \begin{abstract}
-We present a new model for acquiring unrestricted multiword lexicons from large corpora based on  competition among $n$-gram candidates.
+We present a new model for acquiring comprehensive multiword lexicons from large corpora based on  competition among $n$-gram candidates.
 In contrast to the standard approach of simple ranking by association measure, in our model $n$-grams are arranged in a lattice structure based on subsumption and overlap relationships, with nodes inhibiting other nodes in their vicinity when they are selected as a lexical item.
@@
 Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
-The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
+The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
 \newcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics (\ie LPR).
@@
 We also exclude punctuation and lemmatize the corpus.
-Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $i+1$-grams which are also over the threshold.
+Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $i-1$ words of overlap are found, which derives a set of $i+1$-grams which necessarily includes all those over the frequency threshold.
 % TJB: this last sentence is a bit opaque
@@
 LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
-Formally, the LPR for word $w_i$ in the context of a word sequence $w_0,..., w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
+Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
 \begin{displaymath}
-\LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
+\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
 \end{displaymath}
@@
 \noindent
-where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively. 
+where $w_{j,k}$ as predictive context should be understood as not containing $w_{i}$ (similarly for $t_{j,k}$). 
 % TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
@@
 \begin{displaymath}
-\minLPR(w_{0,n}) = \min_{0 \leq i < n }{\LPR(w_i,w_{0,n})}
+\minLPR(w_{1,n}) = \min_{1 \leq i \leq n }{\LPR(w_i,w_{1,n})}
 \end{displaymath}
@@
 The dependence of the explainedness of nodes on their neighbors as discussed in the preceding section effectively prohibits a global optimization of the lattice.
-Fortunately, though a majority of nodes in the lattice are connected to each other though some path, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
+Fortunately, though most of the nodes in the lattice are part of a single main connected component, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
 The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration).
@@
 Lemmatization included removing all inflectional marking from both words and POS tags.
-For English, we took the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.
+For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4 words.
 
@@
 Relative to English, both languages are free-word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS extraction in such languages.
-For Croatian, we used the X corpus, a collection of X.
-The POS regex for Croatian included XXX.
-....
+For Croatian, we used the fhrWaC corpus \cite{snajder2013building}, a filtered version of the Croatian web corpus hrWaC \newcite{ljubesic2014bs}, which is POS-tagged and lemmatized using the tools of \newcite{agic2013lemmatization}.
+Similar to English, the POS regex for Croatian includes simple nouns, adjectives and pronouns, but also other elements that regularly appear inside FS, including both adverbs and copulas.
 For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008} which was roughly the same size (in terms of token count) as the English corpus.
-We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}, and performed noun chunking based on a simple regex over the POS output.
+We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}.
+The POS regex for Japanese covers the same basic nominal structures as English, but also includes case markers and adverbials which intervene between noun and verbs.
+Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) which are removed by lemmatization in Croatian are segmented into independent mophological units in the MeCab output, making the task somewhat different for the two languages.
+
 % TJB: worth including the respective POS regexes in an appendix?
@@
 \newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
-We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: based on written guidelines derived from the definitions of Wray \cite{Wray08} and at least one practice round,three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
+We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of Wray \cite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
 
@@
  \begin{center}
-  \caption{ Results of formulaic sequence identification in sequential BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
+  \caption{ Results of formulaic sequence identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
 	\label{tab:BNC}
@@
 For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
-All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
+All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of general MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
 Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $n-1$-gram, likelihood ratios must consider all combinations of all component $n-1,2,3\ldots$-grams, including, in our case, not only contiguous but also non-contiguous components.
-The corresponding exponential increase in complexity renders it and other such methods impractical for unrestricted FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+The corresponding exponential increase in complexity renders it and other such methods impractical for comprehensive FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
 For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
@@
 The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
-As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
+As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with syntactically-unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
 The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
@@
 
-In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method.
+In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method.
 Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.
@@
 
-We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice.
+We have presented here a new methodology for acquiring comprehensive multiword lexicons from large corpora, using competition in an $n$-gram lattice.
 Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.

### 2017-01-29 tacl.tex
Some typos/typography fixed

--- 2017-01-25 tacl.tex
@@
 
-Our model involves competition among a large set of contiguous and non-contiguous $n$-gram types---connected to each other based on subsumption and overlap relations in a lattice-shaped graph---to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical (and not syntactic) affinity.
-We test our model across 4 large corpora in 3 languages, including 2 relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms recently proposed alternatives, offering both scalability and many avenues for future enhancement.
+A central challenge in building comprehensive multiword lexicons is pairing down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language.
+In particular, a model should attempt to minimize redundancy among the final entries in its lexicon.
+The lattice model proposed here accomplishes this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity.
+We test our approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering both scalability and many avenues for future enhancement.
 
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02} and \newcite{Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
 Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FSs that are shared by a recognizable language community.
@@
 It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers would defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella.
-Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that don't fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}).
+Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella.
+Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}).
 Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
-\figref{fig:terminology} shows the conception of the relationship between FS, MWE and (multiword) named entities that we assume for this paper.
+\figref{fig:terminology} shows the conception of the relationship between FS, MWE, and (multiword) named entities that we assume for this paper.
 
@@
 Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen.
-Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e.\ the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
+Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
 Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
@@
 
-Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb/noun combinations \cite{Fazly09}.
+Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb-noun combinations \cite{Fazly09}.
 The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.
@@
 Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.
-\newcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explcitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.
+\newcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.
 
@@
 Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech (``POS'') combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
-Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases; the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS.
+Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases -- the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS.
 The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence compete with each other to form a compact, parsimonious formulaic vocabulary which best explains the statistics extracted from the corpus.
@@
 Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance, be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
-These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg, if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
+These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
 A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
@@
 The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
+% TJB: added citation and removed "this is confirmed by empirical analysis" as it begs details of the specific analysis, which I think is more of a distraction than anything else at this point
 In a POS-tagged corpus, potential gaps can be identified by a POS regular expression.
@@
 We also exclude punctuation and lemmatize the corpus.
+Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.
+% TJB: this last sentence is a bit opaque
+%=======
+% In a POS-tagged corpus, potential gaps can be identified by a POS regular expression.
+This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall.
+We also exclude punctuation and lemmatize the corpus.
 Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $(i+1)$-grams which are also over the threshold.
+%>>>>>>> origin/master
 
@@
 LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
-Formally, the LPR for word $w_i$ in the context of a word sequence $w_0,..., w_i, ..., w_{n-1}$ with POS tag sequence $t_0, t_1, ..., t_{n-1}$, is given by:
+Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
 \begin{displaymath}
-\LPR(w_i,w_{0,n}) = \max_{0 \leq j < k < n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
+\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
 \end{displaymath}
-where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively.
+%<<<<<<< HEAD
+%
+\noindent
+where $w_{j,k}$ as predictive context should be understood as not containing $w_{i}$ (similarly for $t_{j,k}$). 
+% TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
+%=======
+%where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively. 
+%>>>>>>> origin/master
 
@@
 Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained.
-We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence; when a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
+We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on.
+When a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence.
+When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
 Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it is off.
@@
 For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that corresponds to occurrences of \ex{keep \gap under wraps}.
-This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\dot)$ be the count function,and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
+This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
 Then, the $\cover(t)$ score for a covered node $t$ is:
 \begin{displaymath}
-\cover(t) = \max(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)})
+\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}\Big)
 \end{displaymath}
@@
 \termdef{Clearing} does this by changing the $E_0$ of nodes higher in the lattice when a lower node is turned-on.
-The basic mechanism is similar to covering, except that counts cannot be made use of in the same way; whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
+The basic mechanism is similar to covering, except that counts cannot be made use of in the same way -- whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
 
@@
 \begin{displaymath}
-\clear(t) = \prod_{i=1}^{m}{\min(1,\frac{\minLPR(t)}{\minLPR(u_i)})}
+\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
 \end{displaymath}
@@
 The idea behind covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but for overlaps a penalty is a more appropriate mechanism.
-Let $oc(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1\dotts o_m$ refer to turned-on nodes which overlap with our target node $t$.
+Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$.
 We define $d_1(t)$, the exponential term for the $E_1(t)$, as:
 \begin{displaymath}
-d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{oc(o_i)}}
+	d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(o_i)}}
 \end{displaymath}
@@
 \item We limit the total number of relevant nodes to 5.
-When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation.
-\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice.
+When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation;
+\item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice;
 \item Many nodes have a minLPR which is a little larger than 1.
@@
 
-\section{Evaluation} 
-\label{sec:evaluation}
-
 We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
 In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
-To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM corpus, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
+To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
 Lemmatization included removing all inflectional marking from both words and POS tags.
-For English, we took the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4.
+For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4 words.
 
 The other two languages we include in our evaluation are Croatian and Japanese.
-Both these languages are relatively free-word order, providing valuable test cases of the challenges associated with using an $n$-gram approach to FS extraction in such languages.
-For Croatian, we used the X corpus, a collection of X.
-The POS regex for Croatian included XXX.
-....
+Relative to English, both languages are free-word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS extraction in such languages.
+For Croatian, we used the fhrWaC corpus \cite{snajder2013building}, a filtered version of the Croatian web corpus hrWaC \cite{ljubesic2014bs}, which is POS-tagged and lemmatized using the tools of \newcite{agic2013lemmatization}.
+Similar to English, the POS regex for Croatian includes simple nouns, adjectives and pronouns, but also other elements that regularly appear inside FS, including both adverbs and copulas.
 For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008} which was roughly the same size (in terms of token count) as the English corpus.
-We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}, and performed noun chunking based on a simple regex over the POS output.
+We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}.
+The POS regex for Japanese covers the same basic nominal structures as English, but also includes case markers and adverbials which intervene between noun and verbs.
+Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) which are removed by lemmatization in Croatian are segmented into independent mophological units in the MeCab output, making the task somewhat different for the two languages.
+
 % TJB: worth including the respective POS regexes in an appendix?
 
-\newcite{Brooke15b} introduced a method for evaluating FS extraction without a reference lexicon or direct annotation of the output of a model.
-Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
-We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above.
-Based on written guidelines derived from the definitions of \newcite{Wray08} and at least one practice round, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
+\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
+We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
 
@@
 For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
-All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of unrestricted MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
-Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $n-1$-gram, likelihood ratios must consider all combinations of all component $n-1,2,3\ldots$-grams, including, in our case, not only contiguous but also non-contiguous components.
-The corresponding exponential increase in complexity renders it and other such methods impractical for unrestricted FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of general MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
+Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $(n-1)$-gram, likelihood ratios must consider all combinations of all component $(n-1,2,3\ldots)$-grams, including, in our case, not only contiguous but also non-contiguous components.
+The corresponding exponential increase in complexity renders it and other such methods impractical for comprehensive FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
 For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
@@
 We created small development sets for each corpus and used them to do a thorough testing of parameter settings.
-Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all 4 corpora.
+Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
 We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
@@
 
+%<<<<<<< HEAD
 The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
+As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with syntactically-unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
+The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
+Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
+The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
+
+In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method.
+Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.
+%=======
+%The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
 As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
@@
 The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
-
-In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
+%
+%In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
 Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the F-score by changing the parameters from recommended settings for either model.
+%>>>>>>> origin/master
 
@@
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaticity.
+Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaticity.
 
@@
 
-We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice.
+%<<<<<<< HEAD
+We have presented here a new methodology for acquiring comprehensive multiword lexicons from large corpora, using competition in an $n$-gram lattice.
+Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
+A tool which implements the method as well as the acquired lexicons and test sets are available here.\footnote{removed for anonymity}
+%=======
+%We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice.
 Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
 A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{removed for anonymity}
+%>>>>>>> origin/master
 

### 2017-01-30 tacl.tex
More Jan and length related edits

@@
 \makeatother
-\usepackage[hidelinks]{hyperref}
+%\usepackage[hidelinks]{hyperref}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 
-Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers both produce and process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard processing unit for most research in modern NLP.
+Despite over 25 years of research in computational linguistics aimed at acquiring multiword lexicons using corpora statistics, and growing evidence that speakers process language primarily in terms of memorized sequences \cite{Wray08}, the individual word nonetheless stubbornly remains the \textit{de facto} standard processing unit for most research in modern NLP.
 The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work.
@@
 
-A central challenge in building comprehensive multiword lexicons is pairing down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language.
+Work based on collocation measures often assumes a small, fixed set of part-of-speech (``POS'') combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering a full range of lexicalized multiword units.
+Relaxing this restriction, however, requires dealing with extreme overgeneration -- a central challenge is how to avoid redundancy when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of some partial correspondence with a true multiword lexical item.
+The former can be addressed to some extent using a syntax-sensitive association measure \cite{Brooke15b}, but addressing the latter properly requires an iterative model, where $n$-grams types in essence compete with each other to form a compact, parsimonious vocabulary which best explains the statistics extracted from the corpus.
+We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.
+
+%A central challenge in building comprehensive multiword lexicons is pairing down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language.
 In particular, a model should attempt to minimize redundancy among the final entries in its lexicon.
 The lattice model proposed here accomplishes this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity.
-We test our approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering both scalability and many avenues for future enhancement.
 
@@
 The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
-\newcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics (\ie LPR).
+\newcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
 Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of \newcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases.
-\newcite{Gimpel11} focus specifically on deriving word sequences with gaps using a generative model, with the intent of improving machine translation.
-A general drawback to these generative methods, relative to approaching involving association metrics, is scalability and lack of determinacy.
 
@@
 
-Work that uses collocation measures for multiword lexicon creation often assumes a small, fixed set of part-of-speech (``POS'') combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering the full range of formulaic sequences in a language.
-Relaxing this restriction, however, requires dealing with extreme overgeneration in terms of potential phrases -- the main challenge is how to distinguish good FS in a huge collection of $n$-grams, many of which show basic statistical irregularities due to syntactic properties of the language or as the result of some relationship with a true FS.
-The former can be captured to some extent using a syntax-sensitive association measure like LPR, but addressing the latter requires a full, iterative model, where $n$-grams in essence compete with each other to form a compact, parsimonious formulaic vocabulary which best explains the statistics extracted from the corpus.
-
 Our approach to FS identification involves optimization of the total explanatory power of a lattice where each node corresponds to an $n$-gram type.
 The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes.
-Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS), and explainedness will be calculated differently depending on this status.
-Most fundamentally, $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance, be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
-These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
-A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
-Given these relationships, we maximize the explanatory power of the entire lattice by iterating over the nodes and greedily optimizing the on/off choice relative to the local neighborhood of each node, until convergence.
+Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS).
+The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
+Given these relationships, we by iterating over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
 
@@
 \end{displaymath}
-%<<<<<<< HEAD
-%
+
 \noindent
@@
 % TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
-%=======
-%where $w_{j,k}$ and $t_{j,k}$ should be understood as excluding $w_{i}$ and $t_{i}$ respectively. 
-%>>>>>>> origin/master
 
@@
 
+The $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance, be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
+These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
+A third, undirected mechanism is \termdef{overlapping}, where nodes inhibit each other due to overlaps in the corpus (\eg having both \ex{keep \gap under wraps} and \ex{be keep \gap under} as FS will be avoided).
+
 \subsubsection{Covering}
@@
 Our model includes two types of covering: hard and soft.
-\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other: if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
+\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other: In \figref{fig:example}, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
 We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
@@
 
+\section{Evaluation}
+
 We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
@@
 The other two languages we include in our evaluation are Croatian and Japanese.
-Relative to English, both languages are free-word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS extraction in such languages.
+Relative to English, both languages have freer word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS identification in such languages.
 For Croatian, we used the fhrWaC corpus \cite{snajder2013building}, a filtered version of the Croatian web corpus hrWaC \cite{ljubesic2014bs}, which is POS-tagged and lemmatized using the tools of \newcite{agic2013lemmatization}.
@@
 
+%.
+One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to an task with a known subjective component, is that it is quite sensible to simply discard borderline cases
+
 Other than the inclusion of new languages, our test sets differ from \newcite{Brooke15b} in two ways.
-First, instead of relying on strict majority annotation, we entirely excluded $n$-grams which just one annotator marked as FS.
-One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to an task with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving the reliability of evaluation at the cost of some representativeness.
+First, instead of relying on strict majority annotation, we entirely excluded $n$-grams which just one annotator marked as FS, improving the reliability of evaluation at the cost of some representativeness.
 Second, for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
-The rationale is that the number of positive gapped examples was too low (particularly for the BNC and the Croatian corpus) to provide a reliable independent F-score (see further of discussion of gapped phrases in \secref{sec:discussion}).
+The rationale is that the number of positive gapped examples was too low (particularly for the BNC and the Croatian corpus) to provide a reliable independent F-score (see further discussion in \secref{sec:discussion}).
 Statistics for the four test sets are given in \tabref{tab:stats}.
@@
 For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
-All comparison approaches have themselves been compared against a wide range of association measures in earlier work;\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of general MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
-Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $(n-1)$-gram, likelihood ratios must consider all combinations of all component $(n-1,2,3\ldots)$-grams, including, in our case, not only contiguous but also non-contiguous components.
-The corresponding exponential increase in complexity renders it and other such methods impractical for comprehensive FS identification.} we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+All comparison approaches have themselves been compared against a wide range of association measures in earlier work; we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
 For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
 All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
+
+%\footnote{One popular association measure which is theoretically extensible to $n$-grams of any length but which has not been addressed in the context of general MWE/FS identification is the (log-)likelihood ratio \cite{Dunning93}.
+Calculating a likelihood ratio in the general case involves considering all possible ways an $n$-gram could have been generated statistically from its component words: that is, whereas minLPR only considers the addition of one word to each $(n-1)$-gram, likelihood ratios must consider all combinations of all component $(n-1,2,3\ldots)$-grams, including, in our case, not only contiguous but also non-contiguous components.
+The corresponding exponential increase in complexity renders it and other such methods impractical for comprehensive FS identification.}
 
@@
 
-%<<<<<<< HEAD
 The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
@@
 Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.
-%=======
-%The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
-As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
-The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
-Generally, clearing and overlap node interactions offer a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
-The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
-%
-%In the continuous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
-Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the F-score by changing the parameters from recommended settings for either model.
-%>>>>>>> origin/master
 
@@
 The ICWSM corpus and the Japanese corpus, on the other hand, are mostly blogs and web pages.
-Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, are used almost exclusively in relatively informal genres.
+Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, appear almost exclusively in relatively informal genres.
 The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
@@
 We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS rather than less.
-Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is the relatively fixed-order of English that more often keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints.
+Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English that more often keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints.
 The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS.
-This phenomena actually highlights a problem with the current model, in that gapped and contiguous version of the same $n$-gram sequence are, at present, considered entirely independently.
-Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, or linking contiguous and gapped versions of the same $n$-grams sequence in the lattice model, encouraging them to have the same FS labels.
-% TJB: would be good to have some examples of gapped expressions to better make this point (yes, space permitting)
-
-A third, more ambitious option would be to switch to a dependency representation.
-This option actually requires very little change to the structure of the model presented here, since all the basic relationships in the lattice as well as the minLPR measure could be straightforwardly defined in terms of subgraphs instead of strings.
-One clear negative is the need for a dependency parser for the language and domain of interest, and that there is then no potential for using FS to improve parsing.
-A most subtle issue is that switching to a dependency representation does not entirely eliminate the need for gaps in order to represent a full range of FS: there are gappy FS where the gap term actually forms the syntactic connection between the two parts of the expression, \eg \ex{no amount of \gap can}.
+This phenomena actually highlights a problem with the current model, in that gapped and contiguous versions  of the same $n$-gram sequence (\eg \ex{take away} and {take \gap away}) are, at present, considered entirely independently.
+Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, creating a promoting link between contiguous and gapped versions of the same $n$-grams sequence in the lattice model, or switching to a dependency representation (which, we note, requires very little change to the basic model presented here, but would narrow its applicability).
 
@@
 
-Given our interest in methods which work well on large corpora, the speed of the model is worth mentioning.
-Although considered as an individual process, optimizing the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15a}, but the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
-We note that for all corpora, the lattice optimization algorithm converged within 10 iterations, and only the first two iterations require looking at a majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.
+With respect to speed, although when considered as an individual process the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
+We note that for all 4 corpora, the lattice optimization algorithm converged within 10 iterations.
+
+%, and only the first two iterations require looking at a majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.
 

### 2017-01-30 tacl.tex
Make Figure 1 bigger-font (and smaller in size)
LArge-scale edits, primarily to Methodology

@@
 
-Work based on collocation measures often assumes a small, fixed set of part-of-speech (``POS'') combinations \cite{Evert:Krenn:2001,Pecina10}, an assumption that breaks down entirely when considering a full range of lexicalized multiword units.
-Relaxing this restriction, however, requires dealing with extreme overgeneration -- a central challenge is how to avoid redundancy when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of some partial correspondence with a true multiword lexical item.
-The former can be addressed to some extent using a syntax-sensitive association measure \cite{Brooke15b}, but addressing the latter properly requires an iterative model, where $n$-grams types in essence compete with each other to form a compact, parsimonious vocabulary which best explains the statistics extracted from the corpus.
+Work based on collocation measures tends to assume a small, fixed set of part-of-speech (``POS'') combinations with higher productivity \cite{Evert:Krenn:2001,Pecina10} as a means of reducing overgeneration, with the obvious disadvantage of impeding the generation of a broad-coverage multiword lexicon.
+This is the central challenge addressed in this paper: how to avoid redundancy/computational intractability when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of partial correspondence with a true multiword lexical item.
+Our solution to this challenge takes the form of an iterative model, where $n$-gram types compete with each other in a lattice to generate a compact, parsimonious vocabulary which best explains the statistics extracted from the corpus.
 We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.
@@
 \begin{figure}[!t]
-\center{\includegraphics[width=0.35\textwidth]{FS_diagram_1.pdf}}
 \caption{Multiword Terminology}
+\center{\includegraphics[width=0.3\textwidth]{FS_diagram_1.pdf}}
 \label{fig:terminology}
@@
 
-Other research in MWEs has tended to be rather focused on particular syntactic patterns, looking at, for instance, just verb-noun combinations \cite{Fazly09}.
-The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model; like other models in this space, Schneider et \al make use of existing manual lexical resources and they note that an (unsupervised) automatic lexical resource could be useful addition to the model, though attempts to do so have had mixed results \cite{Riedl16}.
+Other research in MWEs has tended to be rather focused on particular syntactic patterns such as verb-noun combinations \cite{Fazly09}.
+The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model.
+Schneider et \al make use of existing manual lexical resources and note that an (unsupervised) automatic lexical resource could be useful addition to the model, although attempts to do so have achieved mixed success \cite{Riedl16}.
 
@@
 
-Our approach to FS identification involves optimization of the total explanatory power of a lattice where each node corresponds to an $n$-gram type.
+Our approach to FS identification involves optimization of the total explanatory power of a lattice, where each node corresponds to an $n$-gram type.
 The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes.
 Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS).
-The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
-Given these relationships, we by iterating over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
+The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
+Given these relationships, we iterate over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
 
@@
 Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words; we have done a manual analysis using the MWE corpus of \newcite{Schneider14a} which indicates very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.
-Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams.
-The precise definition of gaps is language specific (see \secref{sec:evaluation} for details) but the general idea is that for any particular language there is a relatively small set of syntactic types of limited length that will tend to appear as a gap inside a formulaic sequence \cite{Wasow:2002}.
-% TJB: added citation and removed "this is confirmed by empirical analysis" as it begs details of the specific analysis, which I think is more of a distraction than anything else at this point
-In a POS-tagged corpus, potential gaps can be identified by a POS regular expression.
+An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.}
+Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgement of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English and German \cite{Dehe:2002,Ludeling:2001}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
+Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
 This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall.
-We also exclude punctuation and lemmatize the corpus.
-Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.
-% TJB: this last sentence is a bit opaque
-%=======
-% In a POS-tagged corpus, potential gaps can be identified by a POS regular expression.
-This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall.
-We also exclude punctuation and lemmatize the corpus.
-Note that as long as the count threshold is significantly above 1, efficient extraction of all $n$-grams can be done iteratively ($n$ passes through the corpus) for both types in combination: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then consecutive instances of these $i$-grams are found, a set which will contain all $(i+1)$-grams which are also over the threshold.
-%>>>>>>> origin/master
+We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold.
+As long as the count threshold  is significantly above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.
 
-Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate \termdef{Lexical Predictability Ratios} (LPR) for each word in the $n$-gram are collected.
+Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected.
 LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
@@
 \end{displaymath}
+where $w_{j,k}$ denotes the word sequence $w_j,..., w_{i-1}, w_{i+1}, ..., w_{k}$ excluding $w_{i}$ (similarly for $t_{j,k}$).
+Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1.
 
-\noindent
-where $w_{j,k}$ as predictive context should be understood as not containing $w_{i}$ (similarly for $t_{j,k}$). 
-% TJB: clarify the semantics of the $w_{j,k}$ and $t_{j,k}$ notation
-
-%These conditional probabilities can be derived in the standard way from $n$-gram and POS $n$-gram counts. 
-% TJB: removed; seems to state the obvious
 We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics.
-Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
-% TJB: is this a good thing or bad thing? slight lack of clarity here
-It also ensures that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1.
+%Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
+% TJB: I still find this confusing, given that we haven't formally introduced the lattice at this point; suggest leaving it out
 
@@
 \end{displaymath}
-The use of minimum here should be understood in the context of competition between nodes in the lattice: minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which an $n$-gram holds together, instead it focuses on the word which is its weakest link.
-For example, in the case we are evaluating the quality of \ex{be keep \gap under} as an FS, a general statistical metric might give it a high score due the strong statistical relationship between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
+Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link.
+For example, in the case of \ex{be keep \gap under},\footnote{Recall that our method involves lemmatization, in keeping with which all examples will be presented pre-lemmatized.} a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
 
@@
 When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
-Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it is off.
-The base value of $E_{0}$ is the inverse of minLPR: when the minLPR metric is 1, corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1.
-The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
-There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
 
-We weight these functions by adding exponential terms, reflecting the fact we do not want to override the association measure, but rather modulate it.
-We define $E_0$, then, as minLPR to the negative power of some as yet undefined non-negative function $d_0$:
+Let $E_{1}$ be the explainedness of a node when it is on (corresponding to an $n$-gram which has been identified as an FS), and $E_{0}$ be the explainedness of a node when it is off.
+We calculate $E_{0}$ based on the inverse of minLPR:
 \begin{displaymath}
@@
 \end{displaymath}
-and $E_1$ is the cost parameter $C$ to the negative power of an analogous non-negative function $d_1$:
+and $E_{1}$ based on the inverse of a cost parameter $C$:
 \begin{displaymath}
@@
 \end{displaymath}
-The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.
+where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context, as detailed in the next section.
+When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
+$E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
+There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ to perform best across the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
 
-\begin{figure*}[!tb]
-\center{\includegraphics[width=0.8\textwidth]{FS_diagram_2.pdf}}
+% The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.
+
+\begin{figure}[!tb]
 \caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
+\center{\includegraphics[width=0.5\textwidth]{FS_diagram_2.pdf}}
 \label{fig:example}
-\end{figure*}
+\end{figure}
 
@@
 
-The $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume: that is, the (gapped) $n$-gram \ex{keep \gap under wraps} would, for instance, be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
+The $n$-gram nodes in the lattice are directionally connected to nodes consisting of $(n+1)$-grams which subsume them and $(n-1)$-grams which they subsume.
+For example, as detailed in \figref{fig:example}, the (gapped) $n$-gram \ex{keep \gap under wraps} would be connected ``upwards'' to the node \ex{keep everything under wraps} and connected ``downwards'' to \ex{under wraps}.
 These directional relationships allow for two basic interactions between nodes in the lattice when a node is turned on: \termdef{covering}, which inhibits nodes below (subsumed by) a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model will tend not to choose \ex{under wraps} as an FS); and \termdef{clearing}, which inhibits nodes above a turned-on node (\eg if \ex{keep \gap under wraps} is on, the model would avoid selecting \ex{keep everything under wraps} as an FS).
@@
 Our model includes two types of covering: hard and soft.
-\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other: In \figref{fig:example}, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
-We do this by permanently disabling any covered node, and setting the the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
+\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other.
+In \figref{fig:example}, \eg, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
+We do this by permanently disabling any covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
 This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice.
 Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.
-We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR ratios \cite{Brooke15b}.
+We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR values \cite{Brooke15b}.
 In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.
@@
 \termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that corresponds to occurrences of \ex{keep \gap under wraps}.
+For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}.
 This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
@@
 \end{displaymath}
-This equation is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
+This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
 
@@
 
-A simple but effective solution which avoids introducing parameters makes use of the minLPR values of the relevant nodes.
-In the most common (two node) situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher, which greatly restricts its effect.
-Generalized to consider the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
+A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes.
+In the most common two-node situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher.
+Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
 %in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
@@
 where $u_i$ is the $i$th clearing node of $t$.
-We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which many have higher LPR due to the lexical and syntactic specificity of the FS.
+We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
 For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.
@@
 The third mechanism of node interaction involves $n$-grams which overlap in the corpus.
-Though there are exceptions, it is generally the case that independent formulaic sequences do not overlap.
-For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together, overlapping on the tokens \ex{keep \gap under}, we do not want both being selected as an FS, even in the case where both have high minLPR.
+In general, independent formulaic sequences do not predictably overlap.
+For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR.
 To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of having turned-off nodes, we decrease the explainedness of the turned-on nodes, which serves to express confusion at having overlapping FS.
@@
 Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$.
-We define $d_1(t)$, the exponential term for the $E_1(t)$, as:
+We define $d_1(t)$, the exponential term for $E_1(t)$, as:
 \begin{displaymath}
@@
 
-The dependence of the explainedness of nodes on their neighbors as discussed in the preceding section effectively prohibits a global optimization of the lattice.
+The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice.
 Fortunately, though most of the nodes in the lattice are part of a single main connected component, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
@@
 For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice.
-The order that we perform this has an effect on the result: among the obvious options, good results are obtained when ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
+The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
 
-Given the relationships between nodes that we have defined above, it is obviously not sufficient to consider switching only the present node.
+Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node on.
 If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
-Instead, the algorithm identifies a small set of nodes (relevant nodes) which are the most important to the status of the node under consideration whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
+Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration, whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
 Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.
 
-In practice, we apply the following restrictions, which significantly reduce the runtime without sacrificing the quality of the output lexicon (based on development set testing):
+In practice, we apply the following efficiency restrictions, which significantly reduce the runtime without sacrificing quality (based on development set testing):
 \begin{compactitem}
@@
 \item Many nodes have a minLPR which is a little larger than 1.
-There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with a minLPR of less than 2.
+There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with $\minLPR < 2$.
 \end{compactitem}
 
-\begin{table*}[!bt]
+\section{Evaluation}
+\label{sec:evaluation}
+
+We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
+In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM blog corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
+To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
+Lemmatization included removing all inflectional marking from both words and POS tags.
+For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum of 4 words.
+
+\begin{table}[!bt]
 
  \begin{center}
-  \caption{ Statistics for test sets}
+  \caption{ Statistics for test sets (``Cont'' = contiguous; ``Gap'' = gapped)}
 	 \label{tab:stats}
-	 \begin{tabular}{lccccc}
+	 \begin{tabular}{lc@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c}
 
        \hline
-			& Contiguous FS & Contiguous non-FS & Gapped FS & Gapped non-FS & Fleiss Kappa\\
+			& Cont & Cont & Gap & Gap & \multirow{2}{*}{$\kappa$}\\
+			& FS & non-FS & FS & non-FS & \\
 			 \hline
@@
 
- \end{table*}
-
-\section{Evaluation}
-
-We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
-In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM social media corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
-To facilitate a comparison with \newcite{Newman12}, which does not scale up to a corpus as large as the ICWSM, we also build a lexicon using the 100M token British National Corpus \cite{BNC}, using the standard CLAWS-derived POS tags for the corpus.
-Lemmatization included removing all inflectional marking from both words and POS tags.
-For English, gaps are identified using the same POS regex used in \newcite{Brooke15b}, which includes simple nouns and portions thereof, up to a maximum length of 4 words.
+ \end{table}
 
@@
 We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}.
-The POS regex for Japanese covers the same basic nominal structures as English, but also includes case markers and adverbials which intervene between noun and verbs.
-Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) which are removed by lemmatization in Croatian are segmented into independent mophological units in the MeCab output, making the task somewhat different for the two languages.
+The POS regex for Japanese covers the same basic nominal structures as English, but also includes case markers and adverbials.
+Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) which are removed by lemmatization in Croatian are segmented into independent morphological units in the MeCab output, making the task somewhat different for the two languages.
 
-% TJB: worth including the respective POS regexes in an appendix?
-
-\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model: instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
+\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model.
+Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
 We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
@@
 
-	Lattice \emph{-cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.74 & 0.39 & 0.51 \\
+	Lattice \emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.74 & 0.39 & 0.51 \\
 
-	Lattice \emph{-ovr} & 0.52& \bf{0.51} & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.69 & \bf{0.51} & \bf{0.58} \\
+	Lattice \emph{$-$ovr} & 0.52& \bf{0.51} & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.69 & \bf{0.51} & \bf{0.58} \\
 
@@
  Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
-For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using the SCP as the association measure; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
+For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
 All comparison approaches have themselves been compared against a wide range of association measures in earlier work; we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.

### 2017-01-30 tacl.tex
Minor edit

@@
 
-Work based on collocation measures tends to assume a small, fixed set of part-of-speech (``POS'') combinations with higher productivity \cite{Evert:Krenn:2001,Pecina10} as a means of reducing overgeneration, with the obvious disadvantage of impeding the generation of a broad-coverage multiword lexicon.
+Methods based on association measures tend to assume a small, fixed set of part-of-speech (``POS'') combinations with higher productivity \cite{Evert:Krenn:2001,Pecina10} as a means of reducing overgeneration, with the obvious disadvantage of impeding the generation of a broad-coverage multiword lexicon.
 This is the central challenge addressed in this paper: how to avoid redundancy/computational intractability when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of partial correspondence with a true multiword lexical item.
@@
 An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.}
-Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgement of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English and German \cite{Dehe:2002,Ludeling:2001}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
+Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgement of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
 Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
@@
 %Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
-% TJB: I still find this confusing, given that we haven't formally introduced the lattice at this point; suggest leaving it out
 
@@
 \end{displaymath}
-where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context, as detailed in the next section.
+where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context (and both default to 1), as detailed in the next section.
 When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.

### 2017-01-30 tacl.tex
Down to 10 pages with various small/medium edits

@@
 
-Methods based on association measures tend to assume a small, fixed set of part-of-speech (``POS'') combinations with higher productivity \cite{Evert:Krenn:2001,Pecina10} as a means of reducing overgeneration, with the obvious disadvantage of impeding the generation of a broad-coverage multiword lexicon.
+%Methods based on association measures tend to assume a small, fixed set of part-of-speech (``POS'') combinations with higher productivity \cite{Evert:Krenn:2001,Pecina10} as a means of reducing overgeneration, with the obvious disadvantage of impeding the generation of a broad-coverage multiword lexicon.
 This is the central challenge addressed in this paper: how to avoid redundancy/computational intractability when selecting a lexicon from a huge collection of $n$-grams, many of which show basic statistical irregularities only as a result of their syntactic properties or because of partial correspondence with a true multiword lexical item.
 Our solution to this challenge takes the form of an iterative model, where $n$-gram types compete with each other in a lattice to generate a compact, parsimonious vocabulary which best explains the statistics extracted from the corpus.
+
+A central challenge in building comprehensive multiword lexicons is pairing down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language: allowing for diversity creates significant redundancy among statistically promising candidates.
+The lattice model proposed here addresses this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity.
 We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.
-
-%A central challenge in building comprehensive multiword lexicons is pairing down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language.
-In particular, a model should attempt to minimize redundancy among the final entries in its lexicon.
-The lattice model proposed here accomplishes this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity.
 
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02} and \newcite{Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In other words, a formulaic sequence shows signs of being part of a mental lexicon.
-Though by this definition single individuals or small groups may have their own FS, in this paper, we are only interested in FSs that are shared by a recognizable language community.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02} and \newcite{Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a formulaic sequence shows signs of being part of a mental lexicon.
+Though by this definition individuals or small groups may have their own FS, here we are only interested in FSs that are shared by a recognizable language community.
 
@@
 Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
-Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability (as provided by part-of-speech information) from the overall conditional probability for each word given the other words in the phrase.
+Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
 Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word \cite{Riedl15}.
@@
 The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
-\newcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
+Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
 Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of \newcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases.
@@
 One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses.
-Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold: in order to get very reliable phrases, the threshold is typically set rather high (Biber et \al use 40 occurrences in 1 million words).
+Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold.
 Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures).
 Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.
-\newcite{Sakaguchi16} demonstrate that improving fluency (which is closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.
+\newcite{Sakaguchi16} demonstrate that improving fluency (closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.
 
@@
 An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.}
-Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgement of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
+Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
 Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
@@
 Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1.
-
 We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics.
@@
 Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link.
-For example, in the case of \ex{be keep \gap under},\footnote{Recall that our method involves lemmatization, in keeping with which all examples will be presented pre-lemmatized.} a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
+For example, in the case of \ex{be keep \gap under}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
+
+%\footnote{Recall that our method involves lemmatization, in keeping with which all examples will be presented pre-lemmatized.}
 
@@
 \end{displaymath}
-where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context (and both default to 1), as detailed in the next section.
+where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section.
 When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
 $E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
-There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ to perform best across the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
+There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ gives reasonable results for the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
 
@@
 \subsubsection{Covering}
-
-The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node based on the presence of a node higher in the lattice.
+The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node due to a node higher in the lattice.
 Our model includes two types of covering: hard and soft.
 \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other.
-In \figref{fig:example}, \eg, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and it is better if we collapse these two decisions into one.
-We do this by permanently disabling any covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
+In \figref{fig:example}, \eg, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and we should consider these two $n$-grams as one.
+We do this by permanently disabling any hard covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
 This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice.
-Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant but not overwhelming majority of the counts of a lower node corresponding to the higher node) works well.
+Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant majority of the counts of a lower node corresponding to the higher node) works well.
 We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR values \cite{Brooke15b}.
-In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to greatly limit FS with pronouns without excluding them entirely: they are included only in cases where they are almost completely predictable from the context.
+In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to limit FS with pronouns without excluding them entirely: they are included only in cases where they are definitively formulaic.
 
@@
 In general, covering prefers turning on longer, covering $n$-grams since doing so explains nodes lower in the lattice.
-Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer ones which contain them, beyond the FS-neutral syntactic explanation provided by minLPR.
+Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR.
 \termdef{Clearing} does this by changing the $E_0$ of nodes higher in the lattice when a lower node is turned-on.
@@
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR.
-To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of having turned-off nodes, we decrease the explainedness of the turned-on nodes, which serves to express confusion at having overlapping FS.
-The idea behind covering and clearing is to encourage the model to turn on nodes which effectively explain the presence of nodes above and/or below it in the lattice, but for overlaps a penalty is a more appropriate mechanism.
+To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes, a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
 Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$.
@@
 For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice.
-The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams, since they will tend to be turned on first.
+The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.
 
-Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node on.
+Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node.
 If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
-Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration, whose status should be considered simultaneously: since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
+Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration.
+Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
 Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.
@@
 \item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice;
-\item Many nodes have a minLPR which is a little larger than 1.
+\item Many nodes have a minLPR which is slighlty larger than 1.
 There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with $\minLPR < 2$.
@@
 For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
-All comparison approaches have themselves been compared against a wide range of association measures in earlier work; we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+All comparison approaches have themselves been previously compared against a wide range of association measures; we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
 For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
-All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
+%All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
 
@@
 Though the results across the four corpora are reasonably similar with respect to overall F-score, there are significant discrepancies.
-By using the UNIDIC morpheme representation as the starting unit for Japanese, the model is, in essence, doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
-The result is that there are many more FS for Japanese.
-Precision is very high, and recall is relatively low.
-Under these conditions, methods which tend to increase precision at the cost of recall will be less desirable with respect to F-score, which explains why the full model is not the best in that one case.
-Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types, over length 4, for instance, is almost twice the number in the ICWSM corpus, or almost 14\% of all $n$-gram types.
-One idea for future work is to automatically adapt to the particular properties of the input language/corpus in order to ensure a good balance between precision and recall.
+By using the UNIDIC morpheme representation as the base unit for Japanese, the model is doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
+The result is that there are many more FS for Japanese: precision is high, and recall is relatively low.
+Under these conditions, methods which increase precision at the cost of recall will have worse F-score, which explains why the full lattice model is not the best in that case.
+Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus.
+One idea for future work is to automatically adapt to the input language/corpus in order to ensure a good balance between precision and recall.
 
-At the opposite end of the precision/recall curve, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of the order of about 100 for the other three corpora used here, the BNC statistics includes $n$-grams which appear less than 10 times.
-This might be resolved, of course, by increasing the $n$-gram threshold, or simply avoiding small corpora altogether, but it may be useful to focus effort on how to building comprehensive FS lexicons even in relatively low resource situations.
-One idea we are actively pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.
+At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10.
+This might be resolved by increasing the $n$-gram threshold, or simply avoiding small corpora, but for some applications it may be useful to building comprehensive FS lexicons even in relatively low resource situations.
+One idea we are pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.
 
-There is one other more general explanation for the precision/recall imbalances we see across the four corpora: both the BNC and the Croatian corpus are composed primarily (though not exclusively) of published texts written by professional writers, particularly news.
+There is one other more general explanation for the precision/recall imbalances we see across the four corpora: both the BNC and the Croatian corpus are composed primarily of published texts written by professional writers, particularly news.
 The ICWSM corpus and the Japanese corpus, on the other hand, are mostly blogs and web pages.
 Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, appear almost exclusively in relatively informal genres.
-The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
 
-We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether allowing gaps in our FS would help with these languages.
-We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS rather than less.
-Strikingly rare in Croatian (and to a lesser extent, Japanese), are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English that more often keeps elements of an FS distant from each other in order to satisfy fixed-word-order constraints.
+%The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
+
+We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the potential gaps in FS would help with these languages.
+We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less.
+Strikingly rare in Croatian, in particular, are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English whose fixed-word-order constraints often keep elements of an FS distant from each other.
 The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS.
-This phenomena actually highlights a problem with the current model, in that gapped and contiguous versions  of the same $n$-gram sequence (\eg \ex{take away} and {take \gap away}) are, at present, considered entirely independently.
-Alternatives for dealing with this range from collapsing statistics to create a single node in the lattice, creating a promoting link between contiguous and gapped versions of the same $n$-grams sequence in the lattice model, or switching to a dependency representation (which, we note, requires very little change to the basic model presented here, but would narrow its applicability).
+This phenomena highlights a problem with the current model, in that gapped and contiguous versions  of the same $n$-gram sequence (\eg \ex{take away} and {take \gap away}) are, at present, considered entirely independently.
+Alternatives for dealing with this include collapsing statistics to create a single node in the lattice, creating a promoting link between contiguous and gapped versions of the same $n$-grams sequence in the lattice model, or switching to a dependency representation (which, we note, requires very little change to the basic model presented here, but would narrow its applicability).
 
@@
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalizing to $n$-grams for which the raw LPR statistics are an unreliable indicator of formulaticity.
+Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics are an unreliable indicator of formulaticity.
 
-With respect to speed, although when considered as an individual process the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice was still only a fraction of the time required to collect all the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, considered as end-to-end process, the effect of adding the lattice optimization is fairly minimal.
+With respect to speed, although the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice was still only a fraction of the time required to collect the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, the overall effect of adding the lattice optimization is fairly minimal.
 We note that for all 4 corpora, the lattice optimization algorithm converged within 10 iterations.
@@
 
-Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, the fact that precision and recall are both dependent on the number of positive examples means that F-scores become unreliable when there are very few positive examples.
-To do an independent evaluation of FS with gaps, we would want many more examples than can be produced with straightforward sampling.
-Rather than brute force annotation, one option we could consider is adding additional filtering to the sampling processes (\eg using the LPR metric to exclude large numbers of extremely poor $n$-grams), though it is difficult to do this without significantly biasing the evaluation.
+Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-grams set.
+To do an reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling.
+One option we might consider is adding additional filtering to the sampling processes, for instance using the LPR metric to exclude large numbers of unpromising $n$-grams.
 

### 2017-01-30 tacl.tex
Correct typos & typography

@@
 \usepackage{paralist}
+\usepackage{booktabs}
 \usepackage[pdftex]{graphicx}
@@
 The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work.
-We present a effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition that aims to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which fail to scale to the large corpora which are the main sources of the distributional information in modern NLP systems.
+We present an effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition that aims to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which fail to scale to the large corpora which are the main sources of the distributional information in modern NLP systems.
 
@@
 \begin{figure}[!t]
+\center{\includegraphics[width=0.3\textwidth]{FS_diagram_1.pdf}}
 \caption{Multiword Terminology}
-\center{\includegraphics[width=0.3\textwidth]{FS_diagram_1.pdf}}
 \label{fig:terminology}
@@
 \begin{figure}[!tb]
+\center{\includegraphics[width=0.5\textwidth]{FS_diagram_2.pdf}}
 \caption{A portion of an $n$-gram lattice. Solid lines indicate subsumption, dotted lines overlaps}
-\center{\includegraphics[width=0.5\textwidth]{FS_diagram_2.pdf}}
 \label{fig:example}
@@
 \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other.
-In \figref{fig:example}, \eg, if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and we should consider these two $n$-grams as one.
+In \figref{fig:example}, \eg if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and we should consider these two $n$-grams as one.
 We do this by permanently disabling any hard covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover.
@@
 \termdef{Clearing} does this by changing the $E_0$ of nodes higher in the lattice when a lower node is turned-on.
-The basic mechanism is similar to covering, except that counts cannot be made use of in the same way -- whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
+The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
 
@@
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR.
-To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes, a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
+To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
 Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$.
@@
  \begin{center}
-  \caption{ Statistics for test sets (``Cont'' = contiguous; ``Gap'' = gapped)}
 	 \label{tab:stats}
-	 \begin{tabular}{lc@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c}
+	 %\begin{tabular}{lc@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c}
+	 \begin{tabular}{lrrrrr}
 
-       \hline
-			& Cont & Cont & Gap & Gap & \multirow{2}{*}{$\kappa$}\\
-			& FS & non-FS & FS & non-FS & \\
-			 \hline
+       \toprule
+       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \\
+       \cmidrule(lr){2-3}\cmidrule(lr){4-5}
+			& FS & non-FS & FS & non-FS & $\kappa$ \\
+			 \midrule
 			ICWSM & 169 & 702 & 29 & 916& 0.84 \\
@@
 			Japanese & 124 & 286 & 36 & 341 & 0.81\\
-       \hline
+       \bottomrule
  \end{tabular}
+  %\caption{ Statistics for test sets (``Cont'' = contiguous; ``Gap'' = gapped)}
+  \caption{ Statistics for test sets }
 
@@
 Similar to English, the POS regex for Croatian includes simple nouns, adjectives and pronouns, but also other elements that regularly appear inside FS, including both adverbs and copulas.
-For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008} which was roughly the same size (in terms of token count) as the English corpus.
+For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008}, which was roughly the same size (in terms of token count) as the English corpus.
 We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}.
@@
  \begin{center}
-  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
-Bold is best in column.}
-	 \label{tab:main}
  \begin{tabular}{lcccccccccccccccc}
 
-       \hline
-        \hline
-				& \multicolumn{7}{c}{\bf{English}} & & \multicolumn{3}{c}{\bf{Croatian}} & & \multicolumn{3}{c}{\bf{Japanese}} \\
-       \cline{2-9}			
-       & \multicolumn{3}{c}{\bf{ICWSM}} & &  \multicolumn{3}{c}{\bf{BNC}} & & &&&  && & \\
-       \cline{2-4} \cline{6-8} \cline{10-12} \cline{14-16}
+       \toprule
+				& \multicolumn{7}{c}{\bf{English}} \\
+       \cmidrule(lr){2-8}			
+       & \multicolumn{3}{c}{\bf{ICWSM}} & &  \multicolumn{3}{c}{\bf{BNC}} & & \multicolumn{3}{c}{\bf{Croatian}}  && \multicolumn{3}{c}{\bf{Japanese}} \\
+       \cmidrule(lr){2-4} \cmidrule(lr){6-8} \cmidrule(lr){10-12} \cmidrule(lr){14-16}
            \multicolumn{1}{c}{\bf{Source}}    & P & R & F &   & P & R & F &   & P & R & F &  & P & R & F \\
-            \hline
-           \hline
-
+          \midrule 
 PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.23& 0.09 & 0.15 \\ 
@@
 LPR-seg  &0.53 & 0.42 & 0.47 && 0.37 & 0.44 & 0.40 & & 0.41 & 0.47  & 0.43 &  & 0.77 & 0.34 & 0.47 \\ 
-  \hline
+  \midrule
 
@@
 				Lattice & \bf{0.67} & 0.43 & \bf{0.52} & & \bf{0.40}& 0.60 & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.87} & 0.39 & 0.53 \\ 
-            \hline
-           \hline
+            \bottomrule
 
  \end{tabular}
+  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
+Bold is best in column.}
+	 \label{tab:main}
 
@@
  \begin{center}
-  \caption{ Results of formulaic sequence identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
-	\label{tab:BNC}
 
@@
 
-       \hline
+       \toprule
 			& P & R & F\\
-			 \hline
+			 \midrule
 			PMIrank & 0.20 & 0.29 & 0.23 \\
@@
 			Lattice & 0.47 & 0.63 & \bf{0.54} \\
-       \hline
+       \bottomrule
  \end{tabular}
+  \caption{ Results of formulaic sequence identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
+	\label{tab:BNC}
 
@@
 
-In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar f-scores, though both are well below our Lattice method.
-Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the f-score by changing the parameters from recommended settings for either model.
+In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
+Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the F-score by changing the parameters from recommended settings for either model.
 
@@
 The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS.
-This phenomena highlights a problem with the current model, in that gapped and contiguous versions  of the same $n$-gram sequence (\eg \ex{take away} and {take \gap away}) are, at present, considered entirely independently.
+This phenomena highlights a problem with the current model, in that gapped and contiguous versions  of the same $n$-gram sequence (\eg \ex{take away} and \ex{take \gap away}) are, at present, considered entirely independently.
 Alternatives for dealing with this include collapsing statistics to create a single node in the lattice, creating a promoting link between contiguous and gapped versions of the same $n$-grams sequence in the lattice model, or switching to a dependency representation (which, we note, requires very little change to the basic model presented here, but would narrow its applicability).
@@
 One of the major benefits of this model as compared to alternatives is the relative ease with which additional kinds of interactions between nodes could be implemented.
-Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, \eg, learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
+Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, \eg learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
@@
 With respect to speed, although the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice was still only a fraction of the time required to collect the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, the overall effect of adding the lattice optimization is fairly minimal.
-We note that for all 4 corpora, the lattice optimization algorithm converged within 10 iterations.
+We note that for all four corpora, the lattice optimization algorithm converged within 10 iterations.
 

### 2017-01-31 tacl.tex
Correct typos & typography
Fix to Fig 1; low-level edits throughout; bib fixes

@@
 \newcommand{\gap}{$*$\xspace}
+\newcommand{\z}{\phantom{0}}
 \newcommand{\ex}[1]{\textit{#1}\xspace}
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02} and \newcite{Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a formulaic sequence shows signs of being part of a mental lexicon.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.
 Though by this definition individuals or small groups may have their own FS, here we are only interested in FSs that are shared by a recognizable language community.
 
-In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes many MWEs but also (apparently) compositional linguistic formulas.
+In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} (``MWE'': \newcite{Sag02}, \newcite{Baldwin10}), but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes many MWEs but also compositional linguistic formulas.
 This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to confusion with respect to its interpretation.
-Though in some contexts it has been used in a way that is similar to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}.}  and strong (non-compositional) MWEs.
+Though some define it similarly to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}.}  and strong (non-compositional) MWEs.
 It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella.
-Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}).
+Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) FS such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \dotts's weight in gold}, fall under the FS umbrella.
+Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb} or \ex{government ambiguity}).
 Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
@@
 
-Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen.
+Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}.
+When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen.
 Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
-Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
+Other measures specifically designed to address sequences of larger than two words include: the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones; and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
 Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
@@
 
-The motivation for building lexicons of formulaic sequences naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
+The motivation for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
 One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses.
@@
 The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
-Given these relationships, we iterate over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
+Given these relationships, we iterate over the nodes and greedily optimize the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
 
@@
 Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage.
-An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.}
-Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
+An initial requirement of any such method is an $n$-gram frequency threshold, which we set to 1 instance per 10 million words, following \newcite{Brooke15b}.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.}
+
+We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
 Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
@@
 We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold.
-As long as the count threshold  is significantly above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.
+As long as the count threshold  is substantially above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.
 
 Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected.
-LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
+LPR is a measure of how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
 Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
@@
 
-In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (``\minLPR''):
+In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence:
 \begin{displaymath}
@@
 For example, in the case of \ex{be keep \gap under}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
-
-%\footnote{Recall that our method involves lemmatization, in keeping with which all examples will be presented pre-lemmatized.}
 
@@
 \end{displaymath}
-where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section.
+where $d_0$ and $d_1$ are non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section.
 When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
@@
 Our model includes two types of covering: hard and soft.
+
 \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other.
@@
 Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant majority of the counts of a lower node corresponding to the higher node) works well.
-We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR values \cite{Brooke15b}.
+We also use the concept of hard covering to address the issue of pronouns, based on the observation that pronouns often have high LPR values \cite{Brooke15b}.
 In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to limit FS with pronouns without excluding them entirely: they are included only in cases where they are definitively formulaic.
@@
 where $u_i$ is the $i$th clearing node of $t$.
-We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
+We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
 For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.
@@
 The third mechanism of node interaction involves $n$-grams which overlap in the corpus.
-In general, independent formulaic sequences do not predictably overlap.
+In general, independent FS do not predictably overlap.
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR.
@@
 
-\begin{table}[!bt]
-
- \begin{center}
-	 \label{tab:stats}
-	 %\begin{tabular}{lc@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c}
-	 \begin{tabular}{lrrrrr}
-
-       \toprule
-       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \\
-       \cmidrule(lr){2-3}\cmidrule(lr){4-5}
-			& FS & non-FS & FS & non-FS & $\kappa$ \\
-			 \midrule
-			ICWSM & 169 & 702 & 29 & 916& 0.84 \\
-			BNC & 49 & 403 & 8 & 475 & 0.84 \\
-			Croatian & 64 & 382 & 11 & 456 & 0.87 \\
-			Japanese & 124 & 286 & 36 & 341 & 0.81\\
-       \bottomrule
- \end{tabular}
-  %\caption{ Statistics for test sets (``Cont'' = contiguous; ``Gap'' = gapped)}
-  \caption{ Statistics for test sets }
-
- \end{center}
-
- \end{table}
-
 The other two languages we include in our evaluation are Croatian and Japanese.
@@
 
-\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model.
+\newcite{Brooke15b} introduced a method for evaluating FS extraction without a reference lexicon or direct annotation of the output of a model.
 Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
@@
 One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to an task with a known subjective component, is that it is quite sensible to simply discard borderline cases
+
+\begin{table}[!bt]
+
+ \begin{center}
+   \begin{tabular}{lc@{\,\,\,}cc@{\,\,\,}c@{\,\,\,}c}
+
+       \toprule
+       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \multirow{2}{*}{$\kappa$}\\
+       \cmidrule(lr){2-3}\cmidrule(lr){4-5}
+			& FS & non-FS & FS & non-FS &  \\
+			 \midrule
+			ICWSM    & 169  & 702 & 29 & 916 & 0.84 \\
+			BNC      & \z49 & 403 & \z8& 475 & 0.84 \\
+			Croatian & \z64 & 382 & 11 & 456 & 0.87 \\
+			Japanese & 124  & 286 & 36 & 341 & 0.81\\
+       \bottomrule
+ \end{tabular}
+  \caption{ Statistics for test sets }
+	 \label{tab:stats}
+
+ \end{center}
+
+ \end{table}
 
@@
  \end{tabular}
-  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
+  \caption{ Results of FS identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
 Bold is best in column.}
@@
 			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
+  \midrule
 			Lattice & 0.47 & 0.63 & \bf{0.54} \\
@@
  \end{tabular}
-  \caption{ Results of formulaic sequence identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
+  \caption{ Results of FS identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
 	\label{tab:BNC}
@@
  Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
-For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set.
-All comparison approaches have themselves been previously compared against a wide range of association measures; we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
+For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
+All comparison approaches have themselves been previously compared against a wide range of association measures.
+As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
 For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
@@
 The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
-Generally, using clearing and overlap node interactions offer an relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
+Generally, clearing and overlap node interactions provide a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
 The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
@@
 In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
-Some of the difference seems attributable to fairly severe precision/recall imbalance, though we unable to improve the F-score by changing the parameters from recommended settings for either model.
+Some of the difference seems attributable to fairly severe precision/recall imbalance, though we were unable to improve the F-score by changing the parameters from recommended settings for either model.
 
@@
 At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10.
-This might be resolved by increasing the $n$-gram threshold, or simply avoiding small corpora, but for some applications it may be useful to building comprehensive FS lexicons even in relatively low resource situations.
+This might be resolved by increasing the $n$-gram threshold, or simply avoiding small corpora, but for some applications it may be useful to build comprehensive FS lexicons even in relatively low resource situations.
 One idea we are pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.
@@
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information, for instance some simple distributional statistics which might help the model identify non-compositional semantics, would, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics are an unreliable indicator of formulaticity.
+Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics are an unreliable indicator of formulaticity.
 
@@
 
-Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-grams set.
-To do an reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling.
+Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets.
+To do a reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling.
 One option we might consider is adding additional filtering to the sampling processes, for instance using the LPR metric to exclude large numbers of unpromising $n$-grams.
@@
 
-%<<<<<<< HEAD
 We have presented here a new methodology for acquiring comprehensive multiword lexicons from large corpora, using competition in an $n$-gram lattice.
 Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
-A tool which implements the method as well as the acquired lexicons and test sets are available here.\footnote{removed for anonymity}
-%=======
-%We have presented here a new methodology for acquiring unrestricted multiword lexicons from large corpora, using competition in an $n$-gram lattice.
-Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
-A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{removed for anonymity}
-%>>>>>>> origin/master
+A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{Removed for anonymity}
 

### 2017-01-31 tacl.tex
Last fixes before submission

@@
 \makeatother
-%\usepackage[hidelinks]{hyperref}
+\usepackage[hidelinks]{hyperref}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.
-Though by this definition individuals or small groups may have their own FS, here we are only interested in FSs that are shared by a recognizable language community.
+Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.
 
@@
 Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS).
-The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
+The basis of the calculation of explainedness is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
 Given these relationships, we iterate over the nodes and greedily optimize the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
@@
 The third mechanism of node interaction involves $n$-grams which overlap in the corpus.
-In general, independent FS do not predictably overlap.
+In general, independent FS do not consistently overlap.
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR.
@@
 Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
-Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each iteration turning off the node (if any) which most increases overall explainedness.
+Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each step turning off the node (if any) which most increases overall explainedness.
 
@@
  \end{tabular}
-  \caption{ Results of FS identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
+  \caption{ Results of FS identification in contiguous BNC test set; LocalMaxs = method of da Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
 	\label{tab:BNC}
@@
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics are an unreliable indicator of formulaticity.
+Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics alone are an unreliable indicator of formulaticity.
 

### 2017-03-29 tacl.tex
Added single objective function

@@
 \newcommand{\clear}{\ensuremath{\text{clear}}\xspace}
+\newcommand{\overlap}{\ensuremath{\text{overlap}}\xspace}
 
@@
 
-\subsection{Node explainedness functions}
-
-The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of maximizing the overall explanatory power of the lattice.
-Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained.
-We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on.
-When a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence.
-When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
-
-Let $E_{1}$ be the explainedness of a node when it is on (corresponding to an $n$-gram which has been identified as an FS), and $E_{0}$ be the explainedness of a node when it is off.
-We calculate $E_{0}$ based on the inverse of minLPR:
-\begin{displaymath}
-E_0(t) = \minLPR(t)^{-d_0(t)}
-\end{displaymath}
-and $E_{1}$ based on the inverse of a cost parameter $C$:
-\begin{displaymath}
-E_1(t) = C^{-d_1(t)}
-\end{displaymath}
-where $d_0$ and $d_1$ are non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section.
-When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
-$E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
-There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ gives reasonable results for the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
-
-% The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.
-
 \begin{figure}[!tb]
@@
 This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
+\cover takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.
 
@@
 A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes.
-In the most common two-node situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher.
+In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher.
 Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
@@
 \end{displaymath}
-where $u_i$ is the $i$th clearing node of $t$.
+where $u_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice.
 We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
 For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.
+Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs.
 
-We can now define $d_{0}(t)$ as:
-\begin{displaymath}
-d_0(t) = \cover(t) \cdot \clear(t)
-\end{displaymath}
-Note that the effect of both covering and clearing is to increase explainedness for covered/cleared nodes, which indirectly encourages the model to turn an $n$-gram like \ex{keep \gap under wraps} on in order to explain nodes in its vicinity, even supposing its minLPR were relatively low.
+%We can now define $d_{0}(t)$ as:
+%\begin{displaymath}
+%d_0(t) = \cover(t) \cdot \clear(t)
+%\end{displaymath}
+%Note that the effect of both covering and clearing is to increase explainedness for covered/cleared nodes, which indirectly encourages the model to turn an $n$-gram like \ex{keep \gap under wraps} on in order to explain nodes in its vicinity, even supposing its minLPR were relatively low.
 
@@
 To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
-Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$.
-We define $d_1(t)$, the exponential term for $E_1(t)$, as:
+Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to overlapping nodes, \ie turned-on nodes which overlap with our target node $t$in the corpus.
+We define \overlap(t) as:
 \begin{displaymath}
-	d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(o_i)}}
+	\overlap(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(t,o_i)}}
 \end{displaymath}
 
-The effect of overlaps on the explainedness is hyperbolic: small amounts of overlap have little effect, but with significant overlap it becomes prohibitive, effectively forcing one of the nodes to turn off.
+Overlap takes on values in the range 1 to $+\infty$, also defaulting to 1 when no overlaps exist.
+The effect of overlap is hyperbolic: small amounts of overlap have little effect, but nodes with significant overlap will effectively be forced to turn off.
+
+\subsection{Explainedness}
+
+In order to capture the current state of the model and provide an overall explainedness store, we introduce two indicator functions: $I_{on}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
+The objective function maximized by the model is then the explainedness ($expl$) across all the nodes of the lattice, which can be defined in terms of minLPR and the node interaction functions:
+
+\begin{multline}
+expl(t_1,...,t_N) = \prod_{i=1}^{N}{I_{on}(t_i)  C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i) minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
+\end{multline}
+
+When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero.
+When the node is on, its explainedness is the inverse of a fixed cost hyperparameter C, though this cost is increased if it overlaps with other active nodes.
+All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, C can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.
+There is no upper bound on $C$, but empirically, we have found values in the range $[3,6]$ give reasonable results for the languages presented in this paper.
+
+%\subsection{Node explainedness functions}
+
+%The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of maximizing the overall explanatory power of the lattice.
+Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained.
+We define the explainedness of a node in terms of two functions, capturing the impact on surrounding nodes of a node being either off or on.
+When a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence.
+When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged.
+
+%Let $E_{1}$ be the explainedness of a node when it is on (corresponding to an $n$-gram which has been identified as an FS), and $E_{0}$ be the explainedness of a node when it is off.
+We calculate $E_{0}$ based on the inverse of minLPR:
+%\begin{displaymath}
+%E_0(t) = \minLPR(t)^{-d_0(t)}
+%\end{displaymath}
+%and $E_{1}$ based on the inverse of a cost parameter $C$:
+%\begin{displaymath}
+%E_1(t) = C^{-d_1(t)}
+%\end{displaymath}
+%where $d_0$ and $d_1$ are non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section.
+When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
+$E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
+There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ gives reasonable results for the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.
+
+% The values of $d_0$ and $d_1$ are dependent on the context of the node in the lattice as discussed in the next section, but are both 1 when a node is not influenced by other nodes.
 

### 2017-05-12 reviewer_response.txt
Non-discussion TACL revisions

We would like to thank all of our reviewers for their detailed comments. We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlaps, we have had to pick and choose what we  could add. In cases where we did not change the paper, we have added a justification below.

We should mention one change that wasn't prompted by individual reviewer comments: there were clear misinterpretations by our Japanese annotators from the first round with led to overannotation of FS, and since the original submission of the paper we have done another round of annotation. The Japanese results have therefore changed somewhat, and are in fact more consistent with the other languages.

Reviewer A

>In the introduction, the proposed approach is claimed to be "effective,
expandable, and tractable", however, it is not clear how each of these
claims is evaluated in the paper (effective, expandable and tractable). The
approach is also claimed to have the candidates compete for "the best (most
parsimonious) explanation for statistical irregularities due to lexical
affinity", but concepts like parsimony and lexical affinity need to be
defined (what are they, how candidates display them, and how they are
measured, ...).

Our intent is that effectiveness is demonstrated by our main evaluation. Tractability is demonstrated implicitly by the fact that we apply our method to corpora much larger than many of our competitors can handle. We have added more details about this to the paper, though we do not want to belabour the point, since it is not the primary purpose. Our claim of expandability relates to our discussion of future work, however we have added a bit more discussion about exactly how expansions would be added without major changes to the model.

> The paper should explicitly state what the hypotheses are in relation to the
utility functions, particularly in relation to the approach by Brooke et al.
(2015), which is simpler than the proposed approach. Moreover, the
state-of-the-art has several simpler formulations for the identification of
general formulaic sequences of flexible sizes (e.g. Silva et al. 1999 for
contiguous & non-contiguous cases and Villavicencio et al. 2007 for
contiguous cases), and the text should justify why this particular approach
is appealing, and advantageous in relation to the others. The addition of an
error analysis would help highligh these points, helping to clarify the
advantages of the particular approach especially in relation to Brooke et
al.

We have added a new paragraph discussing in particular why our model does better than others, and an qualitative discussion which includes an error analysis.

Note that we looked at Villavicencio et al. 2007, but it is very limited in scope (they only deal with trigrams) and doesn't provide any workable comparison in the context of unrestricted FS extraction beyond ranking with simple association measures, which, as we mention, have already been shown to be inferior to the more sophisticated models we are comparing against here.

>The paper should also discuss the motivation for each of the node
interaction functions for rewarding/penalizing competitive candidates in the
lattice, including how they are expected to contribute to the overall
performance of the approach and if the authors considered alternative
functions or why these in particular, which linguistic intuition they wanted
to capture, why define E0 in terms of the minLPR and E1 of a cost parameter,
why they are introduced in the explainedness as exponents (why not using a
linear dependence, for example. A suggestion for helping the presentation is
for the authors to rewrite E0 and E1 into a single formula that combines the
three measures in a utility function, as it would be easier to explain (how
E0 and E1 compete, under which circumstances each of them wins),
particularly with the  addition of an example. In addition, when
presentating these functions, one problem is that although d0 and d1 are
used to define E0 and E1 in section 3.2, they are only defined in later
sections (sections 3.3.2 and 3.3.3). As a result the discussion appears too
abstract as the functions have not been completely defined yet. There should
be some explanation for their motivation/intuition, as it's not clear what
they are trying to capture, how E0 and E1 would vary for FS and non-FS, etc.
My suggestion is to first introduce and motivate the ideas behind them, and
later define them together. For d1, there is also a difference in the number
of arguments of "oc" in the text (oc(x,y)) and in the definition of d1
(oc(oi)). d0 is defined as a uniform combination of clear and cover, but it
would be helpful to have a discussion of the effects of different weights
for each of them for the different languages.

We have reorganized the presentation of the model and are now providing an explicit objective function, at the same time getting rid of the confusing forward pointers and many of the extra symbols.

In the discussion, we have added some additional explanation of why these particular interaction functions were used, alternatives we could consider, etc.

>In terms of the methodology, a discussion is needed about the motivation for
adopting Brooke et al.'s lexical predictability ratio (LPR), and for the
modifications proposed, such as the use of minLPR instead of the product of
the LPRs and why the focus is on the weakest link (was there any comparison
between the use of minLPR and the product of LPRs, is it done for efficiency
reasons, etc).  Moreover, the construction of the lattice needs to be
explained, including how the nodes relate to one another. For instance, in
figure 2, the solid lines indicate subsumption, but "keep everything under
wraps" is linked with "be keep * under" via a subsumption relation, even
though the latter contains elements that are not in the former (shouldn't it
be an overlap link?).

We have added a bit more to the discussions of LPR, to be more explicit why LPR is a good metric for our lattice. We've also fixed the incorrect relations you mention, which should hopefully resolve the confusion.

>In terms of the evaluation, the distinction between contiguous and gapped
test sets, which are later merged into a single test set per language when
presenting the results, is not helpful. Instead, maintaining the distinction
would help clarify the advantages of the proposed approach in each language,
particularly in relation to the error analysis.

As we note in the paper, adding the distinction between continguous and gapped simply isn't defensible given the lack of positive gapped examples across some of the datasets (since both precision and recall rely on primarily on true positives). We would very much like to present this distinction, but the scores depend primarily on a handful of examples for some of datasets and the results are erratic, they would confuse rather than elucidate, and would also be problematic with respect to statistic significance. However, we have added some additional discussion of gapped phrases to the Discussion section.

>Additionally, for the
contiguous n-grams in these languages a comparison with LocalMaxs could be
done.

Actually that's not possible. LocalMaxs (like DP-seg) does not scale, due to the fact that it needs to calculate counts for every n-gram in the corpus; it is quicker than DP-Seg, but the memory usage is immense for large corpora. We have added a mention of this fact in the paper.

>Moreover, the authors need to add the statistical significance of the
results in tables 2 and 3 as the approaches often differ only in the second
decimal place.

We have added statistical significance information.

>In Table 2, it would be helpful to have also the results for
only the cover function (Lattice-cl-ovr), to determine how much the other
functions contribute.

Added.

>A figure with the top/bottom candidates proposed by
the approach be helpful.

There are no explicit top/bottom candidates in our model, it's not a ranking model and it would be incorrect to present it as such. N-grams could be ranked by the explainedness of their node, of course, but that doesn't properly reflect their overall influence in the model. We do have a new qualitative analysis with random samples from our lexicon.

> Add the list in an appendix for English and explicitly explain the lists for
Croatian and Japanese. How many expressions and how many cases they cover.

We have added some samples for each language and some general statistics for the lexicons of each language. As should be now clear, the lists of expressions generated by the model is far larger than can be included in a paper. We will 
be separately releasing all the lexicons.

> The paper also needs to add a list of existing MWE lexica or lexical
resources with MWEs available to the community (e.g. those listed in the MWE
community website, or available in WordNet or other resources).

We have to demurr on this. Our paper is not about MWEs specifically, we do not use MWE resources to build our model nor to evaluate it, so a focus on available MWE resources seems a significant detour, especially given the space constraints.  It would also be very difficult to do the topic justice, especially given our cross-linguistic interest.

>Stylistically the text would also benefit from a revision that splits
sentences that are too long (there are several throughout the text). For
instance, the last sentence in the first paragraph of the introduction is 9
lines long: 'We present an effective, expand- able, and above all tractable
new approach to com- prehensive multiword lexicon acquisition that aims to
find a middle ground between standard MWE ac- quisition approaches based on
association measures (Ramisch, 2014), and more sophisticated statistical
models (Newman et al., 2012) which fail to scale to the large corpora which
are the main sources of the distributional information in modern NLP
systems.').

We have split up some of the longer sentences.

> Moreover, some passages are copied from Brooke et al. (2015), but lack the
citation, such as:
     *"Other mea- sures specifically designed to address sequences of larger
than two words include: the c-value (Frantzi et al., 2000), a metric
designed for term extraction which weights term frequency by the log length
of the n-gram while penalizing n-grams that appear in frequent larger ones;
and mutual expectation (Dias et al., 1999), which produces a normalized
statistic that reflects how much a candidate phrase resists the omission of
any particular word." (page 2) and
     *"include that of Newman et al. (2012), who used a generative Dirichlet
Process model which jointly creates a linear segmentation of the corpus and
a multiword vocabulary" (page 3)
There are also other instances, and these need to be rephrased.

We have rephrased the relevant parts of the literature review, though the
basic content is unchanged.

> For the annotations, the text mentions 3 annotators, but doesn't specify
whether they were different for each of the 3 languages.

Yes, since they were native (first language) speakers of each of the relevant
languages, it follows that they were different across languages.

> When comparing the
languages, the paper also mentions that "free word order actually results in
more of a ten- dency towards contiguous FS, not less.", but it is unclear
where this is shown.

We've tried to explain this a bit better.

* “accessible by analogy (e.g., glass limb or government ambiguity)” by
analogy with what? Specify and add the original expression

We have made the analogy explicit.

* “define the explainedness of a node in terms of two functions” Which
two functions?

Hopefully this is clearer in the new formulation

* In section 3.2 can the authors explain how two valid but similar FSs would
be treated  (e.g. keep * under wraps/surveillance)?

The only kind of interaction between these nodes involves their shared
n-gram subsequence (keep * under), as described in the example in the paper. We have expanded the example a bit.

* "We also use the concept of hard covering to ad- dress the issue of
pronouns, based on the observation that pronouns often have high LPR
values". This sentence is too vague. Explain using an example.

We've added an example.

* How was the 2/3 threshold for hard covering determined? Why also have soft
covering?

Using performance in the (English) development set, we have made that clearer. Our intention is that the  "keep * under wraps/surveillance" example shows why soft covering is also important, we have added a bit more explanation.

> * "has been turned on, the covering, blocking, or overlap- ping effects of
these other nodes" --> blocking shoud be clearing

Yes, thanks.

> * For the efficiency restrictions explain if other values have been tested
for them. How did they affect the overall performance? A table detailing the
behavior with different values would be helpful.

We've added a bit more detail, though not as much as you're asking for.

> * "which was roughly the same size (in terms of token count) as the English
corpus" specify which English corpus

The ICWSM. We've added that.

> * In Table 1 the values are less than 2000 (for ICWSM) and 1000 for the
other corpora. Add also the initial numbers for each type of FS/non-FS.

As we mention in the text, to improve the reliability of our evaluation we drop instances where just one annotator tagged as FS. This obviously results in test sets that are less than the original sample size. This should now be clearer.

Reviewer B

> Assuming that the solution is indeed scalable and
empirically viable -- I am wondering if the same idea could be used in the
context of other tasks (morphological composition in morphological lattices,
preferred expressions in lattices of proposed machine translations, etc). It
would be nice if the author could comment on the applicability of the
technical solution in other domains (if there is any).

This is interesting, and so we've added a discussion of the morphology idea to the paper (The short answer is yes).

>In the case of syntax, much research in theoretical linguistics and in
language technology has proposed the idea that idiomatic expressions (of
which MWEs are a special case) are the rule, rather than the exception, in
NL grammar. Among the theoretical proposal one can find versions of
Construction Grammar (Goldberg 1996) where language knowledge is composed of
complete constructions, rather than primitive units (words) and in
technological proposals one can find the idea of Data-Oriented Parsing
(Remko Scha, Rens Bod), wherein each syntactic subtree (with potential slots
for substitution) is an FS-like element that can potentially be used and
reused for analysis and generation. And so: while the relation of the
proposed FS to existing theories of strongly lexicalized fixed expressions
on the one end is clear, it is unclear what is the relation  larger
idiomatic syntactic constructions with lexicalized or unlexicalized slots on
the other end -- and this relation should be made clear, for the work to be
properly situated.

Note that we are not ourselves proposing FS, we are borrowing the theory behind FS from the work of Wray (2002;2008), who includes an extremely thorough discussion of its relationship to other linguistic theories (Chapter 7 of the 2008
book in particular), including Construction Grammar. We have added a bit more detail to our introduction of FS to make it clear that, yes, most "constructions" are FS, and we have added constructions to Figure 1. However, ultimately
this is a technical paper, and we are limited in the space we can dedicate to theoretical concerns.

> The case of morphology is far less clear, however it is equally important,
and it has to do with the basic question of what is the unit that constructs
the FS (or the lattices themselves in empirical terms). Are these words?
morphemes? lemmas? POS? inflections? In the case  of words, what is the
relation of inflected sequences forms / inflected idioms (kicked his bucket
vs kicked her bucket, for instance) -- are they the same? related?
overalapping? subsumed?. As it stands, the discussion of morphology comes
out only later as an afterthought -- where the construction of the lattice
in Japanese (in the evaluation section) involves some morphological
segmentation whereas the lattice construction for the other languages
doesn't. It is thus unclear if the algorithm finds sequences that are of the
same type, or are comparable for that matter, across those languages. The
selected FS may be incomparable in terms of effective length (morpheme
sequences tend to be longer), the status of function words vs. inflection in
FS, and so on. The authors should put forth clearly what is the status of
morphology inside their general theory (and in terms of their regular
expressions), and then later revisit the empirical ramifications of their
decision -- for instance what happens when moving between typologically
different languages.

We have added a bit more to both the introduction of FS as well as the discussion that addresses this point, albeit briefly. Ultimately, in all three languages we are tokenizing and lemmatizing, and building our FS from the result: infected forms will map to one node in the lattice. However, this is not a theoretical choice, but a practical one. It is clear in that to understand characterize FS properly one must go beyond lemmatized words, for instance representing the that there is inflectional flexiblity in the verb "kick" in "kick the bucket" but not the noun "bucket"; we might like to be able to represent this in our model for English and Croatian, but considering mophological segmentation in these languages creates a blow up in complexity with marginal benefits, since a final FS lexicon with correct fixed forms or marking for variability could be derived post hoc based on corpus usage. With Japanese, however, due to the lack of word boundaries morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal. Given that many of the case markers of Japanese correspond to prepositions in European languages (or the possesive marker in English), the actually difference in generated FS is fairly minor, except for the extra overhead of word segmentation in Japanese that is provided by word boundaries in English (in Wray's theory, words are FS by default)

>The author discuss at length the method, the construction of the lattice,
and possible relation between arcs (covering clearing and overlapping) and
their related scores. The objective function however and the respective
optimisation algorithm are discussed informally in passing. I would much
prefer a more precise formalisation of the objective function and greedy
algorithm, possibly with a running example of several states of progress of
the algorithm over a sample lattice. This would also help to clarify what
"locality properties" are at play here, which justify a greedy solution that
is locally optimised. As a more general note, I think it should be made
clear if the target of the lattice construction is a single lattice for the
entire text, optimized at once, or multiple lattices, reflecting different
aspects of the vocabulary, optimized separately.  As a minor note, there are
two many forward references in the text, IMO, which hinder
understandability. Example "where d1 and d2 are ... as detailed in the next
section". I would prefer the details closer to where they are relevant.

We have reorganized the expanation of the method to remove forward references, and have provided an explict objective function and algorithm. We decided, though, that a full example of the optimization algorithm involved too much overhead with only modest explanatory benefits.

By "text", you mean corpus, right? It is hopefully clear that the algorithm 
works at the level of all n-grams for the corpus, and not texts within the

corpus (this is what makes the model practical relative to token-level models
like DP-seg); the nodes of the lattice are n-gram types, not tokens. As it 
happens, most nodes are connected to most other nodes by some pathway in 
the lattice, but there are nodes (mostly individual bigrams) which do not, 
and thus are not part of the main lattice.

> It is unclear to me why comparing the collected lexicon using the proposed
method to a sample set of ngrams that respond to a certain frequency
threashold is a sound comparison-- isnt the frequency threashold just a
simpler and less sophisticated baseline for MWE extraction? It appears that
you use this method not as a baseline, but as an actual method to extract
gold standard for comparison with your method. I understand that others have
used such evaluation methods before -- but I would need much more convincing
in order to accept the claim of efficacy. If I misunderstood, and you do not
use it as a gold for comparison, or you use a different gold, please
clarify.

We are not entirely sure we are intepreting your concern correctly. If the reviewer believes that we are using high-frequency n-grams directly as a gold standard (i.e. we assume that high frequency n-grams are FS simply by virtue of their high frequency), then you have definitely misunderstood: this should be clear given the discussion of the annotation process, where we taken the n-grams and annotated them as being FS or not. To make this absolutely clear, we have included frequency as a baseline association score. It is poor, but obviously would be unbeatable if our gold standard was built based simply on frequency.

A more subtle issue is that using frequency-filtered n-grams as the sampling pool for our FS gold standard means that there are FS in the corpus that cannot possibilty be considered in the evaluation because they do not appear sufficiently. This is true, and unavoidable in this evaluation setup. As discussed in Brooke et al. 2015, sampling from frequent n-grams in the corpus brings with it a number of benefits: in particular, the test set reflects the variety of FS that appear throughout the entire corpus (many of which would not appear in any existing lexicon or in a small sample of texts), annotators can look at variety of examples to make an judgement, and (most importantly) it is possible to calculate a proper F-score. The trade-off, however, is that there needs to be some initial filtering of the sample so that annotation process is not "finding a needle in the haystack" as it would be if you considered all n-grams in the corpus. As we discuss in 3.1, we investigated coverage in an existing English MWE annotated corpus using n-grams from the ICWSM after applying frequency cutoffs and found that type coverage is quite good (token coverage is even better, of course); that is, we are not losing very many FS with our filtering, at least not ones that occur across corpora of the similar genre (both are social media corpora). With a large corpus and an appropriately low frequency cutoff, we believe that annotations of frequency filtered n-gram samples is a reasonable way to solve what is without a doubt a very challenging evaluation problem. We have added a slightly longer justification of the evaluation method to the paper.

Reviewer C:

> Where I had trouble was with the details of the model. First of all, much ofit seemed to be ad hoc; even accepting the notion of LPR from prior work,
there are many heuristic (or at least not obviously natural) choices made to
operationalize the general lattice idea mathematically. Second, even if the
model is reasonable, it is not entirely clear how the different parts fit
together into an optimization problem. There is mention of a parameter C;
and there is a notion of nodes being activated or not (I don’t think
notation is introduced for these binary variables, though it would be
appropriate). Are these the only things that have to be tuned? Is the
calculation of explainedness deterministic based on these? There is a greedy
search to optimize explainedness of the nodes in the lattice, subject to
various heuristics. Presenting a formal algorithm for the optimization may
clarify things considerably.

We have reorganized the method section and added an explicit objective function, which should help with some of your problems. In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g. the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have tried to make this more clear. We have also included psuedocode for optimization algorithm. With regards to the ad hoc parts of the model, we have added a discussion separating the core aspects of the model from some of the more ad hoc choices made in the particular instantions of component functions (such as clearing), making it clear that we believe these can potentially be improved on (both in terms of performance as well as mathematical elegance), and that our primary purpose here is to show that overall architecture of the model is a promising one.

> I think it would also be worth discussing how the lattice model relates back to the cognitive/psychological literature. Would you predict (or are you
aware of any evidence) that node interactions such as covering, clearing,
and overlapping have an analogue in human language processing? Do any of the
design decisions intentionally sacrifice cognitive plausibility for
engineering reasons?

In general, we did not consider cognitive plausibility when creating the model, and we are certainly making no claims as such. For starters, our model makes use of more data than a human being could possibly read in a lifetime; it is clear we identify FS with far less evidence than our model requires. With space, we could discuss our model in the context of the more cognative aspects of the theory of formulaic sequences as proposed by Wray, but given that this wasn't a focus in the development of the model, we think it is really too much of a digression to justify.

> - After the equation for LPR, it would be good to give the intuition:
choosing a context span such that w_i is more likely given its context words
than its context POS tags.

This was removed from an earlier draft for space, and we've added back in.

>- Inter-annotator agreement is surprisingly high. Could you elaborate on
Wray’s criteria for FS that were applied by annotators?

Your surprise about the the Kappa being high is based on a misunderstanding: the kappa number reported in the table is after filtering to remove borderline cases (i.e. it is the kappa for the final test set, not the original sampling). To avoid confusion, we've added the original kappa score which is quite a bit lower. Your intution is correct that there is significant subjectivity to FS identification (more so than MWE annotation), and as such we would never rely on a single annotator for building a FS test set. We have not added more information about Wray's criteria; though it provide a starting point for annotation, more relevant to achieving reasonable agreement are the specific annotation guidelines which we created. Presenting them in the paper would be too much of a digression, but we promise to make them public.

> - I would like to see qualitative analysis of the sequences that were
identified as formulaic (or not) by annotators/the method. E.g.: How many of
them are syntactic constituents? Are there a wide variety of grammatical
kinds of expressions? Are high-frequency as well as low-frequency sequences
detected? What is the distribution in terms of length? What kinds of gapped
sequences are there? It would be nice to see some examples.

In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the infromation you ask for.

> - Related to the previous point: While noting the distinction between FS and
MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
apart from proper names should count as FS, right?

Do you mean as a way of evaluating different systems built on the same corpus, or just to get a sense of coverage more generally? One central problem with using recall for evaluation is that in order to make it fair, there must be some control of the size of the lexicon. Neither our system nor our best performing competitors are ranking models, none of them offer an easy or fair way to simply take the best N words and look at recall. And even if they did, there's other kinds of biases that would come into play: for instance, PMI and similar metrics do well with rare terms that correspond well to the MWE lexicon of WordNet, for instance, which (at the type level) is dominated by certain kinds of terminology (biomedical terms, particularly) which are not really used outside a very specific community. This relates to a more fundamental problem with the idea of using recall in external lexicons as any kind of useful measure: we could not expect any particular corpus (even a very large one) to do justice to the full range of FS/MWE for a language, since most of which appear regularly only within specific genres. For example, we could not expect to build a good lexicon of English verb-particle constructions from a biomedical corpus, because many are too informal to be appropriate for that genre (e.g. "mess up"). We have added more discussion of the genre-specificity of FS to the paper, as part of the qualitative analysis

Though it perhaps does not directly address your comment (since it doesn't involve an external MWE dataset), we were nonetheless inspired to include an analysis of the recall of MWE vs. non-MWE FS in the context of our existing test sets.

>Typographical issues:

- The ovals in Figure 1 and the edges in Figure 2 show up for me on screen
(OS X Preview) but not when printed.
- “pairing down” -> paring down
- “what is typically considered MWE” -> are…MWEs
- “could be useful addition” -> *a* useful addition
- "When the minLPR metric is 1 (crresponding to the case of the syntactic
content predicting": content -> context?

 We have addressed these typos, thanks.

### 2017-05-12 tacl.tex
Non-discussion TACL revisions

@@
 \usepackage[pdftex]{graphicx}
+\usepackage{algorithm,algorithmicx}
+\usepackage[noend]{algpseudocode}
 \makeatletter
@@
 \newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}
+\newcommand{\algref}[2][]{Algorithm#1~\ref{#2}\xspace}
 
@@
 The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work.
-We present an effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition that aims to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which fail to scale to the large corpora which are the main sources of the distributional information in modern NLP systems.
+Here, we present an effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition.
+Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which do not scale to the large corpora, the main source of the distributional information in modern NLP systems.
 
@@
 
-A central challenge in building comprehensive multiword lexicons is pairing down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language: allowing for diversity creates significant redundancy among statistically promising candidates.
+A central challenge in building comprehensive multiword lexicons is paring down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language: allowing for diversity creates significant redundancy among statistically promising candidates.
 The lattice model proposed here addresses this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity.
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.
-Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
+Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.
+Note that the FS framework allows for individual morphemes be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.
 
@@
 Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) FS such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \dotts's weight in gold}, fall under the FS umbrella.
-Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb} or \ex{government ambiguity}).
+Another reason to introduce a different terminology is that there are classes of phrases which are typically considered MWEs that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb}, analogous to \ex{wooden leg}).
 Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
-\figref{fig:terminology} shows the conception of the relationship between FS, MWE, and (multiword) named entities that we assume for this paper.
+\figref{fig:terminology} shows the conception of the relationship between FS, (multiword) constructions, MWE, and (multiword) named entities that we assume for this paper.
 
 \begin{figure}[!t]
-\center{\includegraphics[width=0.3\textwidth]{FS_diagram_1.pdf}}
+\center{\includegraphics[width=0.3\textwidth]{FS_diagram_1_2.pdf}}
 \caption{Multiword Terminology}
@@
 Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
-Other measures specifically designed to address sequences of larger than two words include: the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones; and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word.
+Another measure which addresses sequences of longer than two words is the $c$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones.
+Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word.
 Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
@@
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
-Beyond association measures, other general unsupervised approaches to the multiword unit identification include that of \newcite{Newman12}, who used a generative Dirichlet Process model which jointly creates a linear segmentation of the corpus and a multiword vocabulary of keyphrases.
+An example of an unsupervised approach which does not use association measures, \newcite{Newman12} extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
 
 Other research in MWEs has tended to be rather focused on particular syntactic patterns such as verb-noun combinations \cite{Fazly09}.
-The work of \newcite{Schneider14b} is a rare example of a comprehensive token-level MWE identification system which distinguishes a full range of MWE sequences in the English Web Treebank, including those involving gaps, using a supervised sequence tagging model.
-Schneider et \al make use of existing manual lexical resources and note that an (unsupervised) automatic lexical resource could be useful addition to the model, although attempts to do so have achieved mixed success \cite{Riedl16}.
+The system of \newcite{Schneider14b} distinguishes a full range of MWE sequences in the English Web Treebank, including gapped expressions, using a supervised sequence tagging model.
+Though in theory automatic lexical resources could be a useful addition to the Schneider et \al model, which uses only manual lexical resources, attempts to do so have achieved mixed success \cite{Riedl16}.
 
@@
 We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics.
-%Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
+Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
 
@@
 Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link.
-For example, in the case of \ex{be keep \gap under}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.
+For example, in the case of \ex{be keep \gap under wraps}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under} or \ex{under} and \ex{wraps}, but minLPR is focused on the weaker relationship between \ex{be} and the rest of the phrase.
+This makes it particularly appropriate measure for use in a lattice model of completing $n$-grams, where the choice of \ex{be keep \gap under wraps} versus {keep \gap under wraps} should be based exactly on the extent to which \ex{be} is an essential part of the phrase; the other affinities are, in effect, irrelevant, because they occur in the smaller $n$-gram as well.
 
@@
 This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice.
-Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant majority of the counts of a lower node corresponding to the higher node) works well.
-We also use the concept of hard covering to address the issue of pronouns, based on the observation that pronouns often have high LPR values \cite{Brooke15b}.
+Of course, a threshold for hard covering must be chosen: during development we found that a ratio of $2/3$ (corresponding to a significant majority of the counts of a lower node corresponding to the higher node) worked well.
+We also use the concept of hard covering to address the issue of pronouns, based on the observation that specific pronouns often have high LPR values due to pragmatic biases \cite{Brooke15b}; for instance, private state verbs like \ex{feel} tend to have first person singular subjects.
 In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to limit FS with pronouns without excluding them entirely: they are included only in cases where they are definitively formulaic.
@@
 \termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}.
-This is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
+For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of\ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
+If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy.
+This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
 Then, the $\cover(t)$ score for a covered node $t$ is:
@@
 Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR.
-\termdef{Clearing} does this by changing the $E_0$ of nodes higher in the lattice when a lower node is turned-on.
+\termdef{Clearing} does this by changing the increasing the explainedness of nodes higher in the lattice when a lower node is turned-on.
 The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
@@
 
-In order to capture the current state of the model and provide an overall explainedness store, we introduce two indicator functions: $I_{on}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
+In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{on}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
 The objective function maximized by the model is then the explainedness ($expl$) across all the nodes of the lattice, which can be defined in terms of minLPR and the node interaction functions:
@@
 %where $d_0$ and $d_1$ are non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section.
-When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
+When the minLPR metric is 1 (corresponding to the case of the syntactic context predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$.
 $E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS.
@@
 \subsection{Optimization}
+
+\begin{algorithm}
+	\caption{Optimization algorithm.
+$N$ is an ordered list of the nodes in the lattice.
+Nodes (designated by $n$) contain pointers to the nodes immediately linked to them the lattice.
+States (designated by $s$) indicate whether each node is $ON$ or $OFF$.
+Explainedness values are indicated by $e$.}
+	\label{alg:opt}
+	\begin{algorithmic}
+
+	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
+		\State $s_{start} \gets \Call{SetNode}{s, n, ON}$
+		\State $Q \gets \Call{EmptyQueue}{\null}$
+		\State $e_{best} \gets 0$
+		\State $s_{best} \gets NULL$
+		\State \Call{Push}{Q,$s_{start}$}
+		\Repeat
+			\State $s_{curr} \gets \Call{Pop}{Q}$
+			\State $e_{curr} \gets \Call{CalcExpl}{s_{curr}, N_{af\hspace{-0.1em}f}}$
+			\For{$n_{rev} \textrm{ in } N_{rev}$}
+					\State $s_{new} \gets \Call{SetNode}{s_{curr}, OFF}$
+					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
+					\If{$ e_{new} > e_{curr}$}
+
+					\State \Call{Push}{$Q, s_{new}$}
+					\If{$e_{new} > e_{best}}$:
+							\State $e_{best} \gets e_{new}$
+							\State $s_{best} \gets s_{new}$
+					\EndIf
+					\EndIf
+				\EndFor
+		\Until{\Call{IsEmpty}{Q}}
+	\State \Return $s_{best}$
+	\EndFunction
+\State
+\State \Call{FrequencySortReverse}{$N$}
+\State $s \gets \Call{InitializeAllOff}{N}$
+\Repeat
+	\State $Changed \gets FALSE$
+		\For{$n \textrm{ in } N$}
+		\State $N_{rev} \gets \Call{GetRelevant}{n,N}$
+		\State $N_{af\hspace{-0.1em}f} \gets \Call{GetAffected}{N_{rev},N}$
+		\State $s_{new} \gets \Call{LocalOpt}{s,n,N_{rev},N_{af\hspace{-0.1em}f}}$
+		\If{$s_{new} \neq s$}
+			\State $s \gets s_{new}$
+			\State $Changed \gets TRUE$
+		\EndIf
+		\EndFor
+\Until{$!Changed$}
+\State \Return $s$
+
+\end{algorithmic}
+
+\end{algorithm}
 
@@
 Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node.
-If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, blocking, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
+If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, clearing, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated.
 Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration.
-Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node need be considered.
-Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified, and then a greedy search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and at each step turning off the node (if any) which most increases overall explainedness.
+Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node in the Lattice need be considered.
+Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified.
+Next, a search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and then iteratively considering new states with one relevant node turned off; the search continues as long as there is an improvement in explainedness.
+Since the node interactions are roughly cumulative in their effects, this approach will generally identify the optimal state without the need for an exhaustive search.
+The details of the algorithm are given as Algorithm 1.%\algref{alg:opt}.
 
-In practice, we apply the following efficiency restrictions, which significantly reduce the runtime without sacrificing quality (based on development set testing):
+Omitted from Algorithm 1 for clarity are various low-level efficiencies which prevent the algorithm from reconsidering states already checked or from recalculating the explainedness of nodes when unnecessary.
+We also apply the following efficiency restrictions, which significantly reduce the runtime of the algorithm.
+In each case, more extreme (less efficient) values were individually tested using a development set and found to provide no benefit in terms of the quality of the output lexicon:
 \begin{compactitem}
 \item We limit the total number of relevant nodes to 5.
-When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the change in explainedness across possible configurations of the target and candidate node considered in isolation;
+When there are more than 5 nodes turned on in the vicinity of the target node, the most relevant nodes are selected by ranking candidates by the absolute difference in explainedness across possible configurations of the target and candidate node considered in isolation;
 \item To avoid having to deal with storing and processing trivial overlaps, we exclude overlaps with a count of less than 5 from our lattice;
-\item Many nodes have a minLPR which is slighlty larger than 1.
+\item Many nodes have a minLPR which is slightly larger than 1 (the lowest possible value).
 There is very little chance these nodes will be activated by the algorithm, and so after applying hard covering, we do not consider activating nodes with $\minLPR < 2$.
@@
 \newcite{Brooke15b} introduced a method for evaluating FS extraction without a reference lexicon or direct annotation of the output of a model.
-Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model.
+Instead, $n$-grams are sampled after applying the frequency threshold and then annotated as being either an FS or not.
+Benefits to this as compared to competing evaluation include replicability, the diversity of FS, and the ability to calculate a true F-score.
 We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
-
-%.
-One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to an task with a known subjective component, is that it is quite sensible to simply discard borderline cases
 
@@
  \begin{center}
-   \begin{tabular}{lc@{\,\,\,}cc@{\,\,\,}c@{\,\,\,}c}
+   \begin{tabular}{lc@{\,\,\,}cc@{\,\,\,}cc@{\,\,\,}c}
 
        \toprule
-       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \multirow{2}{*}{$\kappa$}\\
-       \cmidrule(lr){2-3}\cmidrule(lr){4-5}
-			& FS & non-FS & FS & non-FS &  \\
+       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \multicolumn{2}{c}{$\kappa$} \\ %\multirow{2}{*}{$\kappa$}\\
+       \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}
+			& FS & non-FS & FS & non-FS & Pre & Post \\
 			 \midrule
-			ICWSM    & 169  & 702 & 29 & 916 & 0.84 \\
-			BNC      & \z49 & 403 & \z8& 475 & 0.84 \\
-			Croatian & \z64 & 382 & 11 & 456 & 0.87 \\
-			Japanese & 124  & 286 & 36 & 341 & 0.81\\
+			ICWSM    & 169  & 702 & 29 & 916 &0.52 &0.84 \\
+			BNC      & \z49 & 403 & \z8& 475 &0.51 &0.84 \\
+			Croatian & \z64 & 382 & 11 & 456 & 0.58 &0.87 \\
+			Japanese & 102  & 337 & \z9 & 438 & 0.49 &0.82\\
        \bottomrule
@@
 Other than the inclusion of new languages, our test sets differ from \newcite{Brooke15b} in two ways.
-First, instead of relying on strict majority annotation, we entirely excluded $n$-grams which just one annotator marked as FS, improving the reliability of evaluation at the cost of some representativeness.
-Second, for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
-The rationale is that the number of positive gapped examples was too low (particularly for the BNC and the Croatian corpus) to provide a reliable independent F-score (see further discussion in \secref{sec:discussion}).
-Statistics for the four test sets are given in \tabref{tab:stats}.
+One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness.
+To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
+\tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Cohen's Kappa scores before (Pre) and after (Post).
+The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
+The rationale is that the number of positive gapped examples is too low to provide a reliable independent F-score (see further discussion in \secref{sec:discussion}).
 
@@
           \midrule 
-PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.23& 0.09 & 0.15 \\ 
-minLPRrank & 0.49& 0.31 & 0.39 & & 0.25& 0.44 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.51 & 0.14 & 0.22 \\
+Countrank & 0.13& 0.09 & 0.10 && 0.08 & 0.14 & 0.10 && 0.10 & 0.16 & 0.12 && 0.11 & 0.06 & 0.08 \\
+PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.18& 0.08 & 0.11 \\ 
+minLPRrank & 0.49& 0.31 & 0.39 & & 0.25& 0.44 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.47 & 0.21 & 0.29 \\
 
-LPR-seg  &0.53 & 0.42 & 0.47 && 0.37 & 0.44 & 0.40 & & 0.41 & 0.47  & 0.43 &  & 0.77 & 0.34 & 0.47 \\ 
+LPR-seg  &0.53 & 0.42 & 0.47 && 0.37 & 0.44 & 0.40 & & 0.41 & 0.47  & 0.43 &  & 0.69 & 0.43 & 0.53 \\ 
   \midrule
 
-	Lattice \emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.74 & 0.39 & 0.51 \\
+	Lattice \emph{$-$cl$-$ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\
 
-	Lattice \emph{$-$ovr} & 0.52& \bf{0.51} & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.69 & \bf{0.51} & \bf{0.58} \\
+	Lattice \emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\
 
-				Lattice & \bf{0.67} & 0.43 & \bf{0.52} & & \bf{0.40}& 0.60 & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.87} & 0.39 & 0.53 \\ 
+	Lattice \emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
+
+				Lattice & \bf{0.67} & 0.43 & \bf{0.52} & & \bf{0.40}& \bf{0.60} & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
             \bottomrule
@@
  \end{tabular}
-  \caption{ Results of FS identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
+  \caption{ Results of FS identification in various test sets; Countrank= lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
 Bold is best in column.}
@@
  Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
-For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
+For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; neither of these methods scale to the larger corpora.\footnote{DP-seg is far too slow, and LocalMaxs, though faster, calculates counts for all $n$-grams in the corpus, with would require terabytes of RAM for the large corpora.}.
+Because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
 All comparison approaches have themselves been previously compared against a wide range of association measures.
-As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI.
-For each of these two association measures we build a lexicon equal to the size of the lexicon produced by our model.
+As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI and raw frequency.
+For each of these association measures we rank all $n$-grams above the frequency threshold and build a lexicon equal to the size of the lexicon produced by our model.
 %All comparisons here are subject to the same $n$-gram frequency threshold as the main model, since the content of our test sets are also linked to this threshold.
@@
 The result is that there are many more FS for Japanese: precision is high, and recall is relatively low.
-Under these conditions, methods which increase precision at the cost of recall will have worse F-score, which explains why the full lattice model is not the best in that case.
 Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus.
@@
 
-We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the potential gaps in FS would help with these languages.
-We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less.
+We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the handling of gaps would help with identifying FS in these languages.
+We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less, a fact that is reflected in our test sets (the ratio between gapped and ungapped FS) as well as the content of the lexicon.
 Strikingly rare in Croatian, in particular, are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English whose fixed-word-order constraints often keep elements of an FS distant from each other.
@@
 
+Though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons for agglutinative languages.
+In particular, character or phoneme $n$-grams could compete in an identically structured lattice (though without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use, as the denominator of the ratio, phonological predictably (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
+It is likely, though, that further modifications would be necessary to target morphological phenomena, and we leave this for future work.
+
 \section{Conclusion}

### 2017-05-23 reviewer_response.txt

@@
 We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlaps, we have had to pick and choose what we could add.
-In cases where we did not change the paper, we have added a justification below.
+In cases where we did not change the paper, threre is a justification below.
 
@@
 
-We have added a new paragraph discussing in particular why our model does better than others, and an qualitative discussion which includes an error analysis.
+We have added a new paragraph contrasting our method to other algorithms, and an qualitative discussion which doubles as an error analysis.
 
@@
 
-In the discussion, we have added some additional explanation of why these particular interaction functions were used, alternatives we could consider, etc.
+We hope that the general purpose of each interaction in terms of the way that it inhibits other nodes is clear.
+We have added a bit more detail about the choice of the clearing function to both that section as well as the discussion.
 
@@
 We would very much like to present this distinction, but the scores depend primarily on a handful of examples for some of datasets and the results are erratic, they would confuse rather than elucidate, and would also be problematic with respect to statistic significance.
-However, we have added some additional discussion of gapped phrases to the Discussion section.
 
@@
 
-We have rephrased the relevant parts of the literature review, though the
-basic content is unchanged.
+We have rephrased the relevant parts of the literature review, though the basic content is unchanged.
 
@@
 
-Yes, since they were native (first language) speakers of each of the relevant
-languages, it follows that they were different across languages.
+Yes, since they were native (first language) speakers of each of the relevant languages, it follows that they were different across languages.
 
@@
 
-The only kind of interaction between these nodes involves their shared
-n-gram subsequence (keep * under), as described in the example in the paper. We have expanded the example a bit.
+The only kind of interaction between these nodes involves their shared n-gram subsequence (keep * under), as described in the example in the paper. We have expanded the example a bit.
 
@@
 
-We've added a bit more detail, though not as much as you're asking for.
+We've added a bit more detail, though perhaps not as much as you're asking for.
 
@@
 
-We have added a bit more to both the introduction of FS as well as the discussion that addresses this point, albeit briefly.
-Ultimately, in all three languages we are tokenizing and lemmatizing, and building our FS from the result: infected forms will map to one node in the lattice.
+We have added a bit more to both the introduction of FS as well as a paragraph in the discussion that addresses this point.
+Ultimately, in all three languages we are tokenizing and lemmatizing using standards for each language, and building our FS from the result.
 However, this is not a theoretical choice, but a practical one.
-It is clear in that to understand characterize FS properly one must go beyond lemmatized words, for instance representing the that there is inflectional flexiblity in the verb "kick" in "kick the bucket" but not the noun "bucket"; we might like to be able to represent this in our model for English and Croatian, but considering mophological segmentation in these languages creates a blow up in complexity with marginal benefits, since a final FS lexicon with correct fixed forms or marking for variability could be derived post hoc based on corpus usage.
-With Japanese, however, due to the lack of word boundaries morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal.
-Given that many of the case markers of Japanese correspond to prepositions in European languages (or the possesive marker in English), the actually difference in generated FS is fairly minor, except for the extra overhead of word segmentation in Japanese that is provided by word boundaries in English (in Wray's theory, words are FS by default)
+With Japanese, due to the lack of word boundaries, morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal.
+Given that many of the case markers of Japanese correspond to prepositions in European languages (or the possesive marker in English), the actual difference in generated FS is fairly minor, except for the extra overhead of word segmentation in Japanese that is provided by word boundaries in English (in Wray's theory, most words would be FS by default).
 
@@
 In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g.
-the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have tried to make this more clear.
-We have also included psuedocode for optimization algorithm.
+the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have a included psuedocode for optimization algorithm.
 With regards to the ad hoc parts of the model, we have added a discussion separating the core aspects of the model from some of the more ad hoc choices made in the particular instantions of component functions (such as clearing), making it clear that we believe these can potentially be improved on (both in terms of performance as well as mathematical elegance), and that our primary purpose here is to show that overall architecture of the model is a promising one.
@@
 In general, we did not consider cognitive plausibility when creating the model, and we are certainly making no claims as such.
-For starters, our model makes use of more data than a human being could possibly read in a lifetime; it is clear we identify FS with far less evidence than our model requires.
+For starters, our model makes use of more data than a human being could possibly read in a lifetime, it is clear humans identify FS with far less evidence than our model requires.
 With space, we could discuss our model in the context of the more cognative aspects of the theory of formulaic sequences as proposed by Wray, but given that this wasn't a focus in the development of the model, we think it is really too much of a digression to justify.
@@
 
-In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the infromation you ask for.
+In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the information you ask for (implicitly if not explicitly).
 
@@
 "mess up").
-We have added more discussion of the genre-specificity of FS to the paper, as part of the qualitative analysis
+We have added more discussion of the corpus-specificity of FS to the paper, as part of the qualitative analysis.
 
-Though it perhaps does not directly address your comment (since it doesn't involve an external MWE dataset), we were nonetheless inspired to include an analysis of the recall of MWE vs.
+Though it perhaps does not directly address your comment (since it doesn't involve an external MWE dataset), we were nonetheless inspired by your comment to include an analysis of the recall of MWE vs.
 non-MWE FS in the context of our existing test sets.

### 2017-05-23 tacl.tex

@@
 \usepackage[noend]{algpseudocode}
+%\usepackage{luatexja-fontspec}
+%\setmainjfont{MS Mincho} % \mcfamily
+%\setsansjfont{MS Gothic} % \gtfamily
+%\usepackage{xeCJK}
+%\setCJKmainfont{MS Mincho} % for \rmfamily
+%\setCJKsansfont{MS Gothic} % for \sffamily
+\usepackage{CJKutf8}
 \makeatletter
@@
 \newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}
-\newcommand{\algref}[2][]{Algorithm#1~\ref{#2}\xspace}
+%\newcommand{\algref}[2][]{Algorithm#1~\ref{#2}\xspace}
 
@@
 Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs.
+Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.
 
@@
 $N$ is an ordered list of the nodes in the lattice.
-Nodes (designated by $n$) contain pointers to the nodes immediately linked to them the lattice.
+Nodes (designated by $n$) contain pointers to the nodes immediately linked to them in the lattice.
 States (designated by $s$) indicate whether each node is $ON$ or $OFF$.
@@
 	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
-		\State $s_{start} \gets \Call{SetNode}{s, n, ON}$
+		\State $s_{start} \gets \Call{Set}{s, n, ON}$
 		\State $Q \gets \Call{EmptyQueue}{\null}$
@@
 			\For{$n_{rev} \textrm{ in } N_{rev}$}
-					\State $s_{new} \gets \Call{SetNode}{s_{curr}, OFF}$
+					\State $s_{new} \gets \Call{Set}{s_{curr},n_{rev}, OFF}$
 					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
@@
 \Until{$!Changed$}
-\State \Return $s$
 
@@
 The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice.
-Fortunately, though most of the nodes in the lattice are part of a single main connected component, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
+Fortunately, though most of the nodes in the lattice are part of a single connected graph, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions.
 The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration).
@@
 Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration.
-Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node in the Lattice need be considered.
+Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node in the lattice need be considered.
 Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified.
@@
 
-	Lattice \emph{$-$cl$-$ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\
+	Lattice\emph{$-$cl,ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\
 
-	Lattice \emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\
+	Lattice\emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\
 
-	Lattice \emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
+	Lattice\emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
 
@@
 Generally, clearing and overlap node interactions provide a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
+When only covering is used, the results are very similar to \newcite{Brooke15b}, which is unsurprising given the extent to which decomposition and covering are related.
 The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
@@
 
-Though the results across the four corpora are reasonably similar with respect to overall F-score, there are significant discrepancies.
-By using the UNIDIC morpheme representation as the base unit for Japanese, the model is doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
-The result is that there are many more FS for Japanese: precision is high, and recall is relatively low.
-Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus.
+\begin{table*}[!bt]
+
+ \begin{center}
+ \begin{tabular}{lccccccc}
+\hline
+& & & & \multicolumn{4}{c}{\bf{By Length (\%) }} \\
+       \cmidrule(lr){5-8}	
+\bf{Lexicon} & \bf{Size} & \bf{POS types} & \bf{Gapped} (\%) & \bf{2} & \bf{3} & \bf{4}  & \bf{5+} \\ 
+\hline
+English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
+English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & 7.7 \\
+Croatian & 172k & 6.7k & 7.9& 55.0& 31.4 & 10.3 & 3.2 \\
+Japanese & 218k &  29.4k &7.9& 39.5 & 31.1& 16.8 & 12.6 \\
+\hline
+\end{tabular}
+  \caption{Statistics for the lexicons created by our lattice method}
+	 \label{tab:lexstats}
+
+ \end{center}
+
+ \end{table*}
+
+Though the results across the four corpora are reasonably similar with respect to overall F-score, there are some discrepancies.
+By using the standard UNIDIC morpheme representation as the base unit for Japanese, the model ends up doing an extra layer of FS identification, one which is provided by word boundaries in the other languages.
+The result is that there are relatively more FS for Japanese: precision is high, and recall is comparably low.
+Importantly, the initial $n$-gram statistics derived from corpus actually reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus.
 One idea for future work is to automatically adapt to the input language/corpus in order to ensure a good balance between precision and recall.
 
-At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10.
-This might be resolved by increasing the $n$-gram threshold, or simply avoiding small corpora, but for some applications it may be useful to build comprehensive FS lexicons even in relatively low resource situations.
-One idea we are pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.
-
-There is one other more general explanation for the precision/recall imbalances we see across the four corpora: both the BNC and the Croatian corpus are composed primarily of published texts written by professional writers, particularly news.
-The ICWSM corpus and the Japanese corpus, on the other hand, are mostly blogs and web pages.
-Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, appear almost exclusively in relatively informal genres.
-
-%The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
+At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of the relatively small size of the corpus: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10.
+At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions) are also indicative of increased noise.
+This problem could be resolved by increasing the $n$-gram threshold.
+It might also make sense to simply avoid smaller corpora, though for some applications it may be useful to build comprehensive FS lexicons even in relatively low resource situations.
+One idea we are pursing is modifying the calculation of the LPR metric by using a more conservative estimate for probability than maximum likelihood in the case of low counts.
 
 We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the handling of gaps would help with identifying FS in these languages.
-We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less, a fact that is reflected in our test sets (the ratio between gapped and ungapped FS) as well as the content of the lexicon.
+We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less, a fact that is reflected in our test sets (\tabref{tab:stats}) as well as the lexicons themselves (\tabref{tab:lexstats}).
 Strikingly rare in Croatian, in particular, are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English whose fixed-word-order constraints often keep elements of an FS distant from each other.
@@
 
-As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations.
-One of the major benefits of this model as compared to alternatives is the relative ease with which additional kinds of interactions between nodes could be implemented.
-Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, \eg learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
+The statistics in \tabref{tab:lexstats} otherwise reflect the quantity and diversity of FS across the corpora, particularly in terms of the number of POS patterns represented in the lexicon.
+Looking at the most common POS patterns across languages, only noun-noun and adjective-noun combinations ever account for more than 5\% of all word types in any of the lexicons.
+Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
+
+\begin{table*}[!bt]
+
+ \begin{center}
+ \begin{tabular}{|p{2.8cm}|p{12cm}|}
+\hline
+English ICWSM & \ex{heart ache}, \ex{so \gap have some time}, \ex{part of the blame}, \ex{via slashdot}, \ex{any more questions}, \ex{protein expression}, \ex{work in \gap bank}, \ex{al-qaeda terrorist}, \ex{continue discussions}, \ex{I know a lot of people who}\\
+\hline
+English BNC & \ex{go into decline}, \ex{Maureen says}, \ex{primarily as \gap and}, \ex{Peggy Sue}, \ex{square \gap shoulder}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
+\hline
+Croatian & \ex{negativno utjecati na} (negatively affects on), \ex{jedan od dobrih poznavatelja} (one of the best connoisseurs of), \ex{jasno \gap je da} (it is clear \gap that), \ex{promet teretnih vozila} (good vehicle traffic), \ex{odvratiti pozornost} (divert attention), \ex{biti general poslije bitke} (be the general after the battle), \ex{popularni internetski} (popular internet), \ex{izazvati kaos} (cause chaos), \ex{austrijski investitor} (Austrian investor), \ex{ideja o gradnji} (the idea of building) \\
+\hline
+Japanese & \begin{CJK*}{UTF8}{min} \ex{高速\ 道路\ 整備} (highway construction),\ex{年次\ 後期} (the second half of the fiscal year), \ex{労働\ 者\ 派遣\ 事業} {temporary labor agency), \ex{こう\ 言う\ \gap\ が\ 続く} (repeat occurrences of \gap like this),  \ex{風邪\ っ\ 匹} (cold sufferer), \ex{ＤＨＣＰ\ サーバー} (DHCP server), \ex{前期\ 比} (first half comparison), \ex{経営\ 事項\ 審査 } (examination of administrative affairs), \ex{自分\ の\ 文章} (own writing), \ex{深い\ 味わい} (deep flavor) \end{CJK*} \\
+\hline
+\end{tabular}
+  \caption{ 10 randomly selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms when appropriate for readability.}
+	 \label{tab:sample}
+
+ \end{center}
+
+\end{table*}
+
+%The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
+\tabref{tab:sample} contains 10 randomly selected examples from each of the corpora.
+Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, where as \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
+The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is implausible as an FS and likely the result of noise.
+Some FS are dialectal variants, for instance \ex{license endorsed} refers to the British traffic violations.
+
+What is perhaps most striking is the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
+This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this).
+This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly between the European languages).
+Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} (good vehicle traffic), most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} (Austrian investor).
+
+Though we have demonstrated here that the idea of competition within a lattice is a powerful one for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantation of the model, but rather the flexiblity that such a model provides for future research.
+Not only do alternatives like DP-seg and LocalMaxs fail to scale up, there are few obvious ways to improve on their simple underlying algorithms without destroying the elegance of the solution they provide.
+Fast and functional, the LPR decomp approach is nevertheless algorithmically ungainly, involving multiple layers of heuristic filtering.
+Our lattice method is aimed at something between these extremes: a practical, optimizable model, but with various component heuristics that can be improved upon.
+Though the current version of the clearing function is effective and has practical advantages relative to the other simple options that we tested, we think that function could be enhanced by more careful investigation of the statistical properties of FS, identifying to what extent the LPR of words around FS is likely to be inflated.
+
+We can also consider adding new terms to the exponents of the two terms of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
+One which we have considered is creating new connections between identical or similar syntactic patterns, which could serve to encourage the model to make generalizations.
+In English, for instance, it might learn that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
@@
 
-With respect to speed, although the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice was still only a fraction of the time required to collect the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, the overall effect of adding the lattice optimization is fairly minimal.
+With respect to speed, although the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is still only a fraction of the time required to collect the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, the overall effect on runtime of the lattice optimization step is fairly minimal.
+In the BNC, the end-to-end lattice algorithm is several times faster than LocalMaxs (with a fraction of its memory usage), and an order of magnitude faster than DP-Seg.
 We note that for all four corpora, the lattice optimization algorithm converged within 10 iterations.
@@
 
-Finally, though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets.
+Though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets.
 To do a reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling.
@@
 
-Though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons for agglutinative languages.
-In particular, character or phoneme $n$-grams could compete in an identically structured lattice (though without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use, as the denominator of the ratio, phonological predictably (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
-It is likely, though, that further modifications would be necessary to target morphological phenomena, and we leave this for future work.
+Due to the lack of spaces between words and an agglutinative morphology, the standard approach to tokenization and lemmatization in Japanese involves morphological rather than word segmentation.
+In terms of the content of the resulting lexicon we believe the effect of this difference is modest, since much of what is extra in Japanese would simply be individual words in other languages (which could be viewed as being trivially part of the FS lexicon).
+However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words.
+Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as an distinct element of the FS and flexible morphemes becoming gaps.
+However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification.
+Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc using corpus statistics.
+
+Though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons, particularly for agglutinative languages.
+Character or phoneme $n$-grams could compete in an identically structured lattice (though presumably without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use phonological predictably (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
+It is likely, though, that further modifications would be necessary to target morphological phenomena well, and we leave this for future work.
 

### 2017-05-24 tacl.tex
Added MWE/FS comparison

@@
 \section{Background and Related Work}
+
+\label{sec:background}
 
@@
 What is perhaps most striking is the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
-This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this).
+This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \ex{前期\ 比} (first half comparison).
 This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly between the European languages).
@@
 
+In \secref{sec:back}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
+We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators (&\kappa&: 0.73), and then conflicts were resolved through discussion.}.
+First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider} where ``weak MWE'' make up a small fraction of MWE types.
+Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
+This may just reflect, however, the fact that a disproportionate number of MWE were noun-noun compounds, which are fairly easy for the model to identify.
+
 Though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons, particularly for agglutinative languages.

### 2017-05-25 reviewer_response.txt
Added common MWE comparison, significance, reordered discussion

@@
 "mess up").
-We have added more discussion of the corpus-specificity of FS to the paper, as part of the qualitative analysis.
+With the qualitative analysis we have added, the genre-specificity of the FS we extra is hopefully more clear.
 
-Though it perhaps does not directly address your comment (since it doesn't involve an external MWE dataset), we were nonetheless inspired by your comment to include an analysis of the recall of MWE vs.
-non-MWE FS in the context of our existing test sets.
+Though it perhaps does not directly address your comment (since it doesn't involve an external MWE lexicon), we were nonetheless inspired by your comment to include an analysis of the recall of MWE vs.
+non-MWE FS in the context of our existing test sets, and a small investigation of the recall of extremely common MWE from an existing MWE corpus, which sidesteps some of the genre bias issues mentioned above.
 

### 2017-05-25 tacl.tex
Added common MWE comparison, significance, reordered discussion

@@
 \end{multline}
-
+\noindent
 When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero.
@@
 Countrank & 0.13& 0.09 & 0.10 && 0.08 & 0.14 & 0.10 && 0.10 & 0.16 & 0.12 && 0.11 & 0.06 & 0.08 \\
-PMIrank & 0.24& 0.15& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.18& 0.08 & 0.11 \\ 
-minLPRrank & 0.49& 0.31 & 0.39 & & 0.25& 0.44 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.47 & 0.21 & 0.29 \\
+PMIrank & 0.24& 0.14& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.18& 0.08 & 0.11 \\ 
+minLPRrank & 0.49& 0.31 & 0.38 & & 0.25& 0.44 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.47 & 0.21 & 0.29 \\
 
@@
 
-	Lattice\emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
+	Lattice\emph{$-$ovr} & 0.52& 0.53 & 0.53 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
 
-				Lattice & \bf{0.67} & 0.43 & \bf{0.52} & & \bf{0.40}& \bf{0.60} & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
+				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.40}& \bf{0.60} & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
             \bottomrule
@@
   \caption{ Results of FS identification in various test sets; Countrank= lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
-Bold is best in column.}
+Bold is best in column.
+For the ICWSM only, difference relative to best baseline is significant at the $ p < 0.5$ level; the difference for all test sets considered together is significant at the $ p < 0.01$ level}
 	 \label{tab:main}
@@
 Looking at the most common POS patterns across languages, only noun-noun and adjective-noun combinations ever account for more than 5\% of all word types in any of the lexicons.
-Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
+Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach, like the one presented here.
 
@@
 Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, where as \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
-The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is implausible as an FS and likely the result of noise.
+The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise.
 Some FS are dialectal variants, for instance \ex{license endorsed} refers to the British traffic violations.
+More generally, the FS lexicons created by these two corpora are quite distinct.
 
@@
 This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \ex{前期\ 比} (first half comparison).
-This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly between the European languages).
+This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family).
 Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} (good vehicle traffic), most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} (Austrian investor).
 
+Since Zipfian frequency curves naturally extend to multiword FS vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms.
+This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common MWEs like \ex{of course} which manually-built lexicons will cover; most of potential in automatic extraction comes from the long tail.
+However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) annotated from the \newcite{Schneider14a} corpus.
+In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors seems to be mostly the result of longer phrases containing these terms ``winning out'' (in the lattice) over the shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it, for instance \ex{right on time}, \ex{show up on time}, and \ex{start on time}.
+In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting potential for improvement.
+
+In \secref{sec:background}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
+We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators ($\kappa$: 0.73), and then conflicts were resolved through discussion.}.
+First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
+Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
+This may simply reflect, however, the fact that a disproportionate number of MWE were noun-noun compounds, which are fairly easy for the model to identify.
+
+Due to the lack of spaces between words and an agglutinative morphology, the standard approach to tokenization and lemmatization in Japanese involves morphological rather than word segmentation.
+In terms of the content of the resulting lexicon we believe the effect of this difference is modest, since much of the extra FS in Japanese would simply be individual words in other languages (which could be viewed as being trivially part of the FS lexicon).
+However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words.
+Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as an distinct element of the FS and flexible morphemes becoming gaps.
+However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification.
+Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc using corpus statistics.
+
 Though we have demonstrated here that the idea of competition within a lattice is a powerful one for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantation of the model, but rather the flexiblity that such a model provides for future research.
-Not only do alternatives like DP-seg and LocalMaxs fail to scale up, there are few obvious ways to improve on their simple underlying algorithms without destroying the elegance of the solution they provide.
-Fast and functional, the LPR decomp approach is nevertheless algorithmically ungainly, involving multiple layers of heuristic filtering.
+Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without destroying the elegance of the solution they provide and worsening the tractability problem.
+Fast and functional, the LPR decomp approach is nevertheless algorithmically ungainly, involving multiple layers of heuristic-driven filtering with no possibility of correcting errors.
 Our lattice method is aimed at something between these extremes: a practical, optimizable model, but with various component heuristics that can be improved upon.
-Though the current version of the clearing function is effective and has practical advantages relative to the other simple options that we tested, we think that function could be enhanced by more careful investigation of the statistical properties of FS, identifying to what extent the LPR of words around FS is likely to be inflated.
+For instance, though the current version of the clearing function is effective and has practical advantages relative to the other simple options that we tested during development, we think that function could be enhanced by more careful investigation of the statistical properties of FS, identifying to what extent the LPR of words around FS is likely to be inflated.
 
@@
 
-%, and only the first two iterations require looking at a majority of the nodes, since there is no need to revisit a node if nothing has changed in its vicinity.
-
 Though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets.
@@
 
-Due to the lack of spaces between words and an agglutinative morphology, the standard approach to tokenization and lemmatization in Japanese involves morphological rather than word segmentation.
-In terms of the content of the resulting lexicon we believe the effect of this difference is modest, since much of what is extra in Japanese would simply be individual words in other languages (which could be viewed as being trivially part of the FS lexicon).
-However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words.
-Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as an distinct element of the FS and flexible morphemes becoming gaps.
-However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification.
-Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc using corpus statistics.
-
-In \secref{sec:back}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
-We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators (&\kappa&: 0.73), and then conflicts were resolved through discussion.}.
-First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider} where ``weak MWE'' make up a small fraction of MWE types.
-Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
-This may just reflect, however, the fact that a disproportionate number of MWE were noun-noun compounds, which are fairly easy for the model to identify.
-
-Though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons, particularly for agglutinative languages.
-Character or phoneme $n$-grams could compete in an identically structured lattice (though presumably without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use phonological predictably (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
+Finally, though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons, particularly for agglutinative languages.
+Character or phoneme $n$-grams could compete in an identically structured lattice (though presumably without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use phonological predictability (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
 It is likely, though, that further modifications would be necessary to target morphological phenomena well, and we leave this for future work.

### 2017-05-25 tacl.tex
fixed numbers

@@
 
-				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.40}& \bf{0.60} & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
+				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
             \bottomrule
@@
 Bold is best in column.
-For the ICWSM only, difference relative to best baseline is significant at the $ p < 0.5$ level; the difference for all test sets considered together is significant at the $ p < 0.01$ level}
+For the ICWSM only, f-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level}
 	 \label{tab:main}
@@
   \midrule
-			Lattice & 0.47 & 0.63 & \bf{0.54} \\
+			Lattice & 0.46 & 0.61 & \bf{0.53} \\
        \bottomrule

### 2017-05-25 tacl.tex
Missing Japanese

@@
 What is perhaps most striking is the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
-This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \ex{前期\ 比} (first half comparison).
+This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} (first half comparison).
 This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family).

### 2017-05-28 tacl2.tex
Rev

--- 2017-05-25 tacl.tex
@@
 Here, we present an effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition.
-Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14}, and more sophisticated statistical models \cite{Newman12} which do not scale to the large corpora, the main source of the distributional information in modern NLP systems.
+Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14} and more sophisticated statistical models \cite{Newman12} that do not scale to the large corpora, the main source of the distributional information in modern NLP systems.
 
@@
 Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
-Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word \cite{Riedl15}.
+Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure \cite{Riedl15} is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word.
 
@@
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
-An example of an unsupervised approach which does not use association measures, \newcite{Newman12} extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
+Work of \newcite{Newman12} is an example of an unsupervised approach which does not use association measures: it extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
 
@@
 Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold.
-Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures).
+Like FS, lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures).
 Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners.
@@
 Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS).
-The basis of the calculation of explainedness is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
+The basis of the calculation of explainedness is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity.
+Nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
 Given these relationships, we iterate over the nodes and greedily optimize the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.
@@
 
-We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
+We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun-verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
 Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
@@
 LPR is a measure of how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words).
-Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
+Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$ is given by:
 \begin{displaymath}
@@
 We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics.
-Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.
+Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences---an undesirable result.
 
@@
 \termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of\ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
+For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
 If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy.
-This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
+This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1,\dotts, s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
 Then, the $\cover(t)$ score for a covered node $t$ is:
@@
 This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
-\cover takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.
+The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.
 
@@
 
-In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{on}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
-The objective function maximized by the model is then the explainedness ($expl$) across all the nodes of the lattice, which can be defined in terms of minLPR and the node interaction functions:
-
+In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
+The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice, $t_1,\dots,t_N$, which can be defined in terms of minLPR and the node interaction functions:
+%
 \begin{multline}
-expl(t_1,...,t_N) = \prod_{i=1}^{N}{I_{on}(t_i)  C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i) minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
+	\mathit{expl}(t_1,\dots,t_N) = \prod_{i=1}^{N}{I_{\mathit{on}}(t_i)\cdot C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i)\cdot\minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
 \end{multline}
@@
 When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero.
-When the node is on, its explainedness is the inverse of a fixed cost hyperparameter C, though this cost is increased if it overlaps with other active nodes.
-All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, C can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.
+When the node is on, its explainedness is the inverse of a fixed cost hyperparameter $C$, though this cost is increased if it overlaps with other active nodes.
+All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.
 There is no upper bound on $C$, but empirically, we have found values in the range $[3,6]$ give reasonable results for the languages presented in this paper.
@@
 Nodes (designated by $n$) contain pointers to the nodes immediately linked to them in the lattice.
-States (designated by $s$) indicate whether each node is $ON$ or $OFF$.
+States (designated by $s$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$.
 Explainedness values are indicated by $e$.}
@@
 
-	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
-		\State $s_{start} \gets \Call{Set}{s, n, ON}$
+	\Function{LocalOpt}{$s_{\mathit{start}}, n, N_{\mathit{rev}}, N_{\mathit{aff}}$}
+		\State $s_{\mathit{start}} \gets \Call{Set}{s, n, \mathrm{ON}}$
 		\State $Q \gets \Call{EmptyQueue}{\null}$
-		\State $e_{best} \gets 0$
-		\State $s_{best} \gets NULL$
-		\State \Call{Push}{Q,$s_{start}$}
+		\State $e_{\mathit{best}} \gets 0$
+		\State $s_{\mathit{best}} \gets \mathrm{NULL}$
+		\State $\Call{Push}{Q, s_{\mathit{start}}}$
 		\Repeat
-			\State $s_{curr} \gets \Call{Pop}{Q}$
-			\State $e_{curr} \gets \Call{CalcExpl}{s_{curr}, N_{af\hspace{-0.1em}f}}$
-			\For{$n_{rev} \textrm{ in } N_{rev}$}
-					\State $s_{new} \gets \Call{Set}{s_{curr},n_{rev}, OFF}$
-					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
-					\If{$ e_{new} > e_{curr}$}
+			\State $s_{\mathit{curr}} \gets \Call{Pop}{Q}$
+			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{s_{\mathit{curr}}, N_{\mathit{aff}}}$
+			\For{$n_{\mathit{rev}} \textrm{ in } N_{\mathit{rev}}$}
+					\State $s_{\mathit{new}} \gets \Call{Set}{s_{\mathit{curr}},n_{\mathit{rev}}, \mathrm{OFF}}$
+					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, N_{\mathit{aff}}}$
+					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}
 
-					\State \Call{Push}{$Q, s_{new}$}
-					\If{$e_{new} > e_{best}}$:
-							\State $e_{best} \gets e_{new}$
-							\State $s_{best} \gets s_{new}$
+					\State $\Call{Push}{Q, s_{\mathit{new}}}$
+					\If{$e_{\mathit{new}} > e_{\mathit{best}}}$:
+						\State $e_{\mathit{best}} \gets e_{\mathit{new}}$
+							\State $s_{\mathit{best}} \gets s_{\mathit{new}}$
 					\EndIf
@@
 				\EndFor
-		\Until{\Call{IsEmpty}{Q}}
-	\State \Return $s_{best}$
+		\Until{$\Call{IsEmpty}{Q}$}
+	\State \Return $s_{\mathit{best}}$
 	\EndFunction
 \State
-\State \Call{FrequencySortReverse}{$N$}
+\State $\Call{FrequencySortReverse}{N}$
 \State $s \gets \Call{InitializeAllOff}{N}$
 \Repeat
-	\State $Changed \gets FALSE$
+	\State $\mathit{Changed} \gets \mathrm{FALSE}$
 		\For{$n \textrm{ in } N$}
-		\State $N_{rev} \gets \Call{GetRelevant}{n,N}$
-		\State $N_{af\hspace{-0.1em}f} \gets \Call{GetAffected}{N_{rev},N}$
-		\State $s_{new} \gets \Call{LocalOpt}{s,n,N_{rev},N_{af\hspace{-0.1em}f}}$
-		\If{$s_{new} \neq s$}
-			\State $s \gets s_{new}$
-			\State $Changed \gets TRUE$
+		\State $N_{\mathit{rev}} \gets \Call{GetRelevant}{n,N}$
+		\State $N_{\mathit{aff}} \gets \Call{GetAffected}{N_{\mathit{rev}},N}$
+		\State $s_{\mathit{new}} \gets \Call{LocalOpt}{s,n,N_{\mathit{rev}},N_{\mathit{aff}}}$
+		\If{$s_{\mathit{new}} \neq s$}
+			\State $s \gets s_{\mathit{new}}$
+			\State $\mathit{Changed} \gets \mathrm{TRUE}$
 		\EndIf
 		\EndFor
-\Until{$!Changed$}
-
+\Until{$!\mathit{Changed}$}
 \end{algorithmic}
-
 \end{algorithm}
@@
  \begin{center}
-   \begin{tabular}{lc@{\,\,\,}cc@{\,\,\,}cc@{\,\,\,}c}
+	 \begin{tabular}{@{}lc@{\,\,\,}cc@{\,\,\,}cc@{\,\,\,}c@{}}
 
@@
  \begin{center}
+	 \setlength{\tabcolsep}{5.5pt}
 \begin{tabular}{lcccccccccccccccc}
@@
  \end{tabular}
-  \caption{ Results of FS identification in various test sets; Countrank= lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
+ \caption{ Results of FS identification in various test sets; Countrank = lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
 Bold is best in column.
-For the ICWSM only, f-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level}
+For the ICWSM only, F-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level (based on permutation test).}
 	 \label{tab:main}
@@
  Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
-For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; neither of these methods scale to the larger corpora.\footnote{DP-seg is far too slow, and LocalMaxs, though faster, calculates counts for all $n$-grams in the corpus, with would require terabytes of RAM for the large corpora.}.
-Because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
+For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; neither of these methods scale to the larger corpora.\footnote{DP-seg is far too slow, and LocalMaxs, though faster, calculates counts for all $n$-grams in the corpus, with would require terabytes of RAM for the large corpora.} Because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
 All comparison approaches have themselves been previously compared against a wide range of association measures.
@@
  \begin{tabular}{lccccccc}
-\hline
+\toprule
 & & & & \multicolumn{4}{c}{\bf{By Length (\%) }} \\
        \cmidrule(lr){5-8}	
-\bf{Lexicon} & \bf{Size} & \bf{POS types} & \bf{Gapped} (\%) & \bf{2} & \bf{3} & \bf{4}  & \bf{5+} \\ 
-\hline
+\bf{Lexicon} & \bf{Size} & \bf{POS types} & \bf{Gapped} (\%) & 2 & 3 & 4 & 5+ \\ 
+\midrule
 English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
@@
 Japanese & 218k &  29.4k &7.9& 39.5 & 31.1& 16.8 & 12.6 \\
-\hline
+\bottomrule
 \end{tabular}
@@
 \hline
-Croatian & \ex{negativno utjecati na} (negatively affects on), \ex{jedan od dobrih poznavatelja} (one of the best connoisseurs of), \ex{jasno \gap je da} (it is clear \gap that), \ex{promet teretnih vozila} (good vehicle traffic), \ex{odvratiti pozornost} (divert attention), \ex{biti general poslije bitke} (be the general after the battle), \ex{popularni internetski} (popular internet), \ex{izazvati kaos} (cause chaos), \ex{austrijski investitor} (Austrian investor), \ex{ideja o gradnji} (the idea of building) \\
+Croatian & \ex{negativno utjecati na} (negatively affects on), \ex{jedan od dobrih poznavatelja} (one of the best connoisseurs of), \ex{jasno \gap je da} (it is clear to \gap that), \ex{promet teretnih vozila} (good vehicle traffic), \ex{odvratiti pozornost} (divert attention), \ex{biti general poslije bitke} (be the general after the battle), \ex{popularni internetski} (popular internet), \ex{izazvati kaos} (cause chaos), \ex{austrijski investitor} (Austrian investor), \ex{ideja o gradnji} (the idea of building) \\
 \hline
@@
 What is perhaps most striking is the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
-This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \ex{前期\ 比} (first half comparison).
+This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like
+\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} 
+(repeat occurrences of \gap like this) and 
+\begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
+(first half comparison).
 This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family).
@@
 In \secref{sec:background}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
-We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators ($\kappa$: 0.73), and then conflicts were resolved through discussion.}.
-First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
+We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators ($\kappa$: 0.73), and then conflicts were resolved through discussion.} First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
 Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
@@
 However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words.
-Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as an distinct element of the FS and flexible morphemes becoming gaps.
+Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as a distinct element of the FS and flexible morphemes becoming gaps.
 However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification.

### 2017-05-28 reviewer_response.txt
Rev

@@
 
-Added.
+Thank you for the suggestion. This has been added to the revised version.
 
@@
 
-We have split up some of the longer sentences.
+Thank you for your suggestion. We have split up some of the longer sentences, hopefully improving the readability.
 
@@
 
-Yes, since they were native (first language) speakers of each of the relevant languages, it follows that they were different across languages.
+Yes, they were different for each of the 3 languages.
+Since they were native (first language) speakers of each of the relevant languages, we believe this implies that they were different across languages.
 
@@
 
-Hopefully this is clearer in the new formulation
+Hopefully this is clearer in the new formulation.
 
@@
 
+Thank you for your suggestions.
 We have reorganized the expanation of the method to remove forward references, and have provided an explict objective function and algorithm.
@@
 
-We have reorganized the method section and added an explicit objective function, which should help with some of your problems.
+We have reorganized the method section and added an explicit objective function, which should help with some of the problems you identified.
 In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g.

### 2017-05-29 reviewer_response.txt
fixed inconsistent notation

@@
 We would like to thank all of our reviewers for their detailed comments.
-We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlaps, we have had to pick and choose what we could add.
+We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlap, we have had to pick and choose what we could add.
 In cases where we did not change the paper, threre is a justification below.
@@
 As we note in the paper, adding the distinction between continguous and gapped simply isn't defensible given the lack of positive gapped examples across some of the datasets (since both precision and recall rely on primarily on true positives).
-We would very much like to present this distinction, but the scores depend primarily on a handful of examples for some of datasets and the results are erratic, they would confuse rather than elucidate, and would also be problematic with respect to statistic significance.
+We would very much like to present this distinction, but the scores depend primarily on a handful of examples for some of datasets and the results are erratic, they would confuse rather than elucidate.
 
@@
 Ultimately, in all three languages we are tokenizing and lemmatizing using standards for each language, and building our FS from the result.
-However, this is not a theoretical choice, but a practical one.
+However, this is not a theoretical choice, but a practical one; it is undeniable that FSes often involve morphological components that we are overlooking.
 With Japanese, due to the lack of word boundaries, morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal.
@@
 
-Though it perhaps does not directly address your comment (since it doesn't involve an external MWE lexicon), we were nonetheless inspired by your comment to include an analysis of the recall of MWE vs.
-non-MWE FS in the context of our existing test sets, and a small investigation of the recall of extremely common MWE from an existing MWE corpus, which sidesteps some of the genre bias issues mentioned above.
+Though it perhaps does not directly address your comment (since it doesn't involve an external MWE lexicon), we were nonetheless inspired by your comments to include an analysis of the recall of MWE vs.
+non-MWE FS in the context of our existing ICWSM test set, and a small investigation of the recall (also in the ICWSM) of extremely common MWE from another MWE-annotated social media corpus.
 

### 2017-05-29 tacl.tex
fixed inconsistent notation

--- 2017-05-25 tacl.tex
@@
 
-We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
-Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
+We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun-verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}.
+Having said this, there are generally strong syntactic and length restrictions on what can constitute a gap \cite{Wasow:2002}, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
 This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall.
@@
 \termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of\ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
+For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
 If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy.
-This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
+This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $a_1,\dotts, a_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
 Then, the $\cover(t)$ score for a covered node $t$ is:
 \begin{displaymath}
-\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}\Big)
+\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(a_i)}}{c(t)}\Big)
 \end{displaymath}
 This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
-\cover takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.
+The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.
 
@@
 Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR.
-\termdef{Clearing} does this by changing the increasing the explainedness of nodes higher in the lattice when a lower node is turned-on.
+\termdef{Clearing} does this by increasing the explainedness of nodes higher in the lattice when a lower node is turned-on.
 The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
@@
 \begin{displaymath}
-\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
+\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(b_i)}\Big)}
 \end{displaymath}
-where $u_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice.
+where $b_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice.
 We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
@@
 
-In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{on}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
-The objective function maximized by the model is then the explainedness ($expl$) across all the nodes of the lattice, which can be defined in terms of minLPR and the node interaction functions:
-
+In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
+The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice, $t_1,\dots,t_{|T|} \in T$, which can be defined in terms of minLPR and the node interaction functions:
+%
 \begin{multline}
-expl(t_1,...,t_N) = \prod_{i=1}^{N}{I_{on}(t_i)  C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i) minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
+	\mathit{expl}(T) = \prod_{i=1}^{|T|}{I_{\mathit{on}}(t_i)\cdot C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i)\cdot\minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
 \end{multline}
@@
 	\caption{Optimization algorithm.
-$N$ is an ordered list of the nodes in the lattice.
-Nodes (designated by $n$) contain pointers to the nodes immediately linked to them in the lattice.
-States (designated by $s$) indicate whether each node is $ON$ or $OFF$.
+$T$ is an ordered list of the nodes in the lattice.
+Nodes (designated by $t$) contain pointers to the nodes immediately linked to them in the lattice.
+States (designated by $s$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$.
 Explainedness values are indicated by $e$.}
@@
 
-	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
-		\State $s_{start} \gets \Call{Set}{s, n, ON}$
+	\Function{LocalOpt}{$s_{\mathit{start}}, t, T_{\mathit{rev}}, T_{\mathit{aff}}$}
+		\State $s_{\mathit{start}} \gets \Call{Set}{s, t, \mathrm{ON}}$
 		\State $Q \gets \Call{EmptyQueue}{\null}$
-		\State $e_{best} \gets 0$
-		\State $s_{best} \gets NULL$
-		\State \Call{Push}{Q,$s_{start}$}
+		\State $e_{\mathit{best}} \gets 0$
+		\State $s_{\mathit{best}} \gets \mathrm{NULL}$
+		\State $\Call{Push}{Q, s_{\mathit{start}}}$
 		\Repeat
-			\State $s_{curr} \gets \Call{Pop}{Q}$
-			\State $e_{curr} \gets \Call{CalcExpl}{s_{curr}, N_{af\hspace{-0.1em}f}}$
-			\For{$n_{rev} \textrm{ in } N_{rev}$}
-					\State $s_{new} \gets \Call{Set}{s_{curr},n_{rev}, OFF}$
-					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
-					\If{$ e_{new} > e_{curr}$}
+			\State $s_{\mathit{curr}} \gets \Call{Pop}{Q}$
+			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{s_{\mathit{curr}}, T_{\mathit{aff}}}$
+			\For{$t_{\mathit{rev}} \textrm{ in } T_{\mathit{rev}}$}
+					\State $s_{\mathit{new}} \gets \Call{Set}{s_{\mathit{curr}},t_{\mathit{rev}}, \mathrm{OFF}}$
+					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, T_{\mathit{aff}}}$
+					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}
 
-					\State \Call{Push}{$Q, s_{new}$}
-					\If{$e_{new} > e_{best}}$:
-							\State $e_{best} \gets e_{new}$
-							\State $s_{best} \gets s_{new}$
+					\State $\Call{Push}{Q, s_{\mathit{new}}}$
+					\If{$e_{\mathit{new}} > e_{\mathit{best}}}$:
+						\State $e_{\mathit{best}} \gets e_{\mathit{new}}$
+							\State $s_{\mathit{best}} \gets s_{\mathit{new}}$
 					\EndIf
@@
 				\EndFor
-		\Until{\Call{IsEmpty}{Q}}
-	\State \Return $s_{best}$
+		\Until{$\Call{IsEmpty}{Q}$}
+	\State \Return $s_{\mathit{best}}$
 	\EndFunction
 \State
-\State \Call{FrequencySortReverse}{$N$}
-\State $s \gets \Call{InitializeAllOff}{N}$
+\State $\Call{FrequencySortReverse}{T}$
+\State $s \gets \Call{InitializeAllOff}{T}$
 \Repeat
-	\State $Changed \gets FALSE$
-		\For{$n \textrm{ in } N$}
-		\State $N_{rev} \gets \Call{GetRelevant}{n,N}$
-		\State $N_{af\hspace{-0.1em}f} \gets \Call{GetAffected}{N_{rev},N}$
-		\State $s_{new} \gets \Call{LocalOpt}{s,n,N_{rev},N_{af\hspace{-0.1em}f}}$
-		\If{$s_{new} \neq s$}
-			\State $s \gets s_{new}$
-			\State $Changed \gets TRUE$
+	\State $\mathit{Changed} \gets \mathrm{FALSE}$
+		\For{$t \textrm{ in } T$}
+		\State $T_{\mathit{rev}} \gets \Call{GetRelevant}{t,T}$
+		\State $T_{\mathit{aff}} \gets \Call{GetAffected}{T_{\mathit{rev}},T}$
+		\State $s_{\mathit{new}} \gets \Call{LocalOpt}{s,t,T_{\mathit{rev}},T_{\mathit{aff}}}$
+		\If{$s_{\mathit{new}} \neq s$}
+			\State $s \gets s_{\mathit{new}}$
+			\State $\mathit{Changed} \gets \mathrm{TRUE}$
 		\EndIf
 		\EndFor
-\Until{$!Changed$}
-
+\Until{$!\mathit{Changed}$}
 \end{algorithmic}
-
 \end{algorithm}
@@
 We created small development sets for each corpus and used them to do a thorough testing of parameter settings.
-Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
+Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
 We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
@@
  \begin{tabular}{lccccccc}
-\hline
+\toprule
 & & & & \multicolumn{4}{c}{\bf{By Length (\%) }} \\
        \cmidrule(lr){5-8}	
-\bf{Lexicon} & \bf{Size} & \bf{POS types} & \bf{Gapped} (\%) & \bf{2} & \bf{3} & \bf{4}  & \bf{5+} \\ 
-\hline
+\bf{Lexicon} & \bf{Word types} & \bf{POS types} & \bf{Gapped} (\%) & 2 & 3 & 4 & 5+ \\ 
+\midrule
 English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
@@
 
-What is perhaps most striking is the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
-This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \ex{前期\ 比} (first half comparison).
+What is perhaps most striking about the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
+This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like
+\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} 
+(repeat occurrences of \gap like this) and 
+\begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
+(first half comparison).
 This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family).
@@
 
-Though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets.
+%Though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets.
 To do a reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling.

### 2017-05-29 tacl.tex
Edits to end of Methodology + new table

@@
 % TJB macros
-\newcommand{\dotts}{...}
+\newcommand{\dotts}{...\xspace}
 \newcommand{\gap}{$*$\xspace}
@@
 \newcommand{\ex}[1]{\textit{#1}\xspace}
+\newcommand{\gl}[1]{``#1''\xspace}
 \newcommand{\termdef}[1]{\textbf{#1}\xspace}
@@
 \newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}
-%\newcommand{\algref}[2][]{Algorithm#1~\ref{#2}\xspace}
+\newcommand{\algoref}[2][]{Algorithm#1~\ref{#2}\xspace}
 
@@
 In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
-Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.
+Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.
 Note that the FS framework allows for individual morphemes be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.
@@
 It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research.
-Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) FS such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \dotts's weight in gold}, fall under the FS umbrella.
+Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) FS such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of \dotts}, \ex{the rise and fall of \dotts}, \ex{now is not the time to \dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \dotts's weight in gold}, fall under the FS umbrella.
 Another reason to introduce a different terminology is that there are classes of phrases which are typically considered MWEs that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb}, analogous to \ex{wooden leg}).
@@
 The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
-Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probably statistics to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
-Work of \newcite{Newman12} is an example of an unsupervised approach which does not use association measures: it extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
+Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probabilities to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
+The work of \newcite{Newman12} is an example of an unsupervised approach which does not use association measures: it extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
 
@@
 The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes.
-Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS).
-The basis of the calculation of explainedness is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity.
+Each node can be considered either ``on'' (\textit{is an FS}) or ``off'' (\textit{is not an FS}).
+The basis of the calculation of explainedness is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in its vicinity.
 Nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.
@@
 For example, in the case of \ex{be keep \gap under wraps}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under} or \ex{under} and \ex{wraps}, but minLPR is focused on the weaker relationship between \ex{be} and the rest of the phrase.
-This makes it particularly appropriate measure for use in a lattice model of completing $n$-grams, where the choice of \ex{be keep \gap under wraps} versus {keep \gap under wraps} should be based exactly on the extent to which \ex{be} is an essential part of the phrase; the other affinities are, in effect, irrelevant, because they occur in the smaller $n$-gram as well.
+This makes it particularly suited to use in a lattice model of competing $n$-grams, where the choice of \ex{be keep \gap under wraps} versus \ex{keep \gap under wraps} should be based exactly on the extent to which \ex{be} is an essential part of the phrase; the other affinities are, in effect, irrelevant, because they occur in the smaller $n$-gram as well.
 
@@
 
-\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other.
+\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of a subsuming $(n+i)$-gram.
 In \figref{fig:example}, \eg if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and we should consider these two $n$-grams as one.
@@
 This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
-The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.
+The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering occurs.
 
@@
 
-A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes.
+A simple but effective solution which avoids extra hyperparameters is to make use of the minLPR values of the relevant nodes.
 In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher.
@@
 For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR.
-To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
-Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to overlapping nodes, \ie turned-on nodes which overlap with our target node $t$in the corpus.
-We define \overlap(t) as:
+To address this problem, rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
+Let $\mathit{oc}(x,y)$ be the number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to overlapping nodes, \ie turned-on nodes which overlap with target node $t$ in the corpus.
+We define $\overlap(t)$ as:
 \begin{displaymath}
@@
 
-\begin{algorithm}
+\begin{algorithm}[t!]
 	\caption{Optimization algorithm.
@@
 Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified.
-Next, a search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and then iteratively considering new states with one relevant node turned off; the search continues as long as there is an improvement in explainedness.
+Next, a search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and  iteratively considering new states with one relevant node turned off; the search continues as long as there is an improvement in explainedness.
 Since the node interactions are roughly cumulative in their effects, this approach will generally identify the optimal state without the need for an exhaustive search.
-The details of the algorithm are given as Algorithm 1.%\algref{alg:opt}.
+See \algoref{alg:opt} for details.
 
-Omitted from Algorithm 1 for clarity are various low-level efficiencies which prevent the algorithm from reconsidering states already checked or from recalculating the explainedness of nodes when unnecessary.
+Omitted from \algoref{alg:opt} for clarity are various low-level efficiencies which prevent the algorithm from reconsidering states already checked or from recalculating the explainedness of nodes when unnecessary.
 We also apply the following efficiency restrictions, which significantly reduce the runtime of the algorithm.
@@
 
-\begin{table*}[!bt]
+\begin{table*}[!t]
 
  \begin{center}
- \begin{tabular}{|p{2.8cm}|p{12cm}|}
-\hline
-English ICWSM & \ex{heart ache}, \ex{so \gap have some time}, \ex{part of the blame}, \ex{via slashdot}, \ex{any more questions}, \ex{protein expression}, \ex{work in \gap bank}, \ex{al-qaeda terrorist}, \ex{continue discussions}, \ex{I know a lot of people who}\\
-\hline
-English BNC & \ex{go into decline}, \ex{Maureen says}, \ex{primarily as \gap and}, \ex{Peggy Sue}, \ex{square \gap shoulder}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
-\hline
-Croatian & \ex{negativno utjecati na} (negatively affects on), \ex{jedan od dobrih poznavatelja} (one of the best connoisseurs of), \ex{jasno \gap je da} (it is clear to \gap that), \ex{promet teretnih vozila} (good vehicle traffic), \ex{odvratiti pozornost} (divert attention), \ex{biti general poslije bitke} (be the general after the battle), \ex{popularni internetski} (popular internet), \ex{izazvati kaos} (cause chaos), \ex{austrijski investitor} (Austrian investor), \ex{ideja o gradnji} (the idea of building) \\
-\hline
-Japanese & \begin{CJK*}{UTF8}{min} \ex{高速\ 道路\ 整備} (highway construction),\ex{年次\ 後期} (the second half of the fiscal year), \ex{労働\ 者\ 派遣\ 事業} {temporary labor agency), \ex{こう\ 言う\ \gap\ が\ 続く} (repeat occurrences of \gap like this),  \ex{風邪\ っ\ 匹} (cold sufferer), \ex{ＤＨＣＰ\ サーバー} (DHCP server), \ex{前期\ 比} (first half comparison), \ex{経営\ 事項\ 審査 } (examination of administrative affairs), \ex{自分\ の\ 文章} (own writing), \ex{深い\ 味わい} (deep flavor) \end{CJK*} \\
-\hline
+ \begin{tabular}{p{1.5cm}p{14cm}}
+\toprule
+English (ICWSM) & \ex{heart ache}, \ex{so \gap have some time}, \ex{part of the blame}, \ex{via slashdot}, \ex{any more questions}, \ex{protein expression}, \ex{work in \gap bank}, \ex{al-qaeda terrorist}, \ex{continue discussions}, \ex{I know a lot of people who}\\
+\midrule
+English (BNC) & \ex{go into decline}, \ex{Maureen says}, \ex{primarily as \gap and}, \ex{Peggy Sue}, \ex{square \gap shoulder}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
+\midrule
+Croatian & \ex{negativno utjecati na} \gl{negatively affects on},
+% TJB: awkard gloss
+\ex{jedan od dobrih poznavatelja} \gl{one of the best connoisseurs of}, \ex{jasno \gap je da} \gl{it is clear to \gap that}, \ex{promet teretnih vozila} \gl{good vehicle traffic}, \ex{odvratiti pozornost} \gl{divert attention}, \ex{biti general poslije bitke} \gl{be the general after the battle}, \ex{popularni internetski} \gl{popular internet}, \ex{izazvati kaos} \gl{cause chaos}, \ex{austrijski investitor} \gl{Austrian investor}, \ex{ideja o gradnji} \gl{the idea of building} \\
+\midrule
+Japanese & \begin{CJK*}{UTF8}{min} \ex{高速\ 道路\ 整備} \gl{highway construction}, \ex{年次\ 後期} \gl{the second half of the fiscal year}, \ex{労働\ 者\ 派遣\ 事業} \gl{temporary labor agency}, \ex{こう\ 言う\ \gap\ が\ 続く} \gl{repeat occurrences of \gap like this},  \ex{風邪\ っ\ 匹} \gl{cold sufferer}, \ex{ＤＨＣＰ\ サーバー} \gl{DHCP server}, \ex{前期\ 比} \gl{first half comparison}, \ex{経営\ 事項\ 審査 } \gl{examination of administrative affairs}, \ex{自分\ の\ 文章} \gl{own writing}, \ex{深い\ 味わい} \gl{deep flavor} \end{CJK*} \\
+\bottomrule
 \end{tabular}
-  \caption{ 10 randomly selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms when appropriate for readability.}
+  \caption{10 randomly selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms when appropriate for readability.}
 	 \label{tab:sample}

### 2017-05-29 tacl.tex
Edits to end; still slightly over-length

@@
 Instead, $n$-grams are sampled after applying the frequency threshold and then annotated as being either an FS or not.
-Benefits to this as compared to competing evaluation include replicability, the diversity of FS, and the ability to calculate a true F-score.
-We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.
+Benefits of this style of evaluation include replicability, the diversity of FS, and the ability to calculate a true F-score.
+We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other three corpora: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each corpus.
 
@@
 Other than the inclusion of new languages, our test sets differ from \newcite{Brooke15b} in two ways.
-One advantage of a type-based annotation approach (as compared to a corpus annotation), particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness.
+One advantage of a type-based annotation approach, particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness.
 To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
@@
        \cmidrule(lr){2-4} \cmidrule(lr){6-8} \cmidrule(lr){10-12} \cmidrule(lr){14-16}
-           \multicolumn{1}{c}{\bf{Source}}    & P & R & F &   & P & R & F &   & P & R & F &  & P & R & F \\
+      & P & R & F &   & P & R & F &   & P & R & F &  & P & R & F \\
           \midrule 
@@
 
-	Lattice\emph{$-$cl,ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\
+	Lattice \emph{$-$cl,ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\
 
-	Lattice\emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\
+	Lattice \emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\
 
-	Lattice\emph{$-$ovr} & 0.52& 0.53 & 0.53 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
+	Lattice \emph{$-$ovr} & 0.52& 0.53 & 0.53 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
 
@@
  \end{tabular}
- \caption{ Results of FS identification in various test sets; Countrank = lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score.
-Bold is best in column.
-For the ICWSM only, F-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level (based on permutation test).}
+ \caption{ Results of FS identification in various test sets; Countrank = lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke et \al (2015), ``$-$cl'' = no clearing, ``$-$ovr'' = no penalization of overlaps, ``P'' = Precision, ``R'' = Recall, ``F'' = F-score.
+Bold is best in a given column.
+For the ICWSM only, F-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level (based on the permutation test).}
 	 \label{tab:main}
@@
 
- Our primary comparison is with the heuristic LPR model from \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
-For the BNC, we also compare, separately, the DP-seg model from \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; neither of these methods scale to the larger corpora.\footnote{DP-seg is far too slow, and LocalMaxs, though faster, calculates counts for all $n$-grams in the corpus, with would require terabytes of RAM for the large corpora.} Because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
+ Our primary comparison is with the heuristic LPR model of \newcite{Brooke15b}, which is scalable to large corpora and includes gapped $n$-grams.
+For the BNC, we also benchmark against the DP-seg model of \newcite{Newman12} with recommended settings, and the LocalMaxs algorithm of \newcite{Silva99} using SCP; neither of these methods scale to the larger corpora.\footnote{DP-seg is far too slow, and LocalMaxs, though faster, calculates counts for all $n$-grams in the corpus, which would require terabytes of RAM for the large corpora.} Because these other approaches only generate sequential multiword units, we use only the sequential part of the BNC test set for this evaluation.
 All comparison approaches have themselves been previously compared against a wide range of association measures.
@@
 We created small development sets for each corpus and used them to do a thorough testing of parameter settings.
-Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
+Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results with $C=4$, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
 We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
@@
 
-The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}.
-As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with syntactically-unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
-The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages.
+The main results for FS acquisition across the four corpora are shown in \tabref{tab:main}.
+As noted in \secref{sec:background}, simple statistical association measures like PMI do poorly when faced with syntactically-unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose.
+The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across the languages.
 Generally, clearing and overlap node interactions provide a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
 When only covering is used, the results are very similar to \newcite{Brooke15b}, which is unsurprising given the extent to which decomposition and covering are related.
-The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
+The Japanese and ICWSM corpus have relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
 
-In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of Newman \cite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
+In the contiguous FS test set for the BNC (\tabref{tab:BNC}), we found that both the LocalMaxs algorithm and the DP-seg method of \newcite{Newman12} were able to beat our other baseline methods with roughly similar F-scores, though both are well below our Lattice method.
 Some of the difference seems attributable to fairly severe precision/recall imbalance, though we were unable to improve the F-score by changing the parameters from recommended settings for either model.
@@
 
+%\subsection{Overall Results}
+
 Though the results across the four corpora are reasonably similar with respect to overall F-score, there are some discrepancies.
@@
 
-At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of the relatively small size of the corpus: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10.
-At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions) are also indicative of increased noise.
-This problem could be resolved by increasing the $n$-gram threshold.
-It might also make sense to simply avoid smaller corpora, though for some applications it may be useful to build comprehensive FS lexicons even in relatively low resource situations.
-One idea we are pursing is modifying the calculation of the LPR metric by using a more conservative estimate for probability than maximum likelihood in the case of low counts.
+At the opposite extreme, the low precision of the BNC is almost certainly due to its relatively small size: whereas the $n$-gram threshold we used here results in minimum counts of roughly 100 for the other three corpora, the BNC statistics include $n$-grams with counts less than 10.
+At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions, resp.) are also indicative of increased noise.
+This  could be resolved by increasing the $n$-gram threshold.
+It might also make sense to simply avoid smaller corpora, though for some applications a smaller corpus may be unavoidable.
+One idea we are pursing is modifying the calculation of the LPR metric to use a more conservative  probability estimate than maximum likelihood in the case of low counts.
 
-We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the handling of gaps would help with identifying FS in these languages.
+We were interested in Croatian and Japanese in part because of their relatively free word order, and whether the handling of gaps would help with identifying FS in these languages.
 We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less, a fact that is reflected in our test sets (\tabref{tab:stats}) as well as the lexicons themselves (\tabref{tab:lexstats}).
@@
 \end{tabular}
-  \caption{10 randomly selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms when appropriate for readability.}
+  \caption{10 randomly selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms where appropriate for readability.}
 	 \label{tab:sample}
@@
 \tabref{tab:sample} contains 10 randomly selected examples from each of the corpora.
-Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, where as \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
+Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
 The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise.
@@
 What is perhaps most striking about the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
-This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like
+This is expected of course for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like
 \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} 
-(repeat occurrences of \gap like this) and 
+\gl{repeat occurrences of \gap like this} and 
 \begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
-(first half comparison).
+\gl{first half comparison}.
 This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family).
-Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} (good vehicle traffic), most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} (Austrian investor).
+Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} \gl{Austrian investor}.
 
@@
 However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) annotated from the \newcite{Schneider14a} corpus.
-In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors seems to be mostly the result of longer phrases containing these terms ``winning out'' (in the lattice) over the shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it, for instance \ex{right on time}, \ex{show up on time}, and \ex{start on time}.
+In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).
 In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting potential for improvement.
 
+%\subsection{FS vs.\ MWE}
+
 In \secref{sec:background}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
-We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators ($\kappa$: 0.73), and then conflicts were resolved through discussion.} First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
-Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
-This may simply reflect, however, the fact that a disproportionate number of MWE were noun-noun compounds, which are fairly easy for the model to identify.
+We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two native-speaker annotators ($\kappa = 0.73$), and conflicts were resolved through discussion.} First, we note that only 28\% of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
+Even without any explicit representation of compositionality, our model did much better at identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
+This may simply reflect, however, the fact that a disproportionate number of MWEs were noun-noun compounds, which are fairly easy for the model to identify.
 
@@
 
-Though we have demonstrated here that the idea of competition within a lattice is a powerful one for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantation of the model, but rather the flexiblity that such a model provides for future research.
-Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without destroying the elegance of the solution they provide and worsening the tractability problem.
+Though we have demonstrated that competition within a lattice is powerful for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research.
+Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without compromising their elegance and worsening tractability.
 Fast and functional, the LPR decomp approach is nevertheless algorithmically ungainly, involving multiple layers of heuristic-driven filtering with no possibility of correcting errors.
 Our lattice method is aimed at something between these extremes: a practical, optimizable model, but with various component heuristics that can be improved upon.
-For instance, though the current version of the clearing function is effective and has practical advantages relative to the other simple options that we tested during development, we think that function could be enhanced by more careful investigation of the statistical properties of FS, identifying to what extent the LPR of words around FS is likely to be inflated.
+For instance, though the current version of clearing is effective and has practical advantages relative to the other simpler options that we tested, we think that it could be enhanced by more careful investigation of the statistical properties of FS, identifying to what extent the LPR of words around FS is likely to be inflated.
 
 We can also consider adding new terms to the exponents of the two terms of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
-One which we have considered is creating new connections between identical or similar syntactic patterns, which could serve to encourage the model to make generalizations.
+One which we have considered is creating new connections between identical or similar syntactic patterns, which could serve to encourage the model to generalize.
 In English, for instance, it might learn that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics alone are an unreliable indicator of formulaticity.
+Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics are an unreliable indicator of formulaticity.
 
-With respect to speed, although the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is still only a fraction of the time required to collect the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, the overall effect on runtime of the lattice optimization step is fairly minimal.
+With respect to speed, although the optimization of the lattice is several orders of magnitude slower than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is still only a fraction of the time required to collect the statistics necessary to calculate LPR: therefore, the overall effect on runtime of the lattice optimization step is fairly minimal.
 In the BNC, the end-to-end lattice algorithm is several times faster than LocalMaxs (with a fraction of its memory usage), and an order of magnitude faster than DP-Seg.
@@
 
-Finally, though the model presented here was designed specifically for FS extraction, we note that it could be useful for similar tasks such as unsupervised creation of morphological lexicons, particularly for agglutinative languages.
+Finally, though the model presented here was designed specifically for FS extraction, we note that it could be useful for related tasks such as unsupervised learning of morphological lexicons, particularly for agglutinative languages.
 Character or phoneme $n$-grams could compete in an identically structured lattice (though presumably without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use phonological predictability (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
-It is likely, though, that further modifications would be necessary to target morphological phenomena well, and we leave this for future work.
+It is likely, though, that further algorithmic modifications would be necessary to target morphological phenomena well, and we leave this for future work.
 

### 2017-05-29 tacl.tex
minor edits

@@
  \end{tabular}
- \caption{ Results of FS identification in various test sets; Countrank = lexicon created by ranking with frequency PMIrank = lexicon created with ranking pointwise mutual information, minLPRrank = lexicon created by ranking with minLPR, LPRseg = lexicon created by method of Brooke et \al (2015), ``$-$cl'' = no clearing, ``$-$ovr'' = no penalization of overlaps, ``P'' = Precision, ``R'' = Recall, ``F'' = F-score.
+ \caption{Results of FS identification in various test sets: Countrank = ranking with frequency; PMIrank = PMI-based ranking; minLPRrank = ranking with minLPR; LPRseg = the method of Brooke et \al (2015); ``$-$cl'' = no clearing; ``$-$ovr'' = no penalization of overlaps; ``P'' = Precision; ``R'' = Recall; and ``F'' = F-score.
 Bold is best in a given column.
-For the ICWSM only, F-score difference relative to best baseline is significant at the $p < 0.5$ level; the difference for all test sets together is significant at the $ p < 0.01$ level (based on the permutation test).}
+For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$ (all $p$ values based on the permutation test).}
 	 \label{tab:main}
@@
 This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common MWEs like \ex{of course} which manually-built lexicons will cover; most of potential in automatic extraction comes from the long tail.
-However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) annotated from the \newcite{Schneider14a} corpus.
+However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) from the \newcite{Schneider14a} corpus.
 In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).

### 2017-05-30 tacl.tex
Pushed it under 13 pages

@@
 Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link.
-For example, in the case of \ex{be keep \gap under wraps}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under} or \ex{under} and \ex{wraps}, but minLPR is focused on the weaker relationship between \ex{be} and the rest of the phrase.
+For example, in the case of \ex{be keep \gap under wraps} (\figref{fig:example}), a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under} or \ex{under} and \ex{wraps}, but minLPR is focused on the weaker relationship between \ex{be} and the rest of the phrase.
 This makes it particularly suited to use in a lattice model of competing $n$-grams, where the choice of \ex{be keep \gap under wraps} versus \ex{keep \gap under wraps} should be based exactly on the extent to which \ex{be} is an essential part of the phrase; the other affinities are, in effect, irrelevant, because they occur in the smaller $n$-gram as well.
@@
 
-In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
+In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if node $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
 The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice, $t_1,\dots,t_{|T|} \in T$, which can be defined in terms of minLPR and the node interaction functions:
@@
 The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
-The rationale is that the number of positive gapped examples is too low to provide a reliable independent F-score (see further discussion in \secref{sec:discussion}).
+The rationale is that the number of positive gapped examples is too low to provide a reliable independent F-score.
+
+%(see further discussion in \secref{sec:discussion}).
 
@@
 
-	Lattice \emph{$-$ovr} & 0.52& 0.53 & 0.53 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
+	Lattice \emph{$-$ovr} & 0.52& \bf{0.53} & 0.53 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
 
@@
 Bold is best in a given column.
-For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$ (all $p$ values based on the permutation test).}
+For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all $p$ values based on the permutation test (Yeh, 2000).}
 	 \label{tab:main}
@@
 Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results with $C=4$, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
-We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.
+We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with overlap and clearing node interactions turned off.
 
@@
 Generally, clearing and overlap node interactions provide a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.
-When only covering is used, the results are very similar to \newcite{Brooke15b}, which is unsurprising given the extent to which decomposition and covering are related.
+When only covering is used, the results are fairly similar to \newcite{Brooke15b}, which is unsurprising given the extent to which decomposition and covering are related.
 The Japanese and ICWSM corpus have relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
@@
 The result is that there are relatively more FS for Japanese: precision is high, and recall is comparably low.
-Importantly, the initial $n$-gram statistics derived from corpus actually reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus.
+Importantly, the initial $n$-gram statistics actually reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus.
 One idea for future work is to automatically adapt to the input language/corpus in order to ensure a good balance between precision and recall.
@@
 Looking at the most common POS patterns across languages, only noun-noun and adjective-noun combinations ever account for more than 5\% of all word types in any of the lexicons.
-Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach, like the one presented here.
+Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
 
@@
 %The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.
-\tabref{tab:sample} contains 10 randomly selected examples from each of the corpora.
+\tabref{tab:sample} contains 10 randomly selected examples from each of the lexicons produced by our method.
 Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
@@
 Some FS are dialectal variants, for instance \ex{license endorsed} refers to the British traffic violations.
-More generally, the FS lexicons created by these two corpora are quite distinct.
+More generally, the FS lexicons created by these two corpora are quite distinct, sharing less than 50\% of their entries.
 
@@
 This is expected of course for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like
-\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} 
-\gl{repeat occurrences of \gap like this} and 
+\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} \gl{repeat occurrences of \gap like this} and 
 \begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
 \gl{first half comparison}.
-This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family).
-Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} \gl{Austrian investor}.
+This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some do, particularly short ones in related languages).
+Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from, like \ex{austrijski investitor} \gl{Austrian investor}.
 
-Since Zipfian frequency curves naturally extend to multiword FS vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms.
-This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common MWEs like \ex{of course} which manually-built lexicons will cover; most of potential in automatic extraction comes from the long tail.
+Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms.
+This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of potential in automatic extraction comes from the long tail.
 However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) from the \newcite{Schneider14a} corpus.
 In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).
-In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting potential for improvement.
+%In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting potential for improvement.
 
@@
 We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two native-speaker annotators ($\kappa = 0.73$), and conflicts were resolved through discussion.} First, we note that only 28\% of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
-Even without any explicit representation of compositionality, our model did much better at identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34.
+Even without any explicit representation of compositionality, our model did much better at identifying MWE FS than non-MWE FS:  0.71 versus 0.34 recall.
 This may simply reflect, however, the fact that a disproportionate number of MWEs were noun-noun compounds, which are fairly easy for the model to identify.
@@
 Due to the lack of spaces between words and an agglutinative morphology, the standard approach to tokenization and lemmatization in Japanese involves morphological rather than word segmentation.
-In terms of the content of the resulting lexicon we believe the effect of this difference is modest, since much of the extra FS in Japanese would simply be individual words in other languages (which could be viewed as being trivially part of the FS lexicon).
+In terms of the content of the resulting lexicon we believe the effect of this difference on FS extraction is modest, since much of the extra FS in Japanese would simply be single words in other languages (and considered trivially part of the FS lexicon).
 However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words.
@@
 However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification.
-Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc using corpus statistics.
+Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc from the corpus statistics.
 
-Though we have demonstrated that competition within a lattice is powerful for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research.
+Though we have demonstrated that competition within a lattice is a powerful method for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research.
 Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without compromising their elegance and worsening tractability.
@@
 Our lattice method is aimed at something between these extremes: a practical, optimizable model, but with various component heuristics that can be improved upon.
-For instance, though the current version of clearing is effective and has practical advantages relative to the other simpler options that we tested, we think that it could be enhanced by more careful investigation of the statistical properties of FS, identifying to what extent the LPR of words around FS is likely to be inflated.
+For instance, though the current version of clearing is effective and has practical advantages relative to simpler options that we tested, it could be enhanced by more careful investigation of the statistical properties of $n$-grams which contain FS.
 
-We can also consider adding new terms to the exponents of the two terms of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
+We can also consider adding new terms to the exponents of the two parts of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
 One which we have considered is creating new connections between identical or similar syntactic patterns, which could serve to encourage the model to generalize.
@@
 Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure.
-Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics are an unreliable indicator of formulaticity.
+Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on MWEs which could provide a reliable basis for generalization.
 
-With respect to speed, although the optimization of the lattice is several orders of magnitude slower than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is still only a fraction of the time required to collect the statistics necessary to calculate LPR: therefore, the overall effect on runtime of the lattice optimization step is fairly minimal.
-In the BNC, the end-to-end lattice algorithm is several times faster than LocalMaxs (with a fraction of its memory usage), and an order of magnitude faster than DP-Seg.
-We note that for all four corpora, the lattice optimization algorithm converged within 10 iterations.
+For all four corpora, the lattice optimization algorithm converged within 10 iterations.
+Although the optimization of the lattice is nevertheless several orders of magnitude slower than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is still only a fraction of the time required to collect the statistics for LPR calculation, and so the end-to-end runtime of the two methods is comparable.
+In the BNC, the end-to-end lattice method is several times faster than LocalMaxs (with a fraction of its memory usage), and an order of magnitude faster than DP-Seg.
 
@@
 Finally, though the model presented here was designed specifically for FS extraction, we note that it could be useful for related tasks such as unsupervised learning of morphological lexicons, particularly for agglutinative languages.
-Character or phoneme $n$-grams could compete in an identically structured lattice (though presumably without gapped $n$-grams) to be chosen as the best morphemes for the language, and we could straightforwardly adapt LPR to use phonological predictability (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
+Character or phoneme $n$-grams could compete in an identically structured lattice to be chosen as the best morphemes for the language, with LPR adapted to use phonological predictability (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
 It is likely, though, that further algorithmic modifications would be necessary to target morphological phenomena well, and we leave this for future work.
@@
 A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{Removed for anonymity}
+
+\nocite{yeh2000more}
 

### 2017-05-30 tacl.tex
p-value

@@
 Bold is best in a given column.
-For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all $p$ values based on the permutation test (Yeh, 2000).}
+For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all p-values based on the permutation test (Yeh, 2000).}
 	 \label{tab:main}

### 2017-05-30 reviewer_response.txt
Final edits

@@
-We would like to thank all of our reviewers for their detailed comments.
-We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlap, we have had to pick and choose what we could add.
-In cases where we did not change the paper, threre is a justification below.
+We would like to thank all of our reviewers for their detailed comments. We
+have tried to address the important points as best we can, but were limited to
+3 extra pages (beyond the 10 pages of the original submission). As all the
+reviews had numerous suggestions for improvement, with only one obvious area
+of overlap, we have had to pick and choose what we could add. In cases where
+we did not change the paper, we provide a justification below.
 
-We should mention one change that wasn't prompted by individual reviewer comments: there were clear misinterpretations by our Japanese annotators from the first round with led to overannotation of FS, and since the original submission of the paper we have done another round of annotation.
-The Japanese results have therefore changed somewhat, and are in fact more consistent with the other languages.
+We should mention one change that wasn't prompted by individual reviewer
+comments: there were clear misinterpretations by our Japanese annotators from
+the first round with led to overannotation of FS, leading us to to another
+round of annotation and since the original submission. The Japanese results
+have therefore changed somewhat, and are in fact more consistent with the
+other languages.
 
-Reviewer A
+REVIEWER A
 
->In the introduction, the proposed approach is claimed to be "effective,
-expandable, and tractable", however, it is not clear how each of these
-claims is evaluated in the paper (effective, expandable and tractable). The
-approach is also claimed to have the candidates compete for "the best (most
-parsimonious) explanation for statistical irregularities due to lexical
-affinity", but concepts like parsimony and lexical affinity need to be
-defined (what are they, how candidates display them, and how they are
-measured, ...).
+> In the introduction, the proposed approach is claimed to be "effective,
+> expandable, and tractable", however, it is not clear how each of these
+> claims is evaluated in the paper (effective, expandable and tractable). The
+> approach is also claimed to have the candidates compete for "the best (most
+> parsimonious) explanation for statistical irregularities due to lexical
+> affinity", but concepts like parsimony and lexical affinity need to be
+> defined (what are they, how candidates display them, and how they are
+> measured, ...).
 
-Our intent is that effectiveness is demonstrated by our main evaluation.
-Tractability is demonstrated implicitly by the fact that we apply our method to corpora much larger than many of our competitors can handle.
-We have added more details about this to the paper, though we do not want to belabour the point, since it is not the primary purpose.
-Our claim of expandability relates to our discussion of future work, however we have added a bit more discussion about exactly how expansions would be added without major changes to the model.
+Our intent is that effectiveness is demonstrated by our main
+evaluation. Tractability is demonstrated implicitly by the fact that we apply
+our method to corpora much larger than many of our competitors can handle. We
+have added more details about this to the paper, though we do not want to
+belabour the point, since it is not the primary purpose. Our claim of
+expandability relates to our discussion of future work, however we have added
+a bit more discussion about exactly how expansions would be added without
+major changes to the model.
 
 > The paper should explicitly state what the hypotheses are in relation to the
-utility functions, particularly in relation to the approach by Brooke et al.
-(2015), which is simpler than the proposed approach. Moreover, the
-state-of-the-art has several simpler formulations for the identification of
-general formulaic sequences of flexible sizes (e.g. Silva et al. 1999 for
-contiguous & non-contiguous cases and Villavicencio et al. 2007 for
-contiguous cases), and the text should justify why this particular approach
-is appealing, and advantageous in relation to the others. The addition of an
-error analysis would help highligh these points, helping to clarify the
-advantages of the particular approach especially in relation to Brooke et
-al.
+> utility functions, particularly in relation to the approach by Brooke et al.
+> (2015), which is simpler than the proposed approach. Moreover, the
+> state-of-the-art has several simpler formulations for the identification of
+> general formulaic sequences of flexible sizes (e.g. Silva et al. 1999 for
+> contiguous & non-contiguous cases and Villavicencio et al. 2007 for
+> contiguous cases), and the text should justify why this particular approach
+> is appealing, and advantageous in relation to the others. The addition of an
+> error analysis would help highligh these points, helping to clarify the
+> advantages of the particular approach especially in relation to Brooke et
+> al.
 
-We have added a new paragraph contrasting our method to other algorithms, and an qualitative discussion which doubles as an error analysis.
+We have added a new paragraph contrasting our method to other algorithms, and
+a qualitative discussion which doubles as an error analysis.
 
-Note that we looked at Villavicencio et al.
-2007, but it is very limited in scope (they only deal with trigrams) and doesn't provide any workable comparison in the context of unrestricted FS extraction beyond ranking with simple association measures, which, as we mention, have already been shown to be inferior to the more sophisticated models we are comparing against here.
+Note that we looked at Villavicencio et al. 2007, but it is very limited in
+scope (they only deal with trigrams) and doesn't provide any workable
+comparison in the context of unrestricted FS extraction beyond ranking with
+simple association measures, which, as we mention, have already been shown to
+be inferior to the more sophisticated models we are comparing against here.
 
->The paper should also discuss the motivation for each of the node
-interaction functions for rewarding/penalizing competitive candidates in the
-lattice, including how they are expected to contribute to the overall
-performance of the approach and if the authors considered alternative
-functions or why these in particular, which linguistic intuition they wanted
-to capture, why define E0 in terms of the minLPR and E1 of a cost parameter,
-why they are introduced in the explainedness as exponents (why not using a
-linear dependence, for example. A suggestion for helping the presentation is
-for the authors to rewrite E0 and E1 into a single formula that combines the
-three measures in a utility function, as it would be easier to explain (how
-E0 and E1 compete, under which circumstances each of them wins),
-particularly with the  addition of an example. In addition, when
-presentating these functions, one problem is that although d0 and d1 are
-used to define E0 and E1 in section 3.2, they are only defined in later
-sections (sections 3.3.2 and 3.3.3). As a result the discussion appears too
-abstract as the functions have not been completely defined yet. There should
-be some explanation for their motivation/intuition, as it's not clear what
-they are trying to capture, how E0 and E1 would vary for FS and non-FS, etc.
-My suggestion is to first introduce and motivate the ideas behind them, and
-later define them together. For d1, there is also a difference in the number
-of arguments of "oc" in the text (oc(x,y)) and in the definition of d1
-(oc(oi)). d0 is defined as a uniform combination of clear and cover, but it
-would be helpful to have a discussion of the effects of different weights
-for each of them for the different languages.
+> The paper should also discuss the motivation for each of the node
+> interaction functions for rewarding/penalizing competitive candidates in the
+> lattice, including how they are expected to contribute to the overall
+> performance of the approach and if the authors considered alternative
+> functions or why these in particular, which linguistic intuition they wanted
+> to capture, why define E0 in terms of the minLPR and E1 of a cost parameter,
+> why they are introduced in the explainedness as exponents (why not using a
+> linear dependence, for example. A suggestion for helping the presentation is
+> for the authors to rewrite E0 and E1 into a single formula that combines the
+> three measures in a utility function, as it would be easier to explain (how
+> E0 and E1 compete, under which circumstances each of them wins),
+> particularly with the addition of an example. In addition, when presentating
+> these functions, one problem is that although d0 and d1 are used to define
+> E0 and E1 in section 3.2, they are only defined in later sections (sections
+> 3.3.2 and 3.3.3). As a result the discussion appears too abstract as the
+> functions have not been completely defined yet. There should be some
+> explanation for their motivation/intuition, as it's not clear what they are
+> trying to capture, how E0 and E1 would vary for FS and non-FS, etc.  My
+> suggestion is to first introduce and motivate the ideas behind them, and
+> later define them together. For d1, there is also a difference in the number
+> of arguments of "oc" in the text (oc(x,y)) and in the definition of d1
+> (oc(oi)). d0 is defined as a uniform combination of clear and cover, but it
+> would be helpful to have a discussion of the effects of different weights
+> for each of them for the different languages.
 
-We have reorganized the presentation of the model and are now providing an explicit objective function, at the same time getting rid of the confusing forward pointers and many of the extra symbols.
+We have substantially reorganized the presentation of the model, and are now
+providing an explicit objective function, at the same time getting rid of the
+confusing forward pointers and many of the extra symbols.
 
-We hope that the general purpose of each interaction in terms of the way that it inhibits other nodes is clear.
-We have added a bit more detail about the choice of the clearing function to both that section as well as the discussion.
+We hope that the general purpose of each interaction in terms of the way that
+it inhibits other nodes is clear. We have added a bit more detail about the
+choice of the clearing function to both that section as well as the
+discussion.
 
->In terms of the methodology, a discussion is needed about the motivation for
-adopting Brooke et al.'s lexical predictability ratio (LPR), and for the
-modifications proposed, such as the use of minLPR instead of the product of
-the LPRs and why the focus is on the weakest link (was there any comparison
-between the use of minLPR and the product of LPRs, is it done for efficiency
-reasons, etc).  Moreover, the construction of the lattice needs to be
-explained, including how the nodes relate to one another. For instance, in
-figure 2, the solid lines indicate subsumption, but "keep everything under
-wraps" is linked with "be keep * under" via a subsumption relation, even
-though the latter contains elements that are not in the former (shouldn't it
-be an overlap link?).
+> In terms of the methodology, a discussion is needed about the motivation for
+> adopting Brooke et al.'s lexical predictability ratio (LPR), and for the
+> modifications proposed, such as the use of minLPR instead of the product of
+> the LPRs and why the focus is on the weakest link (was there any comparison
+> between the use of minLPR and the product of LPRs, is it done for efficiency
+> reasons, etc).  Moreover, the construction of the lattice needs to be
+> explained, including how the nodes relate to one another. For instance, in
+> figure 2, the solid lines indicate subsumption, but "keep everything under
+> wraps" is linked with "be keep * under" via a subsumption relation, even
+> though the latter contains elements that are not in the former (shouldn't it
+> be an overlap link?).
 
-We have added a bit more to the discussions of LPR, to be more explicit why LPR is a good metric for our lattice.
-We've also fixed the incorrect relations you mention, which should hopefully resolve the confusion.
+We have added a bit more to the discussions of LPR, to be more explicit why
+LPR is a good metric for our lattice. We've also fixed the incorrect relations
+you mention, which should hopefully resolve the confusion.
 
->In terms of the evaluation, the distinction between contiguous and gapped
-test sets, which are later merged into a single test set per language when
-presenting the results, is not helpful. Instead, maintaining the distinction
-would help clarify the advantages of the proposed approach in each language,
-particularly in relation to the error analysis.
+> In terms of the evaluation, the distinction between contiguous and gapped
+> test sets, which are later merged into a single test set per language when
+> presenting the results, is not helpful. Instead, maintaining the distinction
+> would help clarify the advantages of the proposed approach in each language,
+> particularly in relation to the error analysis.
 
-As we note in the paper, adding the distinction between continguous and gapped simply isn't defensible given the lack of positive gapped examples across some of the datasets (since both precision and recall rely on primarily on true positives).
-We would very much like to present this distinction, but the scores depend primarily on a handful of examples for some of datasets and the results are erratic, they would confuse rather than elucidate.
+As we note in the paper, adding the distinction between continguous and gapped
+simply isn't defensible given the lack of positive gapped examples across some
+of the datasets (since both precision and recall rely on primarily on true
+positives). We would very much like to present this distinction, but the
+scores depend primarily on a handful of examples for some of datasets and the
+results are erratic, they would confuse rather than elucidate.
 
->Additionally, for the
-contiguous n-grams in these languages a comparison with LocalMaxs could be
-done.
+> Additionally, for the contiguous n-grams in these languages a comparison
+> with LocalMaxs could be done.
 
-Actually that's not possible.
-LocalMaxs (like DP-seg) does not scale, due to the fact that it needs to calculate counts for every n-gram in the corpus; it is quicker than DP-Seg, but the memory usage is immense for large corpora.
-We have added a mention of this fact in the paper.
+Actually that's not possible. LocalMaxs (like DP-seg) does not scale, due to
+the fact that it needs to calculate counts for every n-gram in the corpus; it
+is quicker than DP-Seg, but the memory usage is immense for large corpora. We
+have added a mention of this fact in the paper.
 
->Moreover, the authors need to add the statistical significance of the
-results in tables 2 and 3 as the approaches often differ only in the second
-decimal place.
+> Moreover, the authors need to add the statistical significance of the
+> results in tables 2 and 3 as the approaches often differ only in the second
+> decimal place.
 
@@
 
->In Table 2, it would be helpful to have also the results for
-only the cover function (Lattice-cl-ovr), to determine how much the other
-functions contribute.
+> In Table 2, it would be helpful to have also the results for only the cover
+> function (Lattice-cl-ovr), to determine how much the other functions
+> contribute.
 
@@
 
->A figure with the top/bottom candidates proposed by
-the approach be helpful.
+> A figure with the top/bottom candidates proposed by the approach be helpful.
 
-There are no explicit top/bottom candidates in our model, it's not a ranking model and it would be incorrect to present it as such.
-N-grams could be ranked by the explainedness of their node, of course, but that doesn't properly reflect their overall influence in the model.
-We do have a new qualitative analysis with random samples from our lexicon.
+There are no explicit top/bottom candidates in our model, as it's not a
+ranking model and it would be incorrect to present it as such. N-grams could
+be ranked by the explainedness of their node, of course, but that doesn't
+properly reflect their overall influence in the model. We do have a new
+qualitative analysis with random samples from our lexicon.
 
 > Add the list in an appendix for English and explicitly explain the lists for
-Croatian and Japanese. How many expressions and how many cases they cover.
+> Croatian and Japanese. How many expressions and how many cases they cover.
 
-We have added some samples for each language and some general statistics for the lexicons of each language.
-As should be now clear, the lists of expressions generated by the model is far larger than can be included in a paper.
-We will
-be separately releasing all the lexicons.
+We have added some samples for each language and some general statistics for
+the lexicons of each language. As should be now clear, the lists of
+expressions generated by the model are far larger than can be included in a
+paper. We will be separately releasing all the lexicons.
 
 > The paper also needs to add a list of existing MWE lexica or lexical
-resources with MWEs available to the community (e.g. those listed in the MWE
-community website, or available in WordNet or other resources).
+> resources with MWEs available to the community (e.g. those listed in the MWE
+> community website, or available in WordNet or other resources).
 
-We have to demurr on this.
-Our paper is not about MWEs specifically, we do not use MWE resources to build our model nor to evaluate it, so a focus on available MWE resources seems a significant detour, especially given the space constraints.
-It would also be very difficult to do the topic justice, especially given our cross-linguistic interest.
+We have to demurr on this. Our paper is not about MWEs specifically, we do not
+use MWE resources to build our model nor to evaluate it, so a focus on
+available MWE resources seems a significant detour, especially given the space
+constraints.  It would also be very difficult to do the topic justice,
+especially given our cross-linguistic interest.
 
->Stylistically the text would also benefit from a revision that splits
-sentences that are too long (there are several throughout the text). For
-instance, the last sentence in the first paragraph of the introduction is 9
-lines long: 'We present an effective, expand- able, and above all tractable
-new approach to com- prehensive multiword lexicon acquisition that aims to
-find a middle ground between standard MWE ac- quisition approaches based on
-association measures (Ramisch, 2014), and more sophisticated statistical
-models (Newman et al., 2012) which fail to scale to the large corpora which
-are the main sources of the distributional information in modern NLP
-systems.').
+> Stylistically the text would also benefit from a revision that splits
+> sentences that are too long (there are several throughout the text). For
+> instance, the last sentence in the first paragraph of the introduction is 9
+> lines long: 'We present an effective, expand- able, and above all tractable
+> new approach to com- prehensive multiword lexicon acquisition that aims to
+> find a middle ground between standard MWE ac- quisition approaches based on
+> association measures (Ramisch, 2014), and more sophisticated statistical
+> models (Newman et al., 2012) which fail to scale to the large corpora which
+> are the main sources of the distributional information in modern NLP
+> systems.').
 
@@
 > Moreover, some passages are copied from Brooke et al. (2015), but lack the
-citation, such as:
-     *"Other mea- sures specifically designed to address sequences of larger
-than two words include: the c-value (Frantzi et al., 2000), a metric
-designed for term extraction which weights term frequency by the log length
-of the n-gram while penalizing n-grams that appear in frequent larger ones;
-and mutual expectation (Dias et al., 1999), which produces a normalized
-statistic that reflects how much a candidate phrase resists the omission of
-any particular word." (page 2) and
-     *"include that of Newman et al. (2012), who used a generative Dirichlet
-Process model which jointly creates a linear segmentation of the corpus and
-a multiword vocabulary" (page 3)
-There are also other instances, and these need to be rephrased.
+> citation, such as:
+>      *"Other mea- sures specifically designed to address sequences of larger
+> than two words include: the c-value (Frantzi et al., 2000), a metric
+> designed for term extraction which weights term frequency by the log length
+> of the n-gram while penalizing n-grams that appear in frequent larger ones;
+> and mutual expectation (Dias et al., 1999), which produces a normalized
+> statistic that reflects how much a candidate phrase resists the omission of
+> any particular word." (page 2) and
+>      *"include that of Newman et al. (2012), who used a generative Dirichlet
+> Process model which jointly creates a linear segmentation of the corpus and
+> a multiword vocabulary" (page 3)
+> There are also other instances, and these need to be rephrased.
 
-We have rephrased the relevant parts of the literature review, though the basic content is unchanged.
+We have rephrased the relevant parts of the literature review, though the
+basic content is unchanged.
 
 > For the annotations, the text mentions 3 annotators, but doesn't specify
-whether they were different for each of the 3 languages.
+> whether they were different for each of the 3 languages.
 
-Yes, they were different for each of the 3 languages.
-Since they were native (first language) speakers of each of the relevant languages, we believe this implies that they were different across languages.
+Yes, they were different for each of the 3 languages. Since they were native
+(first language) speakers of each of the relevant languages, we believe this
+implies that they were different across languages.
 
-> When comparing the
-languages, the paper also mentions that "free word order actually results in
-more of a ten- dency towards contiguous FS, not less.", but it is unclear
-where this is shown.
+> When comparing the languages, the paper also mentions that "free word order
+> actually results in more of a tendency towards contiguous FS, not less.",
+> but it is unclear where this is shown.
 
@@
 
-* “accessible by analogy (e.g., glass limb or government ambiguity)” by
-analogy with what? Specify and add the original expression
+> * “accessible by analogy (e.g., glass limb or government ambiguity)” by
+> analogy with what? Specify and add the original expression
 
@@
 
-* “define the explainedness of a node in terms of two functions” Which
-two functions?
+> * “define the explainedness of a node in terms of two functions” Which two
+> functions?
 
@@
 
-* In section 3.2 can the authors explain how two valid but similar FSs would
-be treated  (e.g. keep * under wraps/surveillance)?
+> * In section 3.2 can the authors explain how two valid but similar FSs would
+> be treated (e.g. keep * under wraps/surveillance)?
 
@@
 
-* "We also use the concept of hard covering to ad- dress the issue of
-pronouns, based on the observation that pronouns often have high LPR
-values". This sentence is too vague. Explain using an example.
+> * "We also use the concept of hard covering to ad- dress the issue of
+> pronouns, based on the observation that pronouns often have high LPR
+> values". This sentence is too vague. Explain using an example.
 
@@
 
-* How was the 2/3 threshold for hard covering determined? Why also have soft
-covering?
+> * How was the 2/3 threshold for hard covering determined? Why also have soft
+> covering?
 
-Using performance in the (English) development set, we have made that clearer.
-Our intention is that the  "keep * under wraps/surveillance" example shows why soft covering is also important, we have added a bit more explanation.
+Using performance in the (English) development set, we have made that
+clearer. Our intention is that the "keep * under wraps/surveillance" example
+shows why soft covering is also important, we have added a bit more
+explanation.
 
 > * "has been turned on, the covering, blocking, or overlap- ping effects of
-these other nodes" --> blocking shoud be clearing
+> these other nodes" --> blocking shoud be clearing
 
@@
 > * For the efficiency restrictions explain if other values have been tested
-for them. How did they affect the overall performance? A table detailing the
-behavior with different values would be helpful.
+> for them. How did they affect the overall performance? A table detailing the
+> behavior with different values would be helpful.
 
-We've added a bit more detail, though perhaps not as much as you're asking for.
+We've added a bit more detail, though perhaps not as much as you're asking for
+(due to space limitations).
 
 > * "which was roughly the same size (in terms of token count) as the English
-corpus" specify which English corpus
+> corpus" specify which English corpus
 
@@
 > * In Table 1 the values are less than 2000 (for ICWSM) and 1000 for the
-other corpora. Add also the initial numbers for each type of FS/non-FS.
+> other corpora. Add also the initial numbers for each type of FS/non-FS.
 
-As we mention in the text, to improve the reliability of our evaluation we drop instances where just one annotator tagged as FS.
-This obviously results in test sets that are less than the original sample size.
-This should now be clearer.
+As we mention in the text, to improve the reliability of our evaluation we
+drop instances where just one annotator tagged as FS. This obviously results
+in test sets that are less than the original sample size. This should now be
+clearer.
 
-Reviewer B
+REVIEWER B
 
-> Assuming that the solution is indeed scalable and
-empirically viable -- I am wondering if the same idea could be used in the
-context of other tasks (morphological composition in morphological lattices,
-preferred expressions in lattices of proposed machine translations, etc). It
-would be nice if the author could comment on the applicability of the
-technical solution in other domains (if there is any).
+> Assuming that the solution is indeed scalable and empirically viable -- I am
+> wondering if the same idea could be used in the context of other tasks
+> (morphological composition in morphological lattices, preferred expressions
+> in lattices of proposed machine translations, etc). It would be nice if the
+> author could comment on the applicability of the technical solution in other
+> domains (if there is any).
 
@@
 
->In the case of syntax, much research in theoretical linguistics and in
-language technology has proposed the idea that idiomatic expressions (of
-which MWEs are a special case) are the rule, rather than the exception, in
-NL grammar. Among the theoretical proposal one can find versions of
-Construction Grammar (Goldberg 1996) where language knowledge is composed of
-complete constructions, rather than primitive units (words) and in
-technological proposals one can find the idea of Data-Oriented Parsing
-(Remko Scha, Rens Bod), wherein each syntactic subtree (with potential slots
-for substitution) is an FS-like element that can potentially be used and
-reused for analysis and generation. And so: while the relation of the
-proposed FS to existing theories of strongly lexicalized fixed expressions
-on the one end is clear, it is unclear what is the relation  larger
-idiomatic syntactic constructions with lexicalized or unlexicalized slots on
-the other end -- and this relation should be made clear, for the work to be
-properly situated.
+> In the case of syntax, much research in theoretical linguistics and in
+> language technology has proposed the idea that idiomatic expressions (of
+> which MWEs are a special case) are the rule, rather than the exception, in
+> NL grammar. Among the theoretical proposal one can find versions of
+> Construction Grammar (Goldberg 1996) where language knowledge is composed of
+> complete constructions, rather than primitive units (words) and in
+> technological proposals one can find the idea of Data-Oriented Parsing
+> (Remko Scha, Rens Bod), wherein each syntactic subtree (with potential slots
+> for substitution) is an FS-like element that can potentially be used and
+> reused for analysis and generation. And so: while the relation of the
+> proposed FS to existing theories of strongly lexicalized fixed expressions
+> on the one end is clear, it is unclear what is the relation larger idiomatic
+> syntactic constructions with lexicalized or unlexicalized slots on the other
+> end -- and this relation should be made clear, for the work to be properly
+> situated.
 
-Note that we are not ourselves proposing FS, we are borrowing the theory behind FS from the work of Wray (2002;2008), who includes an extremely thorough discussion of its relationship to other linguistic theories (Chapter 7 of the 2008
-book in particular), including Construction Grammar.
-We have added a bit more detail to our introduction of FS to make it clear that, yes, most "constructions" are FS, and we have added constructions to Figure 1.
-However, ultimately
-this is a technical paper, and we are limited in the space we can dedicate to theoretical concerns.
+Note that we are not ourselves proposing FS, we are borrowing the theory
+behind FS from the work of Wray (2002;2008), who includes an extremely
+thorough discussion of its relationship to other linguistic theories (Chapter
+7 of the 2008 book in particular), including Construction Grammar. We have
+added a bit more detail to our introduction of FS to make it clear that, yes,
+most "constructions" are FS, and we have added constructions to Figure
+1. However, ultimately this is a technical paper, and we are limited in the
+space we can dedicate to theoretical concerns.
 
 > The case of morphology is far less clear, however it is equally important,
-and it has to do with the basic question of what is the unit that constructs
-the FS (or the lattices themselves in empirical terms). Are these words?
-morphemes? lemmas? POS? inflections? In the case  of words, what is the
-relation of inflected sequences forms / inflected idioms (kicked his bucket
-vs kicked her bucket, for instance) -- are they the same? related?
-overalapping? subsumed?. As it stands, the discussion of morphology comes
-out only later as an afterthought -- where the construction of the lattice
-in Japanese (in the evaluation section) involves some morphological
-segmentation whereas the lattice construction for the other languages
-doesn't. It is thus unclear if the algorithm finds sequences that are of the
-same type, or are comparable for that matter, across those languages. The
-selected FS may be incomparable in terms of effective length (morpheme
-sequences tend to be longer), the status of function words vs. inflection in
-FS, and so on. The authors should put forth clearly what is the status of
-morphology inside their general theory (and in terms of their regular
-expressions), and then later revisit the empirical ramifications of their
-decision -- for instance what happens when moving between typologically
-different languages.
+> and it has to do with the basic question of what is the unit that constructs
+> the FS (or the lattices themselves in empirical terms). Are these words?
+> morphemes? lemmas? POS? inflections? In the case of words, what is the
+> relation of inflected sequences forms / inflected idioms (kicked his bucket
+> vs kicked her bucket, for instance) -- are they the same? related?
+> overalapping? subsumed?. As it stands, the discussion of morphology comes
+> out only later as an afterthought -- where the construction of the lattice
+> in Japanese (in the evaluation section) involves some morphological
+> segmentation whereas the lattice construction for the other languages
+> doesn't. It is thus unclear if the algorithm finds sequences that are of the
+> same type, or are comparable for that matter, across those languages. The
+> selected FS may be incomparable in terms of effective length (morpheme
+> sequences tend to be longer), the status of function words vs. inflection in
+> FS, and so on. The authors should put forth clearly what is the status of
+> morphology inside their general theory (and in terms of their regular
+> expressions), and then later revisit the empirical ramifications of their
+> decision -- for instance what happens when moving between typologically
+> different languages.
 
-We have added a bit more to both the introduction of FS as well as a paragraph in the discussion that addresses this point.
-Ultimately, in all three languages we are tokenizing and lemmatizing using standards for each language, and building our FS from the result.
-However, this is not a theoretical choice, but a practical one; it is undeniable that FSes often involve morphological components that we are overlooking.
-With Japanese, due to the lack of word boundaries, morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal.
-Given that many of the case markers of Japanese correspond to prepositions in European languages (or the possesive marker in English), the actual difference in generated FS is fairly minor, except for the extra overhead of word segmentation in Japanese that is provided by word boundaries in English (in Wray's theory, most words would be FS by default).
+We have added a bit more to both the introduction of FS as well as a paragraph
+in the discussion that addresses this point. Ultimately, in all three
+languages we are tokenizing and lemmatizing using standards for each language,
+and building our FS from the result. However, this is not a theoretical
+choice, but a practical one; it is undeniable that FSes often involve
+morphological components that we are overlooking.  With Japanese, due to the
+lack of morpheme boundaries, morphological segmentation is a more standard
+form of tokenization, and so we have taken advantage of this to bring Japanese
+somewhat closer to our theoretical ideal. Given that many of the case markers
+of Japanese correspond to prepositions in European languages (or the possesive
+marker in English), the actual difference in generated FS is fairly minor,
+except for the extra overhead of word segmentation in Japanese that is
+provided by word boundaries in English (in Wray's theory, most words would be
+FS by default).
 
->The author discuss at length the method, the construction of the lattice,
-and possible relation between arcs (covering clearing and overlapping) and
-their related scores. The objective function however and the respective
-optimisation algorithm are discussed informally in passing. I would much
-prefer a more precise formalisation of the objective function and greedy
-algorithm, possibly with a running example of several states of progress of
-the algorithm over a sample lattice. This would also help to clarify what
-"locality properties" are at play here, which justify a greedy solution that
-is locally optimised. As a more general note, I think it should be made
-clear if the target of the lattice construction is a single lattice for the
-entire text, optimized at once, or multiple lattices, reflecting different
-aspects of the vocabulary, optimized separately.  As a minor note, there are
-two many forward references in the text, IMO, which hinder
-understandability. Example "where d1 and d2 are ... as detailed in the next
-section". I would prefer the details closer to where they are relevant.
+> The author discuss at length the method, the construction of the lattice,
+> and possible relation between arcs (covering clearing and overlapping) and
+> their related scores. The objective function however and the respective
+> optimisation algorithm are discussed informally in passing. I would much
+> prefer a more precise formalisation of the objective function and greedy
+> algorithm, possibly with a running example of several states of progress of
+> the algorithm over a sample lattice. This would also help to clarify what
+> "locality properties" are at play here, which justify a greedy solution that
+> is locally optimised. As a more general note, I think it should be made
+> clear if the target of the lattice construction is a single lattice for the
+> entire text, optimized at once, or multiple lattices, reflecting different
+> aspects of the vocabulary, optimized separately.  As a minor note, there are
+> two many forward references in the text, IMO, which hinder
+> understandability. Example "where d1 and d2 are ... as detailed in the next
+> section". I would prefer the details closer to where they are relevant.
 
-Thank you for your suggestions.
-We have reorganized the expanation of the method to remove forward references, and have provided an explict objective function and algorithm.
-We decided, though, that a full example of the optimization algorithm involved too much overhead with only modest explanatory benefits.
+Thank you for your suggestions. We have reorganized the expanation of the
+method to remove forward references, and have provided an explict objective
+function and algorithm. We decided, though, that a full example of the
+optimization algorithm involved too much overhead with only modest explanatory
+benefits.
 
-By "text", you mean corpus, right? It is hopefully clear that the algorithm 
+By "text", we assume you mean corpus. It is hopefully clear that the algorithm
 works at the level of all n-grams for the corpus, and not texts within the
-
 corpus (this is what makes the model practical relative to token-level models
 like DP-seg); the nodes of the lattice are n-gram types, not tokens. As it
-happens, most nodes are connected to most other nodes by some pathway in 
-the lattice, but there are nodes (mostly individual bigrams) which do not, 
-and thus are not part of the main lattice.
+happens, most nodes are connected to most other nodes by some pathway in the
+lattice, but there are nodes (mostly individual bigrams) which do not, and
+thus are not part of the main lattice.
 
 > It is unclear to me why comparing the collected lexicon using the proposed
-method to a sample set of ngrams that respond to a certain frequency
-threashold is a sound comparison-- isnt the frequency threashold just a
-simpler and less sophisticated baseline for MWE extraction? It appears that
-you use this method not as a baseline, but as an actual method to extract
-gold standard for comparison with your method. I understand that others have
-used such evaluation methods before -- but I would need much more convincing
-in order to accept the claim of efficacy. If I misunderstood, and you do not
-use it as a gold for comparison, or you use a different gold, please
-clarify.
+> method to a sample set of ngrams that respond to a certain frequency
+> threashold is a sound comparison-- isnt the frequency threashold just a
+> simpler and less sophisticated baseline for MWE extraction? It appears that
+> you use this method not as a baseline, but as an actual method to extract
+> gold standard for comparison with your method. I understand that others have
+> used such evaluation methods before -- but I would need much more convincing
+> in order to accept the claim of efficacy. If I misunderstood, and you do not
+> use it as a gold for comparison, or you use a different gold, please
+> clarify.
 
-We are not entirely sure we are intepreting your concern correctly.
-If the reviewer believes that we are using high-frequency n-grams directly as a gold standard (i.e.
-we assume that high frequency n-grams are FS simply by virtue of their high frequency), then you have definitely misunderstood: this should be clear given the discussion of the annotation process, where we taken the n-grams and annotated them as being FS or not.
-To make this absolutely clear, we have included frequency as a baseline association score.
-It is poor, but obviously would be unbeatable if our gold standard was built based simply on frequency.
+We are not entirely sure we are intepreting your concern correctly. It is
+certainly not the case that we are using high-frequency n-grams directly as a
+gold standard (i.e. we assume that high frequency n-grams are FS simply by
+virtue of their high frequency): this should be clear given the discussion of
+the annotation process, where we taken the n-grams and annotated them as being
+FS or not. To make this absolutely clear, we have included frequency as a
+baseline association score. It is poor, but obviously would be unbeatable if
+our gold standard was built based simply on frequency.
 
-A more subtle issue is that using frequency-filtered n-grams as the sampling pool for our FS gold standard means that there are FS in the corpus that cannot possibilty be considered in the evaluation because they do not appear sufficiently.
-This is true, and unavoidable in this evaluation setup.
-As discussed in Brooke et al.
-2015, sampling from frequent n-grams in the corpus brings with it a number of benefits: in particular, the test set reflects the variety of FS that appear throughout the entire corpus (many of which would not appear in any existing lexicon or in a small sample of texts), annotators can look at variety of examples to make an judgement, and (most importantly) it is possible to calculate a proper F-score.
-The trade-off, however, is that there needs to be some initial filtering of the sample so that annotation process is not "finding a needle in the haystack" as it would be if you considered all n-grams in the corpus.
-As we discuss in 3.1, we investigated coverage in an existing English MWE annotated corpus using n-grams from the ICWSM after applying frequency cutoffs and found that type coverage is quite good (token coverage is even better, of course); that is, we are not losing very many FS with our filtering, at least not ones that occur across corpora of the similar genre (both are social media corpora).
-With a large corpus and an appropriately low frequency cutoff, we believe that annotations of frequency filtered n-gram samples is a reasonable way to solve what is without a doubt a very challenging evaluation problem.
-We have added a slightly longer justification of the evaluation method to the paper.
+A more subtle issue is that using frequency-filtered n-grams as the sampling
+pool for our FS gold standard means that there are FS in the corpus that
+cannot possibilty be considered in the evaluation because they do not appear
+sufficiently. This is true, and unavoidable in this evaluation setup. As
+discussed in Brooke et al. 2015, sampling from frequent n-grams in the corpus
+brings with it a number of benefits: in particular, the test set reflects the
+variety of FS that appear throughout the entire corpus (many of which would
+not appear in any existing lexicon or in a small sample of texts), annotators
+can look at variety of examples to make an judgement, and (most importantly)
+it is possible to calculate a proper F-score. The trade-off, however, is that
+there needs to be some initial filtering of the sample so that annotation
+process is not "finding a needle in the haystack" as it would be if you
+considered all n-grams in the corpus. As we discuss in 3.1, we investigated
+coverage in an existing English MWE annotated corpus using n-grams from the
+ICWSM after applying frequency cutoffs and found that type coverage is quite
+good (token coverage is even better, of course); that is, we are not losing
+very many FS with our filtering, at least not ones that occur across corpora
+of the similar genre (both are social media corpora). With a large corpus and
+an appropriately low frequency cutoff, we believe that annotations of
+frequency filtered n-gram samples is a reasonable way to solve what is without
+a doubt a very challenging evaluation problem. We have added a slightly longer
+justification of the evaluation method to the paper.
 
-Reviewer C:
+REVIEWER C:
 
-> Where I had trouble was with the details of the model. First of all, much ofit seemed to be ad hoc; even accepting the notion of LPR from prior work,
-there are many heuristic (or at least not obviously natural) choices made to
-operationalize the general lattice idea mathematically. Second, even if the
-model is reasonable, it is not entirely clear how the different parts fit
-together into an optimization problem. There is mention of a parameter C;
-and there is a notion of nodes being activated or not (I don’t think
-notation is introduced for these binary variables, though it would be
-appropriate). Are these the only things that have to be tuned? Is the
-calculation of explainedness deterministic based on these? There is a greedy
-search to optimize explainedness of the nodes in the lattice, subject to
-various heuristics. Presenting a formal algorithm for the optimization may
-clarify things considerably.
+> Where I had trouble was with the details of the model. First of all, much
+> ofit seemed to be ad hoc; even accepting the notion of LPR from prior work,
+> there are many heuristic (or at least not obviously natural) choices made to
+> operationalize the general lattice idea mathematically. Second, even if the
+> model is reasonable, it is not entirely clear how the different parts fit
+> together into an optimization problem. There is mention of a parameter C;
+> and there is a notion of nodes being activated or not (I don’t think
+> notation is introduced for these binary variables, though it would be
+> appropriate). Are these the only things that have to be tuned? Is the
+> calculation of explainedness deterministic based on these? There is a greedy
+> search to optimize explainedness of the nodes in the lattice, subject to
+> various heuristics. Presenting a formal algorithm for the optimization may
+> clarify things considerably.
 
-We have reorganized the method section and added an explicit objective function, which should help with some of the problems you identified.
-In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g.
-the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have a included psuedocode for optimization algorithm.
-With regards to the ad hoc parts of the model, we have added a discussion separating the core aspects of the model from some of the more ad hoc choices made in the particular instantions of component functions (such as clearing), making it clear that we believe these can potentially be improved on (both in terms of performance as well as mathematical elegance), and that our primary purpose here is to show that overall architecture of the model is a promising one.
+We have reorganized the method section and added an explicit objective
+function, which should help with some of the problems you identified. In terms
+of the central optimization problem, the only variables are exactly the on/off
+status of each node, and, if we exclude the parameters used in the creation of
+the lattice (e.g. the n-gram frequency threshold) and those involved in the
+efficiency restrictions, the only (hyper)parameter in the optimization is C;
+we have a included psuedocode for optimization algorithm. With regards to the
+ad hoc parts of the model, we have added a discussion separating the core
+aspects of the model from some of the more ad hoc choices made in the
+particular instantions of component functions (such as clearing), making it
+clear that we believe these can potentially be improved on (both in terms of
+performance as well as mathematical elegance), and that our primary purpose
+here is to show that overall architecture of the model is a promising one.
 
-> I think it would also be worth discussing how the lattice model relates back to the cognitive/psychological literature. Would you predict (or are you
-aware of any evidence) that node interactions such as covering, clearing,
-and overlapping have an analogue in human language processing? Do any of the
-design decisions intentionally sacrifice cognitive plausibility for
-engineering reasons?
+> I think it would also be worth discussing how the lattice model relates back
+> to the cognitive/psychological literature. Would you predict (or are you
+> aware of any evidence) that node interactions such as covering, clearing,
+> and overlapping have an analogue in human language processing? Do any of the
+> design decisions intentionally sacrifice cognitive plausibility for
+> engineering reasons?
 
-In general, we did not consider cognitive plausibility when creating the model, and we are certainly making no claims as such.
-For starters, our model makes use of more data than a human being could possibly read in a lifetime, it is clear humans identify FS with far less evidence than our model requires.
-With space, we could discuss our model in the context of the more cognative aspects of the theory of formulaic sequences as proposed by Wray, but given that this wasn't a focus in the development of the model, we think it is really too much of a digression to justify.
+In general, we did not consider cognitive plausibility when creating the
+model, and we are certainly making no claims as such. For starters, our model
+makes use of more data than a human being could possibly read in a lifetime,
+and it is clear humans identify FS with far less evidence than our model
+requires. With space, we could discuss our model in the context of the more
+cognitive aspects of the theory of formulaic sequences as proposed by Wray,
+but given that this wasn't a focus in the development of the model, we think
+it is really too much of a digression to justify.
 
 > - After the equation for LPR, it would be good to give the intuition:
-choosing a context span such that w_i is more likely given its context words
-than its context POS tags.
+> choosing a context span such that w_i is more likely given its context words
+> than its context POS tags.
 
-This was removed from an earlier draft for space, and we've added back in.
+This was removed from an earlier draft due to space, and we've added back in.
 
->- Inter-annotator agreement is surprisingly high. Could you elaborate on
-Wray’s criteria for FS that were applied by annotators?
+> - Inter-annotator agreement is surprisingly high. Could you elaborate on
+> Wray’s criteria for FS that were applied by annotators?
 
-Your surprise about the the Kappa being high is based on a misunderstanding: the kappa number reported in the table is after filtering to remove borderline cases (i.e.
-it is the kappa for the final test set, not the original sampling).
-To avoid confusion, we've added the original kappa score which is quite a bit lower.
-Your intution is correct that there is significant subjectivity to FS identification (more so than MWE annotation), and as such we would never rely on a single annotator for building a FS test set.
-We have not added more information about Wray's criteria; though it provide a starting point for annotation, more relevant to achieving reasonable agreement are the specific annotation guidelines which we created.
-Presenting them in the paper would be too much of a digression, but we promise to make them public.
+Your surprise about the the Kappa being high is based on a misunderstanding:
+the kappa number reported in the table is after filtering to remove borderline
+cases (i.e. it is the kappa for the final test set, not the original
+sampling). To avoid confusion, we've added the original kappa score which is
+quite a bit lower. Your intution is correct that there is significant
+subjectivity to FS identification (more so than MWE annotation), and as such
+we would never rely on a single annotator for building a FS test set. We have
+not added more information about Wray's criteria; though it provide a starting
+point for annotation, more relevant to achieving reasonable agreement are the
+specific annotation guidelines which we created. Presenting them in the paper
+would be too much of a digression, but we promise to make them public.
 
 > - I would like to see qualitative analysis of the sequences that were
-identified as formulaic (or not) by annotators/the method. E.g.: How many of
-them are syntactic constituents? Are there a wide variety of grammatical
-kinds of expressions? Are high-frequency as well as low-frequency sequences
-detected? What is the distribution in terms of length? What kinds of gapped
-sequences are there? It would be nice to see some examples.
+> identified as formulaic (or not) by annotators/the method. E.g.: How many of
+> them are syntactic constituents? Are there a wide variety of grammatical
+> kinds of expressions? Are high-frequency as well as low-frequency sequences
+> detected? What is the distribution in terms of length? What kinds of gapped
+> sequences are there? It would be nice to see some examples.
 
-In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the information you ask for (implicitly if not explicitly).
+In the discussion, we have added a thorough analysis of specific examples and
+some statistics, including most of the information you ask for (implicitly if
+not explicitly).
 
 > - Related to the previous point: While noting the distinction between FS and
-MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
-apart from proper names should count as FS, right?
+> MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
+> apart from proper names should count as FS, right?
 
-Do you mean as a way of evaluating different systems built on the same corpus, or just to get a sense of coverage more generally?
-One central problem with using recall for evaluation is that in order to make it fair, there must be some control of the size of the lexicon.
-Neither our system nor our best performing competitors are ranking models, none of them offer an easy or fair way to simply take the best N words and look at recall.
-And even if they did, there's other kinds of biases that would come into play: for instance, PMI and similar metrics do well with rare terms that correspond well to the MWE lexicon of WordNet, for instance, which (at the type level) is dominated by certain kinds of terminology (biomedical terms, particularly) which are not really used outside a very specific community.
-This relates to a more fundamental problem with the idea of using recall in external lexicons as any kind of useful measure: we could not expect any particular corpus (even a very large one) to do justice to the full range of FS/MWE for a language, since most of which appear regularly only within specific genres.
-For example, we could not expect to build a good lexicon of English verb-particle constructions from a biomedical corpus, because many are too informal to be appropriate for that genre (e.g.
-"mess up").
-With the qualitative analysis we have added, the genre-specificity of the FS we extra is hopefully more clear.
+Do you mean as a way of evaluating different systems built on the same corpus,
+or just to get a sense of coverage more generally? One central problem with
+using recall for evaluation is that in order to make it fair, there must be
+some control of the size of the lexicon. Neither our system nor our best
+performing competitors are ranking models, none of them offer an easy or fair
+way to simply take the best N words and look at recall. And even if they did,
+there's other kinds of biases that would come into play: for instance, PMI and
+similar metrics do well with rare terms that correspond well to the MWE
+lexicon of WordNet, for instance, which (at the type level) is dominated by
+certain kinds of terminology (biomedical terms, particularly) which are not
+really used outside a very specific community. This relates to a more
+fundamental problem with the idea of using recall in external lexicons as any
+kind of useful measure: we could not expect any particular corpus (even a very
+large one) to do justice to the full range of FS/MWE for a language, since
+most of which appear regularly only within specific genres. For example, we
+could not expect to build a good lexicon of English verb-particle
+constructions from a biomedical corpus, because many are too informal to be
+appropriate for that genre (e.g. "mess up"). With the qualitative analysis we
+have added, the genre-specificity of the FS we extra is hopefully more clear.
 
-Though it perhaps does not directly address your comment (since it doesn't involve an external MWE lexicon), we were nonetheless inspired by your comments to include an analysis of the recall of MWE vs.
-non-MWE FS in the context of our existing ICWSM test set, and a small investigation of the recall (also in the ICWSM) of extremely common MWE from another MWE-annotated social media corpus.
+Though it perhaps does not directly address your comment (since it doesn't
+involve an external MWE lexicon), we were nonetheless inspired by your
+comments to include an analysis of the recall of MWE vs. non-MWE FS in the
+context of our existing ICWSM test set, and a small investigation of the
+recall (also in the ICWSM) of extremely common MWE from another MWE-annotated
+social media corpus.
 
->Typographical issues:
+> Typographical issues:
 
-- The ovals in Figure 1 and the edges in Figure 2 show up for me on screen
-(OS X Preview) but not when printed.
-- “pairing down” -> paring down
-- “what is typically considered MWE” -> are…MWEs
-- “could be useful addition” -> *a* useful addition
-- "When the minLPR metric is 1 (crresponding to the case of the syntactic
-content predicting": content -> context?
+<snip>
 

### 2017-05-30 tacl.tex
Final edits

@@
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probabilities to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
-The work of \newcite{Newman12} is an example of an unsupervised approach which does not use association measures: it extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
+The work of \newcite{Newman12} is an example of an unsupervised approach which does not use association measures: it extends the Bayesian word segmentation approach of \newcite{Goldwater09} to multiword tokenization, applying a generative Dirichlet Process model which jointly constructs a segmentation of the corpus and a corresponding multiword vocabulary.
 
@@
 To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
-\tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Cohen's Kappa scores before (Pre) and after (Post).
+\tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Cohen's Kappa scores before (``Pre'') and after (``Post'').
 The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
@@
 Bold is best in a given column.
-For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all p-values based on the permutation test (Yeh, 2000).}
+For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all p-values based on the permutation test \protect\cite{yeh2000more}.}
 	 \label{tab:main}
@@
 When only covering is used, the results are fairly similar to \newcite{Brooke15b}, which is unsurprising given the extent to which decomposition and covering are related.
-The Japanese and ICWSM corpus have relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.
+The Japanese and ICWSM corpora have relatively high precision and low recall, whereas both the BNC and Croatian corpora have low precision and high recall.
 
@@
 \midrule
-English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
-English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & 7.7 \\
-Croatian & 172k & 6.7k & 7.9& 55.0& 31.4 & 10.3 & 3.2 \\
-Japanese & 218k &  29.4k &7.9& 39.5 & 31.1& 16.8 & 12.6 \\
+English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & \z7.5  \\
+English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & \z7.7 \\
+Croatian & 172k & \z6.7k & \z7.9& 55.0& 31.4 & 10.3 & \z3.2 \\
+Japanese & 218k &  29.4k &\z7.9& 39.5 & 31.1& 16.8 & 12.6 \\
 \bottomrule
@@
 Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms.
-This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of potential in automatic extraction comes from the long tail.
+This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of the potential in automatic extraction comes from the long tail.
 However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) from the \newcite{Schneider14a} corpus.
@@
 
-\nocite{yeh2000more}
-
 \bibliography{mybib}

### 2017-05-30 reviewer_response.txt
Revised submission

@@
+Submission # 1137
+Action Editor: Noah Smith
+
 We would like to thank all of our reviewers for their detailed comments. We
@@
 
-We should mention one change that wasn't prompted by individual reviewer
-comments: there were clear misinterpretations by our Japanese annotators from
-the first round with led to overannotation of FS, leading us to to another
-round of annotation and since the original submission. The Japanese results
-have therefore changed somewhat, and are in fact more consistent with the
-other languages.
+We should mention one major change that wasn't prompted by individual reviewer
+comments: there were clear misinterpretations by our original Japanese annotators
+which led to overannotation of FS, leading us to do another round of annotation 
+since the original submission. The Japanese results have therefore changed, and
+are in fact more consistent with the other languages.
 
@@
 
-We have added statistical significance information.
+We have added some statistical significance information.
 
@@
 
-Thank you for your suggestion. We have split up some of the longer sentences, hopefully improving the readability.
+Thank you for your suggestion. We have split up some of the longer sentences, 
+hopefully improving the readability.
 
@@
 
-The only kind of interaction between these nodes involves their shared n-gram subsequence (keep * under), as described in the example in the paper. We have expanded the example a bit.
+The only kind of interaction between these nodes involves their shared n-gram 
+subsequence (keep * under), as described in the example in the paper. We have 
+expanded the example a bit.
 
@@
 
-This is interesting, and so we've added a discussion of the morphology idea to the paper (The short answer is yes).
+This is interesting, and so we've added a discussion of the morphology idea to
+the paper (The short answer is yes).
 
@@
 
-Your surprise about the the Kappa being high is based on a misunderstanding:
+Your surprise about the Kappa being high is based on a misunderstanding:
 the kappa number reported in the table is after filtering to remove borderline
@@
 appropriate for that genre (e.g. "mess up"). With the qualitative analysis we
-have added, the genre-specificity of the FS we extra is hopefully more clear.
+have added, the genre-specificity of the FS we extract is hopefully more clear.
 

### 2017-05-30 resubmission-pkg.tex
Revised submission

\documentclass{article}[11pt,oneside]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INPUTS FOR THE NEW PAPER
\newcommand{\subtitle}{Unsupervised Acquisition of Comprehensive Multiword Lexicons using Competition in an $n$-gram Lattice}
\title{Resubmission of TACL \#1137, \\ \subtitle.   \\}

\newcommand{\resubmission}{tacl.pdf}  %% revised version
\newcommand{\origdecision}{original_letter.pdf}  %% name of anonymized original-decision-letter file
\newcommand{\coverfile}{reviewer_response.pdf}  %% name of anonymized cover-letter file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=blue,  %choose some color if you want links to stand out
}
\usepackage{ifthen}
\usepackage{xspace}

\usepackage{times}
\usepackage{fullpage}
\usepackage{pdfpages}

\special{papersize=8.5in,11in}
\pdfpageheight\paperheight
\pdfpagewidth\paperwidth
\setlength\topmargin{-7mm} \setlength\oddsidemargin{-0cm}
\setlength\textheight{22cm} \setlength\textwidth{15.8cm}
\setlength\columnsep{0.25in}  \newlength\titlebox \setlength\titlebox{2.00in}
\setlength\headheight{5pt}   \setlength\headsep{0pt}
\setlength\footskip{1.9cm}
\setlength\leftmargin{0.0in}
\pagestyle{plain}

\setlength{\footskip}{55pt}

\begin{document}
\maketitle

\tableofcontents

\section{Author(s) cover letter responding to the original reviews} Starts on next page.
\includepdf[pages=-,offset=0mm 6mm]{\coverfile}
\section{Revised submission} Starts on next page.
\includepdf[pages=-,offset=0mm 6mm]{\resubmission}
\section{Original decision letter and reviews} Starts on next page.
\includepdf[pages=-,offset=0mm 6mm]{\origdecision}

\end{document}

### 2017-05-30 tacl.tex
Revised submission

@@
 \end{displaymath}
-This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed.
+When applied as an exponent to a minLPR score, it serves as simple, quick-to-calculate approximation of a new minLPR with the counts corresponding to the covering nodes removed from the calculation.
 The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering occurs.
@@
 \termdef{Clearing} does this by increasing the explainedness of nodes higher in the lattice when a lower node is turned-on.
-The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.
+The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams can be directly attributed to the covering $n$-gram), in the reverse direction this logic fails.
 
@@
 To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
-\tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Cohen's Kappa scores before (``Pre'') and after (``Post'').
+\tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Fleiss' Kappa scores before (``Pre'') and after (``Post'').
 The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
@@
 The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise.
-Some FS are dialectal variants, for instance \ex{license endorsed} refers to the British traffic violations.
+Some FS are dialectal variants, for instance \ex{license endorsed} refers to British traffic violations.
 More generally, the FS lexicons created by these two corpora are quite distinct, sharing less than 50\% of their entries.
@@
 In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).
-%In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting potential for improvement.
+In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting the potential for improved handling of this issue.
 
@@
 
-Though we have demonstrated that competition within a lattice is a powerful method for the production of FS lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research.
+Though we have demonstrated that competition within a lattice is a powerful method for the production of multiword lexicons, its usefulness derives less from the specific choices we have made in this instantiation of the model, and more from the flexiblity that such a model provides for future research.
 Not only do alternatives like DP-seg and LocalMaxs fail to scale up to large corpora, there are few obvious ways to improve on their simple underlying algorithms without compromising their elegance and worsening tractability.

### 2017-07-19 response_2.txt
added new response

Reviewer A

>*The annotation guidelines are needed to ensure replicability. Add them as
appendix material.

We've added them, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al. 2015 (though there was some editing, additions, and consolidations, and well as translations into other languages and adaptions to language specific phenomena).

> *In table 5 these examples include a lot of noise. Can the authors comments
how to decide on the criteria for rejecting something as FS.

There is of course some noise, but based on our analysis the noise is fairly consistent with the precision numbers in our evaluation (i.e. most of the ICWSM examples are good FS, whereas about half of the BNC are). Hopefully including the guidelines helps with this, since we don't feel its possible to give succinct explanation of how to decide whether something is an FS: though there are several tests which can help (e.g., can elements be switched out, can the phrase be paraphrased without becoming awkward), at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e. Wray's definition as given at the beginning Section 2.

Reviewer B

> - For readers familiar with machine learning notation, it would be more
intuitive to use y throughout for the variables to be predicted, namely the
binary activation states of n-gram nodes. It may also be more intuitive to
use x instead of t for each "input" (n-gram node). Then covering could be
defined more explicitly as max{0, (c(x)-\sum_{i \in parents(x)} y_i *
c(x_i))/c(x)}, and likewise for other equations. The optimization problem
could be stated formally by wrapping argmax_{y,C} around eq. (1).

We have integrated the y suggestion, though not quite to the extent you have
suggested, since it creates other issues with the presentation.

>- I was a bit confused about the definition of "overlap" at the type vs.
token level: at first I thought the graph was constructed with each node
having its own corpus frequency information, but there are mentions of
counting overlaps in a corpus, and these counts are presumably associated
with edges between type-overlapping nodes. Showing frequency counts in
figure 2 may help clarify this. From figure 2, I assume at a type level, two
nodes overlap if at least one word is shared between the two n-grams, but
neither set of words is a superset of the other (which would be
subsumption), and a gap counts as a special word for determining subsumption
vs. overlap ("keep everything under wraps" and "keep * under wraps" merely
overlap), but two n-grams must share more than a gap to count as
overlapping. Is the ordering of tokens significant for determining overlap?

We've added some clarification of this point. Overlap at the type level consists
exactly of the count of token overlaps in the corpus. Two n-grams types might 
share words at the type level, but are considered overlapping only when there 
is at least one token in the corpus which belong to an instance of each type.

Related to this, we realized that we had left out the important point that 
subsumed n-grams are considered to trivially overlap with subsuming n-grams 
for the purposes of counting their overlap score when both are on (in addition 
to covering and clearing effects which occur when one of the two nodes is off). 
The reverse, though, is not true, since that would basically prohibit any two 
subsuming nodes from turning on (since the count of subsumed node is always larger
than the subsuming one).

Reviewer B

> - In some place, the paper is not an easy read -- I found a few
expressions that were fairly cryptic even for a seasoned reviewer in
NLP, examples include: "the best (i.e., most parsimonious) explanation
for statistical irregularities due to lexical affinity": what does
"parsimonious explanation", "lexical affinity" (S.1), or "explainedness"
of a node (S.3) mean? I would like to see a more formal definition right
where this concepts are introduced.

The word "parsimonious" is used here in its typical, non-technical sense to refer to explanations which cover the data and yet are as simple as possible. It's used in the introduction, and is just intended to give a sense to the reader of what is to come, in terms of the logic of the model. Since its not a term, nor doesn't pretend to be, we don't see the problem.

We have excised the term "lexical affinity", which was intend to point at the predictability that remains after
syntactic predictability is removed in the denominator of LPR, but is admittedly rather cryptic in the introduciton, and is never returned to.

"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition
later (3.3). An earlier draft had expainedness defined immediately, but this required forward pointers to node interaction functions, which the other reviewers disliked. There's a certain amount of interconnectedness here that
makes it impossible to fully satisfy the need to define everything formally up front.

> - Section 2: I found the discussion of formulaic sequence vs. multi-word
generally interesting but could not understand how this distinction
plays a role in the task you are trying to address and the model you
present -- it is frustating for a reviewer to try to follow a one-page
discussion on exact terminology and then jump to the presentation of
related work by noticing that is not that important to understand it
("Regardless of the terminology used..."). An evil reviewer could think
that you try to account for FS because they are easier to handle in your
model: what would be the results on a FS vs. MWE dataset?

"Regardless of the terminology used..." is not intended to imply that the terminology is not
important, just that basic methodologes used for multiword lexicon creation are somewhat
independant of them. We have reworded this.

The point of that section is to be clear about what we are doing, and how it relates to other work in NLP,
where the default term for the targets of this sort of extraction is MWE. The fact that semantic 
non-compositionality is not core to the definition of FS is in fact very important in terms of 
the model we have built. The FS versus MWE distinction is quite important relevant to the motivation 
discussed at the end of that section.

In the discussion, we briefly consider exactly the FS versus MWE distinction you mention.
The answer is that our model is quite good at identifying MWE (better than non-MWE FS),
but it will of course identify some non-MWE FS, and so applying it directly to MWE dataset 
would result in apparently low precision.

>- Section 3: there are a plethora of lexical association measures from
the literature, why using LPR? Also, why using the minimum LPR as
opposed to the product (Brooke et al., 2015). I found your explanation
in the paper rather tentative...

There are a plethora of lexical associations measures, but as we already note the the backgound section,
very few scale to gapped n-grams of unrestricted length (some have no formulation beyond two words, others do, but
are exponential in the statistics that must be collected as n increases). Those that do scale do quite poorly at the general task, as shown here with raw counts and PMI; as we mention in the experiment section, other work which has compared our baseline models here with a wider range of such measures. LPR was specifically designed for FS identification and showed good results in earlier, and in the last paragraph of Section 3.1, we very talk explicitly about why minLPR is the correct measure for this particular use (i.e. the lattice), where each step up a layer of the lattice involves adding a single word, which is what the minLPR metric is focusing on.

>- Section 3.2 why cherry-picking the threshold for hard covering to 2/3
or $C$ in the range [3, 6] as opposed to tune on dev data? Same for the
hyperparameter in the bullet list at the end of 3.4?

"Cherry-picking" suggests we are just picking the best values for our test set, which is certainly not the case. All of the hyperparameters you mention were in fact subject to some early evaluation on development data and then fixed from that point on. We did not rigorously tune them in the machine learning sense, which is perhaps what you mean by "cherry picking"; we wanted to avoid supervision as much as possible, and tuning of that kind is supervision; we picked reasonable values, saw that they worked, and moved on. We've removed the reference to [3 ,6] since it seems to have lead to this misinterpretation: we did some post hoc evaluation of what values of C caused the model performance to drop drastically, but that was unrelated to the selection of 4 as our C value, which happened very early in development.

>- Section 3.4: why not looking also at other node visiting strategies?
E.g., random?

We did test a few options on dev data (based on length and LPR; not random, though, because we wanted a deterministic model), and decided on count based sorting.

>- Section 4: there exists a plethora of datasets for MWE, why not
comparing with other datasets: how were the dataset chosen? Also, why
not using corpora for the same language of different sizes (cf. e.g.,
Riedl and Biemann)?

By datasets, do you mean MWE vocabularies? MWE corpora like the STREUSLE? We don't see what you mean, since no corpus annotated with MWE could possibly have the quanitity of data required to build an unsupervised model like this. In terms of evaluation, the main reason not to use existing MWE datasets is exactly that we are not doing MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally. Though it is possible to use MWE datasets for FS evaluation, see Brooke et al. (2015) who derived a test set from STREUSLE, it requires some hackiness that we felt was indefensible for our main evaluation: we did include a small, targeted evaluation of recall using STREUSLE.  Anyway, we addressed this issue rather thoroughly in the previous reviewer response.

It is worth mentioning (and we've added a small note to the paper) that we do prefer social media and mixed genre corpora, which represent a much more interesting range of FS pheonomena. Since you mention Reidl and Bieman, one criticim we have of that work was that it was focused on extremely specific, technical corpora, and not particularly representative of general FS phenomena across the language as whole.

We in fact do have corpora of different sizes for English, namely the ICWSM and BNC. Perhaps you mean taking smaller
version of the same corpus and seeing the effect of data size? This would be interesting, but it's not a trivial addition, since our test sets are sampled from the corpus; subsampling the corpus would require creating new test sets for those corpus.

- Section 6: When discussing "the time needed to build and optimize the
lattice" it would be good to add exact run-time figures

This is a reasonable idea, but we don't feel entirely confident reporting exactly runtime features due to difficulty in creating a controlled environment (i.e. DP-seg takes over 10 days to run on the BNC, and we can't ensure that our server stays otherwise unused) as well as the fact we can't control for the implementation of the comparison techniques. Instead, we've hedged our discussion a bit.

### 2017-07-24 response_2.txt
First pass on second round fixes

@@
 
-We've added them, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al.
+We've added the English guidelines, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al.
 2015 (though there was some editing, additions, and consolidations, and well as translations into other languages and adaptions to language specific phenomena).
@@
 most of the ICWSM examples are good FS, whereas about half of the BNC are).
-Hopefully including the guidelines helps with this, since we don't feel its possible to give succinct explanation of how to decide whether something is an FS: though there are several tests which can help (e.g., can elements be switched out, can the phrase be paraphrased without becoming awkward), at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e.
-Wray's definition as given at the beginning Section 2.
+Hopefully including the guidelines help with this, since we don't feel its possible to give succinct explanation of how to decide whether something is an FS: though there are several tests discussed in the guidelines, at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e.
+Wray's definition as given at the beginning of Section 2.
+
+> -"that do not scale to the large corpora,"
+-"allows for indi- vidual morphemes be part"
+-"Define terms Trev, Taff, Q, etc in the algorithm  "
+-Add information about the size of the Croatian corpus
+-Table4, the By length % figures don't sum to 100
+-"of a article"
+-"to an good FS"
+-"of the them"
+-"In Section 2, we noted than FS"
+-"inflectional flex- ibilty"
+-Introduce abbreviation for " the LPR decomp approach "
+-"that it is consistently outperforms"
+-In the conclusions the authors refer to MWE lexicons, instead of FS
+lexicons.
+
+We have addressed all this except the abbreviation for LPR decomp (not sure why this necessary beyond what we have already done?) and the last point, which we believe is based on a misunderstanding.
+In the conclusion (and the introduction and title) we talk about "multiword lexicons", which is not the same as MWE lexicon, it is intended to be a more general term including FS lexicons as well as MWE lexicons.
 
@@
 
-We have integrated the y suggestion, though not quite to the extent you have
-suggested, since it creates other issues with the presentation.
+We have integrated this suggestion, though not to full extent you have suggested (i.e. no argmax), since it creates other issues with the presentation.
 
@@
 
-We've added some clarification of this point. Overlap at the type level consists
-exactly of the count of token overlaps in the corpus. Two n-grams types might 
-share words at the type level, but are considered overlapping only when there 
-is at least one token in the corpus which belong to an instance of each type.
+We've added some clarification of this point.
+Overlap at the type level consists exactly of the count of token overlaps in the corpus.
+Two n-grams types might share words at the type level, but are considered overlapping only when there is at least one token in the corpus which belong to an instance of each type (there is no measure of the degree).
+ol() is exactly the number of times there is such a overlap.
 
-Related to this, we realized that we had left out the important point that 
-subsumed n-grams are considered to trivially overlap with subsuming n-grams 
-for the purposes of counting their overlap score when both are on (in addition 
-to covering and clearing effects which occur when one of the two nodes is off). 
-The reverse, though, is not true, since that would basically prohibit any two 
-subsuming nodes from turning on (since the count of subsumed node is always larger
-than the subsuming one).
+Related to this, we realized that we had left out the important point that subsumed n-grams are considered to trivially overlap with subsuming n-grams for the purposes of counting their overlap score when both are on (in addition to the covering and clearing effects which occur when one of the two nodes is off).
+The reverse, though, is not true, since that would basically prohibit any two subsuming nodes from turning on (since the count of subsumed node is always larger than the subsuming one).
 
-Reviewer B
+Reviewer C
 
@@
 It's used in the introduction, and is just intended to give a sense to the reader of what is to come, in terms of the logic of the model.
-Since its not a term, nor doesn't pretend to be, we don't see the problem.
+Since its not a term, nor does it pretend to be, we don't think there's a problem here.
 
-We have excised the term "lexical affinity", which was intend to point at the predictability that remains after
-syntactic predictability is removed in the denominator of LPR, but is admittedly rather cryptic in the introduciton, and is never returned to.
+We have excised the term "lexical affinity", which was intended to point at the predictability that remains after syntactic predictability is removed in the denominator of LPR, but is admittedly rather cryptic in the introduciton, and is never returned to.
 
-"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition
-later (3.3).
+"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition later (3.3).
 An earlier draft had expainedness defined immediately, but this required forward pointers to node interaction functions, which the other reviewers disliked.
-There's a certain amount of interconnectedness here that
-makes it impossible to fully satisfy the need to define everything formally up front.
+There's a certain amount of interconnectedness here that makes it impossible to fully satisfy the need to define everything formally up front.
 
@@
 
-"Regardless of the terminology used..." is not intended to imply that the terminology is not
-important, just that basic methodologes used for multiword lexicon creation are somewhat
-independant of them. We have reworded this.
+"Regardless of the terminology used..." is not intended to imply that the terminology is not important, just that core methodologes used for multiword lexicon creation are somewhat independant of them.
+We have reworded this.
 
-The point of that section is to be clear about what we are doing, and how it relates to other work in NLP,
-where the default term for the targets of this sort of extraction is MWE. The fact that semantic 
-non-compositionality is not core to the definition of FS is in fact very important in terms of 
-the model we have built. The FS versus MWE distinction is quite important relevant to the motivation 
-discussed at the end of that section.
+The point of that section is to be clear about what we are doing, and how it relates to other work in NLP, where the default term for the targets of this sort of extraction is MWE.
+The fact that semantic non-compositionality is not core to the definition of FS is in fact very important in terms of the model we have built.
+The FS versus MWE distinction is quite important relevant to the motivation discussed at the end of that section.
 
 In the discussion, we briefly consider exactly the FS versus MWE distinction you mention.
-The answer is that our model is quite good at identifying MWE (better than non-MWE FS),
-but it will of course identify some non-MWE FS, and so applying it directly to MWE dataset 
-would result in apparently low precision.
+The answer is that our model is quite good at identifying MWE (better than non-MWE FS), but it will of course identify some non-MWE FS, and so applying it directly to MWE dataset would result in apparently low precision.
 
@@
 
-There are a plethora of lexical associations measures, but as we already note the the backgound section,
-very few scale to gapped n-grams of unrestricted length (some have no formulation beyond two words, others do, but
-are exponential in the statistics that must be collected as n increases).
+There are a plethora of lexical association measures, but as we already note the the backgound section, very few scale to gapped n-grams of unrestricted length (some have no formulation beyond two words, others do, but are exponential in the statistics that must be collected as n increases).
 Those that do scale do quite poorly at the general task, as shown here with raw counts and PMI; as we mention in the experiment section, other work which has compared our baseline models here with a wider range of such measures.
-LPR was specifically designed for FS identification and showed good results in earlier, and in the last paragraph of Section 3.1, we very talk explicitly about why minLPR is the correct measure for this particular use (i.e.
-the lattice), where each step up a layer of the lattice involves adding a single word, which is what the minLPR metric is focusing on.
+LPR was specifically designed for FS identification and showed good results in earlier work, and in the last paragraph of Section 3.1, we very talk explicitly about why minLPR is a good measure for this particular use (i.e.
+the lattice), where each movement up a layer of the lattice involves adding a single word, which is what the minLPR metric is focusing on.
 
@@
 All of the hyperparameters you mention were in fact subject to some early evaluation on development data and then fixed from that point on.
-We did not rigorously tune them in the machine learning sense, which is perhaps what you mean by "cherry picking"; we wanted to avoid supervision as much as possible, and tuning of that kind is supervision; we picked reasonable values, saw that they worked, and moved on.
+We did not rigorously tune them in the machine learning sense, which is perhaps what you mean by "cherry picking"; we wanted to avoid supervision as much as possible, and tuning of that kind is a form of supervision.
+We picked reasonable values, saw that they worked using a small amount of development data, and moved on.
 We've removed the reference to [3 ,6] since it seems to have lead to this misinterpretation: we did some post hoc evaluation of what values of C caused the model performance to drop drastically, but that was unrelated to the selection of 4 as our C value, which happened very early in development.
@@
 
-We did test a few options on dev data (based on length and LPR; not random, though, because we wanted a deterministic model), and decided on count based sorting.
+We did test a few options on dev data (based on n-gram length and LPR; not random, though, because we wanted to preserve the deterministic nautre of the model), and decided on count-based sorting.
+However, we don't think this is interesting or important enough to include as a focus in the paper.
 
@@
 By datasets, do you mean MWE vocabularies?
-MWE corpora like the STREUSLE?
-We don't see what you mean, since no corpus annotated with MWE could possibly have the quanitity of data required to build an unsupervised model like this.
-In terms of evaluation, the main reason not to use existing MWE datasets is exactly that we are not doing MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally.
+or MWE corpora like the STREUSLE?
+We're not sure exactly what you mean, since no corpus annotated with MWE could possibly have the quantity of data required to build an unsupervised model like this.
+In terms of evaluation, the main reason not to use existing MWE datasets is exactly that, we are not doing traditional MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally.
 Though it is possible to use MWE datasets for FS evaluation, see Brooke et al.
-(2015) who derived a test set from STREUSLE, it requires some hackiness that we felt was indefensible for our main evaluation: we did include a small, targeted evaluation of recall using STREUSLE.
-Anyway, we addressed this issue rather thoroughly in the previous reviewer response.
+(2015) who derived a test set from STREUSLE (results were entirely consistent with the results using the FS set we also use here), it requires some hackiness that we felt was indefensible for our main evaluation.
+Note we did include a small, targeted evaluation of recall using STREUSLE in the discussion.
+We addressed this issue rather thoroughly in the previous reviewer response.
 
-It is worth mentioning (and we've added a small note to the paper) that we do prefer social media and mixed genre corpora, which represent a much more interesting range of FS pheonomena.
-Since you mention Reidl and Bieman, one criticim we have of that work was that it was focused on extremely specific, technical corpora, and not particularly representative of general FS phenomena across the language as whole.
+It is worth mentioning (and we've added a small note to the paper) that we do prefer social media and mixed genre corpora, which have linguistic diversity and therefore a much more interesting range of FS pheonomena.
+Since you mention Reidl and Bieman, one criticim we have of that work was that it was focused on extremely specific, technical corpora, and not particularly representative of general FS (or MWE) phenomena across the language as whole.
 
-We in fact do have corpora of different sizes for English, namely the ICWSM and BNC. Perhaps you mean taking smaller
-version of the same corpus and seeing the effect of data size?
-This would be interesting, but it's not a trivial addition, since our test sets are sampled from the corpus; subsampling the corpus would require creating new test sets for those corpus.
+We in fact do have corpora of very different sizes for English, namely the ICWSM and BNC (which is about a tenth the size).
+Perhaps you mean taking smaller version of the same corpus and seeing the effect of data size?
+This would be interesting, but it's not a trivial addition, since our test sets are sampled from the corpus; subsampling the corpus would require creating new test sets for that smaller corpus.
 
@@
 
-This is a reasonable idea, but we don't feel entirely confident reporting exactly runtime features due to difficulty in creating a controlled environment (i.e.
+This is a reasonable idea, but we don't feel entirely confident reporting exact runtime figures due to difficulty in creating a controlled environment sufficient (i.e.
 DP-seg takes over 10 days to run on the BNC, and we can't ensure that our server stays otherwise unused) as well as the fact we can't control for the implementation of the comparison techniques.
-Instead, we've hedged our discussion a bit.
+More generally, to set up runtime comparisons properly requires more of a digression than we really want to make at that point in the paper.
+Instead, we've hedged our discussion of runtime a bit.

### 2017-07-24 FS-annotation-English.tex
First pass on second round fixes

\title{Formulaic sequence annotation guidelines}
\author{Julian Brooke}
\date{September 9, 2016}

\documentclass[12pt]{article}

\begin{document}
\maketitle

The annotation task is to identify whether a sequences of words is ``formulaic'' in your language. We are using the definition given by Wray (see attached pdf for more details). She defines a formulaic sequence (FS) as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar''; you can think of FS as being something we’ve learned and have stored in a mental lexicon, and can recognize and retrieve more easily than entirely novel constructions).

FSes cover a wide variety of linguistic phenomena, including some that are sometimes viewed as syntactic in nature (like verb/preposition combinations). The most obvious examples of FS include large, fixed expression such as ``see the light at the end of the tunnel'', but also include much shorter sequences such as semantically non-compositional noun phrases like ``red tape''. A sequence does not need be syntactically complete to be a formulaic sequence, in fact many involving verbs are not: ``become conscious of'' and ``be one of the first to'' are examples of FS which are complete with respect to FS, but have a syntactic gaps which can be filled with a variety of expressions which do not form part of the FS. These gaps can occur with a sequence, for instance ``pick * up'' or ``worth * weight in gold''. Different sequences will have different fillers for these gaps depending on their syntactic role; what distinguishes a gap from part of FS is that the content of a gap is restricted only to general syntactic or semantic categories, whereas parts of a sequence will be restricted to specific words. For example any small physical object can be picked up, justifying a gap in the middle of the phrase ``pick * up'', but the only verbs that regularly come before ``conscious of'' are ``become'' and ``be'', so the expression seems highly lexicalized (i.e. ``prefabricated''), and therefore formulaic.

Wray gives a number of criteria for identifying FS, a few of the most useful for this annotation task are:

\vspace{0.5cm}

\noindent
1.	Semantic non-compositionality. This is the easiest and most obvious indicator: if the sequence of words has a special meaning that is more than the meaning of its parts (like ``red tape'' and ``kick the bucket'').

\vspace{0.5cm}

\noindent
2.	Associated with a specific linguistic situation. An example of this is a phrase like ''it would be great if * could'', which is semantically compositional but also has a larger discourse function that has been formulized, namely as a expression of (unrealized) expectation.

\vspace{0.5cm}

\noindent
3.	The preferred way a native speaker (or a native sub-community) would express an idea. This can include specific, otherwise compositional words like ``global warming'' (as compared to, for instance, ``earth warming''). If you speak another language, it may be useful to think whether the phrase translates directly into another language; if not, try to think of other ways to express the same idea, and see if they feel similarly idiomatic.

\vspace{0.5cm}

Generally speaking, as a native speaker you should have an intuition about which sequences have this special property (they are part of your mental lexicon in some way), or, in case when they aren't a formula you would use, at least some intuition about whether it would be formulaic to some community of native speakers (e.g. ``ventral cord'' is a term doctors would know, even if you don’t). Many names are formulaic sequences, but not if they would not be recognized by some larger community of native speakers (i.e. the name of some random non-famous person), or are otherwise non-standard ways to refer to the entity with extra material that is derived in a rule-based manner (e..g ``Barak Obama'', ``President Obama'', and ``President of the United States'' are FSes, but ``President of the United States Barak Obama'' and ``Mr. Barak Obama'' are not). In English, another special case is phrases like "the crust" and "a stomach ache", which we would consider formulaic because (in common usage) the article is pretty much fixed ("the crust", "the filling" in the context of pies is similar to ``the floor'' ``the ceiling’ when in a building, ‘the library''  or "the sun", "the universe", when living on earth. ``A stomach ache" is like "a cold" vs. "the flu" vs "the runs" vs "cancer", getting an article in this case is pretty idiosyncratic, and therefore deserving of formulaic status.
Here are a larger list of kinds of linguistic phenomena that are often formulaic:

\vspace{0.5cm}

\noindent
compound nouns \\
adjective/noun combinations \\
Names of well-known entities (people, places, locations) \\
verb/preposition combinations (both gappy, and non-gappy) \\
light verb constructions \\
multiword discourse connectives \\
verb/noun combinations \\
verb/adverb combinations \\
Proverbs, idioms, and clichés \\

\vspace{0.5cm}

\noindent
However, almost any sequence could be formulaic, and so you should not use a fixed set of possible syntactic types to limit possible FS. For some FS, there is some variation in the form of some of the words (``become conscious of'' could be ``became conscious of''), and in other cases (like ``red tape'') the form is fixed (``red tapes'' no longer has the idiomatic meaning); when annotating, you will be shown a particular common form but when there is variation in the possible form, you should view it as an annotation of all possible forms, not just the one you're seeing. Be careful with verb forms, don't exclude a form of ``be'' (or some other verb) from the canonical form just because it varies by inflection (``was/were/is up for'' are all good forms). However if the grammatical differences that involve independent words (like perfect aspect in English, which is expressed with ``have''), it should be included in a FS only if the grammatical aspect seems essential to the formula.
Instead of 2 options (FS or not), you are being asked to annotate three options; a sequence can be totally non-formulaic, it can recall a formulaic sequence, or it can be a canonical formulaic sequence. You should annotate the middle option (recalls) when the phrase contains or otherwise immediately brings to mind something you would call an FS (it should recall on its own, without the examples), but there are important parts of the FS missing, or extra elements that are not essential to the FS. Generally speaking, canonical forms should not have extra, highly variable words included on either end, or in the middle. For example, if the n-gram is "he was up for it", both "he" and "it" are extra and shouldn't be included in the canonical form (consider that you can say "they were up for some annotation''). Note that there are of course cases where a pronoun (often ``it'') is part of the canonical form even when it appears at a boundary, for example "it's a shame that", but in those cases you can't switch the pronoun for another one. Note that if a variable pronoun (or some other word) appears within a phrase then that is also not a canonical form. For example, "respect his opinion" only recalls a canonical form, the true canonical form is respect * opinion. More generally, (as alluded to above) canonical forms should not include words that can freely vary across some general semantic or syntactic class; we are only interested in sequences for which there seems to be some special lexical affiliation suggesting a fixed phrase, not a productive process. That said, there could be cases where there are a small, idiosyncratic set of lexical possibilities where we can still say, with some confidence, that each deserves to be considered a formulaic phrase in its own right even if the meaning is the same: for example ``be available in a range of'' and ``comes in a range of'' (size, shapes, colours, etc.) are two semantically equivalent phrases that should both be considered FS, they should not be generalized to ``in a range of'' just because there is a small amount of lexical variation. Similarity, ``the point I'm trying to'' is likely to be completed with ``make''; the fact that ``raise'' is also possible (though less common) does not mean that it should be generalized; ``the point I'm trying to'' simply doesn't stand on its own without a verb, and there are only a handful of possible verbs. That is, if most of the time the phrase is used, a particular element is included, then it should be considered canonical (and the other form non-canonical) even if it can sometimes be elided under certain usage circumstances (e.g. ``as painful as it is'' can sometimes be written as just ``painful as it is'', or when ``the Old World'' loses its ``the'' in adjectival form). If there is a small amount of lexical variation which seems fairly idiosyncratic then prefer the larger versions with each rather than generalizing. If there is both quite a clear preference for a particular lexical choice, but also lots of potential substitutions, then both longer and shorter could be considered canonical: for instance ``there is something wrong with'' seems to merit its own formula, but ``there is something * about'' is also a good general formula. Otherwise, if the options don't seem to particularly distinguish themselves, or seem to be restricted only by a general (word class) rule (e.g. "on Monday"), then prefer a shorter version that doesn't include the element.

You are being shown a small set of examples, which are random instances selected from the corpus. You can use this as evidence to help you decide if a formulaic sequence is canonical, though keep in mind that you are seeing only positive examples; if you think the FS might be smaller than what you see, you will have to rely on your own intuition about whether it occurs on its own. You should also be sensitive to the data in that you should only tag something as formulaic if you think the examples actually show evidence of that formulaticity, even if you think it is possibly FS.

\end{document}

### 2017-07-24 tacl.tex
First pass on second round fixes

@@
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+      \author{Julian Brooke \qquad Timothy Baldwin \\ Computing and Information Systems \\ The University of Melbourne \\ \url{julian.brooke@gmail.com} \\ \url{tb@ldwin.net}
+ \And               Jan Snajder\\
+Electrical Engineering and Computing \\
+ University of Zagreb \\
+  {\tt jan.snajder@fer.hr}}
+
+	\\}
 
@@
 The potential of multiword knowledge to improve both the automatic processing of language as well as offer new understanding of human acquisition and usage of language is the primary motivator of this work.
-Here, we present an effective, expandable, and above all tractable new approach to comprehensive multiword lexicon acquisition.
-Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14} and more sophisticated statistical models \cite{Newman12} that do not scale to the large corpora, the main source of the distributional information in modern NLP systems.
+Here, we present an effective, expandable, and tractable new approach to comprehensive multiword lexicon acquisition.
+Our aim is to find a middle ground between standard MWE acquisition approaches based on association measures \cite{Ramisch14} and more sophisticated statistical models \cite{Newman12} that do not scale to large corpora, the main source of the distributional information in modern NLP systems.
 
@@
 A central challenge in building comprehensive multiword lexicons is paring down the huge space of possibilities without imposing restrictions which disregard a major portion of the multiword vocabulary of a language: allowing for diversity creates significant redundancy among statistically promising candidates.
-The lattice model proposed here addresses this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities due to lexical affinity.
+The lattice model proposed here addresses this primarily by having the candidates---contiguous and non-contiguous $n$-gram types---compete with each other based on subsumption and overlap relations to be selected as the best (\ie most parsimonious) explanation for statistical irregularities.
 We test this approach across four large corpora in three languages, including two relatively free-word-order languages (Croatian and Japanese), and find that this approach consistency outperforms alternatives, offering scalability and many avenues for future enhancement.
@@
 Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.
-Note that the FS framework allows for individual morphemes be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.
+Note that the FS framework allows for individual morphemes to be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.
 
@@
 
-Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}.
+From a practical perspective, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}.
 When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen.
@@
 \termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice.
-For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
+For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance} and \ex{keep it under your hat}), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram.
 If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy.
-This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $a_1,\dotts, a_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes).
-Then, the $\cover(t)$ score for a covered node $t$ is:
+This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, $y_i$ the current FS status for node $x_i$ (0 if off, 1 if on) and $ab(x)$ a function which produces the set of indicies of all nodes above node $x$ in the lattice.
+Then, the $\cover(x_t)$ score for a covered node $t$ is:
 \begin{displaymath}
-\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(a_i)}}{c(t)}\Big)
+\cover(x_t) = \max\Big(0,\frac{c(x_t) - \sum_{i \in ab(x_t)}y_i\cdot{c(x_i)}}{c(x_t)}\Big)
 \end{displaymath}
@@
 \begin{displaymath}
-\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(b_i)}\Big)}
+\clear(x_t) = \prod_{i \in bl(x_t)}{\min\Big(1,\frac{\minLPR(x_t)}{y_i\cdot\minLPR(x_i)}\Big)}
 \end{displaymath}
-where $b_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice.
+where $bl(x_t)$ produces a set of indicies of nodes below $x_t$ in the lattice.
 We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
-For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.
+For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(x_t)$ will be 0.5.
 Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs.
@@
 To address this problem, rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
-Let $\mathit{oc}(x,y)$ be the number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to overlapping nodes, \ie turned-on nodes which overlap with target node $t$ in the corpus.
-We define $\overlap(t)$ as:
+For non-subsuming nodes $x_i$ and $x_j$, let $\mathit{oc}(x_i,x_j)$ be the count of instances of $x_i$ which contain at least one non-gap token of an corresponding instance of $x_j$.
+For subsuming nodes, though, overlap is treated asymmetrically, with $\mathit{oc}(x_i,x_j)$ equal to $c(x_j)$ (the lower count) if $j \in ab(x_i)$, but zero if $j \in bl(x_i)$.
+Given this definition of $\mathit{oc}$, we define $\overlap(x_t)$ as:
 \begin{displaymath}
-	\overlap(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(t,o_i)}}
+	\overlap(x_t) = \frac{c(x_t)}{c(x_t) - \sum_{i=1}^{|X|}{y_i\cdot\mathit{oc}(x_t,x_i)}}
 \end{displaymath}
@@
 
-In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if node $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse.
-The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice, $t_1,\dots,t_{|T|} \in T$, which can be defined in terms of minLPR and the node interaction functions:
+The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice $X$, $x_i,\dots,x_{N}$, which can be defined in terms of minLPR and the node interaction functions:
 %
 \begin{multline}
-	\mathit{expl}(T) = \prod_{i=1}^{|T|}{I_{\mathit{on}}(t_i)\cdot C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i)\cdot\minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
+	\mathit{expl}(X) = \prod_{i=1}^{|X|}{y_i\cdot C^{-\overlap(x_i)}} \\ + (-y_i + 1)\cdot\minLPR(x_i)^{-\cover(x_i) \cdot \clear(x_i)}
 \end{multline}
@@
 All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification.
-There is no upper bound on $C$, but empirically, we have found values in the range $[3,6]$ give reasonable results for the languages presented in this paper.
 
@@
 	\caption{Optimization algorithm.
-$T$ is an ordered list of the nodes in the lattice.
-Nodes (designated by $t$) contain pointers to the nodes immediately linked to them in the lattice.
-States (designated by $s$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$.
-Explainedness values are indicated by $e$.}
+$X$ is an ordered list of the nodes in the lattice.
+Nodes (designated by $x$) contain pointers to the nodes immediately linked to them in the lattice.
+States (designated by $Y$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$.
+Explainedness values are indicated by $e$.
+rev=relevant, aff=affected, curr=current}
 	\label{alg:opt}
@@
 
-	\Function{LocalOpt}{$s_{\mathit{start}}, t, T_{\mathit{rev}}, T_{\mathit{aff}}$}
-		\State $s_{\mathit{start}} \gets \Call{Set}{s, t, \mathrm{ON}}$
+	\Function{LocalOpt}{$Y_{\mathit{start}}, x, X_{\mathit{rev}}, X_{\mathit{aff}}$}
+		\State $Y_{\mathit{start}} \gets \Call{Set}{Y_{\mathit{start}}, x, \mathrm{ON}}$
 		\State $Q \gets \Call{EmptyQueue}{\null}$
 		\State $e_{\mathit{best}} \gets 0$
-		\State $s_{\mathit{best}} \gets \mathrm{NULL}$
-		\State $\Call{Push}{Q, s_{\mathit{start}}}$
+		\State $Y_{\mathit{best}} \gets \mathrm{NULL}$
+		\State $\Call{Push}{Q, Y_{\mathit{start}}}$
 		\Repeat
-			\State $s_{\mathit{curr}} \gets \Call{Pop}{Q}$
-			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{s_{\mathit{curr}}, T_{\mathit{aff}}}$
-			\For{$t_{\mathit{rev}} \textrm{ in } T_{\mathit{rev}}$}
-					\State $s_{\mathit{new}} \gets \Call{Set}{s_{\mathit{curr}},t_{\mathit{rev}}, \mathrm{OFF}}$
-					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, T_{\mathit{aff}}}$
+			\State $Y_{\mathit{curr}} \gets \Call{Pop}{Q}$
+			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{Y_{\mathit{curr}}, X_{\mathit{aff}}}$
+			\For{$x_{\mathit{rev}} \textrm{ in } X_{\mathit{rev}}$}
+					\State $Y_{\mathit{new}} \gets \Call{Set}{Y_{\mathit{curr}},x_{\mathit{rev}}, \mathrm{OFF}}$
+					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, X_{\mathit{aff}}}$
 					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}
 
-					\State $\Call{Push}{Q, s_{\mathit{new}}}$
+					\State $\Call{Push}{Q, Y_{\mathit{new}}}$
 					\If{$e_{\mathit{new}} > e_{\mathit{best}}}$:
 						\State $e_{\mathit{best}} \gets e_{\mathit{new}}$
-							\State $s_{\mathit{best}} \gets s_{\mathit{new}}$
+							\State $Y_{\mathit{best}} \gets Y_{\mathit{new}}$
 					\EndIf
@@
 		\Until{$\Call{IsEmpty}{Q}$}
-	\State \Return $s_{\mathit{best}}$
+	\State \Return $Y_{\mathit{best}}$
 	\EndFunction
 \State
-\State $\Call{FrequencySortReverse}{T}$
-\State $s \gets \Call{InitializeAllOff}{T}$
+\State $\Call{FrequencySortReverse}{X}$
+\State $s \gets \Call{InitializeAllOff}{X}$
 \Repeat
 	\State $\mathit{Changed} \gets \mathrm{FALSE}$
-		\For{$t \textrm{ in } T$}
-		\State $T_{\mathit{rev}} \gets \Call{GetRelevant}{t,T}$
-		\State $T_{\mathit{aff}} \gets \Call{GetAffected}{T_{\mathit{rev}},T}$
-		\State $s_{\mathit{new}} \gets \Call{LocalOpt}{s,t,T_{\mathit{rev}},T_{\mathit{aff}}}$
-		\If{$s_{\mathit{new}} \neq s$}
-			\State $s \gets s_{\mathit{new}}$
+		\For{$x \textrm{ in } X$}
+		\State $X_{\mathit{rev}} \gets \Call{GetRelevant}{x,X}$
+		\State $X_{\mathit{aff}} \gets \Call{GetAffected}{X_{\mathit{rev}},X}$
+		\State $Y_{\mathit{new}} \gets \Call{LocalOpt}{Y,x,X_{\mathit{rev}},X_{\mathit{aff}}}$
+		\If{$Y_{\mathit{new}} \neq Y$}
+			\State $Y \gets Y_{\mathit{new}}$
 			\State $\mathit{Changed} \gets \mathrm{TRUE}$
@@
 For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice.
-The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.
+The order that we perform this has an effect on the result: among the obvious options (LPR, $n$-gram length), in development good results were obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.
 
@@
 
-We evaluate our approach across three different languages including evaluation sets derived from four different corpora.
+We evaluate our approach across three different languages including evaluation sets derived from four different corpora selected for their size and linguistic diversity.
 In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM blog corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
@@
 One advantage of a type-based annotation approach, particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness.
-To this end, we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
-\tabref{tab:stats} contains the counts for the four test sets after this filtering step as well as Fleiss' Kappa scores before (``Pre'') and after (``Post'').
+As such we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
+\tabref{tab:stats} contains the counts for the four test sets after this filtering step and Fleiss' Kappa scores before (``Pre'') and after (``Post'').
 The second change is that for the main evaluation we collapsed gapped and contiguous $n$-grams into a single test set.
@@
 
-				Lattice & \bf{0.67} & 0.44 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
+				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
             \bottomrule
@@
 \midrule
-English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & \z7.5  \\
-English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & \z7.7 \\
+English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.7 & 15.0 & \z7.5  \\
+English BNC & 374k &  30.0k& 26.1& 37.7 & 36.3 & 18.1 & \z7.7 \\
 Croatian & 172k & \z6.7k & \z7.9& 55.0& 31.4 & 10.3 & \z3.2 \\
@@
 \midrule
-English (BNC) & \ex{go into decline}, \ex{Maureen says}, \ex{primarily as \gap and}, \ex{Peggy Sue}, \ex{square \gap shoulder}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
+English (BNC) & \ex{go into decline}, \ex{Maureen says}, \ex{primarily as \gap and}, \ex{Peggy Sue}, \ex{square \gap shoulders}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
 \midrule
@@
 \tabref{tab:sample} contains 10 randomly selected examples from each of the lexicons produced by our method.
-Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of a article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
+Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of an article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
 The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise.
@@
 
-Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of the them) are of course dominated by rarer terms.
+Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of them) are of course dominated by rarer terms.
 This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of the potential in automatic extraction comes from the long tail.
@@
 
-In \secref{sec:background}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
+In \secref{sec:background}, we noted that FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning.
 We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two native-speaker annotators ($\kappa = 0.73$), and conflicts were resolved through discussion.} First, we note that only 28\% of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
@@
 However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words.
-Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as a distinct element of the FS and flexible morphemes becoming gaps.
+Such a framework could, for instance, capture inflectional flexibility versus fixedness directly in the model, with fixed inflectional morphemes included as a distinct element of the FS and flexible morphemes becoming gaps.
 However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification.
@@
 For all four corpora, the lattice optimization algorithm converged within 10 iterations.
-Although the optimization of the lattice is nevertheless several orders of magnitude slower than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is still only a fraction of the time required to collect the statistics for LPR calculation, and so the end-to-end runtime of the two methods is comparable.
-In the BNC, the end-to-end lattice method is several times faster than LocalMaxs (with a fraction of its memory usage), and an order of magnitude faster than DP-Seg.
+Although the optimization of the lattice is several orders of magnitude more complex than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is a fraction of the time required to collect the statistics for LPR calculation, and so the end-to-end runtimes of the two methods are comparable.
+In the BNC, the full lattice method was much faster than LocalMaxs and DP-Seg, though direct runtime comparisons to these methods are of modest value due to differences of both scope and implementation.
 
@@
 We have presented here a new methodology for acquiring comprehensive multiword lexicons from large corpora, using competition in an $n$-gram lattice.
-Our evaluation using annotations of sampled $n$-grams shows that it is consistently outperforms alternatives across several corpora and languages.
-A tool which implements the method, as well as the acquired lexicons and test sets, are available at: \url{http://ANON.YMO.US}.\footnote{Removed for anonymity}
+Our evaluation using annotations of sampled $n$-grams shows that it consistently outperforms alternatives across several corpora and languages.
+A tool which implements the method, as well as the acquired lexicons, annotation guidelines, and test sets, are available at: \url{https://github.com/julianbrooke/LatticeFS}.
 

### 2017-07-27 FS-annotation-Croatian.tex
Jan's fixes and additions

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc} % for PCs

\title{Ozna?avanje formulai?nih nizova u hrvatskome jeziku}
\author{Jan Snajder}
\date{September 19, 2016}

\documentclass[12pt]{article}

\begin{document}
\maketitle

Gornje upute za ozna?avanje ze engleski jezik vrijede i za hrvatski jezik. Primjeri formulai?nih izraza u hrvatskome (popis nije iscrpan):

\begin{itemize}
\item Imeni?ke fraze:
\begin{itemize}
\item ``elektri?na vu?a'', ``kontrola kvalitete'', ``investicijski fond'', ``drugi svjetski rat'', ``Katica
za sve'', ``mali od palube''
\item Tu su osobito ?este kombinacije pridjev+imenica ili imenica+imenica-u-genitivu, a mogu?e su
naravno i složenije kombinacije
\end{itemize}
\item Imena poznatih entiteta (osoba, mjesta, organizacija) – sintakti?ki gledano, to su tako?er imeni?ke fraze:
\begin{itemize}
\item ``Zagreba?ka županija'', ``Fakultet elektrotehnike i ra?unarstva'', ``Justin Bieber'', ``Marks
and Spencer'', ``Balkanska ruta''
\end{itemize}

\item Povratni glagoli:
\begin{itemize}
\item Pravi povratni (rije? ``se'' korištena je kao zamjenica i može se zamijeniti sa ``sebe''): ``predati
se'', ``upustiti se''
\item Uzajamno povratni: ``grliti se'', ``pozdraviti se'',
\item Nepravi povratni (nema prave povratnosti radnje na subjekt, ``se'' je ?estica i ne može se
zamijeniti sa ``sebe''): ``glasati se'', ``veseliti se'', ``?uditi se'', ``smijati se''
\end{itemize}
\item Glagolske fraze:
\begin{itemize}
\item ``pridobiti pažnju'', ``biti u žiži'', ``dati sve od sebe'', ``baciti * u vjetar'', ``može se govoriti
o *'', ``dolaziti na naplatu'', ``sti?i na naplatu''
\end{itemize}
\item Pridjevske fraze:
\begin{itemize}
\item ``koliko toliko'', ``s time povezan'', ``bez presedana''
\end{itemize}
\item Priložne oznake:
\begin{itemize}
\item ``bezbroj puta'', ``svakim danom sve *'', ``malo puno''
\end{itemize}
\item Prijedložne oznake:
\begin{itemize}
\item ``u bližoj okolici'', ``u nepoznatom smjeru'', ``u ovom trenutku''
\end{itemize}
\item Diskursni konektori:
\begin{itemize}
\item ``sve dok je'', ``shodno tome'', ``drugim rije?ima'', ``na primjer''
\end{itemize}
\item Klišeizirane fraze:
\begin{itemize}
\item ``plan i program'', ``može * biti sram'', ``mama ti mogu biti'', ``?i?a mi?a gotova je pri?a'',
``bolje išta nego ništa'', ``nepoznati netko'', ``možda su u šumi'', ``nema govora o *''
\end{itemize}
\end{itemize}
U odnosu na engleski, kod hrvatskoga jezika nailazimo na neke specifi?nosti, ponajviše zbog razlika u
morfologiji (visok stupanj fleksije i derivacije) i sintaksi (relativno slobodan poredak rije?i u re?enici). S druge strane, u hrvatskome ne postoje neki fenomeni koji postoje u engleskome, npr. ?lanovi i frazalni glagoli.

\section*{Morfologija}

Za razliku od engleskog, hrvatski je visoko flektivan jezik, što zna?i da se jedna te ista fraza može
pojavljivati u razli?itim flektivnim oblicima, npr. ``jedan te isti'', ``jedna te ista'', ``jednog te istog'' (primijetite, me?utim, da je u nekim slu?ajevima fraza okamenjena i ne dopušta nikakvu morfološku varijaciju, npr. ``Katicama za sve'' ili ``u bližim okolicama'' nisu formulai?ki nizovi). Pri ozna?avanju, fraza ?e
biti prikazana u obliku u kojem se ona naj?eš?e nalazi u korpusu; taj oblik ne mora nužno biti nautkni?ki
oblik kakav biste našli u rje?niku. Npr., formulai?ki niz ``dvostruka igra'' pojavljuje se u korpusu naj?eš?e u
kosom obliku ``dvostruku igru'' (jer se fraza naj?eš?e koristi kao objekt u akuzativu), pa ?e taj oblik biti
prikazan, me?utim oba oblika se odnose na isti formulai?ki izraz i trebaju se tretirati ravnopravno. Dodatno
?e biti prikazan i potpuno lematizirani oblik izraza (``dvostruki igra''), koji može, ali i ne mora, biti
gramati?ki isrpavan oblik izraza u hrvatskom jeziku. Pri ozna?avanju treba dakle zanemariti sve ove razlike
i ozna?iti formulai?nost niza neovisno o tome u kojem je morfološkom obliku prikazan. Osobito treba obratii
pažnju na supletivne oblike, posebice glagola biti (sam/si/je/smo/ste/su) i sli?no. Npr., ``je u žiži'' je
formulai?ni niz, kao što je to i niz ``su u žiži'' i ``smo u žiži'', što su sve flektivne varijante niza ``biti u žiži''.
Budu?i da se provodi lematizacija, ovi se nizovi tretiraju kao istovjetni, što zna?i da se u popisu ne bi smjele
zasebno pojaviti varijante ovog niza.

Dodatna razlika hrvatskoga u odnosu na engleski jezik u pogledu morfologije jest ta što hrvatski koristi
derivacijsku morfologiju kako bi kodirao neke semanti?ke zna?ajke poput spola osobe koja obavlja
zanimanje (tzv. Mocijski parovi) ili glagolskog aspekta (svršenost i nesvršenost glagola), npr. ``kuhar'' –
``kuharica'', ``dobitnik'' – ``dobitnica'', ``sti?i'' – ``stizati'', ``komentirati'' – ``prokomentirati''. Ove razlike ne?e biti
uklonjene lematizacijom, što zna?i da se, primjerice, fraze ``goli kuhar'' i ``gola kuharica'' tretiraju kao
razli?ite, te formulai?nost svake od njih treba ocijeniti zasebno.

Druga zna?ajna razlika hrvatskoga u odnosu na engleski jezik jest ta što hrvatski dopušta relativno
slobodan poredak rije?i u re?enici. Posljedica toga jest da se u nekim formulai?nim nizovima može mijenjati
poredak rije?i u re?enici (doduše, ta je pojava rijetka, jer formulai?nost obi?no diktira poredak rije?i) ili, što
se doga?a znatno ?eš?e, da se neke rije?i mogu umetati u formulai?ne izraze, bilo da bi se zadovoljila
sintakti?ka pravila hrvatskog ili iz stilskih razloga.

\section*{Sintaksa}

Za engleski je ve? bilo objašenjeno da je mogu?e umetanje rije?i u ``rupe'' (engl. gaps) formulai?nog niza. U
hrvatskom se relativno ?esto pojavljuju rupe koje mogu popuniti modifikatori. Npr. ``stvoriti * atmosferu'' ili
``kazna * zatvora''. Te rupe su ?esto opcionalne, u smislu da je i niz bez rupe tako?er formulai?an.

Tako?er su mogu?e rupe koje popunjavaju objekti. Npr., u formulai?nom nizu ``baciti * u vjetar'', rupu ?e
tipi?no popuniti objekt, izre?en kao imeni?ka fraza ili zamjenica (``baciti novce u vjetar'', ``bacio ih u vjetar'',
``bacio sve svoje novce u vjetar''). Kao i kod engleskog, u ovakvim slu?ajevima fraze ``baciti novce u vjetar''
ili ``bacio ih u vjetar'' nisu formulai?ne, jer rije?i ``novce'' i ``ih'' varijabilan dio niza te ih se može tretirati kao
argumente formulai?nog niza. Shodno tome, poop?eni niz ``baciti * u vjetar'' jest formulai?an niz (s
rupom).

Me?utim, za razliku od engleskog, kod hrvatskog ?e rupe ?esto nastajati zbog slobodnijeg poretka rije?i u
re?enici, i takve ?e rupe uvijek biti opcionalne. Npr., formulai?ni niz ``zadnji trenutak'' može se pojaviti u verziji s rupom, ``zadnji * trenutak'', gdje rupu može popuniti glagolska kopula (``je'', ``smo'', ``ste'', ``su'', …)
ili neki složeniji niz (npr. ``ga je'', ``smo ju'', …). Oba ova niza tretiramo kao formulai?na.

Tako?er vrijedi i obrat: formulai?ni nizovi koji se sastoje od rupe, npr. ``baciti * u vjetar'', mogu se pojaviti
bez rupe. Npr., objekt se može na?i prije ili poslije formulai?nog niza, kao u ``Baca u vjetar dva milijuna
kuna.'' ili ``Ta odluka baca u vjetar sve što je mom?ad napravila.'' Tako?er, opet je mogu?e da rupu popune
rije?i koje se tu moraju na?i zbog sintakse, npr. glagolska kopula ``biti'' za tvorbu perfekta ili futura: ``bacila
je u vjetar'', ``bacit ?e u vjetar''. Tako?er su mogu?e i kombinacije, gdje rupu zajedno popunjavaju i
kopula i objekt, npr. ``bacila je sve svoje novce u vjetar''.
U nastavku sljedi sistematizacija fenomenta uzrokovanih slobodnim poretkom rije?i u re?enici:

\begin{itemize}

\item Transpozicija rije?i u formulai?nom nizu:
\begin{itemize}
\item Transpozicija zamjeni?ke enklitike (povratne zamjenice ``se''):
\begin{itemize}
\item ``veseliti se'' ==> ``se veseli''
\item  ``dati si vremena'' ==> ``si dati vremena''
\end{itemize}
\item Transpozicija glagolske enklitike (kopule):
\begin{itemize}
\item ``lako je tako'' ==> ``je lako tako'', ``tako je lako''
\end{itemize}
\item U ovakvim slu?ajevima, sve transponirane varijante formulai?nog niza tretiramo kao
istovrijedne. Drugim rije?ima, dok god su u nizu iste rije?i, može ih se razli?ito poredati i opet
dobiti formulai?ni niz (naravno, samo za one poretke rije?i koje su u jeziku dopuštene; npr.
``dati vremena si'' nije formulai?an niz).
\end{itemize}

\item Umetanje rije?i u formulai?an niz:
\begin{itemize}
\item Umetanje glagolske enklike (kopule):
\begin{itemize}
\item ``zadnji trenutak'' ==> ``zadnji je trenutak'' ==> ``zadnji * trenutak''
\item ``hrvatska banka'' ==> ``hrvatska je banka'' ==> ``hrvatska * banka''
\item ``zatvoriti poglavlje'' ==> ``zatvorio je poglavlje'' ==> ``zatvoriti * poglavlje''
\end{itemize} 
\item Umetanje zamjeni?ke enklitike:
\begin{itemize}
``zadnji trenutak'' ==> ``zadnji se trenutak'' ==> ``zadnji * trenutak''
\end{itemize}
\item Kombinacije:
\begin{itemize}
\item ``zadnji trenutak'' ==> ``zadnji su ga trenutak'' ==> ``zadnji * trenutak''
\end{itemize}
\item Kod umetanja rije?i, formulai?an niz s umetnutom rije?i ne tretira se kao formulai?an, jer je
umetnuta rije? donekle varijabilna (u svim gornjim primjerima na mjesto rupe mogu?e umetnuti
jednu rije? ili kombinaciju više rije?i). Drugim rije?ima, umetnuti dio treba zamijeniti rupom, a
da bi se niz tretirao kao formulai?an.
\end{itemize}
\end{itemize}

Na primjer, ``zatvoriti poglavlje'' je formulai?an niz (po kriteriju semanti?ke neprozirnosti). Zbog slobodnog
poretka rije?i u re?enici, niz ``zatvoriti * poglavlje'' tako?er tretiramo kao formulai?an. Rupu može popuniti
kopula (``zatvorila je poglavlje'') ili neka složenija kombinacija (``zatvorili su ju?er nakon dugih pregovora
poglavlje''), me?utim nizovi s popunjenom rupom nisu formulai?ni jer su previše specifi?ni. Niz ``je zatvorila
poglavlje'' tako?er nije formulai?an, jer kopula ``je'' nije dio niza.

\end{document}

### 2017-07-27 tacl.tex
Jan's fixes and additions

@@
   {\tt jan.snajder@fer.hr}}
-
-	\\}
 
@@
 Relative to English, both languages have freer word order: we were interested in probing the challenges associated with using an $n$-gram approach to FS identification in such languages.
-For Croatian, we used the fhrWaC corpus \cite{snajder2013building}, a filtered version of the Croatian web corpus hrWaC \cite{ljubesic2014bs}, which is POS-tagged and lemmatized using the tools of \newcite{agic2013lemmatization}.
+For Croatian, we used the 1.2-billion-token fhrWaC corpus \cite{snajder2013building}, a filtered version of the Croatian web corpus hrWaC \cite{ljubesic2014bs}, which is POS-tagged and lemmatized using the tools of \newcite{agic2013lemmatization}.
 Similar to English, the POS regex for Croatian includes simple nouns, adjectives and pronouns, but also other elements that regularly appear inside FS, including both adverbs and copulas.
-For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008}, which was roughly the same size (in terms of token count) as the English corpus.
+For Japanese, we used a subset of the 100M-page web corpus of \newcite{Shinzato+:2008}, which was roughly the same token length as the English corpus.
 We segmented and POS-tagged the corpus with MeCab \cite{Kudo:2008} using the UNIDIC morphological dictionary \cite{Den:2007}.
@@
 
-What is perhaps most striking about the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English.
+One striking thing about the non-English FS is how poorly they translate: many good FS in these languages become extremely awkward when translated into English.
 This is expected of course for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like
@@
 \gl{first half comparison}.
-This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some do, particularly short ones in related languages).
+This highlights the potential importance of focusing on FS when learning a language.
 Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from, like \ex{austrijski investitor} \gl{Austrian investor}.
@@
 Our evaluation using annotations of sampled $n$-grams shows that it consistently outperforms alternatives across several corpora and languages.
-A tool which implements the method, as well as the acquired lexicons, annotation guidelines, and test sets, are available at: \url{https://github.com/julianbrooke/LatticeFS}.
+A tool which implements the method, as well as the acquired lexicons, annotation guidelines, and test set have been made available.\footnote{\url{https://github.com/julianbrooke/LatticeFS}}
+
+\section*{Acknowledgements}
+
+We would like to thank our Australian, Japanese, and Croatian annotators for their hard work on a challenging annotation task.
 

### 2017-07-27 FS-annotation-Croatian.tex
more Jan changes

@@
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[latin1]{inputenc} % for PCs
+%\usepackage[latin1]{inputenc} % for PCs
 
-\title{Ozna?avanje formulai?nih nizova u hrvatskome jeziku}
-\author{Jan Snajder}
+\title{Formulaic Sequence Annotation Guidelines, Croatian supplement}
+\author{Jan \v{S}najder}
 \date{September 19, 2016}
@@
 
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
 \begin{document}
@@
 
-Gornje upute za ozna?avanje ze engleski jezik vrijede i za hrvatski jezik. Primjeri formulai?nih izraza u hrvatskome (popis nije iscrpan):
+Gornje upute za označavanje ze engleski jezik vrijede i za hrvatski jezik. Primjeri formulaičnih izraza u
+hrvatskome (popis nije iscrpan):
 
 \begin{itemize}
-\item Imeni?ke fraze:
+\item Imeničke fraze:
 \begin{itemize}
-\item ``elektri?na vu?a'', ``kontrola kvalitete'', ``investicijski fond'', ``drugi svjetski rat'', ``Katica
+\item ``električna vuča'', ``kontrola kvalitete'', ``investicijski fond'', ``drugi svjetski rat'', ``Katica
 za sve'', ``mali od palube''
-\item Tu su osobito ?este kombinacije pridjev+imenica ili imenica+imenica-u-genitivu, a mogu?e su
+\item Tu su osobito česte kombinacije pridjev+imenica ili imenica+imenica-u-genitivu, a moguće su
 naravno i složenije kombinacije
 \end{itemize}
-\item Imena poznatih entiteta (osoba, mjesta, organizacija) – sintakti?ki gledano, to su tako?er imeni?ke fraze:
+\item Imena poznatih entiteta (osoba, mjesta, organizacija) – sintaktički gledano, to su također imeničke
+fraze:
 \begin{itemize}
-\item ``Zagreba?ka županija'', ``Fakultet elektrotehnike i ra?unarstva'', ``Justin Bieber'', ``Marks
+\item ``Zagrebačka županija'', ``Fakultet elektrotehnike i računarstva'', ``Justin Bieber'', ``Marks
 and Spencer'', ``Balkanska ruta''
@@
 \begin{itemize}
-\item Pravi povratni (rije? ``se'' korištena je kao zamjenica i može se zamijeniti sa ``sebe''): ``predati
+\item Pravi povratni (riječ ``se'' korištena je kao zamjenica i može se zamijeniti sa ``sebe''): ``predati
 se'', ``upustiti se''
 \item Uzajamno povratni: ``grliti se'', ``pozdraviti se'',
-\item Nepravi povratni (nema prave povratnosti radnje na subjekt, ``se'' je ?estica i ne može se
-zamijeniti sa ``sebe''): ``glasati se'', ``veseliti se'', ``?uditi se'', ``smijati se''
+\item Nepravi povratni (nema prave povratnosti radnje na subjekt, ``se'' je  čestica i ne može se
+zamijeniti sa ``sebe''): ``glasati se'', ``veseliti se'', ``čuditi se'', ``smijati se''
 \end{itemize}
@@
 \item ``pridobiti pažnju'', ``biti u žiži'', ``dati sve od sebe'', ``baciti * u vjetar'', ``može se govoriti
-o *'', ``dolaziti na naplatu'', ``sti?i na naplatu''
+o *'', ``dolaziti na naplatu'', ``stići na naplatu''
 \end{itemize}
@@
 \begin{itemize}
-\item ``sve dok je'', ``shodno tome'', ``drugim rije?ima'', ``na primjer''
+\item ``sve dok je'', ``shodno tome'', ``drugim riječima'', ``na primjer''
 \end{itemize}
@@
 \begin{itemize}
-\item ``plan i program'', ``može * biti sram'', ``mama ti mogu biti'', ``?i?a mi?a gotova je pri?a'',
+\item ``plan i program'', ``može * biti sram'', ``mama ti mogu biti'', ``čiča miča gotova je priča'',
 ``bolje išta nego ništa'', ``nepoznati netko'', ``možda su u šumi'', ``nema govora o *''
@@
 \end{itemize}
-U odnosu na engleski, kod hrvatskoga jezika nailazimo na neke specifi?nosti, ponajviše zbog razlika u
-morfologiji (visok stupanj fleksije i derivacije) i sintaksi (relativno slobodan poredak rije?i u re?enici).
-S druge strane, u hrvatskome ne postoje neki fenomeni koji postoje u engleskome, npr.
-?lanovi i frazalni glagoli.
+
+U odnosu na engleski, kod hrvatskoga jezika nailazimo na neke specifičnosti, ponajviše zbog razlika u
+morfologiji (visok stupanj fleksije i derivacije) i sintaksi (relativno slobodan poredak riječi u rečenici). S
+druge strane, u hrvatskome ne postoje neki fenomeni koji postoje u engleskome, npr. članovi i frazalni
+glagoli.
 
@@
 
-Za razliku od engleskog, hrvatski je visoko flektivan jezik, što zna?i da se jedna te ista fraza može
-pojavljivati u razli?itim flektivnim oblicima, npr.
-``jedan te isti'', ``jedna te ista'', ``jednog te istog'' (primijetite, me?utim, da je u nekim slu?ajevima fraza okamenjena i ne dopušta nikakvu morfološku varijaciju, npr.
-``Katicama za sve'' ili ``u bližim okolicama'' nisu formulai?ki nizovi).
-Pri ozna?avanju, fraza ?e
-biti prikazana u obliku u kojem se ona naj?eš?e nalazi u korpusu; taj oblik ne mora nužno biti nautkni?ki
-oblik kakav biste našli u rje?niku. Npr., formulai?ki niz ``dvostruka igra'' pojavljuje se u korpusu naj?eš?e u
-kosom obliku ``dvostruku igru'' (jer se fraza naj?eš?e koristi kao objekt u akuzativu), pa ?e taj oblik biti
-prikazan, me?utim oba oblika se odnose na isti formulai?ki izraz i trebaju se tretirati ravnopravno. Dodatno
-?e biti prikazan i potpuno lematizirani oblik izraza (``dvostruki igra''), koji može, ali i ne mora, biti
-gramati?ki isrpavan oblik izraza u hrvatskom jeziku. Pri ozna?avanju treba dakle zanemariti sve ove razlike
-i ozna?iti formulai?nost niza neovisno o tome u kojem je morfološkom obliku prikazan. Osobito treba obratii
-pažnju na supletivne oblike, posebice glagola biti (sam/si/je/smo/ste/su) i sli?no. Npr., ``je u žiži'' je
-formulai?ni niz, kao što je to i niz ``su u žiži'' i ``smo u žiži'', što su sve flektivne varijante niza ``biti u žiži''.
-Budu?i da se provodi lematizacija, ovi se nizovi tretiraju kao istovjetni, što zna?i da se u popisu ne bi smjele
+Za razliku od engleskog, hrvatski je visoko flektivan jezik, što znači da se jedna te ista fraza može
+pojavljivati u različitim flektivnim oblicima, npr.
+``jedan te isti'', ``jedna te ista'', ``jednog te istog'' (primijetite, međutim, da je u nekim slučajevima fraza okamenjena i ne dopušta nikakvu morfološku
+varijaciju, npr.  ``Katicama za sve'' ili ``u bližim okolicama'' nisu formulai?ki nizovi). . Pri označavanju, fraza će
+biti prikazana u obliku u kojem se ona najčešće nalazi u korpusu; taj oblik ne mora nužno biti nautknički
+oblik kakav biste našli u rječniku. Npr., formulaički niz ``dvostruka igra'''' pojavljuje se u korpusu najčešće u
+kosom obliku  ``dvostruku igru''  (jer se fraza najčešće koristi kao objekt u akuzativu), pa će taj oblik biti
+prikazan, međutim oba oblika se odnose na isti formulaički izraz i trebaju se tretirati ravnopravno. Dodatno
+će biti prikazan i potpuno lematizirani oblik izraza (``dvostruki igra''),, koji može, ali i ne mora, biti
+gramatički isrpavan oblik izraza u hrvatskom jeziku. Pri označavanju treba dakle zanemariti sve ove razlike
+i označiti formulaičnost niza neovisno o tome u kojem je morfološkom obliku prikazan. Osobito treba obratii
+pažnju na supletivne oblike, posebice glagola biti (sam/si/je/smo/ste/su) i slično. Npr.,  ``je u žiži'' je
+formulaični niz, kao što je to i niz ``su u žiži'' i ``smo u žiži'', što su sve flektivne varijante niza ``biti u žiži''.
+Budući da se provodi lematizacija, ovi se nizovi tretiraju kao istovjetni, što znači da se u popisu ne bi smjele
 zasebno pojaviti varijante ovog niza.
@@
 Dodatna razlika hrvatskoga u odnosu na engleski jezik u pogledu morfologije jest ta što hrvatski koristi
-derivacijsku morfologiju kako bi kodirao neke semanti?ke zna?ajke poput spola osobe koja obavlja
+derivacijsku morfologiju kako bi kodirao neke semantičke značajke poput spola osobe koja obavlja
 zanimanje (tzv. Mocijski parovi) ili glagolskog aspekta (svršenost i nesvršenost glagola), npr. ``kuhar'' –
-``kuharica'', ``dobitnik'' – ``dobitnica'', ``sti?i'' – ``stizati'', ``komentirati'' – ``prokomentirati''. Ove razlike ne?e biti
-uklonjene lematizacijom, što zna?i da se, primjerice, fraze ``goli kuhar'' i ``gola kuharica'' tretiraju kao
-razli?ite, te formulai?nost svake od njih treba ocijeniti zasebno.
+``kuharica'', ``dobitnik'' – ``dobitnica'', ``stići'' – ``stizati'', ``komentirati'' – ``prokomentirati''.  Ove razlike neće biti
+uklonjene lematizacijom, što znači da se, primjerice, fraze ``goli kuhar'' i ``gola kuharica'' tretiraju kao
+različite, te formulaičnost svake od njih treba ocijeniti zasebno.
 
-Druga zna?ajna razlika hrvatskoga u odnosu na engleski jezik jest ta što hrvatski dopušta relativno
-slobodan poredak rije?i u re?enici. Posljedica toga jest da se u nekim formulai?nim nizovima može mijenjati
-poredak rije?i u re?enici (doduše, ta je pojava rijetka, jer formulai?nost obi?no diktira poredak rije?i) ili, što
-se doga?a znatno ?eš?e, da se neke rije?i mogu umetati u formulai?ne izraze, bilo da bi se zadovoljila
-sintakti?ka pravila hrvatskog ili iz stilskih razloga.
+Druga značajna razlika hrvatskoga u odnosu na engleski jezik jest ta što hrvatski dopušta relativno
+slobodan poredak riječi u rečenici. Posljedica toga jest da se u nekim formulaičnim nizovima može mijenjati
+poredak riječi u rečenici (doduše, ta je pojava rijetka, jer formulaičnost obično diktira poredak riječi) ili, što
+se događa znatno češće, da se neke riječi mogu umetati u formulaične izraze, bilo da bi se zadovoljila
+sintaktička pravila hrvatskog ili iz stilskih razloga.
 
 \section*{Sintaksa}
+Za engleski je već bilo objašenjeno da je moguće umetanje riječi u ``rupe'' (engl. gaps) formulaičnog niza. U
+hrvatskom se relativno često pojavljuju rupe koje mogu popuniti modifikatori. Npr. ``stvoriti * atmosferu'' ili
+``kazna * zatvora''. Te rupe su često opcionalne, u smislu da je i niz bez rupe također formulaičan.
 
-Za engleski je ve? bilo objašenjeno da je mogu?e umetanje rije?i u ``rupe'' (engl. gaps) formulai?nog niza. U
-hrvatskom se relativno ?esto pojavljuju rupe koje mogu popuniti modifikatori. Npr. ``stvoriti * atmosferu'' ili
-``kazna * zatvora''. Te rupe su ?esto opcionalne, u smislu da je i niz bez rupe tako?er formulai?an.
-
-Tako?er su mogu?e rupe koje popunjavaju objekti. Npr., u formulai?nom nizu ``baciti * u vjetar'', rupu ?e
-tipi?no popuniti objekt, izre?en kao imeni?ka fraza ili zamjenica (``baciti novce u vjetar'', ``bacio ih u vjetar'',
-``bacio sve svoje novce u vjetar''). Kao i kod engleskog, u ovakvim slu?ajevima fraze ``baciti novce u vjetar''
-ili ``bacio ih u vjetar'' nisu formulai?ne, jer rije?i ``novce'' i ``ih'' varijabilan dio niza te ih se može tretirati kao
-argumente formulai?nog niza. Shodno tome, poop?eni niz ``baciti * u vjetar'' jest formulai?an niz (s
+Također su moguće rupe koje popunjavaju objekti. Npr., u formulaičnom nizu ``baciti * u vjetar'', rupu će
+tipično popuniti objekt, izrečen kao imenička fraza ili zamjenica (``baciti novce u vjetar'', ``bacio ih u vjetar'',
+``bacio sve svoje novce u vjetar''). Kao i kod engleskog, u ovakvim slučajevima fraze ``baciti novce u vjetar''
+ili ``bacio ih u vjetar'' nisu formulaične, jer riječi ``novce'' i ``ih'' varijabilan dio niza te ih se može tretirati kao
+argumente formulaičnog niza. Shodno tome, poopćeni niz ``baciti * u vjetar'' jest formulaičan niz (s
 rupom).
 
-Me?utim, za razliku od engleskog, kod hrvatskog ?e rupe ?esto nastajati zbog slobodnijeg poretka rije?i u
-re?enici, i takve ?e rupe uvijek biti opcionalne.
-Npr., formulai?ni niz ``zadnji trenutak'' može se pojaviti u verziji s rupom, ``zadnji * trenutak'', gdje rupu može popuniti glagolska kopula (``je'', ``smo'', ``ste'', ``su'', …)
-ili neki složeniji niz (npr. ``ga je'', ``smo ju'', …). Oba ova niza tretiramo kao formulai?na.
+Međutim, za razliku od engleskog, kod hrvatskog će rupe često nastajati zbog slobodnijeg poretka riječi u
+rečenici, i takve će rupe uvijek biti opcionalne. Npr., formulaični niz ``zadnji trenutak'' može se pojaviti u
+verziji s rupom, ``zadnji * trenutak'', gdje rupu može popuniti glagolska kopula (``je'', ``smo'', ``ste'', ``su'', …)
+ili neki složeniji niz (npr. ``ga je'', ``smo ju'', …). Oba ova niza tretiramo kao formulaična.
 
-Tako?er vrijedi i obrat: formulai?ni nizovi koji se sastoje od rupe, npr. ``baciti * u vjetar'', mogu se pojaviti
-bez rupe. Npr., objekt se može na?i prije ili poslije formulai?nog niza, kao u ``Baca u vjetar dva milijuna
-kuna.'' ili ``Ta odluka baca u vjetar sve što je mom?ad napravila.'' Tako?er, opet je mogu?e da rupu popune
-rije?i koje se tu moraju na?i zbog sintakse, npr. glagolska kopula ``biti'' za tvorbu perfekta ili futura: ``bacila
-je u vjetar'', ``bacit ?e u vjetar''. Tako?er su mogu?e i kombinacije, gdje rupu zajedno popunjavaju i
+Također vrijedi i obrat: formulaični nizovi koji se sastoje od rupe, npr. ``baciti * u vjetar'', mogu se pojaviti
+bez rupe. Npr., objekt se može naći prije ili poslije formulaičnog niza, kao u ``Baca u vjetar dva milijuna
+kuna.'' ili ``Ta odluka baca u vjetar sve što je momčad napravila.'' Također, opet je moguće da rupu popune
+riječi koje se tu moraju naći zbog sintakse, npr. glagolska kopula ``biti'' za tvorbu perfekta ili futura: ``bacila
+je u vjetar'', ``bacit će u vjetar''. Također su moguće i kombinacije, gdje rupu zajedno popunjavaju i
 kopula i objekt, npr. ``bacila je sve svoje novce u vjetar''.
-U nastavku sljedi sistematizacija fenomenta uzrokovanih slobodnim poretkom rije?i u re?enici:
+
+U nastavku sljedi sistematizacija fenomenta uzrokovanih slobodnim poretkom riječi u rečenici:
 
@@
 
-\item Transpozicija rije?i u formulai?nom nizu:
+\item Transpozicija riječi u formulaičnom nizu:
 \begin{itemize}
-\item Transpozicija zamjeni?ke enklitike (povratne zamjenice ``se''):
+\item Transpozicija zamjeničke enklitike (povratne zamjenice ``se''):
 \begin{itemize}
@@
 \end{itemize}
-\item U ovakvim slu?ajevima, sve transponirane varijante formulai?nog niza tretiramo kao
-istovrijedne. Drugim rije?ima, dok god su u nizu iste rije?i, može ih se razli?ito poredati i opet
-dobiti formulai?ni niz (naravno, samo za one poretke rije?i koje su u jeziku dopuštene; npr.
-``dati vremena si'' nije formulai?an niz).
+\item U ovakvim slučajevima, sve transponirane varijante formulaičnog niza tretiramo kao
+istovrijedne. Drugim riječima, dok god su u nizu iste riječi, može ih se različito poredati i opet
+dobiti formulaični niz (naravno, samo za one poretke riječi koje su u jeziku dopuštene; npr.
+``dati vremena si'' nije formulaičan niz).
 \end{itemize}
 
-\item Umetanje rije?i u formulai?an niz:
+\item Umetanje riječi u formulaičan niz:
+
 \begin{itemize}
@@
 \end{itemize}
-\item Kod umetanja rije?i, formulai?an niz s umetnutom rije?i ne tretira se kao formulai?an, jer je
-umetnuta rije? donekle varijabilna (u svim gornjim primjerima na mjesto rupe mogu?e umetnuti
-jednu rije? ili kombinaciju više rije?i). Drugim rije?ima, umetnuti dio treba zamijeniti rupom, a
-da bi se niz tretirao kao formulai?an.
+\item Kod umetanja riječi, formulaičan niz s umetnutom riječi ne tretira se kao formulaičan, jer je
+umetnuta riječ donekle varijabilna (u svim gornjim primjerima na mjesto rupe moguće umetnuti
+jednu riječ ili kombinaciju više riječi). Drugim riječima, umetnuti dio treba zamijeniti rupom, a
+da bi se niz tretirao kao formulaičan.
 \end{itemize}
@@
 
-Na primjer, ``zatvoriti poglavlje'' je formulai?an niz (po kriteriju semanti?ke neprozirnosti). Zbog slobodnog
-poretka rije?i u re?enici, niz ``zatvoriti * poglavlje'' tako?er tretiramo kao formulai?an. Rupu može popuniti
-kopula (``zatvorila je poglavlje'') ili neka složenija kombinacija (``zatvorili su ju?er nakon dugih pregovora
-poglavlje''), me?utim nizovi s popunjenom rupom nisu formulai?ni jer su previše specifi?ni. Niz ``je zatvorila
-poglavlje'' tako?er nije formulai?an, jer kopula ``je'' nije dio niza.
+Na primjer, ``zatvoriti poglavlje'' je formulaičan niz (po kriteriju semantičke neprozirnosti). Zbog slobodnog
+poretka riječi u rečenici, niz ``zatvoriti * poglavlje'' također tretiramo kao formulaičan. Rupu može popuniti
+kopula (``zatvorila je poglavlje'') ili neka složenija kombinacija (``zatvorili su jučer nakon dugih pregovora
+poglavlje''), međutim nizovi s popunjenom rupom nisu formulaični jer su previše specifični. Niz ``je zatvorila
+poglavlje'' također nije formulaičan, jer kopula ``je'' nije dio niza
 

### 2017-07-27 FS-annotation-Japanese.tex
more Jan changes

\documentclass[12pt,letterpaper]{article}

\usepackage{CJKutf8}

\title{Formulaic sequence annotation guidelines, Japanese supplement}
\author{Tim Baldwin}
\date{September 9, 2016}

\begin{document}
\maketitle

\begin{CJK*}{UTF8}{min}
アノテーションの対象は「Formulaic Sequence」（FS）ですが、大まかに説明すると一
般的にネーティブ話者にとって聞き覚えがありそうな複数の形態素からなる表現です。
複合表現（MWE）、すなわち何かしらの非合成ある表現がその一部で、「機械翻訳」、
「出来上がる」、「腕を上げる」などが全部FSとなります。「named entity」（NE）は、
一般的に知られているものであればFSとなります。例えば「東京オリンピック」、「代々
木公園」、「村上春樹」などはFSで、「山田英彦」「宇佐美公園」などはFSにはなりま
せん。それ以外では、「じゃあね」、「〜を傍らに」、「黒ごま」、「〜ざるを得ない」
もFSになります。FSかどうかの判定の手がかりの一つとしては、英語などへの翻訳にお
いて、英語には類似表現がないか、直訳ではおかしなものになるか、英訳も定形した表
現になるか、のいずれかが見られがちです。
\end{CJK*}

\begin{CJK*}{UTF8}{min}
アノテーションのしかたとしては、FS候補をlemmaとUniDicによる複数の形態素として
表示し、その下には、ランダムにサンプリングされた5つ程の例文を表示します。FSと
して認定するためには、少なくとも5つの例文の中の1つが実際のFSの使われ方にならな
くてはいけません。アノテーションは以下の4通りになります。
\end{CJK*}

\begin{CJK*}{UTF8}{min}
\begin{itemize}
\item 「Is a canonical formulaic sequence」 \\
　　　　FS候補がFSに完全一致した場合

\item 「Recalls a formulaic sequence, but not canonical」 \\
　　　　FS候補が部分的にFSに一致しているか、FSの一部になっている場合

\item 「Is not formulaic sequence」 \\
　　　　FS候補がFSあるいはFSの一部になっていない場合

\item 「Encoding error」 \\
　　　　FS候補が文字化けしているため、FSかどうかの判定が不可能な場合
\end{CJK*}

\begin{CJK*}{UTF8}{min}
FS候補が２種類ありますが、まず一つ目は「contiguous FS」（連続FS）で、普通の使
われ方ではFSが連続して、一つにまとまったものです。２つ目は「gappy FS」で、FSの
中には名詞句など含まれるものです。gappy FSの例としては「決して〜ない」、「総合～
会議」が上げられます。それぞれのFSのアノテーションには個別にインタフェースを用
意しています。
\end{CJK*}

\begin{CJK*}{UTF8}{min}
FSの定義とアノテーションの過程を詳しく書いたものを次のように用意しましたが、英
語のみになっているので、あらかじめご了承ください。
\end{CJK*}

\end{document}

### 2017-07-27 tacl.tex
more Jan changes

@@
 
-      \author{Julian Brooke \qquad Timothy Baldwin \\ Computing and Information Systems \\ The University of Melbourne \\ \url{julian.brooke@gmail.com} \\ \url{tb@ldwin.net}
- \And               Jan Snajder\\
-Electrical Engineering and Computing \\
- University of Zagreb \\
-  {\tt jan.snajder@fer.hr}}
+\author{
+Julian Brooke$^{*}$ \quad Jan \v{S}najder$^{\dagger}$ \quad Timothy Baldwin$^{*}$ \\
+$^{*}$\,School of Computing and Information Systems, The University of Melbourne\\
+\texttt{julian.brooke@gmail.com, tb@lwin.net} \\
+$^{\dagger}$\,Faculty of Electrical Engineering and Computing, University
+of Zagreb \\
+\texttt{jan.snajder@fer.hr}\\
+}
+
+%      \author{Julian Brooke \qquad Timothy Baldwin \\ Computing and Information Systems \\ The University of Melbourne \\ \url{julian.brooke@gmail.com} \\ \url{tb@ldwin.net}
+% \And               Jan Snajder\\
+%Electrical Engineering and Computing \\
+% University of Zagreb \\
+%  {\tt jan.snajder@fer.hr}}
 
@@
 
-We would like to thank our Australian, Japanese, and Croatian annotators for their hard work on a challenging annotation task.
+The second author has been supported by an Endeavour Research Fellowship
+of the Australian Government, and in part by the Croatian Science
+Foundation under the project UIP-2014-09-7312. We would also like to thank our Australian, Japanese, and Croatian annotators.
 

### 2017-07-27 FS-annotation-Croatian.tex
fixed 2 more encoding errors
fix HR guidelines

@@
 \usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+\usepackage[croatian]{babel}
+%\usepackage[T1]{fontenc}
 
@@
 
-Gornje upute za označavanje ze engleski jezik vrijede i za hrvatski jezik. Primjeri formulaičnih izraza u
+Upute za označavanje ze engleski jezik u vrijede i za hrvatski jezik. Primjeri formulaičnih izraza u
 hrvatskome (popis nije iscrpan):
@@
 morfologiji (visok stupanj fleksije i derivacije) i sintaksi (relativno slobodan poredak riječi u rečenici). S
-druge strane, u hrvatskome ne postoje neki fenomeni koji postoje u engleskome, npr. članovi i frazalni
+druge strane, u hrvatskome ne postoje neki fenomeni koji postoje u engleskome, npr., članovi i frazalni
 glagoli.
@@
 Za razliku od engleskog, hrvatski je visoko flektivan jezik, što znači da se jedna te ista fraza može
-pojavljivati u različitim flektivnim oblicima, npr.
-``jedan te isti'', ``jedna te ista'', ``jednog te istog'' (primijetite, međutim, da je u nekim slučajevima fraza okamenjena i ne dopušta nikakvu morfološku
-varijaciju, npr.  ``Katicama za sve'' ili ``u bližim okolicama'' nisu formulai?ki nizovi). . Pri označavanju, fraza će
+pojavljivati u različitim flektivnim oblicima, npr., ``jedan te isti'', ``jedna te ista'', ``jednog te istog'' (primijetite, međutim, da je u nekim slučajevima fraza okamenjena i ne dopušta nikakvu morfološku
+varijaciju, npr., ``Katicama za sve'' ili ``u bližim okolicama'' nisu formulaički nizovi). Pri označavanju, fraza će
 biti prikazana u obliku u kojem se ona najčešće nalazi u korpusu; taj oblik ne mora nužno biti nautknički
-oblik kakav biste našli u rječniku. Npr., formulaički niz ``dvostruka igra'''' pojavljuje se u korpusu najčešće u
+oblik kakav biste našli u rječniku. Npr., formulaički niz ``dvostruka igra'' pojavljuje se u korpusu najčešće u
 kosom obliku  ``dvostruku igru''  (jer se fraza najčešće koristi kao objekt u akuzativu), pa će taj oblik biti
 prikazan, međutim oba oblika se odnose na isti formulaički izraz i trebaju se tretirati ravnopravno. Dodatno
-će biti prikazan i potpuno lematizirani oblik izraza (``dvostruki igra''),, koji može, ali i ne mora, biti
-gramatički isrpavan oblik izraza u hrvatskom jeziku. Pri označavanju treba dakle zanemariti sve ove razlike
-i označiti formulaičnost niza neovisno o tome u kojem je morfološkom obliku prikazan. Osobito treba obratii
+će biti prikazan i potpuno lematizirani oblik izraza (``dvostruki igra''), koji može, ali i ne mora, biti
+gramatički ispravan oblik izraza u hrvatskom jeziku. Pri označavanju treba dakle zanemariti sve ove razlike
+i označiti formulaičnost niza neovisno o tome u kojem je morfološkom obliku prikazan. Osobito treba obratiti
 pažnju na supletivne oblike, posebice glagola biti (sam/si/je/smo/ste/su) i slično. Npr.,  ``je u žiži'' je
@@
 derivacijsku morfologiju kako bi kodirao neke semantičke značajke poput spola osobe koja obavlja
-zanimanje (tzv. Mocijski parovi) ili glagolskog aspekta (svršenost i nesvršenost glagola), npr. ``kuhar'' –
+zanimanje (tzv.~mocijski parovi) ili glagolskog aspekta (svršenost i nesvršenost glagola), npr., ``kuhar'' –
 ``kuharica'', ``dobitnik'' – ``dobitnica'', ``stići'' – ``stizati'', ``komentirati'' – ``prokomentirati''.  Ove razlike neće biti
@@
 poredak riječi u rečenici (doduše, ta je pojava rijetka, jer formulaičnost obično diktira poredak riječi) ili, što
-se događa znatno češće, da se neke riječi mogu umetati u formulaične izraze, bilo da bi se zadovoljila
+se događa znatno češće, da se neke riječi mogu umetati u formulaične izraze, da bi se zadovoljila
 sintaktička pravila hrvatskog ili iz stilskih razloga.
@@
 \section*{Sintaksa}
-Za engleski je već bilo objašenjeno da je moguće umetanje riječi u ``rupe'' (engl. gaps) formulaičnog niza. U
+Za engleski je već bilo objašenjeno da je moguće umetanje riječi u ``rupe'' (engl.~\emph{gaps}) formulaičnog niza. U
 hrvatskom se relativno često pojavljuju rupe koje mogu popuniti modifikatori. Npr. ``stvoriti * atmosferu'' ili
@@
 verziji s rupom, ``zadnji * trenutak'', gdje rupu može popuniti glagolska kopula (``je'', ``smo'', ``ste'', ``su'', …)
-ili neki složeniji niz (npr. ``ga je'', ``smo ju'', …). Oba ova niza tretiramo kao formulaična.
+ili neki složeniji niz (npr., ``ga je'', ``smo ju'', \dots). Oba ova niza tretiramo kao formulaična.
 
@@
 
-U nastavku sljedi sistematizacija fenomenta uzrokovanih slobodnim poretkom riječi u rečenici:
+U nastavku slijedi sistematizacija fenomena uzrokovanih slobodnim poretkom riječi u rečenici:
 
@@
 \begin{itemize}
-\item ``veseliti se'' ==> ``se veseli''
-\item  ``dati si vremena'' ==> ``si dati vremena''
+\item ``veseliti se'' $\Rightarrow$ ``se veseli''
+\item  ``dati si vremena'' $\Rightarrow$ ``si dati vremena''
 \end{itemize}
@@
 \begin{itemize}
-\item ``lako je tako'' ==> ``je lako tako'', ``tako je lako''
+\item ``lako je tako'' $\Rightarrow$ ``je lako tako'', ``tako je lako''
 \end{itemize}
@@
 \item Umetanje riječi u formulaičan niz:
-
 \begin{itemize}
-\item Umetanje glagolske enklike (kopule):
+\item Umetanje glagolske enklitike (kopule):
 \begin{itemize}
-\item ``zadnji trenutak'' ==> ``zadnji je trenutak'' ==> ``zadnji * trenutak''
-\item ``hrvatska banka'' ==> ``hrvatska je banka'' ==> ``hrvatska * banka''
-\item ``zatvoriti poglavlje'' ==> ``zatvorio je poglavlje'' ==> ``zatvoriti * poglavlje''
+\item ``zadnji trenutak'' $\Rightarrow$ ``zadnji je trenutak'' $\Rightarrow$ ``zadnji * trenutak''
+\item ``hrvatska banka'' $\Rightarrow$ ``hrvatska je banka'' $\Rightarrow$ ``hrvatska * banka''
+\item ``zatvoriti poglavlje'' $\Rightarrow$ ``zatvorio je poglavlje'' $\Rightarrow$ ``zatvoriti * poglavlje''
 \end{itemize} 
-\item Umetanje zamjeni?ke enklitike:
+\item Umetanje zamjeničke enklitike:
 \begin{itemize}
-``zadnji trenutak'' ==> ``zadnji se trenutak'' ==> ``zadnji * trenutak''
+\item ``zadnji trenutak'' $\Rightarrow$ ``zadnji se trenutak'' $\Rightarrow$ ``zadnji * trenutak''
 \end{itemize}
@@
 \begin{itemize}
-\item ``zadnji trenutak'' ==> ``zadnji su ga trenutak'' ==> ``zadnji * trenutak''
+\item ``zadnji trenutak'' $\Rightarrow$ ``zadnji su ga trenutak'' $\Rightarrow$ ``zadnji * trenutak''
 \end{itemize}
@@
 poglavlje''), međutim nizovi s popunjenom rupom nisu formulaični jer su previše specifični. Niz ``je zatvorila
-poglavlje'' također nije formulaičan, jer kopula ``je'' nije dio niza
+poglavlje'' također nije formulaičan, jer kopula ``je'' nije dio niza.
 

### 2017-08-06 response_2.txt
Tim over and out!

@@
 
->*The annotation guidelines are needed to ensure replicability. Add them as
+> *The annotation guidelines are needed to ensure replicability. Add them as
 appendix material.
 
-We've added the English guidelines, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al.
+We've added the English guidelines to the github repository associated with the paper, though we note the guidelines are not really a contribution of this work, much of its content was created as part of Brooke et al.
 2015 (though there was some editing, additions, and consolidations, and well as translations into other languages and adaptions to language specific phenomena).
@@
 most of the ICWSM examples are good FS, whereas about half of the BNC are).
-Hopefully including the guidelines help with this, since we don't feel its possible to give succinct explanation of how to decide whether something is an FS: though there are several tests discussed in the guidelines, at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e.
+Hopefully including the guidelines helps with this, since we don't feel it's possible to give succinct explanation of how to decide whether something is an FS: though there are several tests discussed in the guidelines, at the core we are always reliant on native speaker intuition about whether a sequence of words is produced as a unit, i.e.
 Wray's definition as given at the beginning of Section 2.
@@
 
-"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition later (3.3).
+"Explainedness" gets an informal explanation just after its introduction in Section 3, and then more formal definition later (Section 3.3).
 An earlier draft had expainedness defined immediately, but this required forward pointers to node interaction functions, which the other reviewers disliked.
@@
 >- Section 3.4: why not looking also at other node visiting strategies?
-E.g., random?
+> E.g., random?
 
@@
 
->- Section 4: there exists a plethora of datasets for MWE, why not
-comparing with other datasets: how were the dataset chosen? Also, why
-not using corpora for the same language of different sizes (cf. e.g.,
-Riedl and Biemann)?
+>- Section 4: there exists a plethora of datasets for MWE, why not comparing
+> with other datasets: how were the dataset chosen? Also, why not using
+> corpora for the same language of different sizes (cf. e.g., Riedl and
+> Biemann)?
 
@@
 In terms of evaluation, the main reason not to use existing MWE datasets is exactly that, we are not doing traditional MWE extraction, but rather FS extraction; the existing MWE datasets have at best very inconsistent treatment of nonMWE FS, generally.
-Though it is possible to use MWE datasets for FS evaluation, see Brooke et al.
-(2015) who derived a test set from STREUSLE (results were entirely consistent with the results using the FS set we also use here), it requires some hackiness that we felt was indefensible for our main evaluation.
+Though it is possible to use MWE datasets for FS evaluation -- see Brooke et al.
+(2015) who derived a test set from STREUSLE (results were entirely consistent with the results using the FS set we also use here) -- it requires some hackiness that we felt was indefensible for our main evaluation.
 Note we did include a small, targeted evaluation of recall using STREUSLE in the discussion.
@@
 
-- Section 6: When discussing "the time needed to build and optimize the
-lattice" it would be good to add exact run-time figures
+> - Section 6: When discussing "the time needed to build and optimize the
+> lattice" it would be good to add exact run-time figures
 

### 2017-08-06 tacl.tex
Tim over and out!

@@
 \newcommand{\overlap}{\ensuremath{\text{overlap}}\xspace}
+\newcommand{\expl}{\ensuremath{\text{expl}}\xspace}
 
@@
 Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word.
-Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
+Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure applicable to any possible syntactic pattern, which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase.
 Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure \cite{Riedl15} is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word.
@@
 
-The motivation for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
+The motivations for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
 One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses.
@@
 In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher.
-Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
+Generalized to the (rare) case of multiple clearing nodes, we define $\clear(x_t)$ as:
 %in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
@@
 
-The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice $X$, $x_i,\dots,x_{N}$, which can be defined in terms of minLPR and the node interaction functions:
+The objective function maximized by the model is then the explainedness (\expl) across all the nodes of the lattice $X$, $x_i,\dots,x_{N}$, which can be defined in terms of \minLPR, the node interaction functions, and the FS status $y_i$ of each node in the lattice:
 %
 \begin{multline}
-	\mathit{expl}(X) = \prod_{i=1}^{|X|}{y_i\cdot C^{-\overlap(x_i)}} \\ + (-y_i + 1)\cdot\minLPR(x_i)^{-\cover(x_i) \cdot \clear(x_i)}
+	\expl(X) = \prod_{i=1}^{|X|}{y_i\cdot C^{-\overlap(x_i)}} \\ 
+        \hspace*{2mm} + (-y_i + 1)\cdot\minLPR(x_i)^{-\cover(x_i) \cdot \clear(x_i)}
 \end{multline}
-\noindent
 When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero.
@@
 Explainedness values are indicated by $e$.
-rev=relevant, aff=affected, curr=current}
+$\mathit{rev}$ = relevant, $\mathit{aff}$ = affected, $\mathit{curr}$ = current}
 	\label{alg:opt}
@@
 
-We evaluate our approach across three different languages including evaluation sets derived from four different corpora selected for their size and linguistic diversity.
+We evaluate our approach across three different languages, including evaluation sets derived from four different corpora selected for their size and linguistic diversity.
 In English, we follow \newcite{Brooke15b} in using a 890M token filtered portion of the ICWSM blog corpus \cite{ICWSM} tagged with the Tree Tagger \cite{Schmid95}.
@@
 Bold is best in a given column.
-For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$; all p-values based on the permutation test \protect\cite{yeh2000more}.}
+For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$ (all $p$-values based on the permutation test: \protect\newcite{yeh2000more}).}
 	 \label{tab:main}
@@
 One striking thing about the non-English FS is how poorly they translate: many good FS in these languages become extremely awkward when translated into English.
-This is expected of course for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like
+This is expected, of course, for idioms like \ex{biti general poslije bitke} \gl{be the general after the battle} (\ie \gl{hindsight is 20/20}), but it extends to other relatively compositional  constructions like
 \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} \gl{repeat occurrences of \gap like this} and 
@@
 Although the optimization of the lattice is several orders of magnitude more complex than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice is a fraction of the time required to collect the statistics for LPR calculation, and so the end-to-end runtimes of the two methods are comparable.
-In the BNC, the full lattice method was much faster than LocalMaxs and DP-Seg, though direct runtime comparisons to these methods are of modest value due to differences of both scope and implementation.
+In the BNC, the full lattice method was much faster than LocalMaxs and DP-Seg, though direct runtime comparisons to these methods are of modest value due to differences in both scope and implementation.
 
@@
 
-The second author has been supported by an Endeavour Research Fellowship
-of the Australian Government, and in part by the Croatian Science
-Foundation under the project UIP-2014-09-7312. We would also like to thank our Australian, Japanese, and Croatian annotators.
+The second author was supported by an Endeavour Research Fellowship
+from the Australian Government, and in part by the Croatian Science
+Foundation under project UIP-2014-09-7312. We would also like to thank
+our English, Japanese, and Croatian annotators.
 

### 2017-08-08 response_2.txt
Final few changes

@@
 
-This is a reasonable idea, but we don't feel entirely confident reporting exact runtime figures due to difficulty in creating a controlled environment sufficient (i.e.
+This is a reasonable idea, but we don't feel entirely confident reporting exact runtime figures due to difficulty in creating a sufficiently controlled environment( i.e.
 DP-seg takes over 10 days to run on the BNC, and we can't ensure that our server stays otherwise unused) as well as the fact we can't control for the implementation of the comparison techniques.

### 2017-08-08 tacl.tex
Final few changes

@@
 
-The motivations for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
+The motivations for building lexicons of FS naturally overlap with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}.
 One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses.
@@
 					\State $Y_{\mathit{new}} \gets \Call{Set}{Y_{\mathit{curr}},x_{\mathit{rev}}, \mathrm{OFF}}$
-					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, X_{\mathit{aff}}}$
+					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{Y_{\mathit{new}}, X_{\mathit{aff}}}$
 					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}
@@
 \end{tabular}
-  \caption{10 randomly selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms where appropriate for readability.}
+  \caption{10 randomly-selected examples from the final FS lexicon from each corpus. Lemmas have been converted to inflected forms where appropriate for readability.}
 	 \label{tab:sample}

### 2017-11-09 tacl.tex
Edits in response to Chief Editor feedback

@@
 $^{*}$\,School of Computing and Information Systems, The University of Melbourne\\
-\texttt{julian.brooke@gmail.com, tb@lwin.net} \\
+\texttt{julian.brooke@gmail.com, tb@ldwin.net} \\
 $^{\dagger}$\,Faculty of Electrical Engineering and Computing, University
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In this, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
 Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.
@@
 Another reason to introduce a different terminology is that there are classes of phrases which are typically considered MWEs that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb}, analogous to \ex{wooden leg}).
-Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
+We also exclude from the definition of both FS and MWE those named entities that refer to people or places that are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
 \figref{fig:terminology} shows the conception of the relationship between FS, (multiword) constructions, MWE, and (multiword) named entities that we assume for this paper.
@@
 Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
-Another measure which addresses sequences of longer than two words is the $c$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones.
+Another measure that addresses sequences of longer than two words is the $C$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger $n$-grams.
 Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word.
@@
 Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
-The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
+The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition.
+Its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probabilities to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
@@
 The system of \newcite{Schneider14b} distinguishes a full range of MWE sequences in the English Web Treebank, including gapped expressions, using a supervised sequence tagging model.
-Though in theory automatic lexical resources could be a useful addition to the Schneider et \al model, which uses only manual lexical resources, attempts to do so have achieved mixed success \cite{Riedl16}.
+Though, in theory, automatic lexical resources could be a useful addition to the Schneider et \al model, which uses only manual lexical resources, attempts to do so have achieved mixed success \cite{Riedl16}.
 
@@
 where $bl(x_t)$ produces a set of indicies of nodes below $x_t$ in the lattice.
-We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
+We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS that may have higher LPR due to the lexical and syntactic specificity of the FS.
 For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(x_t)$ will be 0.5.
@@
 To address this problem, rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS.
-For non-subsuming nodes $x_i$ and $x_j$, let $\mathit{oc}(x_i,x_j)$ be the count of instances of $x_i$ which contain at least one non-gap token of an corresponding instance of $x_j$.
+For non-subsuming nodes $x_i$ and $x_j$, let $\mathit{oc}(x_i,x_j)$ be the count of instances of $x_i$ which contain at least one non-gap token of a corresponding instance of $x_j$.
 For subsuming nodes, though, overlap is treated asymmetrically, with $\mathit{oc}(x_i,x_j)$ equal to $c(x_j)$ (the lower count) if $j \in ab(x_i)$, but zero if $j \in bl(x_i)$.
@@
 The POS regex for Japanese covers the same basic nominal structures as English, but also includes case markers and adverbials.
-Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) which are removed by lemmatization in Croatian are segmented into independent morphological units in the MeCab output, making the task somewhat different for the two languages.
+Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) that are removed by lemmatization in Croatian are segmented into independent morphological units in the MeCab output, making the task somewhat different for the two languages.
 
@@
 One advantage of a type-based annotation approach, particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness.
-As such we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
+As such we entirely excluded from our test set $n$-grams that just one annotator marked as FS.
 \tabref{tab:stats} contains the counts for the four test sets after this filtering step and Fleiss' Kappa scores before (``Pre'') and after (``Post'').
@@
           \midrule 
-Countrank & 0.13& 0.09 & 0.10 && 0.08 & 0.14 & 0.10 && 0.10 & 0.16 & 0.12 && 0.11 & 0.06 & 0.08 \\
-PMIrank & 0.24& 0.14& 0.18 & & 0.12 & 0.25 & 0.16 & & 0.21 &0.32 & 0.26 & & 0.18& 0.08 & 0.11 \\ 
-minLPRrank & 0.49& 0.31 & 0.38 & & 0.25& 0.44 & 0.32 & & 0.36 & 0.45 & 0.40 &  & 0.47 & 0.21 & 0.29 \\
+Countrank & 0.13& 0.09 & 0.10 && 0.08 & 0.14 & 0.10 && 0.08 & 0.12 & 0.10 && 0.11 & 0.06 & 0.08 \\
+PMIrank & 0.24& 0.15& 0.18 & & 0.13 & 0.25 & 0.17 & & 0.21 &0.25 & 0.23 & & 0.18& 0.08 & 0.11 \\ 
+minLPRrank & 0.47& 0.33 & 0.38 & & 0.27& 0.40 & 0.32 & & 0.34 & 0.41 & 0.37 &  & 0.53 & 0.26 & 0.35 \\
 
@@
 
-	Lattice \emph{$-$ovr} & 0.52& \bf{0.53} & 0.53 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\
+	Lattice \emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.60} & 0.56 \\
 
-				Lattice & \bf{0.67} & 0.45 & \bf{0.54} & & \bf{0.38}& 0.58 & \bf{0.46} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.76} & 0.49 & \bf{0.59} \\ 
+				Lattice & \bf{0.67} & 0.43 & \bf{0.52} & & \bf{0.40}& \bf{0.60} & \bf{0.48} & &\bf{0.44} & 0.56 & \bf{0.49} & & \bf{0.78} & 0.48 & \bf{0.59} \\ 
             \bottomrule
@@
 Bold is best in a given column.
-For ICWSM only, F-score difference relative to best baseline is significant at $p < 0.05$; the difference for all test sets together is significant at $ p < 0.01$ (all $p$-values based on the permutation test: \protect\newcite{yeh2000more}).}
+The performance difference of the Lattice model relative to the best baseline for all test sets considered together is significant at $ p < 0.01$ (based on the permutation test: \protect\newcite{yeh2000more}).}
 	 \label{tab:main}
@@
   \midrule
-			Lattice & 0.46 & 0.61 & \bf{0.53} \\
+			Lattice & 0.47 & 0.63 & \bf{0.54} \\
        \bottomrule
@@
 All comparison approaches have themselves been previously compared against a wide range of association measures.
-As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI and raw frequency.
+As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams, according to the measure used in our lattice (minLPR) as well as PMI and raw frequency.
 For each of these association measures we rank all $n$-grams above the frequency threshold and build a lexicon equal to the size of the lexicon produced by our model.
@@
 Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results with $C=4$, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
-We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with overlap and clearing node interactions turned off.
+We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we, present results with overlap and clearing node interactions turned off.
 
@@
 \midrule
-English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.7 & 15.0 & \z7.5  \\
-English BNC & 374k &  30.0k& 26.1& 37.7 & 36.3 & 18.1 & \z7.7 \\
-Croatian & 172k & \z6.7k & \z7.9& 55.0& 31.4 & 10.3 & \z3.2 \\
-Japanese & 218k &  29.4k &\z7.9& 39.5 & 31.1& 16.8 & 12.6 \\
+English ICWSM & 202k & 16.8k & 18.6 & 47.1 & 30.9 & 14.8 & \z7.2  \\
+English BNC & 367k &  29.9k& 26.2& 38.3 & 36.3 & 17.9 & \z7.5 \\
+Croatian & 169k & \z6.6k & \z8.1& 56.3& 30.8 & 9.9 & \z3.0 \\
+Japanese & 219k &  29.1k &\z7.9& 39.6 & 31.0& 16.9 & 12.5 \\
 \bottomrule
@@
 
-At the opposite extreme, the low precision of the BNC is almost certainly due to its relatively small size: whereas the $n$-gram threshold we used here results in minimum counts of roughly 100 for the other three corpora, the BNC statistics include $n$-grams with counts less than 10.
-At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions, resp.) are also indicative of increased noise.
+At the opposite extreme, the low precision of the BNC is almost certainly due to its relatively small size: whereas the $n$-gram threshold we used here results in minimum counts of roughly 100 for the other three corpora, the BNC statistics include $n$-grams with counts of less than 10.
+At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions, respectively) are also indicative of increased noise.
 This  could be resolved by increasing the $n$-gram threshold.
@@
 Looking at the most common POS patterns across languages, only noun-noun and adjective-noun combinations ever account for more than 5\% of all word types in any of the lexicons.
-Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
+Though some of the diversity can, of course, be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
 
@@
 \toprule
-English (ICWSM) & \ex{heart ache}, \ex{so \gap have some time}, \ex{part of the blame}, \ex{via slashdot}, \ex{any more questions}, \ex{protein expression}, \ex{work in \gap bank}, \ex{al-qaeda terrorist}, \ex{continue discussions}, \ex{I know a lot of people who}\\
+English (ICWSM) & \ex{heart ache}, \ex{so \gap have some time}, \ex{part of the blame}, \ex{via slashdot}, \ex{any more questions}, \ex{protein expression}, \ex{work in \gap bank}, \ex{al-qaeda terrorist}, \ex{continue discussions}, \ex{speak about * issue}\\
 \midrule
-English (BNC) & \ex{go into decline}, \ex{Maureen says}, \ex{primarily as \gap and}, \ex{Peggy Sue}, \ex{square \gap shoulders}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
+English (BNC) & \ex{go into decline}, \ex{Maureen says}, \ex{be open to all * in the}, \ex{Peggy Sue}, \ex{square \gap shoulders}, \ex{delivery system for}, \ex{this \gap also includes}, \ex{license endorsed}, \ex{point \gap finger}, \ex{highly \gap asset}\\
 \midrule
@@
 Among the English examples, most of the clear errors are bigrams that reflect particular biases of their respective corpora: The phrase \ex{via slashdot} comes from boilerplate text identifying the source of an article, whereas \ex{Maureen} (from \ex{Maureen says}) is a character in one of the novels included in the BNC.
-The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{primarily as \gap and} from the BNC is not obviously an FS and likely the result of noise.
+The longer FS mostly seem sensible, in that they are plausible lexicalized constructions, though \ex{be open to all * in the} from the BNC seems too long and is likely the result of noise due to insufficient examples.
 Some FS are dialectal variants, for instance \ex{license endorsed} refers to British traffic violations.
@@
 This highlights the potential importance of focusing on FS when learning a language.
-Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from, like \ex{austrijski investitor} \gl{Austrian investor}.
+Though some of the errors seem to be the result of extra material added to a good FS, for instance \ex{promet teretnih vozila} \gl{good vehicle traffic}, most, again, are somewhat inexplicable artifacts of the corpus they were built from, like \ex{austrijski investitor} \gl{Austrian investor}.
 
-Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of them) are of course dominated by rarer terms.
+Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of them) are, of course, dominated by rarer terms.
 This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of the potential in automatic extraction comes from the long tail.
 However, we did investigate the other end of the Zipfian curve by extracting the 20 most common MWEs (including both strong and weak) from the \newcite{Schneider14a} corpus.
-In the ICWSM lexicon, our recall for these common terms was fairly high (0.75), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).
-In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting the potential for improved handling of this issue.
+In the ICWSM lexicon, our recall for these common terms was fairly high (0.7), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).
+In one case that showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting the potential for improved handling of this issue.
 
@@
 We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two native-speaker annotators ($\kappa = 0.73$), and conflicts were resolved through discussion.} First, we note that only 28\% of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types.
-Even without any explicit representation of compositionality, our model did much better at identifying MWE FS than non-MWE FS:  0.71 versus 0.34 recall.
+Even without any explicit representation of compositionality, our model did much better at identifying MWE FS than non-MWE FS:  0.7 versus 0.32 recall.
 This may simply reflect, however, the fact that a disproportionate number of MWEs were noun-noun compounds, which are fairly easy for the model to identify.
@@
 
-We can also consider adding new terms to the exponents of the two parts of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
-One which we have considered is creating new connections between identical or similar syntactic patterns, which could serve to encourage the model to generalize.
+We can also consider adding new types of terms to the exponents of the two parts of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
+One type that we have considered is adding new connections between identical or similar syntactic patterns, which could serve to encourage the model to generalize.
 In English, for instance, it might learn that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
@@
 Our evaluation using annotations of sampled $n$-grams shows that it consistently outperforms alternatives across several corpora and languages.
-A tool which implements the method, as well as the acquired lexicons, annotation guidelines, and test set have been made available.\footnote{\url{https://github.com/julianbrooke/LatticeFS}}
+A tool which implements the method, as well as the acquired lexicons, annotation guidelines, and test sets have been made available.\footnote{\url{https://github.com/julianbrooke/LatticeFS}}
 
@@
 Foundation under project UIP-2014-09-7312. We would also like to thank
-our English, Japanese, and Croatian annotators.
+our English, Japanese, and Croatian annotators, and the TACL reviewers and editors for helping shape this paper into its current form.
 

### 2017-11-17 tacl.tex
Final version

@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In this, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In this, an FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
 Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.

### 2017-11-20 tacl.tex
Merged camera-ready (13 pages)

--- 2017-11-09 tacl.tex
@@
 
-In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In this, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
+In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, an FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework.
 Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians.
@@
 Another reason to introduce a different terminology is that there are classes of phrases which are typically considered MWEs that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb}, analogous to \ex{wooden leg}).
-We also exclude from the definition of both FS and MWE those named entities that refer to people or places that are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
+We also exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}).
 \figref{fig:terminology} shows the conception of the relationship between FS, (multiword) constructions, MWE, and (multiword) named entities that we assume for this paper.
@@
 Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words.
-Another measure that addresses sequences of longer than two words is the $C$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger $n$-grams.
+Another measure which addresses sequences of longer than two words is the $C$-value \cite{Frantzi00} which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones.
 Mutual expectation \cite{Dias99} involves deriving a normalized statistic that reflects the extent to which a phrase resists the omission of any constituent word.
@@
 Typically multiword lexicons are created by ranking $n$-grams according to an association measure and applying a threshold.
-The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition.
-Its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
+The algorithm of \newcite{Silva99} is somewhat more sophisticated, in that it identifies the local maxima of association measures across subsuming $n$-grams within a sentence to identify MWEs of unrestricted length and syntactic composition; its effectiveness beyond noun phrases, however, seems relatively limited \cite{Ramisch12}.
 Brooke et \al \shortcite{Brooke14a,Brooke15b} developed a heuristic method intended for general FS extraction in larger corpora, first using conditional probabilities to do an initial (single pass) coarse-grained segmentation of the corpus, followed by a pass through the resulting vocabulary, breaking larger units into smaller ones based on a tradeoff between marginal and conditional statistics.
@@
 where $bl(x_t)$ produces a set of indicies of nodes below $x_t$ in the lattice.
-We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS that may have higher LPR due to the lexical and syntactic specificity of the FS.
+We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS.
 For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(x_t)$ will be 0.5.
@@
 The POS regex for Japanese covers the same basic nominal structures as English, but also includes case markers and adverbials.
-Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) that are removed by lemmatization in Croatian are segmented into independent morphological units in the MeCab output, making the task somewhat different for the two languages.
+Though our processing of Japanese includes basic lemmatization related to superficial elements like the choice of writing script and politeness markers, many elements (such as case marking) which are removed by lemmatization in Croatian are segmented into independent morphological units in the MeCab output, making the task somewhat different for the two languages.
 
@@
 One advantage of a type-based annotation approach, particularly with regards to annotation with a known subjective component, is that it is quite sensible to simply discard borderline cases, improving reliability at the cost of some representativeness.
-As such we entirely excluded from our test set $n$-grams that just one annotator marked as FS.
+As such we entirely excluded from our test set $n$-grams which just one annotator marked as FS.
 \tabref{tab:stats} contains the counts for the four test sets after this filtering step and Fleiss' Kappa scores before (``Pre'') and after (``Post'').
@@
 All comparison approaches have themselves been previously compared against a wide range of association measures.
-As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams, according to the measure used in our lattice (minLPR) as well as PMI and raw frequency.
+As such, we do not repeat all these comparisons here, but we do consider a lexicon built from ranking $n$-grams according to the measure used in our lattice (minLPR) as well as PMI and raw frequency.
 For each of these association measures we rank all $n$-grams above the frequency threshold and build a lexicon equal to the size of the lexicon produced by our model.
@@
 Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results with $C=4$, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora.
-We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we, present results with overlap and clearing node interactions turned off.
+We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with overlap and clearing node interactions turned off.
 
@@
 
-At the opposite extreme, the low precision of the BNC is almost certainly due to its relatively small size: whereas the $n$-gram threshold we used here results in minimum counts of roughly 100 for the other three corpora, the BNC statistics include $n$-grams with counts of less than 10.
-At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions, respectively) are also indicative of increased noise.
+At the opposite extreme, the low precision of the BNC is almost certainly due to its relatively small size: whereas the $n$-gram threshold we used here results in minimum counts of roughly 100 for the other three corpora, the BNC statistics include $n$-grams with counts less than 10.
+At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions, resp.) are also indicative of increased noise.
 This  could be resolved by increasing the $n$-gram threshold.
@@
 Looking at the most common POS patterns across languages, only noun-noun and adjective-noun combinations ever account for more than 5\% of all word types in any of the lexicons.
-Though some of the diversity can, of course, be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
+Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
 
@@
 
-Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of them) are, of course, dominated by rarer terms.
+Since Zipfian frequency curves naturally extend to multiword vocabulary, our lexicons (and type-based evaluation of them) are of course dominated by rarer terms.
 This is not, we would argue, a serious drawback, since in practical terms there is very little value in focusing on common FS like \ex{of course} which manually-built lexicons already contain; most of the potential in automatic extraction comes from the long tail.
@@
 In the ICWSM lexicon, our recall for these common terms was fairly high (0.7), with errors mostly resulting from longer phrases containing these terms ``winning out'' (in the lattice) over shorter phrases, which have relatively low LPR due to extremely common constituent words; for example, we missed \ex{on time}, but had 19 FS which contain it (e.g.\ \ex{right on time}, \ex{show up on time}, and \ex{start on time}).
-In one case that showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting the potential for improved handling of this issue.
+In one case which showed this same problem, \ex{waste * time}, the lexicon did have its ungapped version, highlighting the potential for improved handling of this issue.
 
@@
 
-We can also consider adding new types of terms to the exponents of the two parts of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
-One type that we have considered is adding new connections between identical or similar syntactic patterns, which could serve to encourage the model to generalize.
+We can also consider adding new terms to the exponents of the two parts of our objective function, analagous to the cover, clear, and overlap functions, based on other relationships between nodes in the lattice.
+One which we have considered is creating new connections between identical or similar syntactic patterns, which could serve to encourage the model to generalize.
 In English, for instance, it might learn that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not.
@@
 
-Finally, though the model presented here was designed specifically for FS extraction, we note that it could be useful for related tasks such as unsupervised learning of morphological lexicons, particularly for agglutinative languages.
+Finally, though the model was designed specifically for FS extraction, we note that it could be useful for related tasks such as unsupervised learning of morphological lexicons, particularly for agglutinative languages.
 Character or phoneme $n$-grams could compete in an identically structured lattice to be chosen as the best morphemes for the language, with LPR adapted to use phonological predictability (\ie based on vowel/consonant ``tags'') instead of syntactic predictability.
-It is likely, though, that further algorithmic modifications would be necessary to target morphological phenomena well, and we leave this for future work.
+It is likely, though, that further algorithmic modifications would be necessary to target morphological phenomena well, which we leave for future work.
 
